### 2024-09-11 article/Article.tex
article/documentation and updated readme

% Template for PLoS
% Version 3.5 March 2018

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}
\usepackage{changepage}
\usepackage[utf8x]{inputenc}
\usepackage{textcomp,marvosym}
\usepackage{cite}
\usepackage{nameref,hyperref}
\usepackage[right]{lineno}
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }
\usepackage[table]{xcolor}
\usepackage{array}
\newcolumntype{+}{!{\vrule width 2pt}}

\usepackage{figchild}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

\bibliographystyle{plos2015}
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{fancy}

\fancyhf{}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below
\newcommand{\microns}{~\textmu m~} % ALL UNITS UPRIGHT WITH SPACE
\newcommand{\invivo}{\textit{in vivo}~}
%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{TWINKLE: An open-source two-photon microscope for teaching and research}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Manuel Schottdorf\textsuperscript{1,*},
P. Dylan Rich\textsuperscript{1},
E. Mika Diamanti\textsuperscript{1}, 
Albert Lin\textsuperscript{1,4}, 
Sina Tafazoli\textsuperscript{1},
Edward H. Nieh\textsuperscript{1,2},
Stephan Y. Thiberge\textsuperscript{1,3*}
\\
\bigskip
\textbf{1} Princeton Neuroscience Institute, Princeton University, Princeton, NJ, USA\\
\textbf{2} School of Medicine, University of Virginia, Charlottesville, VA, USA \\
\textbf{3} Bezos Center for Neural Circuit Dynamics, Princeton University, Princeton, NJ, USA\\
\textbf{4} Center for the Physics of Biological Function, Princeton University, Princeton, NJ, USA\\
\bigskip

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* mschottdorf@princeton.edu\\
* thiberge@princeton.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Many laboratories use two-photon microscopy through commercial suppliers, or open designs of considerable complexity. The integrated nature of these systems complicates customization, troubleshooting as well as grasping the principles of two-photon microscopy. Here, we present ``Twinkle'': a microscope for Two-photon Imaging in Neuroscience, and Kit for Learning and Education. It is a fully open, high-performance and cost-effective research and teaching microscope without any custom parts beyond what can be fabricated in a university machine shop. The instrument features a large field of view, using modern objectives with a long working distance and large back-aperture to maximize the fluorescence signal. We document our experiences using this systems as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open-source scientific instrumentation.

\linenumbers

\section*{Introduction}
%
Two-photon microscopy\cite{Denk1990, Svoboda1997, So2000, Helmchen2005} is a workhorse of modern systems neuroscience across species, and two-photon microscopes exist in many system neuroscience laboratories\cite{Luu2024, Grienberger2022}. For example, in \textit{Mus musculus}, two-photon microscopes have been used to classify the function and neural inventory of the retina \cite{Baden2016}, study sequential activity in cortex \cite{Harvey2012} and subcortical structures \cite{Nieh2021}, led to transformative insights into signals in the dopaminergic reward system \cite{Engelhard2019}, and revealed an organized map among grid cells \cite{Yu2018}. In non-human primates, two-photon microscopes have been used as optical brain computer interfaces \cite{Trautmann2021}, and to survey the spatial organization of motor cortex in reach movements \cite{Ebina2018}. They also have potential to further our understanding of the function of the primate retina \cite{Sharma2016, Schottdorf2021}. In Zebrafish, \textit{Danio rerio}, two-photon microscopy can image the entire brain with single cell resolution \cite{Renninger2013}. Two-photon microscopy has also become a standard method for monitoring neural activity in invertebrates. In the fruit fly, \textit{Drosophila melanogaster}, imaging from sparse, genetically specified neuron populations \cite{Seelig2010, Lin2022} has enabled many circuits to be functionally mapped, including auditory \cite{Baker2022}, courtship \cite{Deutsch2020, Roemschied2023}, and navigation circuits \cite{Kim2017}. Two-photon microscopes have also enabled volumetric pan-neuronal imaging, in which large portions of the whole fly brain can be recorded from with high temporal resolution \cite{Pacheco2021,Brezovec2024}. In \textit{Caenorhabditis elegans}, it allowed to measure an atlas of neural signal propagation \cite{Randi2023}.\newline
However, these systems are expensive and usually hard to customize \cite{Diamanti2021}, while improvements and new inventions are published regularly, such as the incorporation of adaptive optics \cite{Yao2023}, the use of multiple beams for more effective sampling\cite{Song2017}, the combination with two-photon stimulation for all-optical interrogation of neural circuits \cite{Rickgauer2014}, extremely large fields of view for mesoscopic imaging across brain areas \cite{Sofroniew2016}, or the use of delays for effective sampling through extremely large volumes of cortical tissue \cite{Demas2021}.\newline
This popularity suggests the need for a simple platform, at reasonable cost, for practical education, dissemination, methods development and research. We developed a high-performance and cost-effective two-photon microscope that can easily be built in any neuroscience laboratory over the course of several days and can be effectively used for both teaching and research purposes. Reflecting its use for ``\textbf{TW}o-photon \textbf{I}maging in \textbf{N}euroscience, and \textbf{K}it for \textbf{L}earning and \textbf{E}ducation'', we chose the acronym Twinkle. Twinkle's open design makes the building experience ideal for teaching the principles of two-photon microscopy to the next generation of researchers. Here, we share our design, document system performance, explore possible research applications, and report our experiences collected during several teaching workshops.

\section*{Materials and methods}
In two-photon laser-scanning microscopy\cite{Denk1990}, laser light is focused to a small volume. The product of the interaction of light and sample, fluorescent light, is then measured with a sensitive light detector. Moving the volume of light through the sample and combining the detected fluorescence from different $x$ and $y$ positions produces a picture. The key to two-photon microscopy is the light source: A femtosecond-pulsed infrared laser restricts the volume in which fluorescence occurs to a tiny region in the sample with sufficiently high photon density for the near-simultaneous absorption of two photons by a fluorescent molecule \cite{Denk1990, Svoboda1997, So2000, Helmchen2005}.\newline
Here, we design an open and high-performing microscope that uses these principles. As such we have made all optical and mechanical designs, electronics, bill-of-materials, CAD assembly, testing results, and relevant schematics open to the public. Excluding laser and optical table, the cost is around US-\$ 110,000 (2024). A narrative of the design and high-level view is presented here. For further technical details, and complete built documentation, we refer the reader to \nameref{S1_Appendix}, and the repository at \url{https://github.com/BrainCOGS/Microscope}.

\subsection*{Design specifications}
To summarize our design goals, we aimed for a mechanical and optical assembly using as many off-the-shelf components as possible, with only few custom aluminium parts that can be machined in any university machine shop. Our design lacks a microscope body, which is  advantageous for two reasons: it aids the use as a teaching instrument, and facilitates adaptation for \invivo imaging because it provides space for the organism and ancillary hardware. We also avoid any custom optics to aid transparency of the function of the optical system. Our system is also made cost-effective, in part, by the availability of femtosecond laser systems based on fiber technology. Operating at a fixed wavelength, these systems come at the fraction of the cost of a more traditional tunable Ti:Sapphire laser \cite{Bueno2019}.\newline
We aimed for (1) $\gtrapprox20\text{ cm}$ of free space around the objective in all directions to aid integration of the microscope into custom behavior boxes, or sample container, and (2) resolution limited imaging of at least $\approx 700\times 700\text{ \textmu m}^2$ field of view which is typical for imaging brain tissue at cellular resolution. (3) Compared to previous open designs\cite{Rosenegger2014, Mayrhofer2015}, our system can make use of the large back aperture of modern long-working-distance objectives to collect more fluorescence and (4) uses GaAsP photomultiplier tubes to maximize signal to noise.\newline
An overview of the microscope is shown in Fig.~\ref{fig1}. Fig.~\ref{fig1}A shows the system as a cartoon. Full details will be provided below. In short, we chose a Spark Alcor 920 nm pulsed femtosecond laser, whose beam, after $2\times$ magnification with a telescope, reaches the scanning mirrors. The scanning mirrors are geometrically close together in the focal plane of the scan lens. This simplifies the design, but leads to minor distortions across the field of view (a few percent at low magnifications, see below). The combined scan and tube lenses magnify the beam further to fill the back aperture of the objective. Fluorescence from the specimen is then collected and focused on the aperture of two GaAsP photomultiplier tubes with suitable color filters. Fig.~\ref{fig1}B shows the CAD design of the entire assembly with important parts of the optical path labelled. Fig.~\ref{fig1}C shows an annotated picture of the microscope head. Notice that compared to the cartoon in Fig.~\ref{fig1}A, the optical path is folded with several mirrors. These mirrors significantly simplify alignment, and make the design more compact.

\begin{figure}[!t]
    \includegraphics[width=\textwidth]{fig1.jpg}
    \caption{{\bf System overview.} \textbf{A)} Cartoon of the layout. \textbf{B)}
    CAD drawing of the system on an optical table with several key components in the optical path highlighted. The spacing between two holes on the table is 1 inch. \textbf{C)} Photograph of the microscope head with key elements labelled. This section is visible in panel B.}
    \label{fig1}
\end{figure}

\subsection*{Assembly on the table}
Various components are used between the laser and the microscope head to condition the beam, and  for intensity control, Fig.~\ref{fig1}B. Out of the laser head, the beam first encounters a waveplate (AHWP10M-980, Thorlabs). This is a birefringent crystal that can rotate the polarization of the laser. Next, the beam travels through a polarizing beamsplitter cube (PBS103, Thorlabs). This splits the beam into two beams whose relative intensity can be adjusted by the orientation of the waveplate. We set the orientation of the waveplate to split the beam into two beams with 50\% power each to feed a second experimental setup. In the CAD drawing, this beam is sent to a beam block (LB1, Thorlabs). Next, the beam passes through an electro-optic modulator, a Pockels cell (350-80-LA-02, Conoptics). This device allows rapid and electronic control of the laser's power level. It uses a crystal whose refractive index is controlled by an external electric field, combined with a polarizer. This can be thought of as a voltage-controlled wave plate, in which the electric field controls how much light travels through the polarizer. Next, the beam travels through an open mechanical shutter (LS6S2ZM1, Vincent Associates). When closed, the reflection from the shutter is used for calibrating the Pockels cell with a photodiode (PDA36A2, Thorlabs). Following the shutter, the beam travels though a $2\times$ telescope (GBE02-B, Thorlabs). This magnifies the beam diameter by a factor of 2. Past the telescope, the beam is then reflected off several mirrors in a periscope configuration before entering a custom aluminium box housing, mounted to a 95 mm optical rail, that houses the two scanning mirrors (CRS8K/6215H scanning mirror Set, Novanta), shown in blue in  Fig.~\ref{fig1}C. Based on their angles, the two mirrors deflect the beam in x and y position. The beam then travels through scan lens (green) and tube lens (red), the collection optics (yellow) and finally the objective (cyan). The design of these components is covered in the next paragraphs. The steering mirrors in our system are all silver mirrors from Thorlabs. Silver mirrors contribute minimally to dispersion which is inevitable when light travels through various optical components. Limiting the dispersion makes it possible to correct for it with the laser's built-in dispersion compensation.

\subsection*{Optical design: Scan and tube lens}
When using infinity-corrected objectives, the incident light has to be collimated at the back aperture of the objective. In other words, the light rays have to arrive as parallel beams at the back aperture of the objective. When using a collimated laser beam, then scan and tube lens must be configured as a telescope with the scanning mirrors positioned in the conjugated plane of objective back aperture. A typical scan angle of $\pm10\text{ deg}$ positioned at the focal point of the scan lens, combined with two inch diameter optics, determines the scan lens focal length to $f_S=100\text{ mm}$ (cf. Fig.~\ref{fig1}A). To fill the back aperture of the objective with our laser beam, we aimed for a combined magnification of $M=3.75\times=f_T/f_S$. This determined the focal length of the tube lens to $f_T=375\text{ mm}$. This reduces the scan angles at the back aperture of the objective to $20\text{ deg}/3.75\approx 5.3\text{ deg}$ and with a given objective (e.g. Nikon $16\times$ with $f_O=12.5\text{ mm}$) this determines the expected approximate field of view ($\approx 1.2\text{ mm}$).\newline
We assembled the scan and tube these as lens groups from groups of off-the-shelf parts, using the same elements as in \cite{Yao2023}, and further optimizing lenses and spacing in Zemax (an optics design software). Details are provided below. After optimization, the focal lengths of scan and tube lens were 99 mm and 378 mm respectively, deviating around 1\% from their target values (Zemax simulation at 920 nm).
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{fig2.jpg}
    \caption{{\bf Optical design of the excitation pathway.} \textbf{A)} Zemax design with the scanning mirror, tube and scan lens groups. Colors indicate light rays produced by different mirror angles of the scanning mirror. Notice how the rays converge in the focal plane. \textbf{B)} CAD design built around the optical design in A, see also Fig.~\ref{fig1}B. \textbf{C)} Cuts through the scan and tube lens assemblies, which are fabricated from off-the-shelf lenses housed in SM2 lens tubes. The specific lenses are stated in the text. \textbf{D)} Simulation of the optical system's two-photon point spread function (PSF-2p) for 0 deg deflection angle, and two example radial sections. \textbf{E)} PSF-2p in xz direction across the full range of deflection angles, and quantification of Petzval field curvature (blue), and radial (purple) and axial (yellow) full-width-at-half-maximum of the PSF-2p. Error bars are resolution limits of the Huygens PSF estimates in sequential mode.}
    \label{fig2}
\end{figure}
%
Fig.~\ref{fig2}A shows the propagation of light rays for various deflection angles of the scanning mirrors converging on points along a line in the focal plane. The Zemax design was then exported into CAD, and the optomechanics assembled around it, see Fig.~\ref{fig2}B. The CAD design and lens groups are highlighted in Fig.~\ref{fig2}B,C (see Fig.~\ref{fig1}C of a photograph of the same part of the instrument). The key property that we optimized when designing the excitation system was an essentially flat, and diffraction limited focal volume across a wide range of deflection angles of the scanning mirrors. Fig.~\ref{fig2}D shows an estimate of the two-photon point spread function (PSF-2p), computed as the square of the Huygens PSF in Zemax. The maximum scan angle of $\pm 10\text{ deg}$ is limited by vignetting of the two inch diameter optics. Analyzing the PSF-2p across optical deflection angles, Fig.~\ref{fig2}E, suggests very small field curvature. In this simulation, the axial resolution was $\delta z = 5.0\text{ \textmu m}$, and the radial resolution $\delta r = 0.75\text{ \textmu m}$ across a wide range of deflection angles.\newline
The specific elements that allowed for this performance were as follows: For the scan lens, we used an assembly of four lenses, see Fig.~\ref{fig2}C, 1: KPC070AR (Newport); 2: LB1199-B (Thorlabs) and 3\&4: $2\times$ ACT508-200-B (Thorlabs). The $2\times$ ACT508-200-B lenses are arranged back-to-back and provide the majority of the optical power. The symmetric Pl\"ossl design corrects for the odd aberrations: coma, distortion, and lateral colors \cite{Negrean2014, Kidger2001}. The two additional lenses provide corrections to the even aberrations: spherical aberration, astigmatism, and field curvature. We chose the specific lenses and their spacing based on availability from established optics suppliers and the simulation of dozens of combinations in Zemax. The tube lens is inspired by a Petzval design \cite{Smith2007, Kidger2001}, consisting of a pair of achromatic doublets with the same orientation, $2\times$ ACT508-750-A, Thorlabs. We found in simulation that this design performed better than a Pl\"ossl pair where the doublets are symmetric (this was observed by others as well \cite{Hong2022, Bumstead2018, Mayrhofer2015}).\newline
The two lens groups combined provide a magnification of $M=3.75\times$ to produce a beam that slightly underfills the back aperture of the Nikon NA 0.8 $16\times$ LWD objective, effectively reducing its excitation NA to $\approx0.7$. This has various advantages for \invivo imaging (see discussion). Of further note, we used a piezoelectrical collar to mount the objective. The collar can move the objective along the optical axis at a fast rate for imaging across multiple planes.

\subsection*{Optical design: Collection optics}
%
The aim of the collection optics is to collect the most florescence with a small sized sensor. For our system, this is a 5 mm diameter window of the Hamamatsu H16201-40 Photomultiplier tube (PMT) module. This is achieved by imaging the back aperture of the objective on the aperture of the PMT. Since two-photon microscopes form a picture scanning pixel by pixel, there is no strict requirement for the collection optics to be image forming \cite{Tsai2015}. They should, however, collect as much fluorescent light as possible.
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{fig3.jpg}
    \caption{{\bf Optical design of collection system.} \textbf{A)} Zemax design of the collection optics. Colors indicate different emission angles. These rays were computed for the green emission light path. Small letters denote filters: a is a FF665-Di02-40x55; b: an IR block (not shown in the Zemax simulation); c: FF562-Di03-40x52 and d: FF01-525/45-32 (BrightLine; AVR Optics). Small numbers  denote lenses. 1 is a LA1384-A; 2: LB1607-A and 3: ACL25416U-A (all Thorlabs). \textbf{B)} CAD design built around the Zemax model in A, with several covers removed to expose the interior. The light paths from the laser and fluorescent emission are indicated in transparent colors. Notice how the dichroic mirror splits fluorescence and excitation light, and directs the former to the photomultiplier tubes (PMTs). The mirrors/filters and lenses are numbered/lettered as in A). Two more filters were added relative to the simulation. b blocks residual IR excitation light $\lambda>680\text{ nm}$ (FF01-680/SP-50), and e is a FF01-600/52-32 filter for the red channel. \textbf{C)} Shown is the angle collection graph of the collection optics, which shows the fraction of collected light as function of the angle to the optical axis. This was simulated in Zemax for the design in A. The collection optics were optimized to collect essentially all light over an $\approx\pm 8\text{ deg}$ emission angle.}
    \label{fig3}
\end{figure}
%
We incorporated four design principles into our assembly: (1) Fluorescence light must fall approximately perpendicularly on the optical filters. Narrow filters are particularly susceptible to these effect. Although light emitted from the focal plane of an infinity-corrected objective is collimated as it returns from the sample, actual fluorescence weakly diverges due to scattering and diffraction in the material between focal plane and objective (e.g. brain tissue \cite{Zipfel2003, Taddeucci1996}). The detector assembly should therefore be placed as close as possible to the objective where fluorescent light will be nearly collimated. This placement reduces sensitivity to spurious light and allows IR light to travel through the collection optics unimpeded, while fluorescent light is reflected into the optical assembly. This arrangement also has the advantage that possible astigmatism, introduced by curvature of the dichroic in the reflected light, only affects the collection optics which does not have to form an image. (2) The collection lens should be large to maximize the collection of as much fluorescent light as possible. This implies that the collection lens should follow the dichroic mirror as closely as possible. (3) Having the collected photons collimated on the aperture of the photomultiplier tubes reduces the sensitivity of the system on surface inhomogeneities of the detector\cite{Tsai2002, Young2015}. In scanning microscopy, an image is produced as a time series of intensities. It is therefore more important to collect a consistently large portion of fluorescent light, rather than to minimize aberration in the collection optics. We therefore optimized relative illumination as function of the field angle in Zemax. (4) All dichroic mirrors and optical band-pass filters have finite performance. It it therefore advantageous to combine multiple band-pass filters to isolate relevant fluorescence ranges. We aimed to record fluorescence from two well-separated spectral ranges, a green ($525\pm25\text{ nm}$) and a red channel ($600\pm25\text{ nm}$). Beyond an IR block in the collection optics, we chose to only use simple long-pass filters, which means that the red channel is operated in the transmission, and the green channel in the reflection mode (cf. Fig.~\ref{fig1}A).\newline
With these considerations in mind, we assembled the collection optics from off-the-shelf components that were optimized in Zemax, building on previous work \cite{Tsai2002,Tsai2015}. A cartoon is shown in Fig.~\ref{fig3}A. The colors illustrate different sources of fluorescent light. Notice the mild divergence, and approximately collimated beams that enter the aperture of the photomultiplier tube. As previously, this design was exported into CAD, and the optomechanics assembled around it, see Fig.~\ref{fig3}B. Fig.~\ref{fig3}C shows a simulation in Zemax demonstrating that essentially all light up to $\approx\pm 8\text{ deg}$ is arrives at the aperture of the photomultiplier tubes.

\subsection*{Mechanical design}
As mounting system of our microscope, we chose a standard 8 inch thick optical table. The design was done in CAD, and the results shown in Fig.~\ref{fig1}B. The aim was a mechanical assembly that uses as few custom parts as possible. We discuss this further in the discussion section. The components in the CAD files can be assembled and aligned by an experienced researcher in a few days. When used for teaching, a careful assembly and alignment is viable with about a week of work. Regarding the footprint, the system can comfortably be built on an $4\times4$ ft area of table. The microscope documented here was setup on a $4\times8$ ft table, shared with a second microscope. The beam-splitting hardware is shown in Fig.~\ref{fig1}B as well.\newline
The custom mechanical components (e.g. the light-tight aluminium housing of the collection optics) were built in the university's machine shop from aluminium stock or Thorlabs parts. Some parts have tight tolerances which suggests manufacturing in a professional machine shop is preferred. If useful for training, this could however be done by students. An example are the aluminium parts that hold the large dichroic mirrors and optical filters in the collection optics. After drilling the apertures for light to pass through, not much metal is left on the part which can lead to warping and distortions.\newline
Finally, we want to emphasize the difference between a theoretically optimal design in Zemax and finite tolerances in real-world optomechanical parts. It is key for a good microscope design to be robust against such errors. In our design, the objective is fixed, while the mirrors, the tube and scan lens assemblies, and the scanning mirrors can move along the optical axis for alignment. This allows the mechanical components sufficient degrees of freedom to optically align all key parts of the microscope. In the supplement, we go through this alignment procedure which allows a user to find the optimal position of the scanning mirrors in the conjugated plane of the back-aperture of the objective.

\subsection*{Electronic design}
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{fig4.jpg}
    \caption{{\bf Custom electronic control circuit and box.} \textbf{A)} Control circuit to set and read the gain of the two H16201P-40 photomultiplier tube modules used for red and green channel. The two modules are connected with two 4-wire connectors, and their current gain is displayed on a small digital panel meter. \textbf{B)} Wiring of the panel meter for single-ended configuration. \textbf{C)} The circuit in a prototype-box, and mounted to the side of a rack. The two gains for green (top) and red (bottom) channel are visible. A gain of around $\approx0.8$ is typical for Calcium imaging to maximize the faint signal. A gain of $\approx0.6$ is appropriate for very bright samples.}
    \label{fig4}
\end{figure}
%
A simple circuit, see Fig.~\ref{fig4}A, is used to control and display the photomultiplier gain. The H16201P-40 photomultiplier tube module comes with four cables, two for power supply, and two for gain control. These leads are color-coded. We designed a small circuit for resistance programming of the gain, and to display the gain setting voltage on small digital panel meter (Murata DMS-20PC). The circuit for controlling two channels (red and green) is shown in Fig.~\ref{fig4}A. For the tube module, the +15 V supply voltage and ground are provided via the black and red cables. The blue cable is connected to ground via a potentiometer to act as a voltage divider. The gain voltage is then fed back to the module via the white input line, and used for display on the panel meter. We added a 12k resistor between the PMT module, and the potentiometer to limit the control voltage which is safer for the PMT. Optimal signal-to-noise ratio for our systems is usually $\approx 0.7-0.8\text{ V}$. The panel meter needs an additional +5 V supply that we obtain from the +15 V via a resistive divider. The meter is operating in Single-Ended Input Conﬁgurations, see Fig.~\ref{fig4}B. Due to the simplicity of this circuit, we do not solder this on a circuit board, but rather in a prototype development box directly, see Fig.~\ref{fig4}C, which is attached to the rig.\newline
This circuit and the driver boards for the xy scanners need a well regulated power supply, as any noise would directly translate to image noise and distortions. We use an Agilent E3630A supply. The PMT outputs were amplified with two Transimpedance Amplifiers (TIA60, Thorlabs), and directly connected to the data acquisition system.

\subsection*{Ancillary hardware}
Our microscope is controlled with ScanImage \cite{Pologruto2003} running on a Windows PC and this data acquisition (DAQ) system was provided by Vidrio. In our experience, this reduces software issues.\newline
A typical femtosecond pulsed laser source is expensive. Ti:Sapphire lasers are tunable, but particularly expensive. For the work demonstrated here, we used a fixed-wavelength femtosecond laser systems, based on fiber technology (e.g.\cite{Bueno2019,Limpert2006,Wise2012,Young2015}). Operating at a fixed wavelength, these systems come at a fraction of the cost of a more traditional tunable Ti-Sapphire laser, and they take up significantly less real estate on an optical table. The laser was controlled with the same PC as ScanImage through a USB connection. As the beam travels through a number of crystals, lenses, and mirrors with various chromatic properties, significant dispersion is introduced which increases pulse length, reducing the two-photon absorption efficiency. It is possible to compensate for the group-delay dispersion of the microscope by giving the short-wavelength components a sufficient head start so that blue and red components arrive at the sample at the same time. We found, empirically, that the built-in group velocity dispersion compensation of the laser was more than sufficient to tune the system to an optimum, which we found close to $\varphi=-20200\pm170\text{ fs}^2$. Details of this measurement, and some theory, are provided below as a teaching example (cf. Fig.~\ref{fig9}). Regarding light transmission, we found the Spark laser to produce $\approx 2.1\text{ W}$ of light. After the wave plate and beamsplitter cube, $\approx 1.0\text{ W}$ enter the Pockels cell (cf. Fig.~\ref{fig1}B). The Pockels cell is rotated so that the control voltage produces the largest dynamic range of transmitted laser power (we go through the alignment procedure in depth below). At maximum transmission setting of the Pockels cell, we obtain $\approx 260\text{ mW}$ below the objective, corresponding to $\approx1/4$ of the available light. In our hands, this is more than enough for imaging. All pictures presented in this article were obtained with $\approx 15\text{ mW}$ below the objective.

\subsection*{Animal procedure}
All procedures performed in this study were approved by the Institutional Animal Care and Use Committee at Princeton University and were performed in accordance with the Guide for the Care and Use of Laboratory Animals \cite{Guide2011}.

\section*{Results}

\subsection*{System performance}
%
Here, we document the performance of the microscope and a few example applications using a Nikon NA 0.8 16$\times$ LWD objective (N16XLWD-PF, Thorlabs). We first determined the size and properties of the field of view with a 100~\textmu m grid (R1L3S3P, Thorlabs), imaged using a Fluorescein in water film through a standard \#1.5 ($\approx170\text{ \textmu m}$ thick) coverslip, see Fig.~\ref{fig5}A. The field of view was $d\approx1.3\text{ mm}$ along the diagonal, $A\approx 1\text{ mm}^2$ in area and the field curvature below the thickness of a thin Fluorescein film $\lesssim 10\text{ \textmu m}$. This is consistent with our earlier Zemax simulations. When measuring the magnification $M$ in \textmu m/px across the field of view, we observed small deviations of $\Delta M \approx 0.1\text{ \textmu m/px}$ in the center when compared to the edges, while the overall range of magnifications across the field of view was tight, see Fig.~\ref{fig5}B. The average magnification is $M=2.77\pm0.04\text{ \textmu m/px}$, which suggests a deviation from a perfect f-Theta system of $\Delta M/M = 0.1/2.8 \approx 4\%$. Next, we imaged a uniform bath of Fluorescein, see Fig.~\ref{fig5}C. This is a combined measure of the quality of excitation and the efficiency of the collection optics across the field of view. Within the central $700\text{ \textmu m} \times 700\text{ \textmu m}$ region, the signal deviated from uniformity within $\approx 10\%-15\%$ ($\pm 1 \text{ standard deviation}$) suggesting a relatively flat field, see Fig.~\ref{fig5}D, E. Following these measurements, we imaged a bead sample of 0.2\microns diameter in 1\% Agarose (Dragon Green beads; Bangs Laboratories) to measure axial and radial PSFs. The sample is shown in Fig.~\ref{fig5}F. Averaging across the $N=38$ beads in this volume, we measured a radially symmetric full-width-at-half-maximum of $\delta r\approx760\pm30\text{ nm}$, see Fig.~\ref{fig5}G,H, and axially $\delta z \approx 5.4\pm0.9\text{ \textmu m}$, see Fig.~\ref{fig5}I. The theoretical resolution limits\cite{Tsai2002} for our system, underfilled to $\text{NA}=0.7$ at $\lambda=920\text{ nm}$ and water immersion ($n=1.33$) were radially FWHM of $\delta r=0.6\,\lambda/\text{NA}=780\text{ nm}$ and axially $\delta z = 2\,\lambda n/\text{NA}^2=5.0\text{ \textmu m}$. This is consistent with our earlier simulations in Zemax (cf. Fig.~\ref{fig2}), and suggests that our microscope is operating very close to the diffraction limit, and its design specifications.
%
\begin{figure}[t]
    \includegraphics[width=\textwidth]{fig5.jpg}
    \caption{{\bf System capabilities} \textbf{A)} Measurement of the local magnification with a 100\microns calibration target in a thin Fluorescein film below a coverslip. Shown in green is a $700\times700\text{ \textmu m}^2$ square as reference. \textbf{B)} Histogram of the magnifications in A, measured across all squares. \textbf{C)} Two-photon intensity measurements from a uniform bath of Fluorescein. Shown are pixel values (maximum is 32768). \textbf{D)} Horizontal and vertical profiles through the data in C. The green box is indicated by the shaded green area. Range is $\pm 1 \text{ standard deviation}$. \textbf{E)} Histogram of the intensities from within the green box in C. \textbf{F)} Volumetric measurement of a 0.2 \textmu m bead sample in 1\% Agarose. \textbf{G)} Average of N=38 beads. \textbf{H)} Horizontal and vertical profiles through data in G and a Gaussian fit reveal a radial resolution of $760\pm30\text{ nm}$. \textbf{I)} Estimate of the axial resolution shows $5.4\pm0.9\text{ \textmu m}$.}
    \label{fig5}
\end{figure}
%
%
\subsection*{Imaging performance}

\begin{figure}[!t]
    \includegraphics[width=\textwidth]{fig6.jpg}
    \caption{{\bf Example imaging data from simple samples.} \textbf{A)} Autofluorescence of a part of a dandilion flower (Taraxacum officinale) \textit{in vivo}. Notice the pollen grains embedded in the plant material. Optical sectioning allows to focus below the plant surface to the grains. \textbf{B)} Zoom and volumetric image of  a small region (white box) of the sample in A. Optical sectioning shows the surface of the plant and the slice where the pollen grains come into focus. Notice the complex 3D structure of the pollen grains, and their embedding below a layer of red-fluorescent plant material. \textbf{C)} Histological sample showing a stain for glial fibrillary acidic protein in rat astrocytes. \textbf{D)} Image of a cotton napkin (Kimwipe) with depth coded as color. Zooming into a small region (white box) shows how strands of cotton are woven together, and how the pattern changes with depth. Notice how image quality deteriorates in this strongly scattering sample.}
    \label{fig6}
\end{figure}

Confident that the system operates as intended, we next imaged a number of representative samples that are easily available in any teaching lab, namely plant material, a histological and a strongly scattering sample, see Fig.~\ref{fig6}. The first samples was a Dandilion flower (Taraxacum officinale) \cite{Rupprecht2018}. Autofluorescence in plant material is a good test to separate compounds fluorescing in the red and green channels respectively, while also exhibiting complex three-dimensional structure \cite{Cheung2010, Nguyen2001}. Fig.~\ref{fig6}A shows a slice through part of the flower, that reveals red-fluorescent structural plant material, together with green-fluorescent Dandilion pollen grains. The complex 3-D structure is readily apparent if one zooms into a small region (white box), and records a stack, see Fig.~\ref{fig6}B. The pollen grains are hidden under a layer of red-fluorescent plant material as well, which we can easily resolve. Pollen grains are a great sample in a teaching lab, as they are easy to obtain, easy to prepare, and complex when imaged with a two-photon microscope\cite{Rupprecht2018}. The next sample is a mounted primary rat cell culture\cite{Schottdorf2018}, stained for GFAP (Rabbit-Anti-GFAP, ab33922) in the green channel (Donkey-Anti-Rabbit Alexa Fluor 488, ab150061), see Fig.~\ref{fig6}C. This demonstrates the complex structure of glial fibrillary acidic protein in astrocytes. Finally, we imaged a piece of a cellulose napkin (Kimwipe, Fisher Scientific), see Fig.~\ref{fig6}D. This is an example of a strongly scattering sample with complex 3D fibrous structure. To demonstrate this structure, we acquired a volume and color-coded depth. Individual slices at different depths reveal uncorrelated fiber structures. In contrast to our earlier experiments in a less scattering sample (cf. Fig.~\ref{fig5}), the image quality here deteriorates with depth.\newline
Next, we imaged neural activity \textit{in vivo} in both larval zebrafish (Danio rerio) and adult \textit{Drosophila melanogaster}. 
%
\begin{figure}[t]
    \includegraphics[width=\textwidth]{fig7.jpg}
    \caption{{\bf Example Calcium imaging in transgenic Zebrafish (Danio rerio).} \textbf{A)} 3D rendering of a 300~\textmu m deep volumetric image of a 5 day old Zebrafish larva with Fiji\cite{Schindelin2019}. \textbf{B)} Dorsal slice through the same animal and two zoom views down to cellular scale. \textbf{C)} Color-coded $\approx10\text{ min}$ of time-averaged volumetric imaging data of three 20~\textmu m-spaced planes using the piezoelectric collar attached to the objective. The layers are colored in red/green/blue. No motion correction was applied. Notice the blurry averages, caused by motion of the fish. \textbf{D)} Running Suite2p on the data in C produces numerous regions of interest (ROIs) with complex Calcium dynamics. Left: Suite2p applies motion correction, resulting in a much crisper average picture. Right: Time series of a few ROIs over 10 min.}
    \label{fig7}
\end{figure}
%
%
For zebrafish imaging, we used the HuC:H2B-GCaMP6f line of transgenic Zebrafish \cite{Cong2017}. Neurons in this organism expresses the fluorescent protein GCaMP6f in their nuclei whose green fluorescence strongly depends on the cellular concentration of Calcium ions. We imaged a 5-day old larva in 2\% low melting point Agarose in E3 medium, see Fig.~\ref{fig7}. We first performed a volumetric scan of the organism, Fig.~\ref{fig7}A shows a rendering in Fiji \cite{Schindelin2019}, and then focused on a plane with a large number of visible neurons, Fig.~\ref{fig7}B. In a small region, we used our piezoelectric collar to collect volumetric data from three planes, see Fig.~\ref{fig7}C. We processed these data with Suite2p \cite{Pachitariu2016}, which identified many neurons with complex calcium transients, Fig.~\ref{fig7}D.\newline
To image in the adult fruit fly, we head-fixed the fly in a custom 3D-printed mount \cite{Pacheco2021} (Fig.~\ref{fig8}A). We then perform a dissection which removes the cuticle from the back of the head of the fly, providing optical access to the brain. We imaged 6-day-old transgenic adult flies which express GCaMP6s and myr-tdTomato pan-neuronally, labeling all neurons cytoplasmically. We volumetrically imaged a volume approximately 300 x 350 x 50 ~\textmu m in scale, spanning a fraction of the central brain of the fly (Fig.~\ref{fig8}B). We then motion-corrected and segmented the GCaMP6s volume into regions of interest (ROIs) with spatial clustering algorithms \cite{Pacheco2021}, revealing diverse spontaneous calcium activity (Fig.~\ref{fig8}C). 
%
%
\begin{figure}[t]
\begin{center}
    \includegraphics[width=\textwidth]{fig8.jpg}
\end{center}
    \caption{{\bf Example calcium imaging in adult \textit{Drosophila melanogaster}.} \textbf{A)} Imaging from the brain of a head-fixed adult fly \cite{Pacheco2021}. A dissection is performed to remove the cuticle from the back of the fly's head and provide optical access to the brain, and the imaged brain volume is outlined. The transgenic flies express pan-neuronal GCaMP6s and myr-tdTomato, driven by the nsyb promoter. \textbf{B)} Average projections over ten 5~\textmu m-spaced planes of both imaging channels, acquired at a temporal resolution of 1 volume/s. XY boundaries of exemplar ROIs are indicated. \textbf{C)} The channels are motion corrected and spatially clustered ROIs are extracted. Examples of spontaneous calcium activity extracted from ROIs in the brain volume.}
    \label{fig8}
\end{figure}

\subsection*{Teaching}
Twinkle was assembled, disassembled, and reassembled three times by different groups of researchers and students. In the following paragraphs, we summarize our experiences, and produce two examples for what we consider useful learning experiences for two-photon microscopy.\newline
To organize our workshop, we freed around 2 weeks in the summer. On the first day, we provided an introductory lecture going through the principles of two-photon microscopy (cf. Fig.~\ref{fig1}A), safety, and the plan ahead. Next, we completely stripped the optical table and returned Twinkle's components back into their containers. Then reassembly began, first setting up and aligning laser and beam-splitting hardware, then the Pockels cell, the shutter, telescope, and associated beam blocks (cf. Fig.~\ref{fig1}B). This was done over the course of days 1-3 during which students became familiar working with safety goggles, and aligning lasers using a power meter and cards. In particular, the alignment of the Pockels cell requires care, as its orientation has to be carefully set to produce the largest dynamic range of transmitted laser power depending on the control voltage (see teaching examples below). Following the conditioning of the beam, we then proceeded to assemble the mechanics of the microscope head (cf. Fig.~\ref{fig1}C). Reassembling the box housing the scanning mirrors, the lens groups from individual elements, and the collection optics was done from days 3-6 (cf. Fig.~\ref{fig2}, \ref{fig3}, \ref{fig4}) After this was done, we assessed the performance of the instrument and fine tuned it on days 7-8 (cf. Fig.~\ref{fig5}). When properly aligned, we shielded the optical path with sheet metal and Thorlabs tubing, and imaged various samples on day 9 (cf. Figs.~\ref{fig6}, \ref{fig7}, \ref{fig8}). On the last day, day 10, we addressed questions that came up during the course of the workshop.\newline
To exemplify a simple teaching example, see Fig.~\ref{fig9}. Fig.~\ref{fig9}A shows light transmission through the Pockels cell for two different orientations (red and blue) to teach the working principles of the Pockels effect. The optimal angle is shown by the blue dots. A fit to the expected transmitted power curve, 
\begin{eqnarray}
    P(V) = P_0 \sin\left(2\pi\frac{V}{V_0} + \phi \right)^2
\end{eqnarray}
is shown as thin purple line. Deriving this from geometric principles, and aligning the Pockels cell on the table for greatest dynamic range is a relatively straightforward. The students perform these measurement by scanning through voltage settings on the Pockels driver, while monitoring light intensity. This explains to them the particular orientation of the crystal relative to the laser.\newline
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{fig9.jpg}
    \caption{{\bf Examples for teaching principles of two-photon microscopy.} \textbf{A)} Transmitted laser power as function of the control voltage applied to the Pockels crystal for two different crystal orientations. The red orientation is far from the optimum and produces a small dynamic range for intensity control. The blue orientation is close to the optimal. The thin purple line is a best fit (see text). \textbf{B)} Fluorescence in Fluorescein as a function of applied dispersion compensation. A fit allows to estimate the pulse width. Note also the symmetric shoulders not captured by the fit, suggesting a non-Gaussian pulse shape.}
    \label{fig9}
\end{figure}
%
If students are interested in dispersion of the laser pulse and its correction, a more challenging experiment and analysis are shown in Fig.~\ref{fig9}B. Here, students used the fluorescence at fixed laser power for different values of dispersion compensation to infer the laser pulse width. This is possible because the efficiency of two-photon fluorescence depends inversely on the pulse duration \cite{Denk1990}. The laser's built-in dispersion compensation can give the short-wavelength components a head start such that after delays in the optical path, blue and red components can arrive at the sample at the same time. One can write down the expected fluorescence $I$ as function of this group delay dispersion $\varphi$ applied to a $\varphi_0$-dispersed Gaussian pulse of FWHM width $\Delta\tau$ as
\begin{eqnarray}
    I(\varphi) =I_0 \left(1+\alpha\frac{(\varphi+\varphi_0)^2}{\Delta\tau^4}\right)^{-1/2}.
\end{eqnarray}
Here, $\alpha=16\log(2)^2$. This equation can be derived by expressing the Gaussian pulse shape in the Fourier domain, applying a phase-shift along the laser path to quadratic order in the frequency \cite{Young2015}, and computing the result in the time domain. Deriving this expression is a fun at-home exercise. The fit suggests that the various  optical components introduced a dispersion of $\varphi_0\approx20200\pm170\text{ fs}^2$. When removed with the built-in dispersion compensation of the laser, our system operates with a FWHM pulse of $\Delta\tau \approx 150\pm20\text{ fs}$, which is close to, but significantly longer than the $\approx110\text{ fs}$ pulses produced by the laser itself (measured with an autocorrelator). This suggests detectable non-linear dispersion that we cannot compensate with our optics. Note that analyses like these, relating laser physics and fluorescence, are close to the research frontier\cite{Saidi2023}.

\section*{Discussion}

In this article, we have covered the design, building and alignment of a two-photon microscope. We then assessed its performance, and demonstrated several possible use cases, from plant physiology over material science to neuroscience. In the following lines, we will expand on issues raised in passing earlier, and conclude with a note about our instrument in the growing space of open source scientific instrumentation.

\subsection*{Improvements to the microscope}

(1) We used silver mirrors to direct the beam. These reflect around 98\% of incoming light. Dielectric mirrors perform significantly better, typically exceeding 99.5\% reflectivity. With around 8 to 10 mirrors in the beam, this can boost overall transmission by 10\%-20\%, but comes at slightly higher cost and can introduce complex dispersion \cite{Rupprecht2019}. In our experiments, we have not encountered power limitations: For the data presented here, we used only $\approx 15\text{ mW}$ under the objective while at maximum transmission the system allows for up to $\approx 260\text{ mW}$ to leave the objective. For simplicity, and similar to other designs \cite{Sofroniew2016}, we therefore used exclusively silver mirrors. However, for stimulation or ablation experiments, considerations might be different. \newline
(2) In our design, a piezoelectric collar is attached to the objective. Physically moving the objective along the optical axis allows to image several planes. The time required by the piezoelectric collar to stabilize is on the scale of 10 ms. Imaging faster processes requires a different approach, e.g. with an electrically tunable lens (ETL). These lenses have a variable focal length, usually from around 10 cm to infinity, that can be set with a control voltage within $<1\text{ ms}$. A convenient spot for an ETL might be right before the scan assembly, while care should be taken to not focus the beam on the scanning mirrors to avoid damage.\newline
(3) Estimating the pulse duration suggests non-linear dispersion that we cannot correct. This is highly dependent on the laser. For readers interested in this aspect of microscope design, we refer to \cite{Saidi2023, Bueno2019}. If available, other light sources might be worth exploring.\newline
(4) We made the design choice to place the resonant and slow scanning mirrors close together in space while the plane equidistant between the rotational axis of both scan mirrors is conjugate to the back aperture of the objective. This is a compromise that is used by others as well (e.g. Thorlabs' Cerna or earlier designs \cite{Rosenegger2014, Tan1999, Nguyen2001}). Other microscope designs add a pair of lenses between the slow and resonant scanning mirrors to position them in conjugated planes. Our design choice significantly simplifies the design and reduces the amount of glass between laser and sample to reduce dispersion. It does, however, introduce a Barrel distortion that becomes visible at low magnifications.\newline
(5) The fixed $2\times$ beam expander can be replaced with variable/zoom beam expander that allows a user to dial in a particular beam magnification to tweak the point spread function for a particular application\cite{Smith2019}. We have used this in some of our earlier designs, e.g. \cite{Song2017}. While a high numerical aperture is beneficial for high axial resolution and improved separation of somatic and neuropil signals \cite{Kerr2008, Gobel2007}, the large angles at which excitation light is brought into the brain results in longer paths for the light to take. This can lead to more scattering. For experiments aiming to image deep in the brain, a lower NA can be beneficial \cite{Tung2004}. Similarly, the presence of axial brain motion of several \textmu m in awake and behaving animals can introduce movement artifacts at high numerical apertures \cite{Dombeck2007}. That said, even when underfilled by the excitation beam, a large NA of the objective is beneficial to collect as much fluorescent light as possible.\newline
(6) It can be advantageous to combine the two-photon system with wide-field imaging. To this end, the two inch mirror above the collection optics can be replaced with a 800 or 900 nm short-pass filter followed by a tube lens and a camera. This would allow infrared imaging around 700 nm through the collection optics, as it is transparent above 665 nm. While this is relatively straightforward to do \cite{Rosenegger2014}, widefield epipfluorescence is harder to realize.\newline
(7) The collection optics are designed to have an average optical density $>4$ in the range between 400 nm and 460 nm. This is advantageous for use in virtual reality systems, because light leaving a projector can be filtered to this range before projected on a dome surrounding the objective and animal. We have successfully used budget friendly colored glass filters in front of the projector (Schott BG25 or Schott BG5), and long-pass colored glass (Schott RG780) to block projector light from entering the excitation path \cite{Dombeck2007}. Combined with a light shield around the objective, such a projection system will only minimally interfere with imaging (e.g. \cite{Nieh2021}). This is a useful range for visual experiments in mice, but if other model organisms are desired, the optical filters need to be adjusted accordingly.\newline
(8) Relatedly, the collection optics described here, built from lenses with two inch diameter, can accept fluorescent light leaving the objective back aperture in the range of $\pm 8\text{ deg}$. If one intends to image at larger angles, larger lenses in the collection optics can be beneficial \cite{Tsai2015} and some of our microscopes use a collection design with three inch diameter optics \cite{Song2017, Nieh2021}. In our experience, it is difficult to push this further, because large angles reduce the effectiveness of the dichroic mirrors and band-pass filters.\newline
(9) Parts of our microscope can be replaced with commercial products. For example, we have used commercial telecentric scan lenses in the past \cite{Song2017, Rich2024}. These come at higher cost and introduce higher dispersion, but exhibit very low field curvature. While low field curvature is not always considered the highest priority in neuroscience applications, this can be a useful substitution.\newline
(10) Regarding the mechanical design, we decided to not mount the microscope on an xy translation stage. This means that the sample has to be moved laterally relative to the microscope. We did, however, include a z-adjustment through a piezoelectric collar for the objective. This significantly simplifies measurements of point spread functions, and allows rapid volumetric imaging which we consider worth the extra cost. Our laboratory had great success with this design, and we have developed stages for mounting animals that incorporate drives for xy motion. Mounting the microscope itself on an xyz controller that can carry its weight, and precisely aligning the optical path to be parallel to x, y and z displacement is possible but will incur extra cost.\newline
(11) To aid mechanical stability, the aluminium plate forming the base of the head of the microscope could be replaced with a steel plate, or a thicker piece of aluminium, that is less prone to vibrations when bumped into. This would also be important if one wanted to extend the microscope head to provide even more space around the objective.

\subsection*{Teaching advanced methods in neuroscience}
In addition to training researchers on how to set up a two-photon microscope, we aimed to provide examples of imaging data that are not neuroscience related, and do not require the handling of animals or living neurons (cf. Fig.~\ref{fig5}, \ref{fig6}, \ref{fig9}). Other samples are possible as well (such as cheese \cite{Nguyen2001}). Working with such samples can make experiments in a teaching lab easier as such spaces are not always designated animal work areas. If students can work with animals, the instrument is ideally suited for various neuroscience experiments. For example, the Calcium imaging demonstrated in Figs.~\ref{fig7}, \ref{fig8} could be combined with pharmacology to demonstrate changes of neural activity patterns. Or students can learn in a controlled environment how to get optical access to the nervous system and hone in their surgery skills to produce good quality optical windows\cite{Holtmaat2009, Grienberger2022}.
Our microscope was set up in a teaching lab space at the Princeton Neuroscience Institute. Over the course of three years, it was disassembled and re-assembled by various generations of students and postdocs. We found that assembling and aligning the microscope, as described, takes around 10 work-days. These two weeks seem to be a good compromise between depth, and researcher commitment. Various additional content across difficulty levels can be added depending on student interest and abilities (cf. Fig.~\ref{fig9}). For example, and only mentioned in passing before, the history and current applications of the two-photon effect and its use in microscopy is a fascinating subject to explore, e.g. \cite{Sheppard2020, Yao2023}.\newline 
Students might also become interested in further optimizing the optical design, or wonder why many lenses are used in lens groups. Questions like these can sometimes be linked to prior student knowledge. For example, for students interested in astronomy, the tube lens can be thought of as an eye piece with a long focal length and eye relief \cite{Smith2007}. In our system, the tube lens projects the image formed by the scan lens to an exit pupil, the back aperture of the objective. The objective then focuses the collimated beams onto the sample. In astronomy, the eye piece forms collimated beams of the image formed by the objective lens. The beams converge at some distance (the ``eye relief'') to enter the pupil of the eye of a human observer. The lens in the human eye then focuses the collimated beams onto the retina. Pl\"ossl designs in astronomy are known to perform particularly well for long eye relief \cite{Smith2007, Nagler1983}, and are a common design in two-photon microscopes as well (e.g. \cite{Rupprecht2024}). Our design is close to this, but flipped one of the two lenses to a Petzval configuration. In our hands, this configuration performed better \cite{Hong2022, Bumstead2018, Mayrhofer2015}.\newline
For students interested in photography, the scan lens can be thought of as a 100 mm f/2 camera lens. Camera lenses face similar challenges as our scan lens. They have to focus distant objects, at different angles, into the same flat photographic emulsion, while faithfully depicting true angular distances with minimal aberrations. Think for example about stars on the sky, whose light arrives as beams at different angles at the camera lens. Addressing this problem lead to lens designs that were very similar to our scan lens. One important design, sometimes referred to as a Gauss doublet objective \cite{Kidger2001}, features two symmetrically configured doublets providing much of the optical power, while additional lenses control aberrations. For example, the Zeiss Planar lens from 1897 features 6 elements in 4 groups with a symmetric pair of doublets in a design very similar to our scan lens assembly \cite{Rudolf1897}. To help students and researchers explore these sometime challenging subjects theoretically, we provide all Zemax files for the microscope optics. More advanced optimization in Zemax requires the use of their programming API. For example, the simulated point spread functions and their analysis in Fig.~\ref{fig2} were computed in Matlab, using the Zemax API. The code is provided in our repository. This allows for fast optimization of system parameters by effectively scanning through lens spacing, lens types, and the like. This can allow researchers and students to explore the limits and possible future improvements of the system. Experimental modifications of the system are simpler in the format of a workshop. For example, students can swap or rotate lenses and observe the effects. The scan lens assembly is particularly sensitive to this, because the incoming laser beam is concentrated into a small region that gets scanned across the surface of the lens. Small surface imperfections will introduce optical difference across spot positions, and significantly affect field flatness, cf. Fig.~\ref{fig5}C,D,E.\newline
Finally, it can be a useful learning experience to re-use parts from other microscopes, such as xy scanners from a confocal microscope\cite{Nikolenko2013}, and to mix and match parts to learn what works and what does not. It is an important learning experience to understand failure modes. For example, assembling the lens groups can lead to dust when tightening the retaining rings through the anodized aluminium threads. Or the rectangular ``TV screen'' field of view (visible in the figures at zoom level 1 above) is caused by a round, and not elliptical mirror above the scan engine. This mirror clips the beam along one axis. (This is corrected in the CAD files.) When analyzing data, we suggest to use simple programs. Our Image analyses here were done in Fiji \cite{Schindelin2019} combined with simple python and matlab scripts. In our experience, students learn very effectively through hands-on open-ended pedagogy and pursuing their own interests \cite{Zajdel2016}.\newline

\subsection*{Open scientific instrumentation}
In this article, we described the instrument's mode of operation, and provide an overview of the design. For the complete and illustrated built instructions, please see the git repository and attached build instructions. To aid discoverability, we have generated an Open Know How Manifest (OKH-manifest), located in the hardware folder of the git repository at \url{https://github.com/BrainCOGS/Microscope}.\newline
The growing space of open-source instrumentation can improve science in several ways: (1) enabling faster innovation through lower costs and enabling work in low-resource settings. (2) facilitating review and inspection by avoiding black-box designs and (3) providing a benchmark for innovation towards next-generation technology. We hope that our instrument, combined with earlier designs \cite{Rosenegger2014, Mayrhofer2015, Tan1999}, and recent developments like the head mounted microscope \cite{Zong2022} or the Janelia Research Campus microscope \cite{Janelia2024}, can serve as benchmarks for future instruments. Relatedly, we have contributed to other projects that follow this philosophy in microscopy \cite{Scott2018}, but also designing an open source ventilator during the COVID-19 pandemic \cite{LaChance2022,POVMC2022}, and a \textmu-contact printing device \cite{Samhaber2016}. Making these devices fully open has informed the narrative in this article, the design and organization of the published files, and also the choice of a open access journal. Finally, the open approach can make two-photon microscopy more accessible to researchers, thereby greatly expanding the ability to train students in approaching such technology and producing new inventions. In our ventilator work, this has led to one of the first deep-RL controlled devices that performed superior to classical control schemes \cite{Suo2021}. Future will tell how the community will make best use of Twinkle. The world is moving towards more open technology \cite{Schottdorf2024}, in particular in the microscopy community \cite{Hohlbein2022}. We hope that our microscope and its future iterations can play a part in this movement.

\subsection*{Disclaimer}
The aim of our work is to allow anyone to build a high-performance and cost-effective two-photon microscope. However, the information here cannot be exhaustive. We recommend anyone embarking on this journey to engage with the community, to carefully think about effective solutions to their use-case and specific experiment at hand, and to adjust to the ever changing landscape of available technology. When adapting the optical path to their needs, we suggest to start at our lens combinations, and then optimize (at the very least) the lens spacings in Zemax. Technology develops rapidly, and much of the specific components mentioned here will be outdated in a few years. We believe that science progresses best if researchers understand their instrumentation, and leverage the current cutting edge of what is possible to further their science.\newline
This work is free: you can redistribute it and/or modify it under the terms of the Creative Commons Attribution 4.0 International license, version 4 of the License, or (at your option) any later version (CC-BY-4.0). This work is distributed in the hope that it will be useful, but without any warranty, to the extent permitted by law; without even the implied warranty of merchantability or fitness for a particular purpose. A copy of the License is provided in our repository.  For more details, see \url{http://www.gnu.org/licenses/}.

\section*{Supporting information}

\paragraph*{S1 Appendix:}
\label{S1_Appendix}
A document with detailed build instructions and pictures of the microscope.

\paragraph*{\bf Online Repository:} 
\label{repository}
All CAD and optics design files, bill-of-materials, and other useful information: \url{https://github.com/BrainCOGS/Microscope}.

\section*{Acknowledgments}
MS and MD are supported by NIH grant U19NS132720. MS is also supported by a C.V. Starr fellowship and a Burroughs Wellcome Fund's Career Award at the Scientific Interface. AL was supported by the NSF through the Center for the Physics of Biological Function (PHY-1734030). We thank Beatrice Hadiwidjaja for transgenic Zebrafish husbandry, and Drs. Lindsay Collins and Anthony Ambrosini for hospitality and accommodating our tinkering in the teaching lab of the Princeton Neuroscience Institute. We thank Kai Br\"oking for helpful comments.

\section*{Author Contributions}
%  Follow the "CRediT Taxonomy" - plos standard. 
\begin{itemize}
    \item \textbf{Conceptualization}: Stephan Y. Thiberge.
    \item \textbf{Data curation}: Manuel Schottdorf, Mika Diamanti, Albert Lin, Stephan Y. Thiberge.
    \item \textbf{Formal analysis}: Manuel Schottdorf, E. Mika Diamanti, Albert Lin.
    \item \textbf{Funding acquisition}: Stephan Y. Thiberge.
    \item \textbf{Investigation}: Manuel Schottdorf, P. Dylan Rich, E. Mika Diamanti, Albert Lin, Sina Tafazoli, Edward Nieh.
    \item \textbf{Methodology}: Manuel Schottdorf, P. Dylan Rich, E. Mika Diamanti, Albert Lin, Sina Tafazoli, Edward H. Nieh, Stephan Y. Thiberge. 
    \item \textbf{Project administration}: Manuel Schottdorf, Stephan Y. Thiberge.
    \item \textbf{Resources}: Manuel Schottdorf, Stephan Y. Thiberge.
    \item \textbf{Software}: Manuel Schottdorf, E. Mika Diamanti, Albert Lin.
    \item \textbf{Supervision}: Stephan Y. Thiberge.
    \item \textbf{Validation}: Manuel Schottdorf, P. Dylan Rich, E. Mika Diamanti.
    \item \textbf{Visualization}: Manuel Schottdorf, E. Mika Diamanti, Albert Lin.
    \item \textbf{Writing – original draft}: Manuel Schottdorf.
    \item \textbf{Writing – review \& editing}: Manuel Schottdorf, P. Dylan Rich, E. Mika Diamanti, Albert Lin, Sina Tafazoli, Stephan Thiberge.
\end{itemize}

\nolinenumbers

\begin{thebibliography}{10}

\bibitem{Denk1990}
Denk W, Strickler JH, Webb WW. Two-photon laser scanning fluorescence microscopy. Science. 1990 Apr 6;248(4951):73-6. doi: 10.1126/science.2321027. PMID: 2321027.

\bibitem{Svoboda1997}
Svoboda K, Denk W, Kleinfeld D, Tank DW. In vivo dendritic calcium dynamics in neocortical pyramidal neurons. Nature. 1997 Jan 9;385(6612):161-5. doi: 10.1038/385161a0. PMID: 8990119.

\bibitem{So2000}
So PT, Dong CY, Masters BR, Berland KM. Two-photon excitation fluorescence microscopy. Annu Rev Biomed Eng. 2000;2:399-429. doi: 10.1146/annurev.bioeng.2.1.399. PMID: 11701518.

\bibitem{Helmchen2005}
Helmchen F, Denk W. Deep tissue two-photon microscopy. Nat Methods. 2005 Dec;2(12):932-40. PMID: 16299478.

\bibitem{Luu2024}
Luu P, Fraser SE, Schneider F. More than double the fun with two-photon excitation microscopy. Commun Biol. 2024 Mar 26;7(1):364. doi: 10.1038/s42003-024-06057-0. PMID: 38531976; PMCID: PMC10966063.

\bibitem{Grienberger2022}
Grienberger C, Giovannucci A, Zeiger W, Portera-Cailliau C. Two-photon calcium imaging of neuronal activity. Nat Rev Methods Primers. 2022;2(1):67. doi: 10.1038/s43586-022-00147-1. Epub 2022 Sep 1. PMID: 38124998; PMCID: PMC10732251.

\bibitem{Baden2016}
Baden T, Berens P, Franke K, Román Rosón M, Bethge M, Euler T. The functional diversity of retinal ganglion cells in the mouse. Nature. 2016 Jan 21;529(7586):345-50. doi: 10.1038/nature16468. Epub 2016 Jan 6. PMID: 26735013; PMCID: PMC4724341.

\bibitem{Harvey2012}
Harvey CD, Coen P, Tank DW. Choice-specific sequences in parietal cortex during a virtual-navigation decision task. Nature. 2012 Mar 14;484(7392):62-8. doi: 10.1038/nature10918. PMID: 22419153; PMCID: PMC3321074.

\bibitem{Nieh2021}
Nieh EH, Schottdorf M, Freeman NW, Low RJ, Lewallen S, Koay SA, Pinto L, Gauthier JL, Brody CD, Tank DW. Geometry of abstract learned knowledge in the hippocampus. Nature. 2021 Jul;595(7865):80-84. doi: 10.1038/s41586-021-03652-7. Epub 2021 Jun 16. PMID: 34135512; PMCID: PMC9549979.

\bibitem{Engelhard2019}
Engelhard B, Finkelstein J, Cox J, Fleming W, Jang HJ, Ornelas S, Koay SA, Thiberge SY, Daw ND, Tank DW, Witten IB. Specialized coding of sensory, motor and cognitive variables in VTA dopamine neurons. Nature. 2019 Jun;570(7762):509-513. doi: 10.1038/s41586-019-1261-9. Epub 2019 May 29. PMID: 31142844; PMCID: PMC7147811.

\bibitem{Yu2018}
Gu Y, Lewallen S, Kinkhabwala AA, Domnisoru C, Yoon K, Gauthier JL, Fiete IR, Tank DW. A Map-like Micro-Organization of Grid Cells in the Medial Entorhinal Cortex. Cell. 2018 Oct 18;175(3):736-750.e30. doi: 10.1016/j.cell.2018.08.066. Epub 2018 Sep 27. PMID: 30270041; PMCID: PMC6591153.

\bibitem{Trautmann2021}
Trautmann EM, O'Shea DJ, Sun X, Marshel JH, Crow A, Hsueh B, Vesuna S, Cofer L, Bohner G, Allen W, Kauvar I, Quirin S, MacDougall M, Chen Y, Whitmire MP, Ramakrishnan C, Sahani M, Seidemann E, Ryu SI, Deisseroth K, Shenoy KV. Dendritic calcium signals in rhesus macaque motor cortex drive an optical brain-computer interface. Nat Commun. 2021 Jun 17;12(1):3689. doi: 10.1038/s41467-021-23884-5. PMID: 34140486; PMCID: PMC8211867.

\bibitem{Ebina2018}
Ebina T, Masamizu Y, Tanaka YR, Watakabe A, Hirakawa R, Hirayama Y, Hira R, Terada SI, Koketsu D, Hikosaka K, Mizukami H, Nambu A, Sasaki E, Yamamori T, Matsuzaki M. Two-photon imaging of neuronal activity in motor cortex of marmosets during upper-limb movement tasks. Nat Commun. 2018 May 14;9(1):1879. doi: 10.1038/s41467-018-04286-6. PMID: 29760466; PMCID: PMC5951821.

\bibitem{Sharma2016}
Sharma R, Williams DR, Palczewska G, Palczewski K, Hunter JJ. Two-Photon Autofluorescence Imaging Reveals Cellular Structures Throughout the Retina of the Living Primate Eye. Invest Ophthalmol Vis Sci. 2016 Feb;57(2):632-46. doi: 10.1167/iovs.15-17961. PMID: 26903224; PMCID: PMC4771181.

\bibitem{Schottdorf2021}
Schottdorf M, Lee BB. A quantitative description of macaque ganglion cell responses to natural scenes: the interplay of time and space. J Physiol. 2021 Jun;599(12):3169-3193. doi: 10.1113/JP281200. Epub 2021 Jun 1. PMID: 33913164; PMCID: PMC8998785.

\bibitem{Renninger2013}
Renninger SL, Orger MB. Two-photon imaging of neural population activity in zebrafish. Methods. 2013 Aug 15;62(3):255-67. doi: 10.1016/j.ymeth.2013.05.016. Epub 2013 May 31. PMID: 23727462.

\bibitem{Seelig2010}
Seelig JD, Chiappe ME, Lott GK, Dutta A, Osborne JE, Reiser MB, Jayaraman V. Two-photon calcium imaging from head-fixed Drosophila during optomotor walking behavior. Nat Methods. 2010 Jul;7(7):535-40. doi: 10.1038/nmeth.1468. Epub 2010 Jun 6. Erratum in: Nat Methods. 2011 Feb;8(2):184. PMID: 20526346; PMCID: PMC2945246.

\bibitem{Lin2022}
Lin A, Witvliet D, Hernandez-Nunez L, Linderman SW, Samuel ADT, Venkatachalam V. Imaging whole-brain activity to understand behavior. Nat Rev Phys. 2022 May;4(5):292-305. doi: 10.1038/s42254-022-00430-w. Epub 2022 Mar 8. PMID: 37409001; PMCID: PMC10320740.

\bibitem{Baker2022}
Baker CA, McKellar C, Pang R, Nern A, Dorkenwald S, Pacheco DA, Eckstein N, Funke J, Dickson BJ, Murthy M. Neural network organization for courtship-song feature detection in Drosophila. Curr Biol. 2022 Aug 8;32(15):3317-3333.e7. doi: 10.1016/j.cub.2022.06.019. Epub 2022 Jul 5. PMID: 35793679; PMCID: PMC9378594.

\bibitem{Roemschied2023}
Roemschied FA, Pacheco DA, Aragon MJ, Ireland EC, Li X, Thieringer K, Pang R, Murthy M. Flexible circuit mechanisms for context-dependent song sequencing. Nature. 2023 Oct;622(7984):794-801. doi: 10.1038/s41586-023-06632-1. Epub 2023 Oct 11. PMID: 37821705; PMCID: PMC10600009.

\bibitem{Deutsch2020}
Deutsch D, Pacheco D, Encarnacion-Rivera L, Pereira T, Fathy R, Clemens J, Girardin C, Calhoun A, Ireland E, Burke A, Dorkenwald S, McKellar C, Macrina T, Lu R, Lee K, Kemnitz N, Ih D, Castro M, Halageri A, Jordan C, Silversmith W, Wu J, Seung HS, Murthy M. The neural basis for a persistent internal state in Drosophila females. Elife. 2020 Nov 23;9:e59502. doi: 10.7554/eLife.59502. PMID: 33225998; PMCID: PMC7787663.

\bibitem{Kim2017}
Kim SS, Rouault H, Druckmann S, Jayaraman V. Ring attractor dynamics in the Drosophila central brain. Science. 2017 May 26;356(6340):849-853. doi: 10.1126/science.aal4835. Epub 2017 May 4. PMID: 28473639.

\bibitem{Pacheco2021}
Pacheco DA, Thiberge SY, Pnevmatikakis E, Murthy M. Auditory activity is diverse and widespread throughout the central brain of Drosophila. Nat Neurosci. 2021 Jan;24(1):93-104. doi: 10.1038/s41593-020-00743-y. Epub 2020 Nov 23. PMID: 33230320; PMCID: PMC7783861.

\bibitem{Brezovec2024}
Bella E. Brezovec, Andrew B. Berger, Yukun A. Hao, Feng Chen, Shaul Druckmann, Thomas R. Clandinin, Mapping the neural dynamics of locomotion across the Drosophila brain, Current Biology, Volume 34, Issue 4, 2024,
Pages 710-726.e4, ISSN 0960-9822, https://doi.org/10.1016/j.cub.2023.12.063.

\bibitem{Randi2023}
Randi F, Sharma AK, Dvali S, Leifer AM. Neural signal propagation atlas of Caenorhabditis elegans. Nature. 2023 Nov;623(7986):406-414. doi: 10.1038/s41586-023-06683-4. Epub 2023 Nov 1. PMID: 37914938; PMCID: PMC10632145.

\bibitem{Diamanti2021}
Diamanti EM, Reddy CB, Schröder S, Muzzu T, Harris KD, Saleem AB, Carandini M. Spatial modulation of visual responses arises in cortex with active navigation. Elife. 2021 Feb 4;10:e63705. doi: 10.7554/eLife.63705. PMID: 33538692; PMCID: PMC7861612.

\bibitem{Yao2023}
Yao P, Liu R, Broggini T, Thunemann M, Kleinfeld D. Construction and use of an adaptive optics two-photon microscope with direct wavefront sensing. Nat Protoc. 2023 Dec;18(12):3732-3766. doi: 10.1038/s41596-023-00893-w. Epub 2023 Nov 1. PMID: 37914781; PMCID: PMC11033548.

\bibitem{Song2017}
Song A, Charles AS, Koay SA, Gauthier JL, Thiberge SY, Pillow JW, Tank DW. Volumetric two-photon imaging of neurons using stereoscopy (vTwINS). Nat Methods. 2017 Apr;14(4):420-426. doi: 10.1038/nmeth.4226. Epub 2017 Mar 20. PMID: 28319111; PMCID: PMC5551981.

\bibitem{Rickgauer2014}
Rickgauer JP, Deisseroth K, Tank DW. Simultaneous cellular-resolution optical perturbation and imaging of place cell firing fields. Nat Neurosci. 2014 Dec;17(12):1816-24. doi: 10.1038/nn.3866. Epub 2014 Nov 17. PMID: 25402854; PMCID: PMC4459599.

\bibitem{Sofroniew2016}
Sofroniew NJ, Flickinger D, King J, Svoboda K. A large field of view two-photon mesoscope with subcellular resolution for in vivo imaging. Elife. 2016 Jun 14;5:e14472. doi: 10.7554/eLife.14472. PMID: 27300105; PMCID: PMC4951199.

\bibitem{Demas2021}
Demas J, Manley J, Tejera F, Barber K, Kim H, Traub FM, Chen B, Vaziri A. High-speed, cortex-wide volumetric recording of neuroactivity at cellular resolution using light beads microscopy. Nat Methods. 2021 Sep;18(9):1103-1111. doi: 10.1038/s41592-021-01239-8. Epub 2021 Aug 30. Erratum in: Nat Methods. 2021 Dec;18(12):1552. doi: 10.1038/s41592-021-01337-7. PMID: 34462592; PMCID: PMC8958902.

\bibitem{Bueno2019}
Bueno JM, Ávila FJ, Artal P. Comparing the performance of a femto fiber-based laser and a Ti:sapphire used for multiphoton microscopy applications. Appl Opt. 2019 May 10;58(14):3830-3835. doi: 10.1364/AO.58.003830. PMID: 31158196.

\bibitem{Rosenegger2014}
Rosenegger DG, Tran CHT, LeDue J, Zhou N, Gordon GR (2014) A High Performance, Cost-Effective, Open-Source Microscope for Scanning Two-Photon Microscopy that Is Modular and Readily Adaptable. PLoS ONE 9(10): e110475. https://doi.org/10.1371/journal.pone.0110475

\bibitem{Mayrhofer2015}
Mayrhofer JM, Haiss F, Haenni D, Weber S, Zuend M, Barrett MJ, Ferrari KD, Maechler P, Saab AS, Stobart JL, Wyss MT, Johannssen H, Osswald H, Palmer LM, Revol V, Schuh CD, Urban C, Hall A, Larkum ME, Rutz-Innerhofer E, Zeilhofer HU, Ziegler U, Weber B. Design and performance of an ultra-flexible two-photon microscope for in vivo research. Biomed Opt Express. 2015 Oct 2;6(11):4228-37. doi: 10.1364/BOE.6.004228. PMID: 26600989; PMCID: PMC4646533.

\bibitem{Kidger2001}
M. J. Kidger, Fundamental Optical Design (SPIE, 2001).

\bibitem{Negrean2014}
Negrean A, Mansvelder HD. Optimal lens design and use in laser-scanning microscopy. Biomed Opt Express. 2014 Apr 18;5(5):1588-609. doi: 10.1364/BOE.5.001588. PMID: 24877017; PMCID: PMC4026907.

\bibitem{Smith2007}
W. J. Smith, Modern Optical Engineering, 4th ed. (McGraw-Hill Professional, 2007).

\bibitem{Hong2022}
Hong W, Dunsby C. Automatic tube lens design from stock optics for microscope remote-refocusing systems. Opt Express. 2022 Jan 31;30(3):4274-4287. doi: 10.1364/OE.450320. PMID: 35209667.

\bibitem{Bumstead2018}
Bumstead JR, Park JJ, Rosen IA, Kraft AW, Wright PW, Reisman MD, Côté DC, Culver JP. Designing a large field-of-view two-photon microscope using optical invariant analysis. Neurophotonics. 2018 Apr;5(2):025001. doi: 10.1117/1.NPh.5.2.025001. Epub 2018 Feb 19. PMID: 29487876; PMCID: PMC5818100.

\bibitem{Tsai2015}
Tsai PS, Mateo C, Field JJ, Schaffer CB, Anderson ME, Kleinfeld D. Ultra-large field-of-view two-photon microscopy. Opt Express. 2015 Jun 1;23(11):13833-47. doi: 10.1364/OE.23.013833. PMID: 26072755; PMCID: PMC4523368.

\bibitem{Zipfel2003}
Zipfel WR, Williams RM, Webb WW. Nonlinear magic: multiphoton microscopy in the biosciences. Nat Biotechnol. 2003 Nov;21(11):1369-77. doi: 10.1038/nbt899. PMID: 14595365.

\bibitem{Taddeucci1996}
Taddeucci A, Martelli F, Barilli M, Ferrari M, Zaccanti G. Optical properties of brain tissue. J Biomed Opt. 1996 Jan;1(1):117-23. doi: 10.1117/12.227816. PMID: 23014652.

\bibitem{Young2015}
Young MD, Field JJ, Sheetz KE, Bartels RA, Squier J. A pragmatic guide to multiphoton microscope design. Adv Opt Photonics. 2015 Jun 30;7(2):276-378. doi: 10.1364/AOP.7.000276. PMID: 27182429; PMCID: PMC4863715.

\bibitem{Tsai2002}
Tsai PS, et al. Principles, design, and construction of a two photon laser scanning microscope for in vitro and in vivo brain imaging. In: Frostig RD, editor. In Vivo Optical Imaging of Brain Function. CRC Press; Boca Raton: 2002. pp. 113–171. \url{https://neurophysics.ucsd.edu/publications/tsai_book_chapter_crc_2002.pdf}

\bibitem{Pologruto2003}
Pologruto TA, Sabatini BL, Svoboda K. ScanImage: Flexible software for operating laser scanning microscopes. BioMed Eng OnLine 2, 13 (2003). \url{https://doi.org/10.1186/1475-925X-2-13}

\bibitem{Limpert2006}
J. Limpert, F. Roser, T. Schreiber, A. Tunnermapnn, High-power ultrafast fiber laser systems. in IEEE Journal of Selected Topics in Quantum Electronics, vol. 12, no. 2, pp. 233-244, March-April 2006, doi: 10.1109/JSTQE.2006.872729.

\bibitem{Wise2012}
Wise FW. Femtosecond Fiber Lasers Based on Dissipative Processes for Nonlinear Microscopy. IEEE J Sel Top Quantum Electron. 2012;18(4):1412-1421. doi: 10.1109/JSTQE.2011.2179919. PMID: 23869163; PMCID: PMC3712536.

\bibitem{Guide2011}
National Research Council (US) Committee for the Update of the Guide for the Care and Use of Laboratory Animals. Guide for the Care and Use of Laboratory Animals. 8th ed. Washington (DC): National Academies Press (US); 2011. PMID: 21595115.

\bibitem{Rupprecht2018}
Rupprecht P. Springtime for two-photon microscopy. Blogpost April 25 2018, \url{https://gcamp6f.com/2018/04/25/springtime-for-two-photon-microscopy/}

\bibitem{Nguyen2001}
Nguyen QT, Callamaras N, Hsieh C, Parker I. Construction of a two-photon microscope for video-rate Ca(2+) imaging. Cell Calcium. 2001 Dec;30(6):383-93. doi: 10.1054/ceca.2001.0246. PMID: 11728133.

\bibitem{Cheung2010}
Cheung AY, Boavida LC, Aggarwal M, Wu HM, Feijó JA. The pollen tube journey in the pistil and imaging the in vivo process by two-photon microscopy. J Exp Bot. 2010 Apr;61(7):1907-15. doi: 10.1093/jxb/erq062. Epub 2010 Apr 2. PMID: 20363865.

\bibitem{Schottdorf2018}
Schottdorf M. The reconstitution of visual cortical feature selectivity in vitro. PhD Thesis 2018. \url{http://dx.doi.org/10.53846/goediss-6721}

\bibitem{Cong2017}
Cong L, Wang Z, Chai Y, Hang W, Shang C, Yang W, Bai L, Du J, Wang K, Wen Q. Rapid whole brain imaging of neural activity in freely behaving larval zebrafish (Danio rerio). Elife. 2017 Sep 20;6:e28158. doi: 10.7554/eLife.28158. PMID: 28930070; PMCID: PMC5644961.

\bibitem{Schindelin2019}
Schindelin J, Arganda-Carreras I, Frise E, Kaynig V, Longair M, Pietzsch T, Preibisch S, Rueden C, Saalfeld S, Schmid B, Tinevez JY, White DJ, Hartenstein V, Eliceiri K, Tomancak P, Cardona A. Fiji: an open-source platform for biological-image analysis. Nat Methods. 2012 Jun 28;9(7):676-82. doi: 10.1038/nmeth.2019. PMID: 22743772; PMCID: PMC3855844.

\bibitem{Pachitariu2016}
Pachitariu M, Stringer C, Schröder S, Dipoppa M, Rossi LF, Carandini M, Harris KD. (2016). Suite2p: beyond 10,000 neurons with standard two-photon microscopy. BioRxiv, 061507. \url{https://www.biorxiv.org/content/10.1101/061507v2}

\bibitem{Saidi2023}
Saidi S, Shtrahman M. Evaluation of compact pulsed lasers for two-photon microscopy using a simple method for measuring two-photon excitation efficiency. Neurophotonics. 2023 Oct;10(4):044303. doi: 10.1117/1.NPh.10.4.044303. Epub 2023 Nov 14. PMID: 38076726; PMCID: PMC10704185.

\bibitem{Rupprecht2019}
Peter Rupprecht. (2019). PTRRupprecht/Photon-yield-and-pulse-dispersion: Photon yield and pulse dispersion, version 1 (Version version1). Zenodo. https://doi.org/10.5281/zenodo.2592465 \url{https://ptrrupprecht.github.io/Photon-yield-and-pulse-dispersion/}

\bibitem{Smith2019}
Smith, SL (2019). Building a Two-Photon Microscope Is Easy. In: Hartveit, E. (eds) Multiphoton Microscopy. Neuromethods, vol 148. Humana, New York, NY. \url{https://doi.org/10.1007/978-1-4939-9702-2_1}

\bibitem{Kerr2008}
Kerr JN, Denk W. Imaging in vivo: watching the brain in action. Nat Rev Neurosci. 2008 Mar;9(3):195-205. doi: 10.1038/nrn2338. PMID: 18270513.

\bibitem{Gobel2007}
G\"obel W, Helmchen F. In vivo calcium imaging of neural network function. Physiology (Bethesda). 2007 Dec;22:358-65. doi: 10.1152/physiol.00032.2007. PMID: 18073408.

\bibitem{Tung2004}
Tung CK, Sun Y, Lo W, Lin SJ, Jee SH, Dong CY. Effects of objective numerical apertures on achievable imaging depths in multiphoton microscopy. Microsc Res Tech. 2004 Dec;65(6):308-14. doi: 10.1002/jemt.20116. PMID: 15662621.

\bibitem{Dombeck2007}
Dombeck DA, Khabbaz AN, Collman F, Adelman TL, Tank DW. Imaging large-scale neural activity with cellular resolution in awake, mobile mice. Neuron. 2007 Oct 4;56(1):43-57. doi: 10.1016/j.neuron.2007.08.003. PMID: 17920014; PMCID: PMC2268027.

\bibitem{Rich2024}
Rich PD, Thiberge SY, Scott BB, Guo C, Tervo DGR, Brody CD, Karpova AY, Daw ND, Tank DW. Magnetic voluntary head-fixation in transgenic rats enables lifespan imaging of hippocampal neurons. Nat Commun. 2024 May 16;15(1):4154. doi: 10.1038/s41467-024-48505-9. PMID: 38755205; PMCID: PMC11099169.

\bibitem{Holtmaat2009}
Holtmaat A, Bonhoeffer T, Chow DK, Chuckowree J, De Paola V, Hofer SB, Hübener M, Keck T, Knott G, Lee WC, Mostany R, Mrsic-Flogel TD, Nedivi E, Portera-Cailliau C, Svoboda K, Trachtenberg JT, Wilbrecht L. Long-term, high-resolution imaging in the mouse neocortex through a chronic cranial window. Nat Protoc. 2009;4(8):1128-44. doi: 10.1038/nprot.2009.89. Epub 2009 Jul 16. PMID: 19617885; PMCID: PMC3072839.

\bibitem{Sheppard2020}
Sheppard CJR. Multiphoton microscopy: a personal historical review, with some future predictions. J Biomed Opt. 2020 Jan;25(1):1-11. doi: 10.1117/1.JBO.25.1.014511. PMID: 31970944; PMCID: PMC6974959.

\bibitem{Nagler1983}
Nagler A. Plossl type eyepiece for use in astronomical instruments. US-Patent US4482217A 1983
\url{https://patents.google.com/patent/US4482217A/en}

\bibitem{Rupprecht2024}
Rupprecht P, Duss SN, Becker D, Lewis CM, Bohacek J, Helmchen F. Centripetal integration of past events in hippocampal astrocytes regulated by locus coeruleus. Nat Neurosci. 2024 May;27(5):927-939. doi: 10.1038/s41593-024-01612-8. Epub 2024 Apr 3. PMID: 38570661; PMCID: PMC11089000.

\bibitem{Rudolf1897}
Rudolf P. Objekt-Glass. US-Patent US583336A 1897 \url{https://patents.google.com/patent/US583336A/en}.

\bibitem{Nikolenko2013}
Nikolenko V, Yuste R. How to build a two-photon microscope with a confocal scan head. Cold Spring Harb Protoc. 2013 Jun 1;2013(6):588-92. doi: 10.1101/pdb.ip075135. PMID: 23734024.

\bibitem{Zajdel2016}
Zajdel TJ, Maharbiz MM (2016) Teaching design with a tinkering-driven robot hack. Proceedings of 2016 IEEE Frontiers in Education Conference (FIE) \url{https://ieeexplore.ieee.org/document/7757484}

\bibitem{Tan1999}
Tan YP, Llano I, Hopt A, Würriehausen F, Neher E. Fast scanning and efficient photodetection in a simple two-photon microscope. J Neurosci Methods. 1999 Oct 15;92(1-2):123-35. doi: 10.1016/s0165-0270(99)00103-x. PMID: 10595710.

\bibitem{Zong2022}
Zong W, Obenhaus HA, Skytøen ER, Eneqvist H, de Jong NL, Vale R, Jorge MR, Moser MB, Moser EI. Large-scale two-photon calcium imaging in freely moving mice. Cell. 2022 Mar 31;185(7):1240-1256.e30. doi: 10.1016/j.cell.2022.02.017. Epub 2022 Mar 18. PMID: 35305313; PMCID: PMC8970296.

\bibitem{Janelia2024}
Modular In Vivo Multi-photon Microscope 2.2 \url{https://www.janelia.org/open-science/mimms-22-2024}

\bibitem{Scott2018}
Scott BB, Thiberge SY, Guo C, Tervo DGR, Brody CD, Karpova AY, Tank DW. Imaging Cortical Dynamics in GCaMP Transgenic Rats with a Head-Mounted Widefield Macroscope. Neuron. 2018 Dec 5;100(5):1045-1058.e5. doi: 10.1016/j.neuron.2018.09.050. Epub 2018 Oct 25. PMID: 30482694; PMCID: PMC6283673.

\bibitem{LaChance2022}
LaChance J, Schottdorf M, Zajdel TJ, Saunders JL, Dvali S, Marshall C, Seirup L, Sammour I, Chatburn RL, Notterman DA, Cohen DJ. PVP1-The People's Ventilator Project: A fully open, low-cost, pressure-controlled ventilator research platform compatible with adult and pediatric uses. PLoS One. 2022 May 11;17(5):e0266810. doi: 10.1371/journal.pone.0266810. PMID: 35544461; PMCID: PMC9094548.

\bibitem{POVMC2022}
The Princeton Open Ventilation Monitor Collaboration et al. Inexpensive Multipatient Respiratory Monitoring Syshttps://www.yapsutube.com/watch?v=uYOF-YggWAgtem for Helmet Ventilation During COVID-19 Pandemic. ASME. J. Med. Devices. March 2022; 16(1): 011003. https://doi.org/10.1115/1.4053386

\bibitem{Samhaber2016}
Samhaber R, Schottdorf M, El Hady A, Bröking K, Daus A, Thielemann C, Stühmer W, Wolf F. Growing neuronal islands on multi-electrode arrays using an accurate positioning-\textmu CP device. J Neurosci Methods. 2016 Jan 15;257:194-203. doi: 10.1016/j.jneumeth.2015.09.022. Epub 2015 Oct 1. PMID: 26432934.

\bibitem{Suo2021}
D. Suo, U. Ghai, E. Minasyan, P. Gradu, X. Chen, N. Agarwal, C. Zhang, K. Singh, J. LaChance, T. Zajdel, M. Schottdorf, D. Cohen, E. Hazan. Machine Learning for Medical Ventilator Control”, Machine Learning for Health (ML4H), available on arXiv: 2102.06779 (2022)

\bibitem{Schottdorf2024}
Schottdorf M, Yu G, Walker EY. Data science and its future in large neuroscience collaborations. bioRxiv [Preprint]. 2024 Mar 25:2024.03.20.585936. doi: 10.1101/2024.03.20.585936. PMID: 38585895; PMCID: PMC10996530.

\bibitem{Hohlbein2022}
Hohlbein J, Diederich B, Marsikova B, Reynaud EG, Holden S, Jahr W, Haase R, Prakash K. Open microscopy in the life sciences: quo vadis? Nat Methods. 2022 Sep;19(9):1020-1025. doi: 10.1038/s41592-022-01602-3. PMID: 36008630.

\end{thebibliography}

\end{document}

### 2024-09-11 documentation/supplement.tex
article/documentation and updated readme

% Template for PLoS
% Version 3.5 March 2018

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}
\usepackage{changepage}
\usepackage[utf8x]{inputenc}
\usepackage{textcomp,marvosym}
\usepackage{cite}
\usepackage[usenames,svgnames,table]{xcolor}
\usepackage[colorlinks = true,
            urlcolor = RoyalBlue,
            citecolor = Crimson,
            backref= page]{hyperref}
\usepackage[right]{lineno}
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }
\usepackage[table]{xcolor}
\usepackage{array}
\newcolumntype{+}{!{\vrule width 2pt}}

\usepackage{figchild}
\usepackage{enumerate}
\usepackage{sidecap}
\usepackage{wasysym}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

\bibliographystyle{plos2015}
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{fancy}

\fancyhf{}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below
\newcommand{\microns}{~\textmu m~} % ALL UNITS UPRIGHT WITH SPACE
\newcommand{\invivo}{\textit{in vivo}~}
%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

{
\centering\Large\textbf{Supplemental Online Material} 
}
\newline\newline
This supplemental material to the article ``TWINKLE: An open-source two-photon microscope for teaching and research'' describes the assembly, function and alignment of all parts of the microscope. Technical specifications are provided through the CAD files and the Zemax simulations in the online repository.

\tableofcontents
\newpage

\linenumbers

\section{Preface}

\subsection{Safety}
Class 4 lasers are extremely dangerous. A reflection on a surface can be enough to inflict permanent eye damage. Safety protocols must be observed. Consult with your institution's environmental health and safety officer and take proper training before performing any work with a laser system. Learn from people experienced with these devices and work carefully.\newline
During alignment, always wear goggles (ours were ML1 by NoIR LaserShields with an optical density $>7$ in the relevant range around $920\text{ nm}$), remove jewelry and watches, and use the low laser power (“alignment mode”) whenever possible. Once the assembly progresses further, full power mode is necessary. Extra care must be taken then. Always use Laser Viewing Cards to track the laser. We use Thorlabs VRC4. Always be conscious where the beam is, and where the beam goes. The beam must be terminated in beam blockers and should be shielded whenever possible with opaque plastic or anodized aluminium tubes to increase safety.

\subsection{Miscellaneous tools}
\begin{itemize}
    \item Use a high quality duster to remove any residue from optical surfaces. We use a Miller-Stephenson Aero-Duster Ultra MS-222L.
    \item To glue optical filters we used an extra fast setting epoxy (Hardman Double/Bubble Epoxy). To seal small gaps, we use black silicone putty (V-tie self-setting silicone rubber).
    \item We used either McMaster or Thorlabs screwdrivers and hex keys.
    \item For alignment, we used laser viewing cards (VRC4, Thorlabs), cage system alignment plates (VRC4CPT, Thorlabs), and irises (SM1 Graduated Ring-Actuated Iris Diaphragm, SM1D12C, Thorlabs).
\end{itemize}

\subsection{Miscellaneous tips}
\begin{itemize}
    \item Shield the beam as soon as alignment of a particular section is done. This increases safety, and avoids accidentally bumping into aligned components.
    \item \textit{Walking the beam}: Any beam can be threaded through two irises using two mirrors. The first mirror the beam meets is sometimes called the ``position'' mirror as it affects primarily the position of the beam. The second ``angle'' mirror instead primarily affects the angle. Assigning each mirror a separate function (position versus angle) and by adjusting them iteratively, is a good rule of thumb for driving the beam through the 2 irises and eventually hitting a specific point at the desired angle \cite{Thorlabs}. 
    \item Be mindful of reflections from all surfaces. Put back-reflecting component at a slight angle to the beam (e.g. the half wave plate) to avoid back-reflections directly into the laser. The back-reflection can then be caught with an iris placed in front of the laser.
    \item Make sure the beam is at the same height across the table. This can be done with an iris and an IR card. 
    \item Take extra care for directing the beam through the center of all lenses and active optical components.
\end{itemize}

\subsection{Parts and bill-of-materials}
All custom metal pieces are parts of the CAD assembly of the microscope. Ours were manufactured from Aluminium stock in the university machine shop, but other materials are possible. Aluminium has the added benefit of anodization, which can help control stray light. For example, if the microscope was used in a Virtual Reality system, we would anodize the collection optics to reduce scattering from the projector's light.\newline
An overview of the microscope's cost is shown in Tab.~\ref{tab_costs}. Keep in mind that these prices can significantly change over time, while some products can become unobtainable and need to be replaced with a different or newer model.
%
\begin{table}
\begin{center}
  \begin{tabular}{ l c r } \hline
   \textbf{Item} & \textbf{Info} & \textbf{Cost} \\ \hline
\rowcolor{gray!20} 920 nm fs-pulsed Laser  & Spark Alcor 920 + Warranty & 90 k \\
                   ScanImage DAQ-System \& optimized PC & Vidrio & 20 k \\
\rowcolor{gray!20} Piezo collar & Physik Instrumente & 16 k	\\
            $2\times$ PMTs + preamplifiers  & Hamamatsu \& Thorlabs & 12 k \\
\rowcolor{gray!20} Pockels cell             & Conoptics &	11 k \\
                   Objective                & Nikon &  8 k \\
\rowcolor{gray!20} Machining custom parts   & Machine Shop; as per CAD files &  7 k \\
                   Optical filters          & AVR optics \& Semrock &  7 k \\
\rowcolor{gray!20} Lenses + optomechanics   & Thorlabs \& Newport &  7 k \\
                   Galvo-Resonant Scanner set & Novanta &  6 k \\
\rowcolor{gray!20} Electronics/cables/tools & Newark \& McMaster &  5 k \\
                   Mounting rack            & Emcor Enclosures &  3 k \\
\rowcolor{gray!20} Laser shutter            & Uniblitz/Vincent &  2 k \\
                   Laser safety goggles     & Edmund Optics &  1 k \\
\rowcolor{gray!20} Laser power meter        & Coherent &  1 k \\
                   Agarose \& fluorescent beads     & Thermofisher &  1 k \\
  \hline
 \textbf{Total}                    & & \textbf{197 k} \\
  \hline
  \end{tabular}
\end{center}
\caption{\textbf{Overview of the approximate cost in 2024-US\$} Note that this list excludes the optical table, and any other infrastructure costs such as compressors for air, and associated power supplies. This is just a summary. The detailed bill-of-materials is provided in the git repository.}\label{tab_costs}
\end{table}

\subsection{Structure and use of this document}
In the following sections, we will cover the setup and alignment of the microscope. This is split into three parts. The first part covers all components on the optical table that serve to condition the beam. The second part focuses on the  95 mm vertical post that holds the scanning mirror and scan lens assemblies. The third part is the microscope head with the attached collection optics. We will begin with the assembly on the optical table.\newline

Before building your own microscope, read these instructions fully. Check the CAD files, and make sure that the instructions make sense. This document follows closely our own alignment procedure, and we have done our best to be accurate. However, use common sense and do not follow these instructions blindly. Like all open instrumentation (under CC-BY-4.0), this work is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY, to the extent permitted by law; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.

\section{Assembly on the optical table}
%
\subsection{Beam conditioning}
An overview of the system for beam conditioning is shown in Fig.~\ref{sfig1} with key items labelled by capital letters. The following lines will cover the items, and their alignment.
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig1.jpg}
    \caption{{\bf Overall view of the beam conditioning path on the optical table.} Shown is a photograph of the components used to condition the beam for our microscope. Key components of the system are labelled with capital letters. The laser is shown as a red transparent line with intensity color coded. The beamsplitter cube (component D) splits the beam into two, halving its power. The Pockels cell (component G) reduces the power further. The reflections out of the Pockels cell and from the shutter (item J) are shown in yellow. The telescope (item K) magnifies the beam $\times 2$. All parts are explained in the text together with a note on their alignment.}
    \label{sfig1}
\end{figure}
%
\begin{enumerate}[]
    \item \textbf{A)} Laser beam coming out of the laser.

    \item \textbf{B)} Iris (SM1 Graduated Ring-Actuated Iris Diaphragm, SM1D12C, Thorlabs) inside a SM1-Threaded 30 mm cage plate (CP33, Thorlabs).

    \item \textbf{C)} $\diameter1\text{ in}$ mounted achromatic half-wave plate with SM1-threaded mount (AHWP10M-980, Thorlabs) inside a high-precision rotation mount (PRM1, Thorlabs). First, to check that the beam travels centrally through the half-wave plate, use an iris. Then place the half-wave plate at a slight angle to make sure that the beam reflected of the surface of the half-wave plate does not travel back into the laser. Confirm by using a detector card to find the (weak) back reflection. While doing this, terminate the beam traveling through the half-wave plate with a beam block.

    \item \textbf{D)} 10 mm polarizing beamsplitter cube (PBS103, Thorlabs) on a kinematic platform mount (KM100B, Thorlabs) held in place with a large adjustable clamping arm (PM4, Thorlabs). Arrows on the cube indicate which way the beam should go in and where the split beams travel. Similar to the half-wave plate, confirm that the reflection does not travel back to the laser using a detector card. Then adjust the kinematic mount to make sure that the transmitted and split beams travel parallel to the optical table. This is best checked with an iris far after the cube, and a detector card. Finally, adjust the angle on the half-wave plate such that transmitted and split beams have equal power. This has to be done at full-power mode of the laser. We used a Coherent FieldMaxII with a PM10 Thermopile power sensor.

    \item \textbf{E)} Beam block (hidden under the aluminium shield). This blocks the second beam which is not in use in our system (LB1, Thorlabs).

    \item \textbf{F)} $\diameter1\text{ inch}$ protected silver mirror (PF10-03-P01, Thorlabs) inside a kinematic mirror mount (KM100, Thorlabs): Reflects the beam.

    \item \textbf{G)} Pockels cell (350-80-LA-02 with 302RM driver, Conoptics) sitting on a holder (M102A, Conoptics). Properties of light travelling through this device are controlled electrically through the two connected wires. The alignment of the Pockels cell requires two steps: The Pockels cell has to be aligned with the optical axis of the laser, and be rotated relative to the laser's polarization such that the dynamic range is maximized \cite{Conoptics2018, Scientifica2024}. The first step can be done with an alignment tool of identical geometry to the Pockels cell (Conoptics modulator alignment tool 103). The second step requires the Pockels cell to be connected, and a power measurement performed. Importantly, these steps have to be done under full power because the beam profile in alignment mode might be slightly different from the full beam.
    \begin{itemize}
        \item First, install the holder on the table, and position on it the Conoptics Pockels cell alignment tool (Conoptics modulator alignment tool 103).
        \item Use a power meter on the output side, maximize power going through the central bore by manipulating the 4 bottom screws on the holder.
        \item Then switch the laser to full power and optimize the position of the screws for maximum transmission.
        \item Tighten the screws around the alignment tool, and mark on the screws the optical position. This will be important later to reproduce the exact same position of the alignment tool with the Pockels cell.
        \item Connect the Pockels cell (M350-80LA, Conoptics) to the driver as per the Conoptics instructions (p1m and p2m go to J1m and J2m, p1 and p2 go to the controller). The controller settings are shown in Fig.~\ref{sfig2}.
        %
        \begin{SCfigure}
            \includegraphics[width=.75\textwidth]{sfig2.jpg}
          \caption{{\bf Settings on the Pockels Cell controller.} Shown are the controls of the Pockels Cell driver as set in our system. For reference, see \cite{Conoptics2018}. We recommend for people building a microscope to take many such pictures of all settings and elements.}
          \label{sfig2}
        \end{SCfigure}
        %
        \item Next, determine the best orientation of the Pockels cell, by measuring the controller's voltage for different Pockels cell rotations. For each rotation of the Pockels cell, measure its transmission while turning the dial on the Conoptics controller from one end to the other. Iterate this for different orientations of the Pockels cell until an optimum is found. An example of different transmission curves is shown in the main manuscript, Fig. 9A. The optimal orientation allows to adjust the laser power in the widest range.
        \item The Pockels Cell splits the input beam into a transmitted and a rejected beam. The transmitted beam is used, while the energy of the rejected beam is dissipated in a beam block. By changing the control voltage of the Pockels Cell, the power ratio between the transmitted and rejected beam can be adjusted. The rejected beam leaves the Pockels cell through a bore at its side. During alignment, make sure that the rejected beam is properly terminated with a beam block.
        \item To validate the alignment, compute the extinction ratio of the Pockels cell, i.e. the ratio of maximal and minimal light transmission, and compare that number with the data sheet provided by Conoptics. Ours operate in a regime of $\approx 450$.
        \item Next, set the Pockels cell controller to the control voltage corresponding to minimum light transmission.
        \item Tighten the holder, and confirm that the Pockels cell is still well-aligned.
    \end{itemize}

    \item \textbf{H)} Two beam blocks (LB1, Thorlabs). Confirm that the right beam block terminates the waste beam leaving the Pockels cell. The left beam is used for calibrating the Pockels cell in ScanImage (the control software used by our microscope \cite{Vidrio2022, Pologruto2003}), together with a light sensor (I).

    \item \textbf{I)} Si Switchable Gain Detector, 350 - 1100 nm (PDA36A2, Thorlabs). This is used to measure the light transmission through the Pockels cell, by monitoring scattered light from the beam block (H), that comes from the shutter back reflection. Make sure that the gain on the detector is chosen reasonably for laser power and ambient light level. In our system, a gain of 50 dB works well. If the ambient room light is too bright, a SM1-mounted infrared long-pass filter in front of the photodiode can help (e.g. FELH0850, Thorlabs). The goal of setting the gain is well-defined sigmoidal control curve in ScanImage: Light transmission through the Pockels cell starts at a minimum, and increases as the Pockels control voltage increases.

    \item \textbf{J)} 6 mm Shutter (LS6S2ZM1, Vincent Associates) connected to driver (VCM-D1, Vincent Associates) for control of the shutter during imaging. To check that the shutter is properly aligned leave it open and make sure that the beam is not clipped. When closed, the back-reflection has to be terminated in a beam block. This back-reflection combined with a physically close detector (Items H and I above) is used to calibrate the Pockels cell in ScanImage (see below).

    \item \textbf{K)} $2\times$ Beam Expander ($2\times$ Achromatic Galilean Beam Expander, GBE02-B, Thorlabs, inside SM1RC, Thorlabs). This expands the beam sufficiently to fill the apertures of the subsequent optics. Aligning the beam expander requires two steps. First, it has to be aligned to the optical axis. Second, it is critical that the beam stays collimated after the beam expander. For the first alignment, we use two irises, one screwed in the front, and one (on a reasonably long SM1 extension tube) behind the expander. The beam expander has to be positioned such that the irises cut into the beam symmetrically. Then, the expander is on-axis. Next, we need to adjust the collimation of the beam so that the beam is the same size at the exit and after a long distance using several mirrors, see Fig.~\ref{sfig3}. For optimal alignment, adjust the dial on the beam expander until it no convergence or divergence is visible.
    %
    \begin{SCfigure}
        \includegraphics[width=.5\textwidth]{sfig3.jpg}
      \caption{{\bf Method for making sure the beam is collimated.} Using a set of mirrors, the beam (yellow line) can be reflected back and fourth to increase the distance travelled. Along this path (in this example of $\approx 2.5\text{ m}$), the beam must not change size ($<1\text{ mm}$). This is validated with an IR detection card and switching between the forward and return path of the beam. This method allows to control beam divergence after the $2\times$ telescope to below 1 mrad.}
      \label{sfig3}
    \end{SCfigure}
    %
\item \textbf{L)} Iris (SM1D12C inside CP08, both Thorlabs) Used to check alignment.

\item \textbf{M)} Mirror (PF10-03-P0, Thorlabs, inside KCB1) to reflect the beam up at a right angle. For the next steps (in particular finding the optimal scanning mirror position), it is important that the beam travels up perpendicular to the optical table, and parallel to the 95 mm optical rail column that holds the scanning mirrors (next section).

\end{enumerate} 
%
When finished aligning the beam through all the optical components listed above, clamp them down on the table securely. Then shield the beam path with additional SM1 and SM2 tubing to increase safety and to protect the aligned optical components.
%
\subsection{Assembly of the scanning post}

\subsubsection{Components}

Following beam conditioning on the optical table, the beam is reflected up from the optical table towards the ceiling into a box housing the scanning mirrors. This is shown in Fig.~\ref{sfig4}. Following the scanning mirrors, the beam travels up through the scan lens, and directed to the microscope head with another mirror.
%
\begin{figure}[h]
    \includegraphics[width=\textwidth]{sfig4.jpg}
    \caption{{\bf Overall view of the scanning post.} \textbf{A)} Side few. Key components of the system are labelled with capital letters. These are explained in the text together with a note on how to align these components. Importantly, the machined block (C) houses the scanning mirrors, and the scan lens assembly is placed in the SM2 house labelled (E). \textbf{B)} Frontal view. The PMT preamplifiers (component G) and the scanning mirror power supply (component H) are visible.}
    \label{sfig4}
\end{figure}
%
%
\begin{enumerate}[]
    \item \textbf{A)} Mirror (BPF10-03-P0, inside KCB1, with CP12 attached) - turn the beam at a right angle.
    \item \textbf{B)} Broadband filter (WG11010-B, Thorlabs, inside SM1L20 and SM1S20) - filter to keep dust out of the box housing the scanning mirrors.
    \item \textbf{C)} An aluminium box containing the resonant and slow galvanometer set (CRS8K/6215H Galvo Set, Novanta), mounted to 95 mm rail (XT95RC4, Thorlabs). A detailed description is provided below.
    \item \textbf{D)} Empty tubing.
    \item \textbf{E)} Scan lens - See detailed description below.
    \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs). While we used a round 2 inch mirror, this should be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs). This increases the field-of-view because the cross-section of an ellipse at 45 degrees is a circle. At low magnification, a round mirror will lead to vignetting.
    \item \textbf{G)} PMT preamplifier (TIA60, Thorlabs) attached to a 95 mm rail.
    \item \textbf{H)} Power supply for the scanning mirrors (part of the Novanta scanning mirror set) housed in an electronics prototype box.
\end{enumerate}

\subsubsection{Alignment}

\begin{itemize}
    \item First, mount the 95 mm rail to the table. Then attach a bracket to the side to hold the scan lens (component D in Fig.~\ref{sfig3}), and one on top with a cage system to hold a mirror (component F in Fig.~\ref{sfig3}). For alignment with cage systems, we use a cage system alignment plate (VRC4CPT, Thorlabs). The rest of the assembly here will be done without any lenses. The goal is a well-aligned beam that travels through the middle of all parts, and parallel to the optomechanical surfaces.
    \item The box housing the scanning mirrors is connected, trough SM1 tubing, to a mirror (component A in Fig.~\ref{sfig3}). To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}) facing up. These two pieces meet in the air. Sliding a finger across the small gap between the two pieces makes misalignment easy to notice haptically. Mount the box housing the scanning mirrors such that you can not feel the transition from the lower SM1 tubing to the upper SM1 tubing.
    \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}) so that light travels through the center of the scanning mirrors and up the 95 mm rail. This is done with irises. One is attached at the entry port of the scanning mirror box, e.g. in the SM1 tube (component B in Fig.~\ref{sfig4}). Another two irises are attached, as far away as possible, to a 95 mm rail bracket. It is convenient to use the future holder of the scan lens (component D/E in Fig.~\ref{sfig4}). This ensures that the beam will pass through the center of the scan lens. As the mirror (component F in Fig.~\ref{sfig4}) is not installed yet, an IR detection card can conveniently be taped to the ceiling to make sure that the beam is on-axis. Of note, the resonant scanner is at its origin point when no power is being provided, but the slow galvanometer needs to be provided 0 Volt to position the mirror at its origin point. This can be done through the voltage supply, or to a good approximation through ScanImage by setting the scan mode to the highest possible zoom level. In our microscope design, it can be helpful to wiggle the lid to which the scanning mirrors are mounted (item C in Fig.~\ref{sfig4}). This step is tricky and can require some patience. 
    \item When confirmed that the light travels parallel to the 95 mm rail, we attach the mirror (component F in Fig.~\ref{sfig4}), and slide it along the cage rods to a position where the beam is reflected centrally through the caging system and the mount positioned on top of the 95 mm rail. This is done using the same set of two SM2-mounted irises that we used to make sure that light leaves the scanning mirror box without x or y displacement. The beam is now ready to travel through the microscope head.
\end{itemize}

\subsection{Assembly of the microscope head}
%
A picture is shown in Fig.~\ref{sfig5}.
\subsubsection{Components}
%
\begin{figure}[t!]
    \includegraphics[width=\textwidth]{sfig5.jpg}
    \caption{{\bf Overall view of the microscope head.} Key components of the system are labelled with capital letters. These are explained in the text together with a note on how to align these components.}
    \label{sfig5}
\end{figure}
%
\begin{enumerate}[]
    \item \textbf{A)} Empty tube, shielding the bream aligned in the previous section.
    \item \textbf{B)} Protected silver Mirror (PF30-03-P01, Thorlabs) inside KS3 and clamped down with XE25CL2 and another clamp. This mirror directs the beam through the tube lens. We will refer to this part as ``big mirror''. This is the first mirror that we will have to align.
    \item \textbf{C)} Tube lens - See detailed description below.
    \item \textbf{D)} Empty, just a tube used for spacing because the distance between the scan lens, tube lens, and objective is important.
    \item \textbf{E)} Tube holder (LCP01, Thorlabs) - just there to hold the lens straight, use with ER series 6 mm rods (ER6-P4, Thorlabs).
    \item \textbf{F)} Elliptical mirror (PFE20-P01 inside KCB2EC, both Thorlabs). We will refer to this part as ``collection mirror''. This is the second mirror that we will align.
\end{enumerate}
%
%
\subsubsection{Setup and alignment}

\begin{itemize}
    \item Mount the two 95 mm posts to the table.
    \item Mount the collection optics box to the Aluminium stage, and then mount the stage to the 95 mm rail. Do not install the photomultiplier tubes yet. These devices are light sensitive, and more alignment needs to be done before we are ready to install them.
    \item Equip the Aluminium stage with brackets and cage mounts to hold SM2 tubing (A, D and E in Fig.~\ref{sfig5}).
    \item First, we position the big mirror at a $45^\circ$ angle (component B in Fig.~\ref{sfig5}). Place two irises after the big mirror, one at the future position of the tube lens (component C in Fig.~\ref{sfig5}) and one far away beyond the future position of the collection mirror (component F in Fig.~\ref{sfig5}). Aligning the big mirror is fiddly, but can be achieved with small adjustments of its position in x and y, and the tilt of its housing. We found it helpful to use a 45 degree angled rod to guide the mirror in the direction parallel to its surface. Whichever method is used, this step can take some time. Importantly, do not adjust the set screws of the mirror on the scanning post (component F in Fig.~\ref{sfig4}) because that is already aligned.
    \item Install the collection mirror (component F in Fig.~\ref{sfig5}). Then position an iris in place of the future objective, and one as far away as possible just above the optical table. Shift the mirror along the rail and adjust its tilt via the set screws so that the beam is aligned with the two irises.
\end{itemize}

\subsubsection{Scan and tube lens alignment}

After the beam's alignment is confirmed by traveling through the two irises, it is time to install, and align scan and tube lens. Remember that (1) the distance between the tube lens (component C in Fig.~\ref{sfig5}) and scan lens (component G in Fig.~\ref{sfig5}) has to be 100 mm + 375 mm = 475 mm while (2) the scanning mirror set (component H in Fig.~\ref{sfig5}) has to be positioned in the focal plane of the scan lens, while (3) the objective back aperture is positioned in the focal plane of the tube lens (see Fig. 1 in the main manuscript). In our design, the objective is fixed. Therefore we have to perform the lens alignment in several steps, conceptually beginning at the back-aperture of the objective.

\begin{itemize}
    \item Before starting, make sure the lens groups in the tube and scan lens assembly are mounted correctly. Specifically, when inserted into one of our previously aligned SM2 mounting rings, they should focus the beam, but must not incur a lateral or angular displacement. To test this, one can screw them into component E in Fig.~\ref{sfig4}, and observe the beam far away on a wall. The lens groups must not change the position of this spot, only its size. Only proceed if the lens groups were assembled and mounted correctly.
    \item The first lens group to be installed is the tube lens assembly. Position the tube lens such that the beam, at maximum zoom level, is focused at the back-aperture plane of the objective. As the objective is not installed yet, an IR detection card can be placed at its future location. We designed the microscope such that the tube lens assembly is to be mounted on a 1 inch long SM2 extension to the cage plates (Component D in Fig.~\ref{sfig5}. See also the diagram in the section on ``Tube lens Assembly'' below). Observe how the focal plane changes when moving the tube lens along the optical rails (component E in Fig.~\ref{sfig4}). When its correct position is confirmed, tighten the set screws on the optical cage.
    \item Next, install the scan lens above the scanning mirror box. The spacing between tube lens and scan lens is critical because the beam leaving the tube lens has to be collimated. To test this, remove the elliptical mirror (component F in Fig.~\ref{sfig4}) from its housing, and observe the spot on a wall far away, while moving the scan lens up and down on the 95 mm optical rail. Find a position at which the beam neither converges, nor diverges after the tube lens, and the spot on the wall has the same size as the beam right after the tube lens. Only then is the beam well collimated. Clamp down the scan lens on its rail.
    \item Next, reinstall the elliptical mirror (component F in Fig.~\ref{sfig4}), and observe the back-aperture of the objective, while moving the scanning mirror box up and down. The scan mirrors have to be positioned in so that they are conjugated to the back aperture of the objective. It is positioned correctly when the well-collimated light converges on the back aperture of the objective across scan angles. Make sure that (1) no beam clipping is visible on high zoom along the optical path. (2) In the conjugated plane of the scan lens, a nice and crisp plane should be visible on an IR card, produced by the scanning beams focused down to a point. (3) The fast resonant scan combined with the slow scan gives the beam a visible dynamic, a ``wobble''. If the scanning mirror box is positioned correctly, then, the beam at the objective back aperture will not translate while scanning because all deflection angles converge on the back aperture (cf. Fig. 1 in the main manuscript). In other words, the ``wobble'' becomes minimal at the plane conjugated to the scan mirrors. Notice how adjustment of the scan mirrors relative to the scan lens can bring this conjugate plane to any point below the collection optics. Now, adjust the height of the scanning mirror box to a point so that the minimal-wobble plane is located at the back aperture of the objective and clamp down the scanning mirror box. For a useful illustration of this method, see also \cite{Yao2023}. Of note, this step of fine-tuning the position of the scan box up and down along the 95 mm optical rail is the reason why we stressed the importance of the alignment of the scanning post, the components A in Fig.~\ref{sfig3} and M in Fig.~\ref{sfig1} earlier. It was critical that across the various heights used here, the scanning mirror box was precisely aligned with the beam.
    \item Shield the beam with more SM1 and SM2 tubing to protect the beam from misalignment, the optics from dust, and the user from accidentally exposing themselves to the beam.
\end{itemize}
%
\subsection{Installing objective and photomultiplier tubes}
%
\subsubsection{Components}
%
\begin{SCfigure}
    \includegraphics[width=.5\textwidth]{sfig6.jpg}
  \caption{{\bf Side view of the microscope head.} Key components of the system are labelled with capital letters. These are explained in the text together with a note on how to align these components.\newline
  Set up like this, we were measuring the amount of light traveling through the system. Note the detector taped to the objective with green tape.\newline
  Also note that the photomultiplier tubes (component C) are light sensitive and need to be installed in the dark. We recommend to switch off the room lights when handling them, and allowing your eyes to adapt to the dark over several minutes. After installation into the collection optics, the lights can safely be used. The objective is easy to install, and just screwed into the piezoelectric collar, component F.}
  \label{sfig6}
\end{SCfigure}
%
The optics and optomechanics are now essentially in working order. The last missing steps towards a working microscope are the installation of the objective, and the photomultiplier tubes. These elements are visible in a side view of the microscope head, see Fig.~\ref{sfig6}.
%
\begin{enumerate}[]
    \item \textbf{A)} Adjustable lens tube (SM2V05, Thorlabs), made flush with the collection box to stop room light entering the optics. Otherwise this will increase the background signal during use of the microscope. 
    \item \textbf{B)} Aluminium box housing the collection optics - See detailed description below.
    \item \textbf{C)} Two photomultiplier tubes (``PMTs'', Hamamatsu H16201-40). Their shielded output cable (black) and the control and power supply cables (color-coded wire) are also visible.
    \item \textbf{D)} PMT Transimpedance Amplifier (Thorlabs TIA60) - amplifier for the PMTs. Set the output offset on the PMT amplifier such that no signal equals 0 V. The amplifiers are directly connected to the PMT output on the input and ScanImage on the output.
    \item \textbf{E)} Control signals and power supply for the PMTs going to the custom PMT control box.
    \item \textbf{F)} Piezoelectric objective collar (P-725K085: PIFOC(R) 400 \textmu m travel, Physik Instrumente).
    \item \textbf{G)} The microscope's objective (Nikon N16XLWD-PF, Thorlabs).
\end{enumerate}
%
\subsubsection{Objective installation}
Before installing the objective, double check that the beam is collimated below the piezoelectric collar, and on-axis. To do so set the ScanImage zoom level to high and with the use of two irises confirm that the beam is not clipped. Then screw the objective into the collar.

\subsubsection{PMT installation}
PMTs are light sensitive. Always store them with their aperture covered with black tape when not in use. When removing the tape for installation, this installation into the collection box must be done in darkness and as quickly as possible. We recommend to use black silicone putty (V-tie self setting silicone rubber), and have it ready for use to seal the gap between the PMTs and the aluminium box. Switch the room lights off, wait a few minutes to adapt to the darkness then mount the PMTs on their respective ports.

\subsection{Shield the light path}
Now that your microscope is ready, finish shielding the light path with SM1 and SM2 tubing, and cover the optical table with sheet metal. We use bent Aluminium sheet, placed on small columns made from T-slotted rail.

\section{Last steps}
%
\subsection{No signal?}
If no picture is visible, check:
\begin{itemize}
    \item Is a fluorescent sample under the objective? A bright simple will be useful, such as a fluorescent plastic slide (FSK5, Thorlabs). Is the sample positioned in a suitable distance from the objective? Note that the focal plane is only a few \textmu m wide. If no fluorescence is produced in this optical slice, no signal will be visible in ScanImage.
    \item If the objective requires water immersion, has a drop of water been placed between the sample and the objective.
    \item Are all beam blocks removed from the path? Check with IR cards along the way. Below the objective, the IR light should be focused to a tight spot.
    \item Are the PMTs operating as intended? This can be checked with a light-source like a flashlight close to the objective. This should noticeably increase the noise in the picture.
\end{itemize}
%
\subsection{Validation and tuning}
%
Validation and tuning is done in several steps.
\begin{itemize}
    \item The first sample to image should be a fluorescent plastic slide (FSK5, Thorlabs). These are bright and uniform. It can be helpful to scratch the surface of the slide to find a feature to focus on. With this sample, the group delay dispersion can be adjusted for maximum signal. It should also validate that the field-of-view is as intended, and no obstructions exist in the beam path.
    \item Next, image a calibrated scale to validate the microscope's magnification. We used a reference slide featuring a 100 \textmu m grid (Thorlabs R1L3S3). This slide was covered with a drop of Fluorescein solution in water and a standard coverslip. Find the calibration grid, and compute the magnification in \textmu m/pixel. It should be approximately equal in x and y direction. Our microscope has sufficiently small field curvature that despite the thin film of dye, the entire grid should be visible. An example is shown in Fig.~\ref{sfig7}A.
    \item Next, measure (at very low laser power to not saturate the PMTs) the two photon intensity from a uniform bath of Fluorescein, see Fig.~\ref{sfig7}B. This measures field flatness. Alignment problems either in the excitation or collection path will make this image less uniform. Of note, small alignment errors in particular of the scan lens can have a major effect on field flatness. If your field is not as uniform as the example shown, we recommend to check the scan lens first.
    \item Finally, use a fluorescent bead sample to measure the microscope's point spread function (PSF), see Fig.~\ref{sfig7}C. This will reveal more subtle misalignments or aberrations in the optics. We use a mix of 5000:1 100 nm fluorescent beads (``Dragon Green'' 480/520 from Bangs Laboratories) in in 1\% Agarose. To prepare this sample, take the beads from the fridge, vortex the container, take the 10 \textmu l and 49.5 g of water. Then microwave the mix with 0.5 g of Agarose until the solution is clear. While warm, place a drop on a microscope slide, and cover with a coverslip. Bring your sample to the microscope, and record a z-stack. Use low laser power to not damage the bead, or saturate the PMTs. The example shown was recorded with 5\% laser power at 99.9 zoom for 40 z-slices with 0.5 \textmu m spacing. The PSF profile should be symmetric, and a faint, but also symmetric, Airy ring visible around the bead, around 5 \textmu m away from center of the bead (see Fig. 2D in the main manuscript).
\end{itemize}
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig7.jpg}
    \caption{{\bf Three key validation samples.} \textbf{A)} Image of a reference slide with a 100 \textmu m grid to measure the microscope's magnification. Note how the entire grid is in focus, suggesting small field curvature. \textbf{B)} Two photon intensity from a uniform bath of Fluorescein. This shows that the microscope can effectively elicit and collect fluorescence across the field of view. \textbf{C)} A volumetric image of fluorescent beads in Agarose. This is used to compute the axial and radial width of the microscope's point spread function. Use low laser powers for these measurements to not saturate the PMTs and to produce correct results.}
    \label{sfig7}
\end{figure}
%
%
\section{Assembly of subcomponents}
In the remaining sections, we will cover the microscope's sub-assemblies and their construction, beginning with the lens groups.
%
\subsection{Tube lens assembly}
The tube lens assembly is made of two cemented doublets $2\times$ ACT508-750-B (Thorlabs), see Fig.~\ref{sfig8}A. The letter ``B'' signifies that these lenses have an anti-reflective coating in the IR range. For assembly, the lenses are placed on a lens assembly tool, and a SM2 housing is lowered above them, for an example see Fig.~\ref{sfig8}B. This methods has to be used for the lenses to be seated correctly. The individual steps for the tube lens group are as follows:

\begin{itemize}
    \item Place the first element on top of the spanner wrench (Thorlabs SPW604) using lens paper. Check the lens thoroughly. Dust can be blown away with a duster, finger prints wiped off with Methanol and a lens cleaning tissue (cf. Fig.~\ref{sfig8}B).
    \item Blow it with the air duster. 
    \item Slide the SM2L10 tube over the element until it sits in the end. Sometimes it needs to be wiggled, but do not force it.
    \item Flip the whole thing over.
    \item Now the element is in the tube. Tighten it with a SM2 retaining ring.
    \item Insert a second SM2 retaining ring for spacing. 
    \item Repeat the previous steps to install the second lens above the SM2 retaining ring
    \item Flip again, blow with air, and set the lens in place with a third SM2 retaining ring. This produces the configuration shown in Fig.~\ref{sfig8}A.
    \item Be careful with dust and fingerprints when putting elements into the tube. Confirm that there are no fingerprints, and no dust particles trapped on or between the lenses.
\end{itemize}
%
Our simulations indicate that the lens spacing between the two doublets is not critical, and the approximate clearance provided by two SM2 spacer rings is sufficient. This is shown in Fig.~\ref{sfig8}A. For more precise placement, a spacer ring like the one shown in Fig.~\ref{sfig8}B can be used. This will be important for the slightly more complex scan lens assembly described in the next section.
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig8.jpg}
    \caption{{\bf Assembly of lens groups.} \textbf{A)} Tube lens assembly with the two doublets held in place with spacer rings. \textbf{B)} Assembly method of lenses: Lenses and spacer rings are stacked on a SM2 spanner, ready for the SM2 tubing to be lowered around them. \textbf{C)} Design of the scan lens assembly. Notice the custom spacer rings in blue. The distance between the last element of the scan lens assembly and the scanning mirror box is $\approx 1.35 \text{ inches}$. \textbf{D)} The assembled scan lens group in its SM2 housing.}
    \label{sfig8}
\end{figure}
%
\subsection{Scan lens assembly}

\begin{itemize}
    \item Place the KPC070AR, a plano-concave lens, on the spanner wrench with the plane side facing out. Check the lens thoroughly for dust and finger prints.
    \item Slide the SM2 tube over the elements until they sit at the end of the tube. Sometimes it needs to be wiggled, to make sure the lenses are seated properly.
    \item Flip the whole thing over.
    \item Tighten it with a SM2 retaining ring.
    \item Next, place the LB1199-B lens on the wrench. This is a bi-convex lens for which the orientation is irrelevant. Flip over the assembly, and tighten the lens with a second SM2 retaining ring. 
    \item For the third and fourth lens, place an ACT508-200-B lens, a spacer ring, the second ACT508-200-B lens, and two spacer rings on the wrench. Make sure you remove all dust from the various surfaces. Flip over the assembly, and tighten the lens with a third SM2 retaining ring. 
    \item Check the assembly for trapped dust or fingerprints. This will produce a lens group like the one shown in Fig.~\ref{sfig8}D.
\end{itemize}

\subsection{Assembly of the collection optics}
%
The collection optics are made from several components, including optical filters, lenses, and custom metal pieces. Fig.~\ref{sfig9}A shows a cut through the CAD drawing. The function is described in the main manuscript. A pictures of the collection optics box is shown in Fig.~\ref{sfig9}B with key components labelled. Here, we will focus on the assembly and their alignment.
%
\begin{figure}[h]
    \includegraphics[width=\textwidth]{sfig9.jpg}
    \caption{{\bf Assembly of the collection optics.} \textbf{A)} The assembled collection optics with bottom cover removed, perspective from below. \textbf{B)} The collection optics during the assembly process, similar to panel A. Key components are labelled (see text).}
    \label{sfig9}
\end{figure}
%
\begin{enumerate}[]
    \item \textbf{A)} The construction of the collection optics box starts with a side panel attached to the base with stainless steel button head hex screws, 8-32 thread size, 1/2 inch long.
    \item \textbf{B)} Next, we attach the front panel. This is connected  with stainless steel Phillips flat head screws, 82 degree countersink angle, 4-40 Thread, 1/8 in long and undercut.
    \item \textbf{C)} Then we install the first lens, a LA1384-A plano-convex lens (Thorlabs), see also Fig.~\ref{sfig8}A. The flat side of the lens sits against the lip inside of its Aluminium holder. The convex side points towards the PMTs. The lens is glued in place with three dots of Epoxy (because 3 points make a plane, and 4 can bend the lens). When gluing, make sure to dab the glue on and pull AWAY from the center of the mirror. That way any glue strands do not fall onto the mirror. When the glue has set, the holder is screwed into the wall. 
    \item \textbf{D)} The next lens to be installed is a biconvex lens (LB1607-A, Thorlabs). This lens is symmetric, so can be oriented in any way. It is also epoxied on three spots and the holder screwed into the wall, see Fig.~\ref{sfig9}A.
    \item \textbf{E)} Next, we glue the first dichroic mirror to its holder. This dichroic mirror separates IR light from fluorescence (FF665-Di02-40X55, AVR Optics). Its orientation is important. The caret points TOWARDS the metal piece. The filter is then glued in place with three dots of Epoxy, and the triangular holder screwed into the wall.
    \item \textbf{F)} Next, we fix the condenser lenses (ACL25416U-A, Thorlabs) in their housing plates. The convex part is facing towards the inside of the box, and set with nylon set screws (Stainless Steel Nylon-Tip Set Screw, 4-40 Thread, 1/8 inch long). The holders are then fixed together with Stainless Steel Socket Head Screw, 8-32 Thread Size, 3/8 inch long.
    \item \textbf{G)} With the condensers in place, we can install the optical band-pass filters in front of them. First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread, 1/8in long). Orientation is important: The arrow is facing outwards, i.e. away from the inside of the box and towards the PMT along the light path.
    \item \textbf{H)} Next we install the 600 nm band-pass filter for the red channel (Semrock Brightline FF01-600/52-32, AVR Optics). Like the 525 nm filter, it is secured with nylon set screws and the arrow points away from the inside of the box and towards the PMT.
    \item \textbf{I)} Next, we attach the dichroic mirror that splits red and green light (Semrock Brightline FF562-Di03-40X52, AVR Optics) to its metal holder. The caret points towards the metal holder, such that the side the caret is pointing to contacts the metal when it is glued in place. When the glue has set, the mirror casing is screwed in place using stainless steel socket head screw, 4-40 Thread Size, 5/16 inches long.
    \item \textbf{J)} The piece containing the 525 nm and 600 nm band-pass filters and the dichroic mirror is connected to the larger metal box with stainless steel socket head screw, 4-40 Thread Size, 3/4 inches long.
    \item \textbf{K)} The bottom piece (bottom per the view of the picture in Fig.~\ref{sfig9}B) of the PMT box is attached using 4-40, undercut, 3/16 inch screws.
    \item \textbf{L)} PMT plate. The PMT attaches to the FLAT side of the PMT plates. The other side has a shallow cut out for the screw head to sit. The plate with the PMT attached screws into the rest of the assembly using 4-40 5/16 inch, socket cap screws.
    \item \textbf{M)} Next, we install an IR block filter (Semrock BrightLine Multiphoton Filter FF01-680/SP-50, AVR Optics). This filter is sandwiched between two rings (SM2RR).
    \item \textbf{N)} Then we close the second panel with 8/32, 1/2 inch, socket cap screws.
    \item \textbf{O)} The piezoelectric holder is attached to the aluminium part using the adapter that comes with it. Do not damage the Serial cable.
    \item \textbf{P)} The lid is attached using 8/32, 3/8 inch, undercut screws. Finish off by securing the rest of the front plate screws (component B) using 4-40 thread, 1/8 inch screws. Screw in the piece holding M to the lid using 4-40, 1/2 inch, socket cap screws.
    \item \textbf{Q)} Attach the top cover using 4-40, undercut, 3/16 inch screws.
\end{enumerate}
%
\subsection{Assembly of the scanning mirror housing}
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig10.jpg}
    \caption{{\bf The scanning mirror box.} \textbf{A)} The custom aluminium box housing the pair of scanning mirrors. \textbf{B)} Close-up of the same box with key parts labelled: A: Two broadband windows (WG11010-B, Thorlabs) to keep dust out. B: Attachment of the box to the 95 mm optical rail. C: An Iris used for alignment, and D: SM1 tubing. \textbf{C)} Bottom part of the aluminium box. A: The windows, and B: screws to attach the box to the drop-on rail carriage via four 0.75 inch tall 1 inch diameter posts. \textbf{D)} The scanning mirrors are mounted to the lid using heat transfer compound. E: Anodized aluminium block holding the scanning mirrors. F: One of the scanning mirror assemblies, G: The aluminium lid and H: The scanning mirrors. \textbf{E)} Same as \textbf{D} but different angle. \textbf{F)} Same as \textbf{E} but different angle. I: Cables controlling the scanning mirrors.}
    \label{sfig10}
\end{figure}
%
The scanning mirror housing is a machined piece of aluminium holding the Novanta scanning mirror set against the 95 mm optical rail, see Fig.~\ref{sfig10}. It also shields the scanning mirrors from dust in the environment, and protects the environment from audible noise produced by the scanning mirrors. The housing is composed of a box, mounted to the 95 mm rail (Fig.~\ref{sfig10}A), and a lid to which the Novanta scanners are mounted (Fig.~\ref{sfig10}B,C). When mounting the black anodized holder, make sure to apply heat transfer compound between the holder and the lid (we use Wakefield Thermal Joint Compound Type 120-5 Silicone). While the resonant scanner does not dissipate much heat, the slow galvanometer becomes warm in normal operation, and this heat needs to be dissipated. This is particularly important when pushing to fast responses, and driving the slow galvanometer with larger currents.\newline
After receiving the scanning mirrors, they need to be installed in the black anodized Aluminium block. Make sure to put the resonant scanner in first (the piece sitting at an angle) before the slow galvanometer (the piece sitting parallel to the mount). Both pieces should have stops that keep you from pushing them into the mount too far.\\
The box has two windows that are SM1 threaded. Position the dust filters (WG11010-B, Thorlabs) in these bores with appropriate retaining rings. We used a SM1 to SM2 converter ring at the exit, Fig.~\ref{sfig10}B, only because we had that part available from an earlier project.

\subsection{Scanning mirror power supply}
%
The scanning mirrors come with driver circuit boards. We place them in a prototype box, and connect the driver board's power supply and signal lines to connectors, see Fig.~\ref{sfig11}A. The power connectors accept banana plugs. The signals are connected to BNC connectors. The other key parts are as follows.
%
\begin{figure}[t]
    \includegraphics[width=\textwidth]{sfig11.jpg}
  \caption{{\bf Scanner electronics.} \textbf{A)} Overview of all scanning mirror parts. Key parts are labelled with capital letters. Optomechanics were covered in Fig.~\ref{sfig10}. All electrical drivers were placed in the yellow circuit box. \textbf{B)} Power supply and connection of the scanning mirrors with key parts labelled by capital letters. The inset shows the scanning mirror driver boards provided by Novanta and mounted in the yellow circuit box. The smaller driver circuit (blue) powers the resonant scanner. The larger circuit board (green) drives the slow galvanometer. The circuit boards are mounted to the Aluminium walls with screws and heat transfer compound.}
  \label{sfig11}
\end{figure}
%
Fig.~\ref{sfig11}A shows as the housing box (component A) and xy scanning mirror set (component B) that we discussed above. Components C are the cables connecting the scanning mirrors to their driver boards. These driver boards are housed in a yellow prototype box, and connected to accept power (component D), and signals (component F). Fig.~\ref{sfig11}B shows the power supply of the scanning mirrors. The slow galvanometer needs a $\pm 28\text{ V}$ supply. This is provided through the three black/white/red cables (-28 V, 0 V, +28 V) from the right power supply. The second power supply to the left provides 12 V for the resonant scanner. The supplies are connected to the power supply ports on the prototype box, and the signal lines are connected to the Vidrio DAQ system. Key components in the figure are labelled with capital letters. These are as follows:
\begin{itemize}
    \item \textbf{A)} Power supply (GPD-3303D, Gw Instek) with two channels, both set to 28 V.
    \item \textbf{B)} Have CH 1 turned on.
    \item \textbf{C)} Press the ``Ser/Indep'' button. This wires the two channels together to a shared references to provide the $\pm 28\text{ V}$ and the 0 V reference line.
    \item \textbf{D)} This enables our power supply unit. Only when pressed, power is sourced to the galvanometer driver board.
    \item \textbf{E)} CC/CV indicator light. Make sure that the device is set to CV (constant voltage).
    \item \textbf{F)} The -28 V output line (black). This is connected to the -28 V line on the electronics box (shown below).
    \item \textbf{G)} The reference lines, 0 V (white) connected to the 0 V line on the electronics box.
    \item \textbf{H)} Connects the reference line to ground.
    \item \textbf{I)} The +28 V output line (red) connected to the +28 V line on the electronics box.
    \item \textbf{J)} Power supply (E3630A, Keysight) set to 12 V to power the resonant scanners.
    \item \textbf{K)} Black channel is the references, and connected to black port on the controller box.
    \item \textbf{L)} Red channel, set to +12 V, is connected to the red port on the controller box.
    \item \textbf{M)} Coaxial connector controlling ``Zoom'' (the resonant scanners's amplitude).
    \item \textbf{N)} Coaxial connector for ``Sync'' (the resonant galvanometer's digital synchronization signal)
    \item \textbf{O)} Coaxial connector for controlling the slow galvanometer.
\end{itemize}
Make sure the power generator settings are correct before plugging in the scanning mirrors. Check this with a good multimeter and do not just trust the display. Of further note, the scanning mirror driver boards cannot be mixed and matched. Every board has a unique ID that is matched to the scanner. Double check that they are connected correctly before powering up.

\subsection{Assembly of PMT control circuits}
The last part to be assembled is the control circuitry for the photomultiplier tubes. This is shown in Fig.~\ref{sfig12}. The circuit is shown and explained in the main manuscript. Here, we will cover the assembly. In short, the circuit allows a user to set the gain of the H16201P-40 photomultiplier tube module with a potentiometer \cite{Hamamatsu2024}, while displaying the control voltage on a small digital panel meter (Murata DMS-20PC). The supply of this circuit is a well regulated +15 V supply that also powers the PMTs. The panel meter needs a +5 V supply that we obtain from the +15 V via a voltage divider. The PMT is supplied directly with the +15 V. It also sources a signal through the blue cable that is connected to ground via a voltage divider, using a potentiometer. This voltage divider produces the control voltage that is fed back to the module via the white input line, and used for display on the panel meter. Due to the simplicity of this circuit, we do not solder this on a circuit board, but rather in a prototype development box directly, see Fig.~\ref{sfig11}A,B, which is attached to the rig.
%
\begin{figure}[t]
    \includegraphics[width=\textwidth]{sfig12.jpg}
  \caption{{\bf Custom electronics.} \textbf{A)} Picture of the control box. Component A are the displays for the control voltage for red and green channels. Component B are the two potentiometers to set the two channel gains. \textbf{B)} Inside view of the potentiometer box with key components labelled (see text). \textbf{C)} Connector attached to the controller box before plugging into the PMTs. \textbf{D)} Connector from the Control box to the PMT cables. \textbf{E)} Outputs of the PMTs. Note the four color-coded American wire gauge \#28 cables, and the coaxial signal line\cite{Hamamatsu2024}.}
  \label{sfig12}
\end{figure}
%
The first components to be wired up are the Murata DMS-20PC displays. The circuit diagram is shown in the main manuscript \textcolor{red}{Fig. 4}.
\begin{itemize}
    \item Solder pins 7 and 8 together on each of the two displays. The displays are component \textbf{A} in Fig.~\ref{sfig12}A,B.
    \item Solder 2.5 inch long, and 5 inch long pieces of wires to pin 12 on the top display.
    \item Solder the other end of the 2.5 inch piece of wire and a new 1 inch piece of wire to pin 3 (+5 V return).
    \item Solder the other end of the 1 inch piece of wire and a 1.5 inch and 3 inch pieces to display pin 6 (DP1).
    \item Solder the other end of the 1.5 inch piece and another 1 inch piece to pin 3 (+5 V return) of the bottom display.
    \item Solder the other end of the 1 inch piece and a new 2 inch piece to pin 6 (DP1) of the bottom display.
    \item Solder the other end of the 2 inch piece to pin 12 (input lo) of the bottom display.
    \item Solder the other end of the 3 inch piece from pin 6 (DP1) of the top display and a new 12 inch piece of wire to the middle pin of the left potentiometer.
    \item Solder a 12 inch piece of wire to pin 3 (closest to the knob) on the left potentiometer (50 kOhm, 3590S-1-503L, Bourns). These are the two big blue parts, component \textbf{B}, in Fig.~\ref{sfig12}A,B.
    \item Solder a 12 inch piece of wire and 5 inch piece of wire to pin 11 (input hi) on the top display.
    \item Solder the other end of the 5 inch piece of wire to pin 1 (furthest from the knob) on the left potentiometer.
    \item Solder a 5 inch piece of wire to pin 1 and pin 2 (+5 V supply) of the top display.
    \item Solder the other end of the 5 inch piece of wire to the middle pin on the side opposite to where it says ON/ON on the switch.
    \item Solder a 12 inch piece of wire and 5 inch piece of wire to pin 11 (input hi) on the bottom display.
    \item Solder the other side of the 5 inch piece of wire to pin 1 (further from the knob) on the right potentiometer.
    \item Solder a 12 inch piece of wire to pin 3 (closest to the knob) on the right potentiometer.
    \item Solder a 12 inch piece of wire and the other end of the wire connected to pin 12 of the top display to pin 2 (middle pin) on the right potentiometer.
    \item Solder a 6 inch piece of wire to the middle pin on the side adjacent to where it says ON/ON on the switch (component \textbf{C}).
    \item Solder a 3 inch piece of wire to the left pin (left with the words being oriented the correct direction) on the side adjacent to where it says ON/ON on the switch.
    \item Solder the other end of the 3 inch piece of wire and a 12 inch piece of wire to the left pin (left with words being oriented the correct direction) of the second switch on the side opposite to ON/ON words.
    \item Solder a 12 inch piece of wire to middle pin on the second switch on the side opposite to the ON/ON words.
    \item Solder a 6 inch piece of wire to left pin on the potentiometer used for the  +5 V supply of the display (component \textbf{D}).
    \item Solder a 6 inch piece of wire to right pin on the same potentiometer.
    \item Solder a 4 inch piece of wire to center pin on the same potentiometer. 
    \item Connect the left and right pins to the banana plugs and set the potentiometer to 5V going across BEFORE connecting the middle wire to the rest of the controller circuit! 
    \item Solder the other end of the 4 inch wire and another 4 inch piece of wire to the middle pin on the second switch on the side adjacent to the ON/ON words.
    \item Solder the other end of the 4 inch piece of wire to the right pin (right with words being oriented in the correct direction) on the side opposite to the ON/ON words on the first switch.
    \item Solder a 5 inch piece of wire to the right pin (right with words being oriented the correct direction) on the side adjacent to where it says ON/ON on the second switch.
    \item Solder the other end of the wire to pin 1 and pin 2 (+5 V supply) on the bottom display.
    \item Trim the wires from the middle pin of the gain adjusters by around 5 inches, connect those two wires, the wire furthest from the dial on the potentiometer, and two 12 inch wires by twisting together.
    \item Solder a 3 inch wire to the white banana plug and screw it in the housing. This is component \textbf{E} in in Fig.~\ref{sfig12}B.
    \item Solder a 3 inch wire to the red banana plug and screw it in the housing.
    \item Connect the twisted together wires to the white banana plug.
    \item Connect the wire closest to the dial on the potentiometer and the left pin (left with words being oriented in the correct direction) on the second switch on the side opposite to the ON/ON words to the red banana plug.
    \item Solder one of the wires from the white banana plug to pin 2 of the top 4-pin female connector. This connection is item \textbf{F} in Fig.~\ref{sfig12}B. The 4-pin connector that will plug into this port is shown in in Fig.~\ref{sfig12}C.
    \item Solder the wire from the pin closest to the knob on the left potentiometer to pin 3 of the top 4-pin female connector. Put a 12k Ohm resistor within the path of the wire (component \textbf{G} in white heat-shrink tubing). This limits the control voltage to approx. 0.8 V, which is safer for the PMT \cite{Hamamatsu2024}. We discuss this in the main manuscript.
    \item Solder the wire from pin 11 on the top display to pin 1 of the top 4-pin female connector (M16 4 Pin Connector).
    \item Solder the wire from the middle pin on side adjacent to ON/ON words on the top switch to pin 4 of the top 4-pin female connector.
    \item Do the previous 4 steps for the other 4-pin female connector.
\end{itemize}
%
This concludes the assembly of the control box. The connection of this box to the PMTs is made through a custom cable. A male connector, shown in in Fig.~\ref{sfig12}C, plugs into the control box on one end, and into a female plug soldered to the PMT module on the other. This is shown in in Fig.~\ref{sfig12}D. The PMT module has four colored control lines attached to, see in Fig.~\ref{sfig12}E, that are wired to this connector. The specific type, shown in Fig.~\ref{sfig12}D, is a Wire-Pro, Inc. (WPI) 126-195 connector.

\section{Software and control}
%
\subsection{Laser settings}
The laser control depends on the system used. The Alcor 920 laser is controlled through a USB interface, and software that runs on the same PC as ScanImage. The software is used to switch on the laser, switch between alignment and full-power mode, and to adjust the group delay dispersion.

\subsection{Shutter settings}
The shutter controller has various settings that allow either manual control, or control via ScanImage. In our system, a ``Local/Remote'' toggle switch selects between those options. A second important toggle switch is ``N.O./N.C.''. In the ``N.C.'' position, the shutter will be activated open by an input pulse signal. In the ``N.O.'' position the shutter will be activated closed. If ScanImage's shutter control signal is not correctly actuating the shutter, very likely this toggle switch needs to be flipped.
%
\subsection{Setting up ScanImage}
%
\begin{figure}[t]
    \includegraphics[width=\textwidth]{sfig13.jpg}
  \caption{{\bf Setup Vidrio DAQ system.} \textbf{A)} Wiring of the four input channels. These are connected to the PMT preamplifiers, and for our system digitized at 14 bit resolution. \textbf{B)} Data acquisition panel connected to the microscope's various control and signal lines. Capital letters are explained in the text.}
  \label{sfig13}
\end{figure}
%
At this point, all hardware is set up and aligned. The next step is configuring ScanImage, the software used to control the microscope \cite{Pologruto2003, Vidrio2022} to communicate with the various components. This is done through a number of coaxial lines that connect the Vidrio data acquisition system with the microscope hardware, see Fig.~\ref{sfig13}. Our system is connected, on the back, to the two PMT outputs, see Fig.~\ref{sfig13}A. The front panel links the system to eight signals, Fig.~\ref{sfig13}B. These are
\begin{itemize}
    \item \textbf{A)} \texttt{Analog-out}: X-resonant zoom control.
    \item \textbf{B)} \texttt{Analog-out}: Y-slow control.
    \item \textbf{C)} \texttt{Analog-out}: Piezo control for the objective collar.
    \item \textbf{D)} \texttt{Analog-in}: Piezo feedback from the objective collar.
    \item \textbf{E)} \texttt{Analog-in}: Pockels cell feedback.
    \item \textbf{F)} \texttt{Analog-out}: Pockels cell control.
    \item \textbf{G)} \texttt{Digital}: Resonant scanner sync.
    \item \textbf{H)} \texttt{Digital}: Shutter control.
\end{itemize} 
%
When connected, ScanImage needs to be configure to make use of these connections. The process is as follows.

\begin{itemize}
    \item Type \texttt{ScanImage} into Matlab and press Enter.
    \item Login using the correct credentials.
    \item Under \texttt{Machine Data File}, click \texttt{New}.
    \item Type in a filename and click \texttt{Save}.
    \item Select \texttt{Blank Configuration}.
    \item Next we need to add all the devices of the microscope. Start by clicking the \texttt{Devices} tab, and pressing \texttt{+} to add each new device.
    \item Shutter
    \begin{itemize}
        \item Select \texttt{Digital Shutter} and click \texttt{Add}.
        \item Type in a name like \texttt{Shutter1}.
        \item In the new window, select \texttt{/vDAQ0/D1.0} for \texttt{Control Channel}. This will depend on how you have wired up the control line to the front panel.
        \item \texttt{Open time (seconds)} remains at the default of 0.5 s.
        \item Check the \texttt{Invert Output} box.
        \item Click \texttt{Apply}.
        \item Make sure the shutter itself (on the driver box) is on \texttt{STD} for the key and the toggle switches (see above) are set to \texttt{N.C.} and \texttt{Remote}.
    \end{itemize}
    \item Pockels cell:
    \begin{itemize}
        \item Select \texttt{Pockels Cell} and click \texttt{Add}.
        \item Type in a name like \texttt{Pockels1}.
        \item In the new window, select \texttt{/vDAQ0/AO11} for \texttt{Control Channel}. Again, this will depend on the channel that the Pockels driver is connected to.
        \item For \texttt{Feedback Channel (optional)}, select \texttt{/vDAQ0/AI4}. This is connected to the photodiode directed at the beam block for the shutter. The gain should be chosen for a good signal. In our system, a gain of 50 dB works well. If the ambient room light is too bright, a SM1-mounted infrared long-pass filter in front of the photodiode can help (e.g. FELH0850, Thorlabs). The goal of setting the gain is sigmoidal control curve in ScanImage: Light transmission starts at a minimum, and increases as the control voltage increases.
        \item Under \texttt{Control output [Volt]}, change \texttt{Max} to \texttt{1.7}. This is the maximum control voltage applied to the Pockels cell driver.
        \item When calibrating, notice how it takes about 1.7 V to reach 100\% laser power.
        \item Leave the \texttt{Open shutters for calibration} field unchecked because our shutter is positioned after the Pockels cell and the reflection off the closed shutter used for calibration with a photodiode.
        \item Leave everything else in the \texttt{Basic} tab unchanged.
        \item Leave everything else in the \texttt{Calibration Settings} and \texttt{Advanced} tabs unchanged.
        \item Click \texttt{Apply}.
    \end{itemize}
    \item Slow galvanometer:
    \begin{itemize}
        \item Select \texttt{Analog Galvo} and click \texttt{Add}
        \item Type in a name like \texttt{Y-galvo}
        \item In the new window, select \texttt{/vDAQ0/AO1} for \texttt{Control Channel}. This will depend on the port that the galvanometer is connected to.
        \item The rest of the defaults have to be adjusted as per the Galvanometer's specifications. For our slow galvanometer, these are as follows.
        \item Change \texttt{Volts per optical degree [V/deg]} to \texttt{0.7692}.
        \item Change \texttt{Angular range [optical degrees]} to \texttt{26}.
        \item Change \texttt{Park position [optical degrees} to \texttt{13}.
    \end{itemize}
    \item Resonant scanner:
    \begin{itemize}
        \item Select \texttt{Resonant Scanner} and click \texttt{Add}.
        \item Type in a name like \texttt{X-res}.
        \item In the new window select \texttt{/vDAQ0/D0.0} for \texttt{Sync Channel}. This will depend on your wiring.
        \item For \texttt{Zoom Control Channel}, select \texttt{/vDAQ0/AO0}.
        \item Leave everything else unchanged. We used a 8 kHz scanner.
        \item Click \texttt{Apply}.
    \end{itemize}
    \item Piezoelectric objective collar.
    \begin{itemize}
        \item Select \texttt{PI E709} and click \texttt{Add}.
        \item For \texttt{Serial port / USB}, select \texttt{COM1}.
        \item For \texttt{Control Channel}, select \texttt{/vDAQ0/AO2}. This will depend on your wiring.
        \item For \texttt{Feedback Channel}, select \texttt{/vDAQ0/AI2}. This will depend on your wiring.
        \item Click \texttt{Read From Device} and numbers should automatically update.
        \item Click \texttt{Apply}.
        \item Click \texttt{Calib} on the new Piezo widget.
        \item Should be able to feel piezoelectric mount vibrate with hand when it calibrates.
        \item Check \texttt{Enable Stack} on the main ScanImage window and the \texttt{STACK CONTROLS} windows should pop up.
        \item Better to do \texttt{step} instead of \texttt{sawtooth} for resonant scanner since we are averaging images; with \texttt{sawtooth}, we would be averaging difference Z depths together
        \item Select 10 \texttt{Frames per Slice}, 5 \texttt{Number of Slices}, 10 \texttt{Number of Volumes}, and 5 for \texttt{Step Size [um]}.
        \item Click \texttt{Test Waveform}.
        \item In new window, click \texttt{Optimize Waveform}.
        \item Ringing at the beginning and end of steps can be corrected with \texttt{Actuator lag}.
    \end{itemize}

    \item After adding the devices, we have to create an imaging system by clicking the \texttt{ScanImage} tab and click \texttt{+ Add Imaging System +}.
    \item In the new window, under \texttt{vDAQ Scan System}, click \texttt{Add} and type in a name like \texttt{My microscope}.
    \item In the new window, select \texttt{X-res} under \texttt{Resonant Scanner}.
    \item For \texttt{Y-Galvo}, select \texttt{Y-galvo}.
    \item Check off \texttt{Use} for \texttt{Shutter1}.
    \item Check off \texttt{Use} for \texttt{Pockels1}.
    \item Check off \texttt{Use} for \texttt{Piezo1}.
    \item Under \texttt{Channel}, check off \texttt{Invert} for all 4 channels.
    \item Leave everything under the \texttt{Triggers}, \texttt{Advanced}, and \texttt{I2C} tabs unchanged.
    \item Of note: (1) Under \texttt{Advanced}, \texttt{Reverse line read} \textcolor{red}{Edward states ``reverses the image. We talked about this in the video that Esme’s scope needs this''. Why?} (2) The setting \texttt{I2C} is used for syncing with behavior.
    \item Click \texttt{Apply}.
\end{itemize}
%

\section{Recommendations for use}
Make a point of regularly checking your microscope. Lenses can get dirty, the path misaligned, and components age.
%
\begin{itemize}
    \item Measure (1) the laser's power levels, (2) the Pockels cell calibration and (3) check exposed lenses and mirrors for dust and fingerprints with a flashlight. This is fast and should be done before every experiment.
    \item When the microscope is not in use, it is good practice to switch off all components, except the scanning mirror power supplies, the PMT preamplifiers, and the photodiode.
    \item Every couple of month, switch the red and green PMTs to check for signs of aging and validate their performance on a fluorescent slide or sample of known brightness. The PMTs age and will need to be replaced, depending on use, after a few years. They should be treated with care: power ramped up and down slowly, and saturation should be avoided. We use a rotation system in which new PMTs are typically used for the green channel. When their performance becomes worse, they often have a few more months or years in the (typically brighter) red channel in them.
    \item Every couple of month, image a bead sample to validate the PSF.
    \item Be mindful of imaging artifacts. When suspecting an issue, go back to the basics, and isolate the error.
\end{itemize}
%
Of note, for virtual reality experiments that involve a Styrofoam treadmill floating on an air cushion, or any other experiment using compressed air, make sure to place an oil trap in the air line. This avoids oil droplets being deposited onto the optics; especially the elliptic mirror right above the objective. Small Styrofoam particles also get deposited on the lenses which need to be dusted from time to time. Try to shield the laser path as much as possible to keep dust and dirt away from optical components.

\nolinenumbers

\begin{thebibliography}{10}

\bibitem{Thorlabs}
Two Steering Mirrors Can be Used to Walk a Laser Beam to a New Path. Thorlabs 2024. 
\url{https://www.thorlabs.com/newgrouppage9.cfm?objectgroup_id=14221} and \url{https://www.youtube.com/watch?v=qzxILY6nOmA}

\bibitem{Conoptics2018}
Pockels Cell Concepts. Conoptics 2018.
\url{https://www.conoptics.com/wp-content/uploads/2018/06/SI2018-PockelsCellConcepts-190618-0009-18094.pdf}

\bibitem{Scientifica2024}
\#LabHacks: Aligning your Pockels cell for two-photon imaging. Scientifica 2024.
\url{https://www.scientifica.uk.com/neurowire/labhacks-aligning-your-pockels-cell-for-two-photon-imaging}

\bibitem{Vidrio2022}
Online documentation of ScanImage. Vidrio 2024. \url{https://docs.scanimage.org/index.html}

\bibitem{Pologruto2003}
Pologruto TA, Sabatini BL, Svoboda K. ScanImage: Flexible software for operating laser scanning microscopes. BioMed Eng OnLine 2, 13 (2003). \url{https://doi.org/10.1186/1475-925X-2-13}

\bibitem{Yao2023}
Yao P, Liu R, Broggini T, Thunemann M, Kleinfeld D. Construction and use of an adaptive optics two-photon microscope with direct wavefront sensing. Nat Protoc. 2023 Dec;18(12):3732-3766. doi: 10.1038/s41596-023-00893-w. Epub 2023 Nov 1. PMID: 37914781; PMCID: PMC11033548.

\bibitem{Hamamatsu2024}
Technical note on the Photomultiplier Tube Modules Series
H16200/H16201/H16204, Hamamatsu Photonics 2014 \url{https://www.hamamatsu.com/eu/en/product/optical-sensors/pmt/pmt-module/current-output-type/H16201-40.html}

\end{thebibliography}

\end{document}

### 2024-09-12 article/Article.tex
updated article, pdfs, README

@@
 \\
-Manuel Schottdorf\textsuperscript{1,*},
-P. Dylan Rich\textsuperscript{1},
-E. Mika Diamanti\textsuperscript{1}, 
-Albert Lin\textsuperscript{1,4}, 
-Sina Tafazoli\textsuperscript{1},
-Edward H. Nieh\textsuperscript{1,2},
-Stephan Y. Thiberge\textsuperscript{1,3*}
+Manuel Schottdorf\textsuperscript{1,*}, % 0000-0002-5468-4255
+P. Dylan Rich\textsuperscript{1}, % 0000-0001-9782-7984
+E. Mika Diamanti\textsuperscript{1}, % 0000-0003-1199-3362
+Albert Lin\textsuperscript{1,4}, % 0000-0002-4541-5889
+Sina Tafazoli\textsuperscript{1}, % 0000-0003-1926-0227
+Edward H. Nieh\textsuperscript{1,2}, % 0000-0003-2154-6224
+Stephan Y. Thiberge\textsuperscript{1,3*} % 0000-0002-6583-6613
 \\
@@
 As such we have made all optical and mechanical designs, electronics, bill-of-materials, CAD assembly, testing results, and relevant schematics open to the public.
-Excluding laser and optical table, the cost is around US-\$ 110,000 (2024).
+Excluding laser and optical table, the cost is around US-\$ 110k (2024).
 A narrative of the design and high-level view is presented here.
@@
 Full details will be provided below.
-In short, we chose a Spark Alcor 920 nm pulsed femtosecond laser, whose beam, after $2\times$ magnification with a telescope, reaches the scanning mirrors.
+In short, we chose a Spark Alcor 920 nm femtosecond pulsed laser, whose beam, after $2\times$ magnification with a telescope, reaches the scanning mirrors.
 The scanning mirrors are geometrically close together in the focal plane of the scan lens.
@@
 We set the orientation of the waveplate to split the beam into two beams with 50\% power each to feed a second experimental setup.
-In the CAD drawing, this beam is sent to a beam block (LB1, Thorlabs).
+In the CAD drawing, this second beam is sent to a beam block (LB1, Thorlabs).
 Next, the beam passes through an electro-optic modulator, a Pockels cell (350-80-LA-02, Conoptics).
@@
 Nikon $16\times$ with $f_O=12.5\text{ mm}$) this determines the expected approximate field of view ($\approx 1.2\text{ mm}$).\newline
-We assembled the scan and tube these as lens groups from groups of off-the-shelf parts, using the same elements as in \cite{Yao2023}, and further optimizing lenses and spacing in Zemax (an optics design software).
+We assembled the scan and tube lenses as lens groups from off-the-shelf parts, using the same elements as in \cite{Yao2023}, and further optimizing lenses and spacing in Zemax (an optics design software).
 Details are provided below.
@@
 Colors indicate light rays produced by different mirror angles of the scanning mirror.
-Notice how the rays converge in the focal plane.
+Notice how the rays converge in the image plane.
 \textbf{B)} CAD design built around the optical design in A, see also Fig.~\ref{fig1}B.
@@
 \textbf{D)} Simulation of the optical system's two-photon point spread function (PSF-2p) for 0 deg deflection angle, and two example radial sections.
-\textbf{E)} PSF-2p in xz direction across the full range of deflection angles, and quantification of Petzval field curvature (blue), and radial (purple) and axial (yellow) full-width-at-half-maximum of the PSF-2p.
+\textbf{E)} PSF-2p in the xz plane across the full range of deflection angles.
+Shown below is Petzval field curvature (blue), and radial (purple) and axial (yellow) full-width-at-half-maximum of the PSF-2p.
 Error bars are resolution limits of the Huygens PSF estimates in sequential mode.}
@@
 %
-Fig.~\ref{fig2}A shows the propagation of light rays for various deflection angles of the scanning mirrors converging on points along a line in the focal plane.
+Fig.~\ref{fig2}A shows the propagation of light rays for various deflection angles of the scanning mirrors, and how the beams converge on a line under the objective.
 The Zemax design was then exported into CAD, and the optomechanics assembled around it, see Fig.~\ref{fig2}B.
@@
 %
-We incorporated four design principles into our assembly: (1) Fluorescence light must fall approximately perpendicularly on the optical filters.
-Narrow filters are particularly susceptible to these effect.
-Although light emitted from the focal plane of an infinity-corrected objective is collimated as it returns from the sample, actual fluorescence weakly diverges due to scattering and diffraction in the material between focal plane and objective (e.g.
+We incorporated four design principles into our assembly: (1) Fluorescence light must fall approximately perpendicularly on the optical filters for the filters to work correctly.
+Narrow filters are particularly susceptible to this.
+Although light emitted from the image plane of an infinity-corrected objective is collimated as it returns from the sample, actual fluorescence weakly diverges due to scattering and diffraction in the material between image plane and objective (e.g.
 brain tissue \cite{Zipfel2003, Taddeucci1996}).
@@
 This allows the mechanical components sufficient degrees of freedom to optically align all key parts of the microscope.
-In the supplement, we go through this alignment procedure which allows a user to find the optimal position of the scanning mirrors in the conjugated plane of the back-aperture of the objective.
+In the supplement, \nameref{S1_Appendix}, we go through this alignment procedure in detail.
 
@@
 This is a combined measure of the quality of excitation and the efficiency of the collection optics across the field of view.
-Within the central $700\text{ \textmu m} \times 700\text{ \textmu m}$ region, the signal deviated from uniformity within $\approx 10\%-15\%$ ($\pm 1 \text{ standard deviation}$) suggesting a relatively flat field, see Fig.~\ref{fig5}D, E.
+Within the central $700\text{ \textmu m} \times 700\text{ \textmu m}$ region, the signal deviated from uniformity within $\approx 13\%$ ($\pm 1 \text{ standard deviation}$) suggesting a relatively flat field, see Fig.~\ref{fig5}D, E.
 Following these measurements, we imaged a bead sample of 0.2\microns diameter in 1\% Agarose (Dragon Green beads; Bangs Laboratories) to measure axial and radial PSFs.
@@
 For zebrafish imaging, we used the HuC:H2B-GCaMP6f line of transgenic Zebrafish \cite{Cong2017}.
-Neurons in this organism expresses the fluorescent protein GCaMP6f in their nuclei whose green fluorescence strongly depends on the cellular concentration of Calcium ions.
+Neurons in this organism express the fluorescent protein GCaMP6f in their nuclei whose green fluorescence strongly depends on the cellular concentration of Calcium ions.
 We imaged a 5-day old larva in 2\% low melting point Agarose in E3 medium, see Fig.~\ref{fig7}.
@@
 is shown as thin purple line.
-Deriving this from geometric principles, and aligning the Pockels cell on the table for greatest dynamic range is a relatively straightforward.
-The students perform these measurement by scanning through voltage settings on the Pockels driver, while monitoring light intensity.
-This explains to them the particular orientation of the crystal relative to the laser.\newline
+Deriving this from geometric principles, and aligning the Pockels cell on the table for greatest dynamic range is relatively straightforward and the students perform these measurement by scanning through voltage settings on the Pockels driver, while monitoring light intensity.
+This explains to them the optimal orientation of the crystal relative to the laser.\newline
 %
@@
 Our microscope was set up in a teaching lab space at the Princeton Neuroscience Institute.
-Over the course of three years, it was disassembled and re-assembled by various generations of students and postdocs.
+It was disassembled and re-assembled by various generations of students and postdocs.
 We found that assembling and aligning the microscope, as described, takes around 10 work-days.
@@
 When adapting the optical path to their needs, we suggest to start at our lens combinations, and then optimize (at the very least) the lens spacings in Zemax.
-Technology develops rapidly, and much of the specific components mentioned here will be outdated in a few years.
+Technology develops rapidly, and many of the specific components mentioned here will be outdated in a few years.
 We believe that science progresses best if researchers understand their instrumentation, and leverage the current cutting edge of what is possible to further their science.\newline
@@
 
-\paragraph*{S1 Appendix:}
+\paragraph*{S1 Appendix}
 \label{S1_Appendix}
@@
 
-\paragraph*{\bf Online Repository:} 
+\paragraph*{\bf Online Repository}
 \label{repository}

### 2024-09-12 documentation/supplement.tex
updated article, pdfs, README

@@
 This supplemental material to the article ``TWINKLE: An open-source two-photon microscope for teaching and research'' describes the assembly, function and alignment of all parts of the microscope.
-Technical specifications are provided through the CAD files and the Zemax simulations in the online repository.
+Technical specifications are provided through the CAD files and the Zemax simulations in the online repository at \url{https://github.com/BrainCOGS/Microscope}.
 
@@
 \begin{itemize}
-    \item Use a high quality duster to remove any residue from optical surfaces. We use a Miller-Stephenson Aero-Duster Ultra MS-222L.
+    \item Use a high quality duster to remove any residue from optical surfaces.
+We use a Miller-Stephenson Aero-Duster Ultra MS-222L, in addition to lens tissues (MC-5, Thorlabs) and Methanol (Sigma-Aldrich).
     \item To glue optical filters we used an extra fast setting epoxy (Hardman Double/Bubble Epoxy). To seal small gaps, we use black silicone putty (V-tie self-setting silicone rubber).
@@
 All custom metal pieces are parts of the CAD assembly of the microscope.
-Ours were manufactured from Aluminium stock in the university machine shop, but other materials are possible.
+Ours were manufactured from aluminium stock in the university machine shop, but other materials are possible.
 Aluminium has the added benefit of anodization, which can help control stray light.
@@
     \item \textbf{H)} Two beam blocks (LB1, Thorlabs).
-Confirm that the right beam block terminates the waste beam leaving the Pockels cell.
-The left beam is used for calibrating the Pockels cell in ScanImage (the control software used by our microscope \cite{Vidrio2022, Pologruto2003}), together with a light sensor (I).
+Confirm that the right beam block terminates the rejected beam leaving the Pockels cell.
+The left beam block is used for calibrating the Pockels cell in ScanImage (the control software used by our microscope \cite{Vidrio2022, Pologruto2003}), together with a light sensor (I).
 
@@
     %
-\item \textbf{L)} Iris (SM1D12C inside CP08, both Thorlabs) Used to check alignment.
+\item \textbf{L)} Iris (SM1D12C inside CP08, both Thorlabs) used to check alignment.
 
 \item \textbf{M)} Mirror (PF10-03-P0, Thorlabs, inside KCB1) to reflect the beam up at a right angle.
-For the next steps (in particular finding the optimal scanning mirror position), it is important that the beam travels up perpendicular to the optical table, and parallel to the 95 mm optical rail column that holds the scanning mirrors (next section).
+For the next steps (in particular finding the optimal scanning mirror position), it is important that the beam travels up perpendicularly to the optical table, and parallel to the 95 mm optical rail column that holds the scanning mirrors (next section).
 
@@
 Following beam conditioning on the optical table, the beam is reflected up from the optical table towards the ceiling into a box housing the scanning mirrors.
-This is shown in Fig.~\ref{sfig4}.
+This is shown in Fig.~\ref{sfig4}A,B.
 Following the scanning mirrors, the beam travels up through the scan lens, and directed to the microscope head with another mirror.
@@
 The rest of the assembly here will be done without any lenses.
-The goal is a well-aligned beam that travels through the middle of all parts, and parallel to the optomechanical surfaces.
+The goal is a well-aligned beam that travels through the center of all parts, and parallel to the optomechanical surfaces.
     \item The box housing the scanning mirrors is connected, trough SM1 tubing, to a mirror (component A in Fig.~\ref{sfig3}).
@@
 Mount the box housing the scanning mirrors such that you can not feel the transition from the lower SM1 tubing to the upper SM1 tubing.
-    \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}) so that light travels through the center of the scanning mirrors and up the 95 mm rail.
+    \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}A) so that light travels through the center of the scanning mirrors and up the 95 mm rail.
 This is done with irises.
 One is attached at the entry port of the scanning mirror box, e.g.
-in the SM1 tube (component B in Fig.~\ref{sfig4}).
+in the SM1 tube (component B in Fig.~\ref{sfig4}A).
 Another two irises are attached, as far away as possible, to a 95 mm rail bracket.
@@
     \item Mount the two 95 mm posts to the table.
-    \item Mount the collection optics box to the Aluminium stage, and then mount the stage to the 95 mm rail.
+    \item Mount the collection optics box to the aluminium stage, and then mount the stage to the 95 mm rail.
 Do not install the photomultiplier tubes yet.
 These devices are light sensitive, and more alignment needs to be done before we are ready to install them.
-    \item Equip the Aluminium stage with brackets and cage mounts to hold SM2 tubing (A, D and E in Fig.~\ref{sfig5}).
+    \item Equip the aluminium stage with brackets and cage mounts to hold SM2 tubing (A, D and E in Fig.~\ref{sfig5}).
     \item First, we position the big mirror at a $45^\circ$ angle (component B in Fig.~\ref{sfig5}).
@@
     \item Install the collection mirror (component F in Fig.~\ref{sfig5}).
-Then position an iris in place of the future objective, and one as far away as possible just above the optical table.
-Shift the mirror along the rail and adjust its tilt via the set screws so that the beam is aligned with the two irises.
+Then position an iris in place of the future objective, and a second iris as far away as possible just above the optical table.
+Use an adapter with external $\text{M}32\times0.75$ threads and internal SM1 threads (SM1A33, Thorlabs) to attach the irises to the objective collar.
+Then shift the collection mirror along the rail and adjust its tilt via the set screws so that the beam is aligned with the two irises.
 \end{itemize}
@@
 Specifically, when inserted into one of our previously aligned SM2 mounting rings, they should focus the beam, but must not incur a lateral or angular displacement.
-To test this, one can screw them into component E in Fig.~\ref{sfig4}, and observe the beam far away on a wall.
+To test this, one can screw them into component E in Fig.~\ref{sfig5}, and observe the beam far away on a wall.
 The lens groups must not change the position of this spot, only its size.
@@
 See also the diagram in the section on ``Tube lens Assembly'' below).
-Observe how the focal plane changes when moving the tube lens along the optical rails (component E in Fig.~\ref{sfig4}).
+Observe how the focal plane changes when moving the tube lens along the optical rails (Component E in Fig.~\ref{sfig5}).
 When its correct position is confirmed, tighten the set screws on the optical cage.
@@
 The spacing between tube lens and scan lens is critical because the beam leaving the tube lens has to be collimated.
-To test this, remove the elliptical mirror (component F in Fig.~\ref{sfig4}) from its housing, and observe the spot on a wall far away, while moving the scan lens up and down on the 95 mm optical rail.
+To test this, remove the elliptical mirror (component F in Fig.~\ref{sfig5}) from its housing, and observe the spot on a wall far away, while moving the scan lens up and down on the 95 mm optical rail.
 Find a position at which the beam neither converges, nor diverges after the tube lens, and the spot on the wall has the same size as the beam right after the tube lens.
@@
 Clamp down the scan lens on its rail.
-    \item Next, reinstall the elliptical mirror (component F in Fig.~\ref{sfig4}), and observe the back-aperture of the objective, while moving the scanning mirror box up and down.
+    \item Next, reinstall the elliptical mirror (component F in Fig.~\ref{sfig5}), and observe the back-aperture of the objective, while moving the scanning mirror box up and down.
 The scan mirrors have to be positioned in so that they are conjugated to the back aperture of the objective.
@@
 For a useful illustration of this method, see also \cite{Yao2023}.
-Of note, this step of fine-tuning the position of the scan box up and down along the 95 mm optical rail is the reason why we stressed the importance of the alignment of the scanning post, the components A in Fig.~\ref{sfig3} and M in Fig.~\ref{sfig1} earlier.
+Of note, this step of fine-tuning the position of the scan box up and down along the 95 mm optical rail is the reason why we stressed the importance of the alignment of the scanning post, the components A in Fig.~\ref{sfig4} and M in Fig.~\ref{sfig1} earlier.
 It was critical that across the various heights used here, the scanning mirror box was precisely aligned with the beam.
@@
 PMTs are light sensitive.
-Always store them with their aperture covered with black tape when not in use.
+Always store them with their aperture covered with blackout tape when not in use (AT205-1.0 black aluminium foil tape, Thorlabs).
 When removing the tape for installation, this installation into the collection box must be done in darkness and as quickly as possible.
@@
 Now that your microscope is ready, finish shielding the light path with SM1 and SM2 tubing, and cover the optical table with sheet metal.
-We use bent Aluminium sheet, placed on small columns made from T-slotted rail.
+We use bent aluminium sheet, placed on small columns made from T-slotted rail.
 
@@
 Check the lens thoroughly.
-Dust can be blown away with a duster, finger prints wiped off with Methanol and a lens cleaning tissue (cf.
-Fig.~\ref{sfig8}B).
+Dust can be blown away with a duster, finger prints wiped off with Methanol and a lens cleaning tissue.
     \item Blow it with the air duster. 
@@
 \subsection{Scan lens assembly}
-
+The scan lens assembly is shown in Fig.~\ref{sfig8}C. The individual steps for the scan lens group are as follows:
 \begin{itemize}
@@
     \item \textbf{B)} Next, we attach the front panel. This is connected  with stainless steel Phillips flat head screws, 82 degree countersink angle, 4-40 Thread, 1/8 in long and undercut.
-    \item \textbf{C)} Then we install the first lens, a LA1384-A plano-convex lens (Thorlabs), see also Fig.~\ref{sfig8}A.
-The flat side of the lens sits against the lip inside of its Aluminium holder.
+    \item \textbf{C)} Then we install the first lens, a LA1384-A plano-convex lens (Thorlabs), see Fig.~\ref{sfig9}.
+The flat side of the lens sits against the lip inside of its aluminium holder.
 The convex side points towards the PMTs.
@@
 It also shields the scanning mirrors from dust in the environment, and protects the environment from audible noise produced by the scanning mirrors.
-The housing is composed of a box, mounted to the 95 mm rail (Fig.~\ref{sfig10}A), and a lid to which the Novanta scanners are mounted (Fig.~\ref{sfig10}B,C).
-When mounting the black anodized holder, make sure to apply heat transfer compound between the holder and the lid (we use Wakefield Thermal Joint Compound Type 120-5 Silicone).
+The housing is composed of a box, mounted to the 95 mm rail (Fig.~\ref{sfig10}A,B,C), and a lid to which the Novanta scanners are mounted (Fig.~\ref{sfig10}D,E,F).
+When mounting the black anodized holder, make sure to apply heat transfer compound between the holder and the lid (we use Wakefield Thermal Joint Compound Type 120-5 Silicone, cf.
+Fig.~\ref{sfig10}D,E).
 While the resonant scanner does not dissipate much heat, the slow galvanometer becomes warm in normal operation, and this heat needs to be dissipated.
 This is particularly important when pushing to fast responses, and driving the slow galvanometer with larger currents.\newline
-After receiving the scanning mirrors, they need to be installed in the black anodized Aluminium block.
+After receiving the scanning mirrors, they need to be installed in the black anodized aluminium block.
 Make sure to put the resonant scanner in first (the piece sitting at an angle) before the slow galvanometer (the piece sitting parallel to the mount).
@@
 The larger circuit board (green) drives the slow galvanometer.
-The circuit boards are mounted to the Aluminium walls with screws and heat transfer compound.}
+The circuit boards are mounted to the aluminium walls with screws and heat transfer compound.}
   \label{sfig11}
@@
 This voltage divider produces the control voltage that is fed back to the module via the white input line, and used for display on the panel meter.
-Due to the simplicity of this circuit, we do not solder this on a circuit board, but rather in a prototype development box directly, see Fig.~\ref{sfig11}A,B, which is attached to the rig.
+Due to the simplicity of this circuit, we do not solder this on a circuit board, but rather in a prototype development box directly, see Fig.~\ref{sfig12}A,B, which is attached to the rig.
 %
@@
 %
-The first components to be wired up are the Murata DMS-20PC displays. The circuit diagram is shown in the main manuscript \textcolor{red}{Fig. 4}.
+The first components to be wired up are the Murata DMS-20PC displays. The circuit diagram is shown in the main manuscript Fig. 4.
 \begin{itemize}
@@
     \item Under \texttt{Channel}, check off \texttt{Invert} for all 4 channels.
-    \item Leave everything under the \texttt{Triggers}, \texttt{Advanced}, and \texttt{I2C} tabs unchanged.
-    \item Of note: (1) Under \texttt{Advanced}, \texttt{Reverse line read} \textcolor{red}{Edward states ``reverses the image.
-We talked about this in the video that Esme’s scope needs this''.
-Why?} (2) The setting \texttt{I2C} is used for syncing with behavior.
+    \item Leave everything under the \texttt{Triggers}, \texttt{Advanced}, and \texttt{I2C} tabs unchanged. Of note: The setting \texttt{I2C} is used for syncing with behavior.
     \item Click \texttt{Apply}.

### 2024-09-13 article/Article.tex
updated articles
Mk3. This is the version _before Stephan's cleanup_

Update Article.tex

@@
 \section*{Abstract}
-Many laboratories use two-photon microscopy through commercial suppliers, or open designs of considerable complexity.
+Many laboratories use two-photon microscopy through commercial suppliers, or homemade designs of considerable complexity.
 The integrated nature of these systems complicates customization, troubleshooting as well as grasping the principles of two-photon microscopy.
@@
 It is a fully open, high-performance and cost-effective research and teaching microscope without any custom parts beyond what can be fabricated in a university machine shop.
-The instrument features a large field of view, using modern objectives with a long working distance and large back-aperture to maximize the fluorescence signal.
+The instrument features a large field of view, using a modern objective with a long working distance and large back-aperture to maximize the fluorescence signal.
 We document our experiences using this systems as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open-source scientific instrumentation.
@@
 The product of the interaction of light and sample, fluorescent light, is then measured with a sensitive light detector.
-Moving the volume of light through the sample and combining the detected fluorescence from different $x$ and $y$ positions produces a picture.
+Moving the volume of light through the sample and combining the detected fluorescence from different $x$ and $y$ positions produces an image.
 The key to two-photon microscopy is the light source: A femtosecond-pulsed infrared laser restricts the volume in which fluorescence occurs to a tiny region in the sample with sufficiently high photon density for the near-simultaneous absorption of two photons by a fluorescent molecule \cite{Denk1990, Svoboda1997, So2000, Helmchen2005}.\newline
@@
 In this article, we described the instrument's mode of operation, and provide an overview of the design.
-For the complete and illustrated built instructions, please see the git repository and attached build instructions.
-To aid discoverability, we have generated an Open Know How Manifest (OKH-manifest), located in the hardware folder of the git repository at \url{https://github.com/BrainCOGS/Microscope}.\newline
+For the complete and illustrated built instructions, please see \nameref{S1_Appendix} and our \nameref{repository}.
+To aid discoverability, we have generated an Open Know How Manifest (OKH-manifest), located in the Online Repository.
+Our project is also certified by the open source hardware association (OSHWA UID
+US002677, \url{https://certification.oshwa.org/us002677.html}).\newline
 The growing space of open-source instrumentation can improve science in several ways: (1) enabling faster innovation through lower costs and enabling work in low-resource settings.
 (2) facilitating review and inspection by avoiding black-box designs and (3) providing a benchmark for innovation towards next-generation technology.
-We hope that our instrument, combined with earlier designs \cite{Rosenegger2014, Mayrhofer2015, Tan1999}, and recent developments like the head mounted microscope \cite{Zong2022} or the Janelia Research Campus microscope \cite{Janelia2024}, can serve as benchmarks for future instruments.
+We hope that our instrument, combined with earlier designs \cite{Rosenegger2014, Mayrhofer2015, Tan1999}, and recent developments like the head mounted microscope \cite{Zong2022} or the Janelia Research Campus microscope \cite{Janelia2024}, can serve as a benchmark for future instruments.
 Relatedly, we have contributed to other projects that follow this philosophy in microscopy \cite{Scott2018}, but also designing an open source ventilator during the COVID-19 pandemic \cite{LaChance2022,POVMC2022}, and a \textmu-contact printing device \cite{Samhaber2016}.
-Making these devices fully open has informed the narrative in this article, the design and organization of the published files, and also the choice of a open access journal.
+Making these devices fully open has informed the narrative in this article, the design and organization of the published files, and also the choice of an open access journal.
 Finally, the open approach can make two-photon microscopy more accessible to researchers, thereby greatly expanding the ability to train students in approaching such technology and producing new inventions.
-In our ventilator work, this has led to one of the first deep-RL controlled devices that performed superior to classical control schemes \cite{Suo2021}.
+In our ventilator work, this has led to one of the first devices using deep reinforcement learning that performed superior to classical control schemes \cite{Suo2021}.
 Future will tell how the community will make best use of Twinkle.
@@
 
-\paragraph*{\bf Online Repository}
+\paragraph*{Online Repository}
 \label{repository}

### 2024-09-19 article/Article.tex
Stephan's edits for Article + Supplement

@@
 The instrument features a large field of view, using a modern objective with a long working distance and large back-aperture to maximize the fluorescence signal.
-We document our experiences using this systems as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open-source scientific instrumentation.
+We document our experiences using these systems as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open-source scientific instrumentation.
 
@@
 Two-photon microscopy\cite{Denk1990, Svoboda1997, So2000, Helmchen2005} is a workhorse of modern systems neuroscience across species, and two-photon microscopes exist in many system neuroscience laboratories\cite{Luu2024, Grienberger2022}.
-For example, in \textit{Mus musculus}, two-photon microscopes have been used to classify the function and neural inventory of the retina \cite{Baden2016}, study sequential activity in cortex \cite{Harvey2012} and subcortical structures \cite{Nieh2021}, led to transformative insights into signals in the dopaminergic reward system \cite{Engelhard2019}, and revealed an organized map among grid cells \cite{Yu2018}.
+For example, in the animal model \textit{Mus musculus} (mouse), two-photon microscopes have been used to classify the function and neural inventory of the retina \cite{Baden2016}, study sequential activity in cortex \cite{Harvey2012} and subcortical structures \cite{Nieh2021}, led to transformative insights into signals in the dopaminergic reward system \cite{Engelhard2019}, and revealed an organized map among grid cells \cite{Yu2018}.
 In non-human primates, two-photon microscopes have been used as optical brain computer interfaces \cite{Trautmann2021}, and to survey the spatial organization of motor cortex in reach movements \cite{Ebina2018}.
@@
 In \textit{Caenorhabditis elegans}, it allowed to measure an atlas of neural signal propagation \cite{Randi2023}.\newline
-However, these systems are expensive and usually hard to customize \cite{Diamanti2021}, while improvements and new inventions are published regularly, such as the incorporation of adaptive optics \cite{Yao2023}, the use of multiple beams for more effective sampling\cite{Song2017}, the combination with two-photon stimulation for all-optical interrogation of neural circuits \cite{Rickgauer2014}, extremely large fields of view for mesoscopic imaging across brain areas \cite{Sofroniew2016}, or the use of delays for effective sampling through extremely large volumes of cortical tissue \cite{Demas2021}.\newline
-This popularity suggests the need for a simple platform, at reasonable cost, for practical education, dissemination, methods development and research.
+However, these systems can be expensive and difficult to customize \cite{Diamanti2021}, while improvements and new inventions are published regularly, such as the incorporation of adaptive optics to improve the signal amplitude \cite{Yao2023}, the combination of two-photon imaging with two-photon stimulation for all-optical interrogation of neural circuits \cite{Nikolenko2008, Packer2012,Rickgauer2014}, and extremely large fields of view for mesoscopic imaging across brain areas \cite{Sofroniew2016}.
+Recently, several approaches have also been developed to increase the size of the volumes being imaged beyond the limits set by the traditional sampling strategy while keeping the time resolution constant.
+New approaches probing extended regions simultaneously rely on signal demixing to reconstitute the underlying structure \cite{Song2017, Kazemipour2019}.
+Another approach uses a set of axially separated and temporally distinct foci to record the entire axial imaging range near-simultaneously \cite{Demas2021}.\newline
+The two-photon methods' popularity suggests the need for a simple platform, at reasonable cost, for practical education, dissemination, methods development and research.
 We developed a high-performance and cost-effective two-photon microscope that can easily be built in any neuroscience laboratory over the course of several days and can be effectively used for both teaching and research purposes.
@@
 \section*{Materials and methods}
-In two-photon laser-scanning microscopy\cite{Denk1990}, laser light is focused to a small volume.
-The product of the interaction of light and sample, fluorescent light, is then measured with a sensitive light detector.
-Moving the volume of light through the sample and combining the detected fluorescence from different $x$ and $y$ positions produces an image.
-The key to two-photon microscopy is the light source: A femtosecond-pulsed infrared laser restricts the volume in which fluorescence occurs to a tiny region in the sample with sufficiently high photon density for the near-simultaneous absorption of two photons by a fluorescent molecule \cite{Denk1990, Svoboda1997, So2000, Helmchen2005}.\newline
+In two-photon laser-scanning microscopy\cite{Denk1990}, laser light is focused to a small excitation volume,  the ``focal point'', which is moved across the sample by the intermediary of resonant and galvanometric scanning mirrors.
+As the focal point probes different locations, different quantities of fluorescence signal are detected.
+An image is then formed, mapping the detector photocurrent values to the locations of excitation volume: low and high photocurrents becoming respectively dark and bright pixels.
+Central to two-photon fluorescence excitation is the light source: a femtosecond-pulsed infrared laser of sufficient pulse energy to achieve, when focused by an objective lens, a photon density high enough for simultaneous absorption of two photons by a fluorescent molecule \cite{Denk1990, Svoboda1997, So2000, Helmchen2005}.
 Here, we design an open and high-performing microscope that uses these principles.
@@
 To summarize our design goals, we aimed for a mechanical and optical assembly using as many off-the-shelf components as possible, with only few custom aluminium parts that can be machined in any university machine shop.
-Our design lacks a microscope body, which is  advantageous for two reasons: it aids the use as a teaching instrument, and facilitates adaptation for \invivo imaging because it provides space for the organism and ancillary hardware.
-We also avoid any custom optics to aid transparency of the function of the optical system.
-Our system is also made cost-effective, in part, by the availability of femtosecond laser systems based on fiber technology.
-Operating at a fixed wavelength, these systems come at the fraction of the cost of a more traditional tunable Ti:Sapphire laser \cite{Bueno2019}.\newline
-We aimed for (1) $\gtrapprox20\text{ cm}$ of free space around the objective in all directions to aid integration of the microscope into custom behavior boxes, or sample container, and (2) resolution limited imaging of at least $\approx 700\times 700\text{ \textmu m}^2$ field of view which is typical for imaging brain tissue at cellular resolution.
-(3) Compared to previous open designs\cite{Rosenegger2014, Mayrhofer2015}, our system can make use of the large back aperture of modern long-working-distance objectives to collect more fluorescence and (4) uses GaAsP photomultiplier tubes to maximize signal to noise.\newline
+Our design  facilitates the adaptation for \invivo imaging by providing a large space for the organism and ancillary hardware.
+Our system is made cost-effective, in part, by the availability of femtosecond laser systems based on fiber technology.
+Operating at a fixed wavelength, these systems come at the fraction of the cost of a tunable Ti:Sapphire laser \cite{Bueno2019}.\newline
+We aimed for (1) $\gtrapprox20\text{ cm}$ of free space around the objective in all directions to aid integration of the microscope with various peripheral equipment such as behavior recording and stimulation, and the sample stage, and (2) imaging on a  $\approx 700\times 700\text{ \textmu m}^2$ minimum size field of view which is typical for imaging brain tissue at cellular resolution.
+(3) Compared to earliest open designs\cite{Rosenegger2014, Mayrhofer2015}, our system can make use of the large Numerical Aperture (NA) of  modern long-working-distance objectives to collect more fluorescence, but requires to adapt our design to their larger back apertures \cite{Janelia2024}.\newline
 An overview of the microscope is shown in Fig.~\ref{fig1}.
@@
 Full details will be provided below.
-In short, we chose a Spark Alcor 920 nm femtosecond pulsed laser, whose beam, after $2\times$ magnification with a telescope, reaches the scanning mirrors.
-The scanning mirrors are geometrically close together in the focal plane of the scan lens.
-This simplifies the design, but leads to minor distortions across the field of view (a few percent at low magnifications, see below).
+In short, we chose a Spark Alcor 920 nm femtosecond pulsed laser, whose beam diameter is  extended by a $2\times$ magnification telescope, before it reaches the scanning mirrors.
+The scanning mirrors are purchased as a mount-assembled set.
+Located as close as possible to each other, as we will see in the alignment procedure, neither of them can be exactly positioned in the focal plane of the scan lens.
+The choice of mounted scanners simplifies the design and construction, but it also leads to some optical distortions across the field of view.
+We found that this distortion does not exceed a few percent in our design (see below).
 The combined scan and tube lenses magnify the beam further to fill the back aperture of the objective.
-Fluorescence from the specimen is then collected and focused on the aperture of two GaAsP photomultiplier tubes with suitable color filters.
+Fluorescence from the specimen is then collected and brought to the aperture of two GaAsP photomultiplier tubes with suitable color filters.
 Fig.~\ref{fig1}B shows the CAD design of the entire assembly with important parts of the optical path labelled.
@@
 Notice that compared to the cartoon in Fig.~\ref{fig1}A, the optical path is folded with several mirrors.
-These mirrors significantly simplify alignment, and make the design more compact.
+These mirrors make the microscope assembly more compact.
 
@@
     \includegraphics[width=\textwidth]{fig1.jpg}
-    \caption{{\bf System overview.} \textbf{A)} Cartoon of the layout. \textbf{B)}
-    CAD drawing of the system on an optical table with several key components in the optical path highlighted.
+    \caption{{\bf System overview.} \textbf{A)} Cartoon of the layout.
+\textbf{B)} CAD drawing of the system on an optical table with several key components in the optical path highlighted.
 The spacing between two holes on the table is 1 inch.
@@
 Out of the laser head, the beam first encounters a waveplate (AHWP10M-980, Thorlabs).
-This is a birefringent crystal that can rotate the polarization of the laser.
+This is a birefringent crystal that can rotate the linear polarization of the laser to any angle.
 Next, the beam travels through a polarizing beamsplitter cube (PBS103, Thorlabs).
-This splits the beam into two beams whose relative intensity can be adjusted by the orientation of the waveplate.
-We set the orientation of the waveplate to split the beam into two beams with 50\% power each to feed a second experimental setup.
+This splits the beam into two orthogonal polarization components whose relative intensity is adjusted by the orientation of the waveplate.
+We set the orientation of the waveplate to split the beam into equal power components,  the second one being eventually used for a second microscope installed on the other extremity of the table.
 In the CAD drawing, this second beam is sent to a beam block (LB1, Thorlabs).
@@
 This can be thought of as a voltage-controlled wave plate, in which the electric field controls how much light travels through the polarizer.
-Next, the beam travels through an open mechanical shutter (LS6S2ZM1, Vincent Associates).
-When closed, the reflection from the shutter is used for calibrating the Pockels cell with a photodiode (PDA36A2, Thorlabs).
-Following the shutter, the beam travels though a $2\times$ telescope (GBE02-B, Thorlabs).
-This magnifies the beam diameter by a factor of 2.
-Past the telescope, the beam is then reflected off several mirrors in a periscope configuration before entering a custom aluminium box housing, mounted to a 95 mm optical rail, that houses the two scanning mirrors (CRS8K/6215H scanning mirror Set, Novanta), shown in blue in  Fig.~\ref{fig1}C.
-Based on their angles, the two mirrors deflect the beam in x and y position.
-The beam then travels through scan lens (green) and tube lens (red), the collection optics (yellow) and finally the objective (cyan).
+Next, the beam travels through an open mechanical 6 mm diameter shutter (LS6S2ZM1, Vincent Associates).
+When closed, the laser reflected on the shutter reflective blades is sent to another beam block.
+Beam blocks are not perfect absorber, so we can use advantageoulsy the weak back scattered light from the beam block to calibrate the Pockels cell.
+In our set-up, a photodiode (PDA36A2, Thorlabs) is thus facing the beam block.
+Following the shutter, the beam travels though a $2\times$ telescope (GBE02-B, Thorlabs) doubling its diameter.
+Past the telescope, the beam is then reflected off several mirrors in a periscope configuration before entering a custom aluminium box housing, mounted to a 95 mm optical rail (XT95 serie, Thorlabs), that houses the two scanning mirrors (CRS8K/6215H scanning mirror Set, Novanta), shown in blue in  Fig.~\ref{fig1}C.
+Leaving the scanners, the beam then travels first through the scan lens (green) and tube lens (red), pass through the long pass dichroic mirror of the collection box assembly  (yellow) and finally the objective (cyan).
 The design of these components is covered in the next paragraphs.
-The steering mirrors in our system are all silver mirrors from Thorlabs.
+The steering mirrors in our system are all P01 silver protected mirrors from Thorlabs.
 Silver mirrors contribute minimally to dispersion which is inevitable when light travels through various optical components.
@@
 \subsection*{Optical design: Scan and tube lens}
-When using infinity-corrected objectives, the incident light has to be collimated at the back aperture of the objective.
-In other words, the light rays have to arrive as parallel beams at the back aperture of the objective.
-When using a collimated laser beam, then scan and tube lens must be configured as a telescope with the scanning mirrors positioned in the conjugated plane of objective back aperture.
-A typical scan angle of $\pm10\text{ deg}$ positioned at the focal point of the scan lens, combined with two inch diameter optics, determines the scan lens focal length to $f_S=100\text{ mm}$ (cf.
+Like for all modern microscopes, infinity-corrected objectives are being used in this design.
+The incident laser light has to be collimated at the back aperture of the objective.
+For this reason, scan and tube lens must be carefully configured as a telescope.
+Additionally, to guaranty the laser beam enters the objective back-aperture with the same amount of clipping, the scanning mirrors must be positioned in the conjugated plane of objective back-aperture.
+In many commercial infinity corrected microscope designs, the distance between the tube lens and the objective can be chosen within a certain range.
+In our design however, we added the constraint of positioning the objective and tube lens in a telescope, i.e.
+the distance between each is the sum of their focal.
+While this has no real impact, it prepares the assembly for possible upgrade where methods such as remote focusing could be used \cite{Botcherby2007, Botcherby2012, Sofroniew2016}.
+Our design was initiated by choosing a proper focal length for the custom assembly serving as a scan lens.
+We settled on a focal length $f_S=100\text{ mm}$  scan lens built from two inch diameter components \cite{Yao2023}.
+This choice was influenced by the availability of off the shelves lenses and the specific scanning range of the scanners (typically $\pm10\text{ deg}$)  (cf.
 Fig.~\ref{fig1}A).
-To fill the back aperture of the objective with our laser beam, we aimed for a combined magnification of $M=3.75\times=f_T/f_S$.
-This determined the focal length of the tube lens to $f_T=375\text{ mm}$.
-This reduces the scan angles at the back aperture of the objective to $20\text{ deg}/3.75\approx 5.3\text{ deg}$ and with a given objective (e.g.
-Nikon $16\times$ with $f_O=12.5\text{ mm}$) this determines the expected approximate field of view ($\approx 1.2\text{ mm}$).\newline
-We assembled the scan and tube lenses as lens groups from off-the-shelf parts, using the same elements as in \cite{Yao2023}, and further optimizing lenses and spacing in Zemax (an optics design software).
-Details are provided below.
-After optimization, the focal lengths of scan and tube lens were 99 mm and 378 mm respectively, deviating around 1\% from their target values (Zemax simulation at 920 nm).
+To fill the back aperture of the objective with our laser beam, we aimed for a combined magnification of $M=3.75\times=f_T/f_S$, making the focal length of the tube lens  $f_T=375\text{ mm}$.
+With these choices, the resulting scanning angles at the back aperture of the objective are $\pm10\text{ deg}/3.75\approx\pm2.7\text{ deg}$ and with our chosen objective (Nikon $16\times$ with $f_O=12.5\text{ mm}$) the expected approximate is field of view diameter is $\approx 1.2\text{ mm}$).\newline
+The tube lens was also assembled as a lens group from off-the-shelf parts. The  relative positions of the two groups components were  optimized using Zemax . Details are provided below.
 %
@@
 Fig.~\ref{fig2}A shows the propagation of light rays for various deflection angles of the scanning mirrors, and how the beams converge on a line under the objective.
-The Zemax design was then exported into CAD, and the optomechanics assembled around it, see Fig.~\ref{fig2}B.
+Note that in our simulation, in the absence of a model for our commercial objective, we replaced it by a perfect geometrical lens.
+Once the separation between optical elements was optimized, a model was exported in CAD (Autodesk Inventor and Fusion 360), and the optomechanics was designed around it, see Fig.~\ref{fig2}B.
 The CAD design and lens groups are highlighted in Fig.~\ref{fig2}B,C (see Fig.~\ref{fig1}C of a photograph of the same part of the instrument).
-The key property that we optimized when designing the excitation system was an essentially flat, and diffraction limited focal volume across a wide range of deflection angles of the scanning mirrors.
+The key properties that we optimized when designing the excitation system was an essentially flat, and diffraction limited focal point across the deflection angle range of the scanning mirrors.
 Fig.~\ref{fig2}D shows an estimate of the two-photon point spread function (PSF-2p), computed as the square of the Huygens PSF in Zemax.
-The maximum scan angle of $\pm 10\text{ deg}$ is limited by vignetting of the two inch diameter optics.
-Analyzing the PSF-2p across optical deflection angles, Fig.~\ref{fig2}E, suggests very small field curvature.
+Analyzing the PSF-2p across optical deflection angles, Fig.~\ref{fig2}E, suggests very small field curvature if the objective used behaves close to a perfect geometrical lens.
 In this simulation, the axial resolution was $\delta z = 5.0\text{ \textmu m}$, and the radial resolution $\delta r = 0.75\text{ \textmu m}$ across a wide range of deflection angles.\newline
@@
 We chose the specific lenses and their spacing based on availability from established optics suppliers and the simulation of dozens of combinations in Zemax.
-The tube lens is inspired by a Petzval design \cite{Smith2007, Kidger2001}, consisting of a pair of achromatic doublets with the same orientation, $2\times$ ACT508-750-A, Thorlabs.
-We found in simulation that this design performed better than a Pl\"ossl pair where the doublets are symmetric (this was observed by others as well \cite{Hong2022, Bumstead2018, Mayrhofer2015}).\newline
+The tube lens is inspired by a Petzval lens design \cite{Smith2007, Kidger2001}, consisting of a pair of achromatic doublets with the same orientation, $2\times$ ACT508-750-A, Thorlabs, a design performing better than a Pl\"ossl pair as observed by others as well \cite{Hong2022, Bumstead2018, Mayrhofer2015}.\newline
 The two lens groups combined provide a magnification of $M=3.75\times$ to produce a beam that slightly underfills the back aperture of the Nikon NA 0.8 $16\times$ LWD objective, effectively reducing its excitation NA to $\approx0.7$.
-This has various advantages for \invivo imaging (see discussion).
+This can be advantageous for \invivo Calcium imaging in certain conditions (see discussion).
 Of further note, we used a piezoelectrical collar to mount the objective.
@@
 %
-The aim of the collection optics is to collect the most florescence with a small sized sensor.
-For our system, this is a 5 mm diameter window of the Hamamatsu H16201-40 Photomultiplier tube (PMT) module.
-This is achieved by imaging the back aperture of the objective on the aperture of the PMT.
-Since two-photon microscopes form a picture scanning pixel by pixel, there is no strict requirement for the collection optics to be image forming \cite{Tsai2015}.
-They should, however, collect as much fluorescent light as possible.
+The aim of the collection optics is to bring the fluorescence signal coming out the back aperture of the objective toward the  5 mm diameter photocathode of the Hamamatsu H16201-40 Photomultiplier tube (PMT) module.
 %
@@
 These rays were computed for the green emission light path.
-Small letters denote filters: a is a FF665-Di02-40x55; b: an IR block (not shown in the Zemax simulation); c: FF562-Di03-40x52 and d: FF01-525/45-32 (BrightLine; AVR Optics).
+Small letters denote filters: a is a FF665-Di02-40x55; b: an NIR blocking filter (FF01-680/SP-50 ) (not shown in the Zemax simulation); c: FF562-Di03-40x52 and d: FF01-525/45-32 (BrightLine; AVR Optics).
 Small numbers  denote lenses.
@@
 b blocks residual IR excitation light $\lambda>680\text{ nm}$ (FF01-680/SP-50), and e is a FF01-600/52-32 filter for the red channel.
-\textbf{C)} Shown is the angle collection graph of the collection optics, which shows the fraction of collected light as function of the angle to the optical axis.
+\textbf{C)} Shown is the angle collection graph of the collection optics, which shows the fraction of collected light as function of the angle it emerges from the objective back-aperture.
 This was simulated in Zemax for the design in A.
@@
 %
-We incorporated four design principles into our assembly: (1) Fluorescence light must fall approximately perpendicularly on the optical filters for the filters to work correctly.
-Narrow filters are particularly susceptible to this.
-Although light emitted from the image plane of an infinity-corrected objective is collimated as it returns from the sample, actual fluorescence weakly diverges due to scattering and diffraction in the material between image plane and objective (e.g.
-brain tissue \cite{Zipfel2003, Taddeucci1996}).
-The detector assembly should therefore be placed as close as possible to the objective where fluorescent light will be nearly collimated.
-This placement reduces sensitivity to spurious light and allows IR light to travel through the collection optics unimpeded, while fluorescent light is reflected into the optical assembly.
-This arrangement also has the advantage that possible astigmatism, introduced by curvature of the dichroic in the reflected light, only affects the collection optics which does not have to form an image.
-(2) The collection lens should be large to maximize the collection of as much fluorescent light as possible.
-This implies that the collection lens should follow the dichroic mirror as closely as possible.
-(3) Having the collected photons collimated on the aperture of the photomultiplier tubes reduces the sensitivity of the system on surface inhomogeneities of the detector\cite{Tsai2002, Young2015}.
-In scanning microscopy, an image is produced as a time series of intensities.
-It is therefore more important to collect a consistently large portion of fluorescent light, rather than to minimize aberration in the collection optics.
-We therefore optimized relative illumination as function of the field angle in Zemax.
-(4) All dichroic mirrors and optical band-pass filters have finite performance.
-It it therefore advantageous to combine multiple band-pass filters to isolate relevant fluorescence ranges.
+We incorporated several design principles into our assembly: (1) The collection lens should be large to maximize the collection of as much fluorescent light as possible.
+This implies that the collection lens should also follow the NIR long-pass dichroic mirror as closely as possible.
+(2) The collected light should be then guided through an elongated but diameter limited space where  another dichroic and filters (Green/Red) will be located.
+It should therefore propagate as close to parallel as possible from the collection lens axis.
+This also favors satisfactory performance of the optical filters which are often specified for zero degree incidence.
+(3) Having the collected photons close to collimated on the aperture of the photomultiplier tubes reduces the sensitivity of the system to surface inhomogeneities of the detector\cite{Tsai2002, Tsai2015, Young2015}.\newline
 We aimed to record fluorescence from two well-separated spectral ranges, a green ($525\pm25\text{ nm}$) and a red channel ($600\pm25\text{ nm}$).
-Beyond an IR block in the collection optics, we chose to only use simple long-pass filters, which means that the red channel is operated in the transmission, and the green channel in the reflection mode (cf.
-Fig.~\ref{fig1}A).\newline
-With these considerations in mind, we assembled the collection optics from off-the-shelf components that were optimized in Zemax, building on previous work \cite{Tsai2002,Tsai2015}.
+Zemax was used to select the lenses of the collection unit and their relative position, while attempting to maximize the collection of light by the detectors.
 A cartoon is shown in Fig.~\ref{fig3}A.
-The colors illustrate different sources of fluorescent light.
+The colors illustrate different point sources of fluorescent light in the sample plane.
 Notice the mild divergence, and approximately collimated beams that enter the aperture of the photomultiplier tube.
 As previously, this design was exported into CAD, and the optomechanics assembled around it, see Fig.~\ref{fig3}B.
-Fig.~\ref{fig3}C shows a simulation in Zemax demonstrating that essentially all light up to $\approx\pm 8\text{ deg}$ is arrives at the aperture of the photomultiplier tubes.
+Fig.~\ref{fig3}C shows a simulation in Zemax demonstrating that our design brings nearly all the light escaping the objective back-aperture with an angle below  $\approx8\text{ deg}$ to the aperture of the photomultiplier tubes.
 
 \subsection*{Mechanical design}
-As mounting system of our microscope, we chose a standard 8 inch thick optical table.
-The design was done in CAD, and the results shown in Fig.~\ref{fig1}B.
+Our microscope was mounted on a 16 inch thick optical table.
+The design was done in CAD Inventor and Fusion 360 (Autodesk), and the results shown in Fig.~\ref{fig1}B.
 The aim was a mechanical assembly that uses as few custom parts as possible.
-We discuss this further in the discussion section.
-The components in the CAD files can be assembled and aligned by an experienced researcher in a few days.
+This is relatively easy to achieve for the excitation path, but hardly practical for the collection system which require to be both efficient and light tight.
+The components shown in the CAD files can be assembled and aligned by an experienced researcher in a few days.
 When used for teaching, a careful assembly and alignment is viable with about a week of work.
@@
 An example are the aluminium parts that hold the large dichroic mirrors and optical filters in the collection optics.
-After drilling the apertures for light to pass through, not much metal is left on the part which can lead to warping and distortions.\newline
+After drilling the apertures for light to pass through, little metal is left on the part which can potentially lead to warping and distortions if not machined with precision.\newline
 Finally, we want to emphasize the difference between a theoretically optimal design in Zemax and finite tolerances in real-world optomechanical parts.
 It is key for a good microscope design to be robust against such errors.
-In our design, the objective is fixed, while the mirrors, the tube and scan lens assemblies, and the scanning mirrors can move along the optical axis for alignment.
+In our design, the objective is fixed, while the mirrors, the tube and scan lens assemblies, and the scanning mirrors can be re-positioned along the optical axis for alignment.
 This allows the mechanical components sufficient degrees of freedom to optically align all key parts of the microscope.
@@
 
-\subsection*{Electronic design}
+\subsection*{Scanners power supplies and controllers enclosure}
+
+The scanning mirrors are active components.
+They are controlled by two circuit boards supplied with external power.
+The driver board of the resonant scanner does not dissipate much heat, but the drivers of the slow galvanometer can become warm in normal operation.
+This heat needs to be dissipated.
+We mount the circuit boards in a custom electronics box (Gold Box, Acopian), making sure to use heat transfer compound between the circuit boards and the aluminium box, and to mount them securely together with screws.
+At time of purchase, we requested the controller of the slow galvanometer to be configured for usage at $\pm 28\text{ V}$ (the manufacturer default is $\pm 24\text{ V}$ ).
+This overall improves dynamical properties.
+The controller requires three voltage inputs, respectively -28 V, 0 V, and +28 V.
+The 0 V is also grounded.
+The second power supply provides 12 V for the resonant scanner.
+It is beneficial to choose a power supply that can stably produce these currents for years.
+We have made good experiences with Agilent E3630A, and the Instek GPD-3303D.
+Importantly, double check the power generator with a good multimeter before connecting the driver boards.
+Please also see \nameref{S1_Appendix} for a detailed illustration.
+
+\subsection*{PMTs control circuit}
 %
@@
 These leads are color-coded.
-We designed a small circuit for resistance programming of the gain, and to display the gain setting voltage on small digital panel meter (Murata DMS-20PC).
+A small circuit for resistance programming of the gain was design which also displays the gain setting voltage on small digital panel meter (Murata DMS-20PC).
 The circuit for controlling two channels (red and green) is shown in Fig.~\ref{fig4}A.
@@
 The gain voltage is then fed back to the module via the white input line, and used for display on the panel meter.
-We added a 12k resistor between the PMT module, and the potentiometer to limit the control voltage which is safer for the PMT.
-Optimal signal-to-noise ratio for our systems is usually $\approx 0.7-0.8\text{ V}$.
+A 12k resistor between the PMT module and the potentiometer was added to limit the control voltage which is safer for the PMT.
+Optimal signal-to-noise ratio for the PMTs is usually $\approx 0.7-0.8\text{ V}$.
 The panel meter needs an additional +5 V supply that we obtain from the +15 V via a resistive divider.
 The meter is operating in Single-Ended Input Conﬁgurations, see Fig.~\ref{fig4}B.
-Due to the simplicity of this circuit, we do not solder this on a circuit board, but rather in a prototype development box directly, see Fig.~\ref{fig4}C, which is attached to the rig.\newline
-This circuit and the driver boards for the xy scanners need a well regulated power supply, as any noise would directly translate to image noise and distortions.
-We use an Agilent E3630A supply.
+Due to the simplicity of this circuit, we do not solder this on a circuit board, but rather in a prototype development box directly, see Fig.~\ref{fig4}C, which is attached to the rig.
+This circuit needs a well regulated power supply.
+For convenience, we also use an Agilent E3630A.
 The PMT outputs were amplified with two Transimpedance Amplifiers (TIA60, Thorlabs), and directly connected to the data acquisition system.
@@
 \subsection*{Ancillary hardware}
-Our microscope is controlled with ScanImage \cite{Pologruto2003} running on a Windows PC and this data acquisition (DAQ) system was provided by Vidrio.
-In our experience, this reduces software issues.\newline
-A typical femtosecond pulsed laser source is expensive.
-Ti:Sapphire lasers are tunable, but particularly expensive.
+Our microscope is controlled with ScanImage \cite{Pologruto2003} running on a Windows PC equipped with a data acquisition system (DAQ), both from the same supplier (MBF Bioscience).\newline
+Typical  Ti:Sapphire tunable femtosecond pulsed laser source can be expensive.
 For the work demonstrated here, we used a fixed-wavelength femtosecond laser systems, based on fiber technology (e.g.\cite{Bueno2019,Limpert2006,Wise2012,Young2015}).
-Operating at a fixed wavelength, these systems come at a fraction of the cost of a more traditional tunable Ti-Sapphire laser, and they take up significantly less real estate on an optical table.
+These systems come at a fraction of the cost, and they take up significantly less real estate on an optical table.
 The laser was controlled with the same PC as ScanImage through a USB connection.
-As the beam travels through a number of crystals, lenses, and mirrors with various chromatic properties, significant dispersion is introduced which increases pulse length, reducing the two-photon absorption efficiency.
+As the beam travels through a number of crystals, lenses, and mirrors with various chromatic properties, significant dispersion is introduced which increases pulse duration, reducing the two-photon absorption efficiency.
 It is possible to compensate for the group-delay dispersion of the microscope by giving the short-wavelength components a sufficient head start so that blue and red components arrive at the sample at the same time.
@@
 Regarding light transmission, we found the Spark laser to produce $\approx 2.1\text{ W}$ of light.
-After the wave plate and beamsplitter cube, $\approx 1.0\text{ W}$ enter the Pockels cell (cf.
+After the half-wave plate and beamsplitter cube, $\approx 1.0\text{ W}$ enter the Pockels cell (cf.
 Fig.~\ref{fig1}B).
 The Pockels cell is rotated so that the control voltage produces the largest dynamic range of transmitted laser power (we go through the alignment procedure in depth below).
-At maximum transmission setting of the Pockels cell, we obtain $\approx 260\text{ mW}$ below the objective, corresponding to $\approx1/4$ of the available light.
-In our hands, this is more than enough for imaging.
+At maximum transmission setting of the Pockels cell, we obtain $\approx 260\text{ mW}$ below the objective, a large value, as it is exceeding the maximum recommended power for cortical imaging mouse \cite{Song2017}.
 All pictures presented in this article were obtained with $\approx 15\text{ mW}$ below the objective.
@@
 We first determined the size and properties of the field of view with a 100~\textmu m grid (R1L3S3P, Thorlabs), imaged using a Fluorescein in water film through a standard \#1.5 ($\approx170\text{ \textmu m}$ thick) coverslip, see Fig.~\ref{fig5}A.
-The field of view was $d\approx1.3\text{ mm}$ along the diagonal, $A\approx 1\text{ mm}^2$ in area and the field curvature below the thickness of a thin Fluorescein film $\lesssim 10\text{ \textmu m}$.
-This is consistent with our earlier Zemax simulations.
-When measuring the magnification $M$ in \textmu m/px across the field of view, we observed small deviations of $\Delta M \approx 0.1\text{ \textmu m/px}$ in the center when compared to the edges, while the overall range of magnifications across the field of view was tight, see Fig.~\ref{fig5}B.
-The average magnification is $M=2.77\pm0.04\text{ \textmu m/px}$, which suggests a deviation from a perfect f-Theta system of $\Delta M/M = 0.1/2.8 \approx 4\%$.
-Next, we imaged a uniform bath of Fluorescein, see Fig.~\ref{fig5}C.
-This is a combined measure of the quality of excitation and the efficiency of the collection optics across the field of view.
-Within the central $700\text{ \textmu m} \times 700\text{ \textmu m}$ region, the signal deviated from uniformity within $\approx 13\%$ ($\pm 1 \text{ standard deviation}$) suggesting a relatively flat field, see Fig.~\ref{fig5}D, E.
-Following these measurements, we imaged a bead sample of 0.2\microns diameter in 1\% Agarose (Dragon Green beads; Bangs Laboratories) to measure axial and radial PSFs.
-The sample is shown in Fig.~\ref{fig5}F.
-Averaging across the $N=38$ beads in this volume, we measured a radially symmetric full-width-at-half-maximum of $\delta r\approx760\pm30\text{ nm}$, see Fig.~\ref{fig5}G,H, and axially $\delta z \approx 5.4\pm0.9\text{ \textmu m}$, see Fig.~\ref{fig5}I.
-The theoretical resolution limits\cite{Tsai2002} for our system, underfilled to $\text{NA}=0.7$ at $\lambda=920\text{ nm}$ and water immersion ($n=1.33$) were radially FWHM of $\delta r=0.6\,\lambda/\text{NA}=780\text{ nm}$ and axially $\delta z = 2\,\lambda n/\text{NA}^2=5.0\text{ \textmu m}$.
-This is consistent with our earlier simulations in Zemax (cf.
-Fig.~\ref{fig2}), and suggests that our microscope is operating very close to the diffraction limit, and its design specifications.
+The field of view exceeded $\approx 1\text{ mm}^2$ ($d\approx1.3\text{ mm}$ along the diagonal), and the field curvature was below the thickness of the thin Fluorescein film $\lesssim 10\text{ \textmu m}$.
+The maximum scan angle was limited by vignetting of the two inch diameter optics (we discuss this further in the teaching section).
+When measuring the local scale in \textmu m/px at low magnification across the field of view, we observed small deviations of $\Delta S \approx 0.1\text{ \textmu m/px}$ in the center when compared to the edges, while the overall range of magnifications across the field of view was tight, see Fig.~\ref{fig5}B.
+The average scale is $S=2.77\pm0.04\text{ \textmu m/px}$, which suggests a deviation from uniformity of $\Delta S/S = 0.1/2.8 \approx 4\%$.
 %
@@
 %
-%
+Next, we imaged a uniform bath of Fluorescein, see Fig.~\ref{fig5}C.
+This measures the quality of excitation and the efficiency of the collection optics across the field of view.
+Within the central $700\text{ \textmu m} \times 700\text{ \textmu m}$ region, the signal deviated from uniformity within $\approx 13\%$ ($\pm 1 \text{ standard deviation}$), see Fig.~\ref{fig5}D, E.
+Following these measurements, we imaged a bead sample of 0.2\microns diameter in 1\% Agarose (Dragon Green beads; Bangs Laboratories) to measure axial and radial PSFs.
+The sample is shown in Fig.~\ref{fig5}F.
+Averaging across the $N=38$ beads in this volume, we measured a radially symmetric full-width-at-half-maximum of $\delta r\approx760\pm30\text{ nm}$, see Fig.~\ref{fig5}G,H, and axially $\delta z \approx 5.4\pm0.9\text{ \textmu m}$, see Fig.~\ref{fig5}I.
+The theoretical resolution limits\cite{Tsai2002} for our system, underfilled to $\text{NA}=0.7$ at $\lambda=920\text{ nm}$ and water immersion ($n=1.33$) were radially FWHM of $\delta r=0.6\,\lambda/\text{NA}=780\text{ nm}$ and axially $\delta z = 2\,\lambda n/\text{NA}^2=5.0\text{ \textmu m}$.
+This is consistent with our earlier simulations in Zemax (cf.
+Fig.~\ref{fig2}), and suggests that our microscope is operating very close to the diffraction limit, and its design specifications.
+
 \subsection*{Imaging performance}
@@
 
-Confident that the system operates as intended, we next imaged a number of representative samples that are easily available in any teaching lab, namely plant material, a histological and a strongly scattering sample, see Fig.~\ref{fig6}.
+Confident that the system operates as intended, we next imaged a number of representative samples that are readily available to us, namely plant material, a histological and a strongly scattering sample, see Fig.~\ref{fig6}.
 The first samples was a Dandilion flower (Taraxacum officinale) \cite{Rupprecht2018}.
@@
 Neurons in this organism express the fluorescent protein GCaMP6f in their nuclei whose green fluorescence strongly depends on the cellular concentration of Calcium ions.
-We imaged a 5-day old larva in 2\% low melting point Agarose in E3 medium, see Fig.~\ref{fig7}.
+We imaged a 5-day old larvaimmobilized in 2\% low melting point Agarose in E3 medium, see Fig.~\ref{fig7}.
 We first performed a volumetric scan of the organism, Fig.~\ref{fig7}A shows a rendering in Fiji \cite{Schindelin2019}, and then focused on a plane with a large number of visible neurons, Fig.~\ref{fig7}B.
@@
 Here, students used the fluorescence at fixed laser power for different values of dispersion compensation to infer the laser pulse width.
-This is possible because the efficiency of two-photon fluorescence depends inversely on the pulse duration \cite{Denk1990}.
+This is possible because the efficiency of two-photon fluorescence depends inversely on the pulse duration \cite{Denk1990, Zipfel2003}.
 The laser's built-in dispersion compensation can give the short-wavelength components a head start such that after delays in the optical path, blue and red components can arrive at the sample at the same time.
@@
 Here, $\alpha=16\log(2)^2$.
-This equation can be derived by expressing the Gaussian pulse shape in the Fourier domain, applying a phase-shift along the laser path to quadratic order in the frequency \cite{Young2015}, and computing the result in the time domain.
+This equation can be derived by expressing the Gaussian pulse shape in the Fourier domain, applying a phase-shift along the laser path to quadratic order in the frequency, and computing the result in the time domain.
 Deriving this expression is a fun at-home exercise.
@@
 Physically moving the objective along the optical axis allows to image several planes.
-The time required by the piezoelectric collar to stabilize is on the scale of 10 ms.
-Imaging faster processes requires a different approach, e.g.
-with an electrically tunable lens (ETL).
+The time required by the piezoelectric collar to stabilize can reach the scale of 10 ms when using large and heavy objectives.
+In these cases, volumetric imaging is  best achieved using a ramp where the objective is constantly moving at the same speed, rather than doing steps of constant height for every planes.
+Electrically tunable lens (ETL) can be an alternative to the piezoobjective.
 These lenses have a variable focal length, usually from around 10 cm to infinity, that can be set with a control voltage within $<1\text{ ms}$.
-A convenient spot for an ETL might be right before the scan assembly, while care should be taken to not focus the beam on the scanning mirrors to avoid damage.\newline
+A convenient spot for an ETL might be right before the scan assembly, while care should be taken to not focus the beam on the scanning mirrors to avoid damage.
+\newline
 (3) Estimating the pulse duration suggests non-linear dispersion that we cannot correct.
@@
 If available, other light sources might be worth exploring.\newline
-(4) We made the design choice to place the resonant and slow scanning mirrors close together in space while the plane equidistant between the rotational axis of both scan mirrors is conjugate to the back aperture of the objective.
-This is a compromise that is used by others as well (e.g.
+(4) We made the design choice to use a  resonant and slow scanning mirror pair positioned close together in the same mount.
+Rasther than the mirrors themselves, it is the plane equidistant between the rotational axis of both scan mirrors that is conjugated to the back aperture of the objective.
+This is a compromise that is used by many (e.g.
 Thorlabs' Cerna or earlier designs \cite{Rosenegger2014, Tan1999, Nguyen2001}).
-Other microscope designs add a pair of lenses between the slow and resonant scanning mirrors to position them in conjugated planes.
+Alternative microscope designs add a pair of lenses between the slow and resonant scanning mirrors to position them in conjugated planes.
 Our design choice significantly simplifies the design and reduces the amount of glass between laser and sample to reduce dispersion.
-It does, however, introduce a Barrel distortion that becomes visible at low magnifications.\newline
+It does, however, introduce a slight Barrel distortion that becomes visible at low magnifications.\newline
 (5) The fixed $2\times$ beam expander can be replaced with variable/zoom beam expander that allows a user to dial in a particular beam magnification to tweak the point spread function for a particular application\cite{Smith2019}.
-We have used this in some of our earlier designs, e.g.
-\cite{Song2017}.
 While a high numerical aperture is beneficial for high axial resolution and improved separation of somatic and neuropil signals \cite{Kerr2008, Gobel2007}, the large angles at which excitation light is brought into the brain results in longer paths for the light to take.
@@
 That said, even when underfilled by the excitation beam, a large NA of the objective is beneficial to collect as much fluorescent light as possible.\newline
-(6) It can be advantageous to combine the two-photon system with wide-field imaging.
+(6) It can be interesting to some to combine the two-photon system with wide-field imaging.
 To this end, the two inch mirror above the collection optics can be replaced with a 800 or 900 nm short-pass filter followed by a tube lens and a camera.
@@
 While this is relatively straightforward to do \cite{Rosenegger2014}, widefield epipfluorescence is harder to realize.\newline
-(7) The collection optics are designed to have an average optical density $>4$ in the range between 400 nm and 460 nm.
+(7) Our fluorescence filters have an average optical density $>4$ in the range between 400 nm and 460 nm.
 This is advantageous for use in virtual reality systems, because light leaving a projector can be filtered to this range before projected on a dome surrounding the objective and animal.
 We have successfully used budget friendly colored glass filters in front of the projector (Schott BG25 or Schott BG5), and long-pass colored glass (Schott RG780) to block projector light from entering the excitation path \cite{Dombeck2007}.
-Combined with a light shield around the objective, such a projection system will only minimally interfere with imaging (e.g.
+Combined with a light shield around the objective \cite{Dombeck2010}, such a projection system will only minimally interfere with imaging (e.g.
 \cite{Nieh2021}).
 This is a useful range for visual experiments in mice, but if other model organisms are desired, the optical filters need to be adjusted accordingly.\newline
-(8) Relatedly, the collection optics described here, built from lenses with two inch diameter, can accept fluorescent light leaving the objective back aperture in the range of $\pm 8\text{ deg}$.
-If one intends to image at larger angles, larger lenses in the collection optics can be beneficial \cite{Tsai2015} and some of our microscopes use a collection design with three inch diameter optics \cite{Song2017, Nieh2021}.
-In our experience, it is difficult to push this further, because large angles reduce the effectiveness of the dichroic mirrors and band-pass filters.\newline
-(9) Parts of our microscope can be replaced with commercial products.
-For example, we have used commercial telecentric scan lenses in the past \cite{Song2017, Rich2024}.
-These come at higher cost and introduce higher dispersion, but exhibit very low field curvature.
+(8) Parts of our microscope can be replaced with commercial products.
+For example, we have used commercial telecentric scan lenses in the past \cite{Song2017, Rich2024} in combination with a three inch diameter tube lens.
+These come at higher cost and introduce higher dispersion, but exhibit very low field curvature on a very large field of view.
 While low field curvature is not always considered the highest priority in neuroscience applications, this can be a useful substitution.\newline
-(10) Regarding the mechanical design, we decided to not mount the microscope on an xy translation stage.
-This means that the sample has to be moved laterally relative to the microscope.
-We did, however, include a z-adjustment through a piezoelectric collar for the objective.
-This significantly simplifies measurements of point spread functions, and allows rapid volumetric imaging which we consider worth the extra cost.
-Our laboratory had great success with this design, and we have developed stages for mounting animals that incorporate drives for xy motion.
-Mounting the microscope itself on an xyz controller that can carry its weight, and precisely aligning the optical path to be parallel to x, y and z displacement is possible but will incur extra cost.\newline
-(11) To aid mechanical stability, the aluminium plate forming the base of the head of the microscope could be replaced with a steel plate, or a thicker piece of aluminium, that is less prone to vibrations when bumped into.
+(9) To aid mechanical stability, the aluminium plate forming the base of the head of the microscope could be replaced with a steel plate, or a thicker piece of aluminium, that is less prone to vibrations when bumped into.
 This would also be important if one wanted to extend the microscope head to provide even more space around the objective.
@@
 
+\bibitem{Rickgauer2014}
+Rickgauer JP, Deisseroth K, Tank DW.
+Simultaneous cellular-resolution optical perturbation and imaging of place cell firing fields.
+Nat Neurosci.
+2014 Dec;17(12):1816-24.
+doi: 10.1038/nn.3866.
+Epub 2014 Nov 17.
+PMID: 25402854; PMCID: PMC4459599.
+
+\bibitem{Nikolenko2008}
+Nikolenko V, Watson BO, Araya R, Woodruff A, Peterka DS, Yuste R.
+SLM Microscopy: Scanless Two-Photon Imaging and Photostimulation with Spatial Light Modulators.
+Front Neural Circuits.
+2008 Dec 19;2:5.
+doi: 10.3389/neuro.04.005.2008.
+PMID: 19129923; PMCID: PMC2614319.
+
+\bibitem{Packer2012}
+Packer AM, Peterka DS, Hirtz JJ, Prakash R, Deisseroth K, Yuste R.
+Two-photon optogenetics of dendritic spines and neural circuits.
+Nat Methods.
+2012 Dec;9(12):1202-5.
+doi: 10.1038/nmeth.2249.
+Epub 2012 Nov 11.
+PMID: 23142873; PMCID: PMC3518588.
+
+\bibitem{Sofroniew2016}
+Sofroniew NJ, Flickinger D, King J, Svoboda K.
+A large field of view two-photon mesoscope with subcellular resolution for in vivo imaging.
+Elife.
+2016 Jun 14;5:e14472.
+doi: 10.7554/eLife.14472.
+PMID: 27300105; PMCID: PMC4951199.
+
 \bibitem{Song2017}
@@
 
-\bibitem{Rickgauer2014}
-Rickgauer JP, Deisseroth K, Tank DW.
-Simultaneous cellular-resolution optical perturbation and imaging of place cell firing fields.
-Nat Neurosci.
-2014 Dec;17(12):1816-24.
-doi: 10.1038/nn.3866.
-Epub 2014 Nov 17.
-PMID: 25402854; PMCID: PMC4459599.
-
-\bibitem{Sofroniew2016}
-Sofroniew NJ, Flickinger D, King J, Svoboda K.
-A large field of view two-photon mesoscope with subcellular resolution for in vivo imaging.
-Elife.
-2016 Jun 14;5:e14472.
-doi: 10.7554/eLife.14472.
-PMID: 27300105; PMCID: PMC4951199.
+\bibitem{Kazemipour2019}
+Kazemipour A, Novak O, Flickinger D, Marvin JS, Abdelfattah AS, King J, Borden PM, Kim JJ, Al-Abdullatif SH, Deal PE, Miller EW, Schreiter ER, Druckmann S, Svoboda K, Looger LL, Podgorski K.
+Kilohertz frame-rate two-photon tomography.
+Nat Methods.
+2019 Aug;16(8):778-786.
+doi: 10.1038/s41592-019-0493-9.
+Epub 2019 Jul 29.
+PMID: 31363222; PMCID: PMC6754705.
 
@@
 
+\bibitem{Janelia2024}
+Modular In Vivo Multi-photon Microscope 2.2 \url{https://www.janelia.org/open-science/mimms-22-2024}
+
+\bibitem{Botcherby2007}
+Botcherby EJ, Juskaitis R, Booth MJ, Wilson T. Aberration-free optical refocusing in high numerical aperture microscopy. Opt Lett. 2007 Jul 15;32(14):2007-9. doi: 10.1364/ol.32.002007. PMID: 17632625.
+
+\bibitem{Botcherby2012}
+Botcherby EJ, Smith CW, Kohl MM, Débarre D, Booth MJ, Juškaitis R, Paulsen O, Wilson T.
+Aberration-free three-dimensional multiphoton imaging of neuronal activity at kHz rates.
+Proc Natl Acad Sci U S A.
+2012 Feb 21;109(8):2919-24.
+doi: 10.1073/pnas.1111662109.
+Epub 2012 Feb 6.
+PMID: 22315405; PMCID: PMC3286923.
+
 \bibitem{Kidger2001}
@@
 PMID: 26072755; PMCID: PMC4523368.
-
-\bibitem{Zipfel2003}
-Zipfel WR, Williams RM, Webb WW. Nonlinear magic: multiphoton microscopy in the biosciences. Nat Biotechnol. 2003 Nov;21(11):1369-77. doi: 10.1038/nbt899. PMID: 14595365.
-
-\bibitem{Taddeucci1996}
-Taddeucci A, Martelli F, Barilli M, Ferrari M, Zaccanti G. Optical properties of brain tissue. J Biomed Opt. 1996 Jan;1(1):117-23. doi: 10.1117/12.227816. PMID: 23014652.
 
@@
 
+\bibitem{Zipfel2003}
+Zipfel WR, Williams RM, Webb WW. Nonlinear magic: multiphoton microscopy in the biosciences. Nat Biotechnol. 2003 Nov;21(11):1369-77. doi: 10.1038/nbt899. PMID: 14595365.
+
 \bibitem{Saidi2023}
@@
 
+\bibitem{Tan1999}
+Tan YP, Llano I, Hopt A, Würriehausen F, Neher E.
+Fast scanning and efficient photodetection in a simple two-photon microscope.
+J Neurosci Methods.
+1999 Oct 15;92(1-2):123-35.
+doi: 10.1016/s0165-0270(99)00103-x.
+PMID: 10595710.
+
 \bibitem{Smith2019}
@@
 
+\bibitem{Dombeck2010}
+Dombeck DA, Harvey CD, Tian L, Looger LL, Tank DW.
+Functional imaging of hippocampal place cells at cellular resolution during virtual navigation.
+Nat Neurosci.
+2010 Nov;13(11):1433-40.
+doi: 10.1038/nn.2648.
+Epub 2010 Oct 3.
+PMID: 20890294; PMCID: PMC2967725.
+
 \bibitem{Rich2024}
@@
 
-\bibitem{Tan1999}
-Tan YP, Llano I, Hopt A, Würriehausen F, Neher E.
-Fast scanning and efficient photodetection in a simple two-photon microscope.
-J Neurosci Methods.
-1999 Oct 15;92(1-2):123-35.
-doi: 10.1016/s0165-0270(99)00103-x.
-PMID: 10595710.
-
 \bibitem{Zong2022}
@@
 PMID: 35305313; PMCID: PMC8970296.
-
-\bibitem{Janelia2024}
-Modular In Vivo Multi-photon Microscope 2.2 \url{https://www.janelia.org/open-science/mimms-22-2024}
 

### 2024-09-19 documentation/supplement.tex
Stephan's edits for Article + Supplement

@@
     \item Shield the beam as soon as alignment of a particular section is done. This increases safety, and avoids accidentally bumping into aligned components.
-    \item \textit{Walking the beam}: Any beam can be threaded through two irises using two mirrors.
+    \item \textit{Walking the beam}: Any beam can be aligned through two irises using two mirrors.
 The first mirror the beam meets is sometimes called the ``position'' mirror as it affects primarily the position of the beam.
@@
 All custom metal pieces are parts of the CAD assembly of the microscope.
-Ours were manufactured from aluminium stock in the university machine shop, but other materials are possible.
-Aluminium has the added benefit of anodization, which can help control stray light.
-For example, if the microscope was used in a Virtual Reality system, we would anodize the collection optics to reduce scattering from the projector's light.\newline
+Ours were manufactured from aluminium stock in the university machine shop.
+Aluminium has the added benefit of anodization, which can help control scattered light.
 An overview of the microscope's cost is shown in Tab.~\ref{tab_costs}.
@@
 \rowcolor{gray!20} 920 nm fs-pulsed Laser  & Spark Alcor 920 + Warranty & 90 k \\
-                   ScanImage DAQ-System \& optimized PC & Vidrio & 20 k \\
+                   ScanImage DAQ-System \& optimized PC & MBF Bioscience& 20 k \\
 \rowcolor{gray!20} Piezo collar & Physik Instrumente & 16 k	\\
@@
 The third part is the microscope head with the attached collection optics.
-We will begin with the assembly on the optical table.\newline
-
+We will begin with the assembly on the optical table.
+All along, we assume the reader will have downloaded and opened the CAD model as we will rely heavily on it.\newline
 Before building your own microscope, read these instructions fully.
@@
 Like all open instrumentation (under CC-BY-4.0), this work is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY, to the extent permitted by law; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.
+Further, prior to the construction, check carefully the instruction manual of the scanning mirrors, photomultiplier tubes (PMTs), power supplies, Pockels cell, ScanImage, the Piezoelectric objective collar, and the filter mounting instructions.
 
@@
 The telescope (item K) magnifies the beam $\times 2$.
+The empty SM1 tube is an anodized aluminum SM1 lens tube cover (SC600, Thorlabs).
 All parts are explained in the text together with a note on their alignment.}
@@
     \item \textbf{I)} Si Switchable Gain Detector, 350 - 1100 nm (PDA36A2, Thorlabs).
-This is used to measure the light transmission through the Pockels cell, by monitoring scattered light from the beam block (H), that comes from the shutter back reflection.
+This is used for the laser power calibration  of the light transmitted through the Pockels cell.
+The detector is facing the beam block (H) and monitors the light that comes from the shutter back reflection when closed.
 Make sure that the gain on the detector is chosen reasonably for laser power and ambient light level.
@@
 To check that the shutter is properly aligned leave it open and make sure that the beam is not clipped.
-When closed, the back-reflection has to be terminated in a beam block.
-This back-reflection combined with a physically close detector (Items H and I above) is used to calibrate the Pockels cell in ScanImage (see below).
-
-    \item \textbf{K)} $2\times$ Beam Expander ($2\times$ Achromatic Galilean Beam Expander, GBE02-B, Thorlabs, inside SM1RC, Thorlabs).
-This expands the beam sufficiently to fill the apertures of the subsequent optics.
+When closed, the back-reflection is sent to a beam block.
+For this reason the shutter is not mounted exactly perpendicular to the incident beam but at a slight angle.
+
+    \item \textbf{K)} $2\times$ Beam expander ($2\times$ Achromatic Galilean Beam Expander, GBE02-B, Thorlabs, inside SM1RC, Thorlabs).
 Aligning the beam expander requires two steps.
-First, it has to be aligned to the optical axis.
-Second, it is critical that the beam stays collimated after the beam expander.
+First, it has to be aligned on the beam axis.
+Second, the beam needs to remain collimated after the beam expander, which is achieved by tuning the expander collar.
 For the first alignment, we use two irises, one screwed in the front, and one (on a reasonably long SM1 extension tube) behind the expander.
-The beam expander has to be positioned such that the irises cut into the beam symmetrically.
-Then, the expander is on-axis.
-Next, we need to adjust the collimation of the beam so that the beam is the same size at the exit and after a long distance using several mirrors, see Fig.~\ref{sfig3}.
-For optimal alignment, adjust the dial on the beam expander until it no convergence or divergence is visible.
+The beam expander has to be positioned such that the beam travels through both iris, and such that the irises cut into the beam symmetrically.
+Next, we need to adjust the collimation of the beam using the expander collimation collar.
+It needs to be tuned so that the beam is the same size at the exit and after a long distance using several mirrors, see Fig.~\ref{sfig3}.
     %
@@
     %
-\item \textbf{L)} Iris (SM1D12C inside CP08, both Thorlabs) used to check alignment.
+\item \textbf{L)} Iris (SM1D12C mounted on a CP08 plate, both Thorlabs) used to check alignment.
 
@@
 When finished aligning the beam through all the optical components listed above, clamp them down on the table securely.
-Then shield the beam path with additional SM1 and SM2 tubing to increase safety and to protect the aligned optical components.
+Then shield the beam path with additional SM1 and SM2 tubing, and tubing cover (e.g.
+Thorlabs SC600, SM1 Anodized Aluminum Lens Tube Cover) to increase safety and to protect the aligned optical components.
 %
@@
     \item \textbf{B)} Broadband filter (WG11010-B, Thorlabs, inside SM1L20 and SM1S20) - filter to keep dust out of the box housing the scanning mirrors.
-    \item \textbf{C)} An aluminium box containing the resonant and slow galvanometer set (CRS8K/6215H Galvo Set, Novanta), mounted to 95 mm rail (XT95RC4, Thorlabs).
+    \item \textbf{C)} An aluminium box containing the resonant and slow galvanometer set (CRS8K/6215H Resonant-Galvo Set, Novanta), mounted to 95 mm rail (XT95RC4, Thorlabs).
 A detailed description is provided below.
-    \item \textbf{D)} Empty tubing.
+    \item \textbf{D)} Empty tubing (SM2V05, adjustable SM2 Lens Tube, Thorlabs).
     \item \textbf{E)} Scan lens - See detailed description below.
     \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs).
-While we used a round 2 inch mirror, this should be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs).
-This increases the field-of-view because the cross-section of an ellipse at 45 degrees is a circle.
+While we used a round 2 inch mirror, this could be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs).
+This would increase the field-of-view because the cross-section of an ellipse at 45 degrees is a circle.
 At low magnification, a round mirror will lead to vignetting.
@@
     \item First, mount the 95 mm rail to the table.
-Then attach a bracket to the side to hold the scan lens (component D in Fig.~\ref{sfig3}), and one on top with a cage system to hold a mirror (component F in Fig.~\ref{sfig3}).
+Then attach a bracket (all from the XT95 series, Thorlabs) to the side to hold the scan lens (component D in Fig.~\ref{sfig3}), and one on top with a cage system to hold a mirror (component F in Fig.~\ref{sfig3}).
 For alignment with cage systems, we use a cage system alignment plate (VRC4CPT, Thorlabs).
@@
 To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}) facing up.
-These two pieces meet in the air.
-Sliding a finger across the small gap between the two pieces makes misalignment easy to notice haptically.
-Mount the box housing the scanning mirrors such that you can not feel the transition from the lower SM1 tubing to the upper SM1 tubing.
+These two pieces meet in mid-air.
+The gap in between can be reduced to zero using adjustable length SM1 lens tube (e.g.
+SM1V10, Thorlabs, not shown in CAD) and can be further closed by a small portion of  lens tube cover (SC600, Thorlabs).
     \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}A) so that light travels through the center of the scanning mirrors and up the 95 mm rail.
@@
 \begin{enumerate}[]
-    \item \textbf{A)} Empty tube, shielding the bream aligned in the previous section.
+    \item \textbf{A)} Empty tube, shielding the beam aligned in the previous section.
     \item \textbf{B)} Protected silver Mirror (PF30-03-P01, Thorlabs) inside KS3 and clamped down with XE25CL2 and another clamp.
@@
 Switch the room lights off, wait a few minutes to adapt to the darkness then mount the PMTs on their respective ports.
+Of note, when ordering the PMTs from Hamamatsu, one can request PMTs with particularly low dark count to reduce noise.
 
 \subsection{Shield the light path}
-Now that your microscope is ready, finish shielding the light path with SM1 and SM2 tubing, and cover the optical table with sheet metal.
-We use bent aluminium sheet, placed on small columns made from T-slotted rail.
+Now that your microscope is ready, finish shielding the light path with SM1 and SM2 tubing, lens tube cover (SC600, Thorlabs), and cover the optical table with sheet metal.
+We use bent 1 mm aluminium sheet, placed on small columns made from T-slotted rail.
 
@@
     \item Finally, use a fluorescent bead sample to measure the microscope's point spread function (PSF), see Fig.~\ref{sfig7}C.
-This will reveal more subtle misalignments or aberrations in the optics.
+This will reveal more subtle misalignment and aberration in the optics.
 We use a mix of 5000:1 100 nm fluorescent beads (``Dragon Green'' 480/520 from Bangs Laboratories) in in 1\% Agarose.
@@
 \textbf{B)} The collection optics during the assembly process, similar to panel A.
-Key components are labelled (see text).}
+Key components are labelled (see text).
+EDITS TO MAKE IN THE ARROWS}
     \label{sfig9}
@@
 First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread, 1/8in long).
-Orientation is important: The arrow is facing outwards, i.e.
-away from the inside of the box and towards the PMT along the light path.
+Orientation is important: For this brand of filters, the arrow is following the light path, i.e.
+away from the inside of the box and towards the PMT.
     \item \textbf{H)} Next we install the 600 nm band-pass filter for the red channel (Semrock Brightline FF01-600/52-32, AVR Optics).
@@
 When the glue has set, the mirror casing is screwed in place using stainless steel socket head screw, 4-40 Thread Size, 5/16 inches long.
+The glue used is a 5min non-sagging Epoxy.
+Three dichroic was attached with 3 points of glue of minimal volume.
     \item \textbf{J)} The piece containing the 525 nm and 600 nm band-pass filters and the dichroic mirror is connected to the larger metal box with stainless steel socket head screw, 4-40 Thread Size, 3/4 inches long.
@@
     \item \textbf{L)} PMT plate.
-The PMT attaches to the FLAT side of the PMT plates.
+The PMT attaches to the flat side of the PMT plates with 4 specialized low profile screws (CBSTSR2-6, Misumi).
 The other side has a shallow cut out for the screw head to sit.
+.
 The plate with the PMT attached screws into the rest of the assembly using 4-40 5/16 inch, socket cap screws.
@@
     \caption{{\bf The scanning mirror box.} \textbf{A)} The custom aluminium box housing the pair of scanning mirrors.
-\textbf{B)} Close-up of the same box with key parts labelled: A: Two broadband windows (WG11010-B, Thorlabs) to keep dust out.
+\textbf{B)} Close-up of the same box with key parts labelled: A: Two windows (WG11010-B, Thorlabs) to keep dust out.
 B: Attachment of the box to the 95 mm optical rail.
@@
 %
-The scanning mirror housing is a machined piece of aluminium holding the Novanta scanning mirror set against the 95 mm optical rail, see Fig.~\ref{sfig10}.
-It also shields the scanning mirrors from dust in the environment, and protects the environment from audible noise produced by the scanning mirrors.
+The scanning mirror housing is a machined piece of aluminium holding the Novanta scanning mirror set against the 95 mm optical rail (XT95, Thorlabs), see Fig.~\ref{sfig10}.
+It also shields the scanning mirrors from dust in the environment, and protects the environment from audible noise produced by the resonant scanning mirrors.
 The housing is composed of a box, mounted to the 95 mm rail (Fig.~\ref{sfig10}A,B,C), and a lid to which the Novanta scanners are mounted (Fig.~\ref{sfig10}D,E,F).
@@
 This is particularly important when pushing to fast responses, and driving the slow galvanometer with larger currents.\newline
-After receiving the scanning mirrors, they need to be installed in the black anodized aluminium block.
-Make sure to put the resonant scanner in first (the piece sitting at an angle) before the slow galvanometer (the piece sitting parallel to the mount).
-Both pieces should have stops that keep you from pushing them into the mount too far.\\
-The box has two windows that are SM1 threaded.
-Position the dust filters (WG11010-B, Thorlabs) in these bores with appropriate retaining rings.
-We used a SM1 to SM2 converter ring at the exit, Fig.~\ref{sfig10}B, only because we had that part available from an earlier project.
+
+The two box apertures (beam input and output) have NIR antireflection coated flat BK7 windows (WG11010-B, Thorlabs) secured with SM1 tubes and retaining rings (SM1RR, Thorlabs).
+We used a SM1 to SM2 converter ring at the exit, Fig.~\ref{sfig10}B, to ease checking alignment with downstream mounts and optics.
 
@@
 Fig.~\ref{sfig11}B shows the power supply of the scanning mirrors.
-The slow galvanometer needs a $\pm 28\text{ V}$ supply.
-This is provided through the three black/white/red cables (-28 V, 0 V, +28 V) from the right power supply.
+At time of purchase, we requested the controller of the slow galvanometer mirror to be configured for usage at $\pm 28\text{ V}$  (manufacturer default is $\pm 24\text{ V}$ ).
+This overall improves dynamical properties.
+The controller requires three voltage inputs, respectively -28 V, 0 V, and +28 V.
+The 0 V is also grounded.
 The second power supply to the left provides 12 V for the resonant scanner.
-The supplies are connected to the power supply ports on the prototype box, and the signal lines are connected to the Vidrio DAQ system.
+The supplies are connected to the power supply ports on the prototype box, and the signal lines are connected to the MBF Bioscience DAQ system.
 Key components in the figure are labelled with capital letters.
@@
 \begin{itemize}
-    \item \textbf{A)} Power supply (GPD-3303D, Gw Instek) with two channels, both set to 28 V.
+    \item \textbf{A)} Power supply (GPD-3303D, Gw Instek) with two channels configured in series, both set to 28 V.
     \item \textbf{B)} Have CH 1 turned on.
@@
     \item \textbf{I)} The +28 V output line (red) connected to the +28 V line on the electronics box.
+Conform the correct voltage with a reliable multimeter BEFORE powering up the galvanometer controller.
+(We use a Fluke 117)
     \item \textbf{J)} Power supply (E3630A, Keysight) set to 12 V to power the resonant scanners.
-    \item \textbf{K)} Black channel is the references, and connected to black port on the controller box.
-    \item \textbf{L)} Red channel, set to +12 V, is connected to the red port on the controller box.
+    \item \textbf{K)} Black cable is the reference, and connected to black port on the controller box. Just below the connectors M/N/O.
+    \item \textbf{L)} Red channel, set to +12 V, is connected to the red port on the controller box. Just below the connectors M/N/O.
     \item \textbf{M)} Coaxial connector controlling ``Zoom'' (the resonant scanners's amplitude).
@@
 \end{itemize}
-Make sure the power generator settings are correct before plugging in the scanning mirrors.
-Check this with a good multimeter and do not just trust the display.
+Make sure the power supply settings are correct before plugging in the scanning mirrors.
+Confirm this independently with a good multimeter (e.g.
+Fluke 117) and do not just trust the display.
 Of further note, the scanning mirror driver boards cannot be mixed and matched.
@@
         \item Select \texttt{Analog Galvo} and click \texttt{Add}
-        \item Type in a name like \texttt{Y-galvo}
+        \item Type in a name like \texttt{Y-Galvo}
         \item In the new window, select \texttt{/vDAQ0/AO1} for \texttt{Control Channel}. This will depend on the port that the galvanometer is connected to.
@@
     \item In the new window, select \texttt{X-res} under \texttt{Resonant Scanner}.
-    \item For \texttt{Y-Galvo}, select \texttt{Y-galvo}.
+    \item For \texttt{Y-Galvo}, select \texttt{Y-Galvo}.
     \item Check off \texttt{Use} for \texttt{Shutter1}.
@@
     \item When the microscope is not in use, it is good practice to switch off all components, except the scanning mirror power supplies, the PMT preamplifiers, and the photodiode.
-    \item Every couple of month, switch the red and green PMTs to check for signs of aging and validate their performance on a fluorescent slide or sample of known brightness.
-The PMTs age and will need to be replaced, depending on use, after a few years.
+    \item Every once in a while, switch the red and green PMTs to check for signs of aging and validate their performance on a fluorescent slide or sample of known brightness.
+The PMTs can degrade and may need to be replaced, depending on use, after several years.
 They should be treated with care: power ramped up and down slowly, and saturation should be avoided.
@@
 When their performance becomes worse, they often have a few more months or years in the (typically brighter) red channel in them.
-    \item Every couple of month, image a bead sample to validate the PSF.
+    \item It is recommended to periodically image a bead sample to validate the PSF, as well as a Fluorescein bath to detect possible misalignment.
     \item Be mindful of imaging artifacts. When suspecting an issue, go back to the basics, and isolate the error.
@@
 %
-Of note, for virtual reality experiments that involve a Styrofoam treadmill floating on an air cushion, or any other experiment using compressed air, make sure to place an oil trap in the air line.
-This avoids oil droplets being deposited onto the optics; especially the elliptic mirror right above the objective.
-Small Styrofoam particles also get deposited on the lenses which need to be dusted from time to time.
-Try to shield the laser path as much as possible to keep dust and dirt away from optical components.
+ For safety, it is good practice to shield the laser path. In addition to safety concerns, it will also help in keeping dust and dirt away from optical components.
 

### 2024-09-19 article/Article.tex
Final edits to text + README

@@
 It is a fully open, high-performance and cost-effective research and teaching microscope without any custom parts beyond what can be fabricated in a university machine shop.
-The instrument features a large field of view, using a modern objective with a long working distance and large back-aperture to maximize the fluorescence signal.
-We document our experiences using these systems as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open-source scientific instrumentation.
+The instrument features a large field of view, using a modern objective with a long working distance and large back aperture to maximize the fluorescence signal.
+We document our experiences using this system as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open-source scientific instrumentation.
 
@@
 Recently, several approaches have also been developed to increase the size of the volumes being imaged beyond the limits set by the traditional sampling strategy while keeping the time resolution constant.
-New approaches probing extended regions simultaneously rely on signal demixing to reconstitute the underlying structure \cite{Song2017, Kazemipour2019}.
+New approaches probing extended regions rely on signal demixing to reconstitute the underlying structure \cite{Song2017, Kazemipour2019}.
 Another approach uses a set of axially separated and temporally distinct foci to record the entire axial imaging range near-simultaneously \cite{Demas2021}.\newline
@@
 Here, we design an open and high-performing microscope that uses these principles.
-As such we have made all optical and mechanical designs, electronics, bill-of-materials, CAD assembly, testing results, and relevant schematics open to the public.
+As such we have made all optical and mechanical designs, electronics, bill of materials, CAD assembly, testing results, and relevant schematics open to the public.
 Excluding laser and optical table, the cost is around US-\$ 110k (2024).
@@
 When closed, the laser reflected on the shutter reflective blades is sent to another beam block.
-Beam blocks are not perfect absorber, so we can use advantageoulsy the weak back scattered light from the beam block to calibrate the Pockels cell.
+Beam blocks are not perfect absorber, so we can use advantageously the weak back scattered light from the beam block to calibrate the Pockels cell.
 In our set-up, a photodiode (PDA36A2, Thorlabs) is thus facing the beam block.
 Following the shutter, the beam travels though a $2\times$ telescope (GBE02-B, Thorlabs) doubling its diameter.
-Past the telescope, the beam is then reflected off several mirrors in a periscope configuration before entering a custom aluminium box housing, mounted to a 95 mm optical rail (XT95 serie, Thorlabs), that houses the two scanning mirrors (CRS8K/6215H scanning mirror Set, Novanta), shown in blue in  Fig.~\ref{fig1}C.
-Leaving the scanners, the beam then travels first through the scan lens (green) and tube lens (red), pass through the long pass dichroic mirror of the collection box assembly  (yellow) and finally the objective (cyan).
+Past the telescope, the beam is then reflected off several mirrors in a periscope configuration before entering a custom aluminium box housing, mounted to a 95 mm optical rail (XT95 series, Thorlabs), that houses the two scanning mirrors (CRS8K/6215H scanning mirror set, Novanta), shown in blue in  Fig.~\ref{fig1}C.
+Leaving the scanners, the beam then travels first through the scan lens (green) and tube lens (red), passes through the long pass dichroic mirror of the collection box assembly (yellow) and finally the objective (cyan).
 The design of these components is covered in the next paragraphs.
@@
 For this reason, scan and tube lens must be carefully configured as a telescope.
-Additionally, to guaranty the laser beam enters the objective back-aperture with the same amount of clipping, the scanning mirrors must be positioned in the conjugated plane of objective back-aperture.
+Additionally, to guaranty the laser beam enters the objective back aperture with the same amount of clipping, the scanning mirrors must be positioned in the conjugated plane of objective back aperture.
 In many commercial infinity corrected microscope designs, the distance between the tube lens and the objective can be chosen within a certain range.
-In our design however, we added the constraint of positioning the objective and tube lens in a telescope, i.e.
-the distance between each is the sum of their focal.
+In our design, we added the constraint of positioning the objective and tube lens in a telescope, i.e.
+the distance between them, $d_{TO}$, is the sum of the tube lens and objective's focal length, $d_{TO} = f_O + f_T$.
 While this has no real impact, it prepares the assembly for possible upgrade where methods such as remote focusing could be used \cite{Botcherby2007, Botcherby2012, Sofroniew2016}.
@@
 We settled on a focal length $f_S=100\text{ mm}$  scan lens built from two inch diameter components \cite{Yao2023}.
-This choice was influenced by the availability of off the shelves lenses and the specific scanning range of the scanners (typically $\pm10\text{ deg}$)  (cf.
+This choice was influenced by the availability of off-the-shelf lenses and the specific scanning range of the scanners (typically $\pm10\text{ deg}$, cf.
 Fig.~\ref{fig1}A).
 To fill the back aperture of the objective with our laser beam, we aimed for a combined magnification of $M=3.75\times=f_T/f_S$, making the focal length of the tube lens  $f_T=375\text{ mm}$.
-With these choices, the resulting scanning angles at the back aperture of the objective are $\pm10\text{ deg}/3.75\approx\pm2.7\text{ deg}$ and with our chosen objective (Nikon $16\times$ with $f_O=12.5\text{ mm}$) the expected approximate is field of view diameter is $\approx 1.2\text{ mm}$).\newline
-The tube lens was also assembled as a lens group from off-the-shelf parts. The  relative positions of the two groups components were  optimized using Zemax . Details are provided below.
+With these choices, the resulting scanning angles at the back aperture of the objective are $\pm10\text{ deg}/3.75\approx\pm2.7\text{ deg}$ and with our chosen objective (Nikon $16\times$ with $f_O=12.5\text{ mm}$) the expected approximate field of view diameter is $\approx 1.2\text{ mm}$).\newline
+The tube lens was also assembled as a lens group from off-the-shelf parts.
+The relative positions of the components in the two lens groups were optimized in Ansys Zemax OpticStudio.
+Details are provided below.
 %
@@
 These rays were computed for the green emission light path.
-Small letters denote filters: a is a FF665-Di02-40x55; b: an NIR blocking filter (FF01-680/SP-50 ) (not shown in the Zemax simulation); c: FF562-Di03-40x52 and d: FF01-525/45-32 (BrightLine; AVR Optics).
+Small letters denote filters: a is a FF665-Di02-40x55; b: a near-infrared blocking filter (FF01-680/SP-50) (not shown in the Zemax simulation); c: FF562-Di03-40x52 and d: FF01-525/45-32 (BrightLine; AVR Optics).
 Small numbers  denote lenses.
@@
 b blocks residual IR excitation light $\lambda>680\text{ nm}$ (FF01-680/SP-50), and e is a FF01-600/52-32 filter for the red channel.
-\textbf{C)} Shown is the angle collection graph of the collection optics, which shows the fraction of collected light as function of the angle it emerges from the objective back-aperture.
+\textbf{C)} Shown is the angle collection graph of the collection optics, which shows the fraction of collected light as function of the angle it emerges from the objective back aperture.
 This was simulated in Zemax for the design in A.
-The collection optics were optimized to collect essentially all light over an $\approx\pm 8\text{ deg}$ emission angle.}
+The collection optics were optimized to collect essentially all light over a $\approx\pm 8\text{ deg}$ emission angle.}
     \label{fig3}
@@
 We incorporated several design principles into our assembly: (1) The collection lens should be large to maximize the collection of as much fluorescent light as possible.
-This implies that the collection lens should also follow the NIR long-pass dichroic mirror as closely as possible.
-(2) The collected light should be then guided through an elongated but diameter limited space where  another dichroic and filters (Green/Red) will be located.
+This implies that the collection lens should also follow the long-pass dichroic mirror as closely as possible.
+(2) The collected light should be then guided through an elongated but diameter limited space where another dichroic mirror and filters (Green/Red) will be located.
 It should therefore propagate as close to parallel as possible from the collection lens axis.
@@
 As previously, this design was exported into CAD, and the optomechanics assembled around it, see Fig.~\ref{fig3}B.
-Fig.~\ref{fig3}C shows a simulation in Zemax demonstrating that our design brings nearly all the light escaping the objective back-aperture with an angle below  $\approx8\text{ deg}$ to the aperture of the photomultiplier tubes.
+Fig.~\ref{fig3}C shows a simulation in Zemax demonstrating that our design brings nearly all the light escaping the objective back aperture with an angle below  $\approx8\text{ deg}$ to the aperture of the photomultiplier tubes.
 
@@
 \subsection*{Scanners power supplies and controllers enclosure}
-
 The scanning mirrors are active components.
 They are controlled by two circuit boards supplied with external power.
-The driver board of the resonant scanner does not dissipate much heat, but the drivers of the slow galvanometer can become warm in normal operation.
+The driver board of the resonant scanner does not dissipate much heat, but the driver of the slow galvanometer can become warm in normal operation.
 This heat needs to be dissipated.
@@
 The second power supply provides 12 V for the resonant scanner.
-It is beneficial to choose a power supply that can stably produce these currents for years.
+It is beneficial to choose a power supply that can stably produce these voltages for years.
 We have made good experiences with Agilent E3630A, and the Instek GPD-3303D.
-Importantly, double check the power generator with a good multimeter before connecting the driver boards.
+Importantly, double check the power supplies with a good multimeter before connecting the driver boards.
 Please also see \nameref{S1_Appendix} for a detailed illustration.
@@
 These leads are color-coded.
-A small circuit for resistance programming of the gain was design which also displays the gain setting voltage on small digital panel meter (Murata DMS-20PC).
+A small circuit for resistance programming of the gain was designed which also displays the gain setting voltage on a small digital panel meter (Murata DMS-20PC).
 The circuit for controlling two channels (red and green) is shown in Fig.~\ref{fig4}A.
@@
 The panel meter needs an additional +5 V supply that we obtain from the +15 V via a resistive divider.
-The meter is operating in Single-Ended Input Conﬁgurations, see Fig.~\ref{fig4}B.
+The meter is operating in single-ended input conﬁguration, see Fig.~\ref{fig4}B.
 Due to the simplicity of this circuit, we do not solder this on a circuit board, but rather in a prototype development box directly, see Fig.~\ref{fig4}C, which is attached to the rig.
@@
 The Pockels cell is rotated so that the control voltage produces the largest dynamic range of transmitted laser power (we go through the alignment procedure in depth below).
-At maximum transmission setting of the Pockels cell, we obtain $\approx 260\text{ mW}$ below the objective, a large value, as it is exceeding the maximum recommended power for cortical imaging mouse \cite{Song2017}.
+At maximum transmission setting of the Pockels cell, we obtain $\approx 260\text{ mW}$ below the objective, a large value, as it is exceeding the maximum recommended power for cortical imaging in mice \cite{Song2017}.
 All pictures presented in this article were obtained with $\approx 15\text{ mW}$ below the objective.
@@
 Neurons in this organism express the fluorescent protein GCaMP6f in their nuclei whose green fluorescence strongly depends on the cellular concentration of Calcium ions.
-We imaged a 5-day old larvaimmobilized in 2\% low melting point Agarose in E3 medium, see Fig.~\ref{fig7}.
+We imaged a 5-day old larva immobilized in 2\% low melting point Agarose in E3 medium, see Fig.~\ref{fig7}.
 We first performed a volumetric scan of the organism, Fig.~\ref{fig7}A shows a rendering in Fiji \cite{Schindelin2019}, and then focused on a plane with a large number of visible neurons, Fig.~\ref{fig7}B.
@@
 In these cases, volumetric imaging is  best achieved using a ramp where the objective is constantly moving at the same speed, rather than doing steps of constant height for every planes.
-Electrically tunable lens (ETL) can be an alternative to the piezoobjective.
+An electrically tunable lens (ETL) can be an alternative to the piezoobjective.
 These lenses have a variable focal length, usually from around 10 cm to infinity, that can be set with a control voltage within $<1\text{ ms}$.
-A convenient spot for an ETL might be right before the scan assembly, while care should be taken to not focus the beam on the scanning mirrors to avoid damage.
 \newline
@@
 (4) We made the design choice to use a  resonant and slow scanning mirror pair positioned close together in the same mount.
-Rasther than the mirrors themselves, it is the plane equidistant between the rotational axis of both scan mirrors that is conjugated to the back aperture of the objective.
+Rather than the mirrors themselves, it is the plane equidistant between the rotational axis of both scan mirrors that is conjugated to the back aperture of the objective.
 This is a compromise that is used by many (e.g.
@@
 This is advantageous for use in virtual reality systems, because light leaving a projector can be filtered to this range before projected on a dome surrounding the objective and animal.
-We have successfully used budget friendly colored glass filters in front of the projector (Schott BG25 or Schott BG5), and long-pass colored glass (Schott RG780) to block projector light from entering the excitation path \cite{Dombeck2007}.
+We have successfully used budget friendly colored glass filters in front of the projector (Schott BG25 or Schott BG5) to block projector light from entering the excitation path \cite{Dombeck2007}.
 Combined with a light shield around the objective \cite{Dombeck2010}, such a projection system will only minimally interfere with imaging (e.g.
@@
 (This is corrected in the CAD files.) When analyzing data, we suggest to use simple programs.
-Our Image analyses here were done in Fiji \cite{Schindelin2019} combined with simple python and matlab scripts.
+Our image analyses here were done in Fiji \cite{Schindelin2019} combined with simple python and matlab scripts.
 In our experience, students learn very effectively through hands-on open-ended pedagogy and pursuing their own interests \cite{Zajdel2016}.\newline
@@
 To aid discoverability, we have generated an Open Know How Manifest (OKH-manifest), located in the Online Repository.
-Our project is also certified by the open source hardware association (OSHWA UID
-US002677, \url{https://certification.oshwa.org/us002677.html}).\newline
+Our project is also certified by the open source hardware association (OSHWA UID US002677).\newline
 The growing space of open-source instrumentation can improve science in several ways: (1) enabling faster innovation through lower costs and enabling work in low-resource settings.
@@
 \label{repository}
-All CAD and optics design files, bill-of-materials, and other useful information: \url{https://github.com/BrainCOGS/Microscope}.
+All CAD and optics design files, bill of materials, and other useful information: \url{https://github.com/BrainCOGS/Microscope}.
 

### 2024-09-19 documentation/supplement.tex
Final edits to text + README

@@
 
-\subsection{Parts and bill-of-materials}
+\subsection{Parts and bill of materials}
 All custom metal pieces are parts of the CAD assembly of the microscope.
@@
 This is just a summary.
-The detailed bill-of-materials is provided in the git repository.}\label{tab_costs}
+The detailed bill of materials is provided in the git repository.}\label{tab_costs}
 \end{table}
@@
 We will begin with the assembly on the optical table.
-All along, we assume the reader will have downloaded and opened the CAD model as we will rely heavily on it.\newline
+All along, we assume the reader will have downloaded and opened the CAD model as we will rely heavily on it.
+Further, check carefully the instruction manuals of the scanning mirrors, photomultiplier tubes (PMTs), power supplies, Pockels cell, ScanImage, the Piezoelectric objective collar, and the filter mounting instructions.\newline
 Before building your own microscope, read these instructions fully.
@@
 This document follows closely our own alignment procedure, and we have done our best to be accurate.
-However, use common sense and do not follow these instructions blindly.
+However, use common sense.
+Do not follow these instructions blindly (or you will follow these instructions blindly).
 Like all open instrumentation (under CC-BY-4.0), this work is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY, to the extent permitted by law; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.
-Further, prior to the construction, check carefully the instruction manual of the scanning mirrors, photomultiplier tubes (PMTs), power supplies, Pockels cell, ScanImage, the Piezoelectric objective collar, and the filter mounting instructions.
 
@@
 \begin{enumerate}[]
-    \item \textbf{A)} Laser beam coming out of the laser.
+    \item \textbf{A)} Laser head emitting the laser beam (red).
 
@@
 
-    \item \textbf{C)} $\diameter1\text{ in}$ mounted achromatic half-wave plate with SM1-threaded mount (AHWP10M-980, Thorlabs) inside a high-precision rotation mount (PRM1, Thorlabs).
-First, to check that the beam travels centrally through the half-wave plate, use an iris.
+    \item \textbf{C)} $\diameter1\text{ inch}$ mounted achromatic half-wave plate with SM1-threaded mount (AHWP10M-980, Thorlabs) inside a high-precision rotation mount (PRM1, Thorlabs).
+First, use an iris to check that the beam travels centrally through the half-wave plate.
 Then place the half-wave plate at a slight angle to make sure that the beam reflected of the surface of the half-wave plate does not travel back into the laser.
@@
 This will be important later to reproduce the exact same position of the alignment tool with the Pockels cell.
-        \item Connect the Pockels cell (M350-80LA, Conoptics) to the driver as per the Conoptics instructions (p1m and p2m go to J1m and J2m, p1 and p2 go to the controller).
+        \item Connect the Pockels cell (M350-80-LA, Conoptics) to the driver as per the Conoptics instructions (p1m and p2m go to J1m and J2m, p1 and p2 go to the controller).
 The controller settings are shown in Fig.~\ref{sfig2}.
@@
 
-\item \textbf{M)} Mirror (PF10-03-P0, Thorlabs, inside KCB1) to reflect the beam up at a right angle.
+\item \textbf{M)} Mirror (PF10-03-P01, Thorlabs, inside KCB1) to reflect the beam up at a right angle.
 For the next steps (in particular finding the optimal scanning mirror position), it is important that the beam travels up perpendicularly to the optical table, and parallel to the 95 mm optical rail column that holds the scanning mirrors (next section).
@@
 \begin{enumerate}[]
-    \item \textbf{A)} Mirror (BPF10-03-P0, inside KCB1, with CP12 attached) - turn the beam at a right angle.
+    \item \textbf{A)} Mirror (PF10-03-P01, inside KCB1, with CP12 attached) - turn the beam at a right angle.
     \item \textbf{B)} Broadband filter (WG11010-B, Thorlabs, inside SM1L20 and SM1S20) - filter to keep dust out of the box housing the scanning mirrors.
@@
     \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs).
-While we used a round 2 inch mirror, this could be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs).
+While we used a round 2 inch mirror, this should be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs).
 This would increase the field-of-view because the cross-section of an ellipse at 45 degrees is a circle.
@@
     \item The box housing the scanning mirrors is connected, trough SM1 tubing, to a mirror (component A in Fig.~\ref{sfig3}).
-To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}) facing up.
+To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}).
 These two pieces meet in mid-air.
@@
 After the beam's alignment is confirmed by traveling through the two irises, it is time to install, and align scan and tube lens.
-Remember that (1) the distance between the tube lens (component C in Fig.~\ref{sfig5}) and scan lens (component G in Fig.~\ref{sfig5}) has to be 100 mm + 375 mm = 475 mm while (2) the scanning mirror set (component H in Fig.~\ref{sfig5}) has to be positioned in the focal plane of the scan lens, while (3) the objective back aperture is positioned in the focal plane of the tube lens (see Fig.
+Remember that (1) the distance between the tube lens (component C in Fig.~\ref{sfig5}) and scan lens (component G in Fig.~\ref{sfig5}) has to be 100 mm + 375 mm = 475 mm while (2) the scanning mirror set (component H in Fig.~\ref{sfig5}) has to be positioned in the focal plane of the scan lens (see Fig.
 1 in the main manuscript).
@@
 If no fluorescence is produced in this optical slice, no signal will be visible in ScanImage.
-    \item If the objective requires water immersion, has a drop of water been placed between the sample and the objective.
+    \item If the objective requires water immersion, has a drop of water been placed between the sample and the objective?
     \item Are all beam blocks removed from the path? Check with IR cards along the way. Below the objective, the IR light should be focused to a tight spot.
@@
 Notice the custom spacer rings in blue.
-The distance between the last element of the scan lens assembly and the scanning mirror box is $\approx 1.35 \text{ inches}$.
+The distance between the last element of the scan lens assembly and the scanning mirror box is $\approx 1.35 \text{ inch}$.
 \textbf{D)} The assembled scan lens group in its SM2 housing.}
@@
 The convex part is facing towards the inside of the box, and set with nylon set screws (Stainless Steel Nylon-Tip Set Screw, 4-40 Thread, 1/8 inch long).
-The holders are then fixed together with Stainless Steel Socket Head Screw, 8-32 Thread Size, 3/8 inch long.
+The holders are then fixed together with stainless steel socket head screw, 8-32 thread size, 3/8 inch long.
     \item \textbf{G)} With the condensers in place, we can install the optical band-pass filters in front of them.
-First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread, 1/8in long).
+First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread, 1/8 inch long).
 Orientation is important: For this brand of filters, the arrow is following the light path, i.e.
@@
 The caret points towards the metal holder, such that the side the caret is pointing to contacts the metal when it is glued in place.
-When the glue has set, the mirror casing is screwed in place using stainless steel socket head screw, 4-40 Thread Size, 5/16 inches long.
-The glue used is a 5min non-sagging Epoxy.
+When the glue has set, the mirror casing is screwed in place using stainless steel socket head screw, 4-40 thread size, 5/16 inch long.
+The glue used is a 5 min non-sagging Epoxy.
 Three dichroic was attached with 3 points of glue of minimal volume.
-    \item \textbf{J)} The piece containing the 525 nm and 600 nm band-pass filters and the dichroic mirror is connected to the larger metal box with stainless steel socket head screw, 4-40 Thread Size, 3/4 inches long.
+    \item \textbf{J)} The piece containing the 525 nm and 600 nm band-pass filters and the dichroic mirror is connected to the larger metal box with stainless steel socket head screw, 4-40 thread size, 3/4 inch long.
     \item \textbf{K)} The bottom piece (bottom per the view of the picture in Fig.~\ref{sfig9}B) of the PMT box is attached using 4-40, undercut, 3/16 inch screws.
@@
 The other side has a shallow cut out for the screw head to sit.
-.
 The plate with the PMT attached screws into the rest of the assembly using 4-40 5/16 inch, socket cap screws.
@@
     \item \textbf{N)} Then we close the second panel with 8/32, 1/2 inch, socket cap screws.
-    \item \textbf{O)} The piezoelectric holder is attached to the aluminium part using the adapter that comes with it. Do not damage the Serial cable.
+    \item \textbf{O)} The piezoelectric holder is attached to the aluminium part using the adapter that comes with it. Be careful to not damage the Serial Cable connected to the holder.
     \item \textbf{P)} The lid is attached using 8/32, 3/8 inch, undercut screws.
@@
 \textbf{C)} Bottom part of the aluminium box.
-A: The windows, and B: screws to attach the box to the drop-on rail carriage via four 0.75 inch tall 1 inch diameter posts.
+A: the windows, and B: screws to attach the box to the drop-on rail carriage via four 0.75 inch tall 1 inch diameter posts.
 \textbf{D)} The scanning mirrors are mounted to the lid using heat transfer compound.
@@
 The scanning mirror housing is a machined piece of aluminium holding the Novanta scanning mirror set against the 95 mm optical rail (XT95, Thorlabs), see Fig.~\ref{sfig10}.
-It also shields the scanning mirrors from dust in the environment, and protects the environment from audible noise produced by the resonant scanning mirrors.
+It also shields the scanning mirrors from dust in the environment, and protects the environment from audible noise produced by the resonant scanning mirror.
 The housing is composed of a box, mounted to the 95 mm rail (Fig.~\ref{sfig10}A,B,C), and a lid to which the Novanta scanners are mounted (Fig.~\ref{sfig10}D,E,F).
@@
 
-The two box apertures (beam input and output) have NIR antireflection coated flat BK7 windows (WG11010-B, Thorlabs) secured with SM1 tubes and retaining rings (SM1RR, Thorlabs).
+The two box apertures (beam input and output) have near-infrared antireflection-coated flat BK7 windows (WG11010-B, Thorlabs) secured with SM1 tubes and retaining rings (SM1RR, Thorlabs).
 We used a SM1 to SM2 converter ring at the exit, Fig.~\ref{sfig10}B, to ease checking alignment with downstream mounts and optics.
@@
 The scanning mirrors come with driver circuit boards.
-We place them in a prototype box, and connect the driver board's power supply and signal lines to connectors, see Fig.~\ref{sfig11}A.
+We place them in a prototype box (EG6, Gold Box, Acopian), and connect the driver board's power supply and signal lines to connectors for easier access, see Fig.~\ref{sfig11}A.
+The driver boards are mounted to the aluminium walls of the prototype box with heat transfer compound (Wakefield Thermal Joint Compound Type 120-5 Silicone).
 The power connectors accept banana plugs.
 The signals are connected to BNC connectors.
-The other key parts are as follows.
 %
@@
 Fig.~\ref{sfig11}B shows the power supply of the scanning mirrors.
-At time of purchase, we requested the controller of the slow galvanometer mirror to be configured for usage at $\pm 28\text{ V}$  (manufacturer default is $\pm 24\text{ V}$ ).
+At time of purchase, we requested the controller of the slow galvanometer mirror to be configured for usage at $\pm 28\text{ V}$  (manufacturer default is $\pm 24\text{ V}$).
 This overall improves dynamical properties.
@@
     \item \textbf{I)} The +28 V output line (red) connected to the +28 V line on the electronics box.
-Conform the correct voltage with a reliable multimeter BEFORE powering up the galvanometer controller.
-(We use a Fluke 117)
+Conform the correct voltage with a reliable multimeter BEFORE powering up the galvanometer controller, e.g.
+with a Fluke 117.
     \item \textbf{J)} Power supply (E3630A, Keysight) set to 12 V to power the resonant scanners.
@@
 Make sure the power supply settings are correct before plugging in the scanning mirrors.
-Confirm this independently with a good multimeter (e.g.
+Confirm this independently with a reliable multimeter (e.g.
 Fluke 117) and do not just trust the display.
@@
     \item Solder a 4 inch piece of wire to center pin on the same potentiometer. 
-    \item Connect the left and right pins to the banana plugs and set the potentiometer to 5V going across BEFORE connecting the middle wire to the rest of the controller circuit! 
+    \item Connect the left and right pins to the banana plugs and set the potentiometer to 5 V going across BEFORE connecting the middle wire to the rest of the controller circuit! 
     \item Solder the other end of the 4 inch wire and another 4 inch piece of wire to the middle pin on the second switch on the side adjacent to the ON/ON words.
@@
     \item Solder the other end of the wire to pin 1 and pin 2 (+5 V supply) on the bottom display.
-    \item Trim the wires from the middle pin of the gain adjusters by around 5 inches, connect those two wires, the wire furthest from the dial on the potentiometer, and two 12 inch wires by twisting together.
+    \item Trim the wires from the middle pin of the gain adjusters by around 5 inch, connect those two wires, the wire furthest from the dial on the potentiometer, and two 12 inch wires by twisting together.
     \item Solder a 3 inch wire to the white banana plug and screw it in the housing. This is component \textbf{E} in in Fig.~\ref{sfig12}B.

### 2024-12-28 article/Article.tex
Revision of article
Addresses the reviewer concerns:
(1) Changes to text and organization
(2) New Fig 1 and suppl. Fig. 11

@@
 % \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\newcommand\thickhline{\noalign{\global\savedwidtch\arrayrulewidth\global\arrayrulewidth 2pt}%
 \hline
@@
 \\
-Manuel Schottdorf\textsuperscript{1,*}, % 0000-0002-5468-4255
+Manuel Schottdorf\textsuperscript{1,2*}, % 0000-0002-5468-4255
 P. Dylan Rich\textsuperscript{1}, % 0000-0001-9782-7984
 E. Mika Diamanti\textsuperscript{1}, % 0000-0003-1199-3362
-Albert Lin\textsuperscript{1,4}, % 0000-0002-4541-5889
+Albert Lin\textsuperscript{1,3}, % 0000-0002-4541-5889
 Sina Tafazoli\textsuperscript{1}, % 0000-0003-1926-0227
-Edward H. Nieh\textsuperscript{1,2}, % 0000-0003-2154-6224
-Stephan Y. Thiberge\textsuperscript{1,3*} % 0000-0002-6583-6613
+Edward H. Nieh\textsuperscript{1,4}, % 0000-0003-2154-6224
+Stephan Y. Thiberge\textsuperscript{1,5*} % 0000-0002-6583-6613
 \\
@@
 \textbf{1} Princeton Neuroscience Institute, Princeton University, Princeton, NJ, USA\\
-\textbf{2} School of Medicine, University of Virginia, Charlottesville, VA, USA \\
-\textbf{3} Bezos Center for Neural Circuit Dynamics, Princeton University, Princeton, NJ, USA\\
-\textbf{4} Center for the Physics of Biological Function, Princeton University, Princeton, NJ, USA\\
+\textbf{2} Psychological and Brain Sciences, University of Delaware, Newark, DE, USA\\
+\textbf{3} Center for the Physics of Biological Function, Princeton University, Princeton, NJ, USA\\
+\textbf{4} Department of Pharmacology, School of Medicine, University of Virginia, Charlottesville, VA, USA \\
+\textbf{5} Bezos Center for Neural Circuit Dynamics, Princeton University, Princeton, NJ, USA\\
 \bigskip
@@
 % Use the asterisk to denote corresponding authorship and provide email address in note below.
-* mschottdorf@princeton.edu\\
+* maschott@udel.edu\\
 * thiberge@princeton.edu
@@
 Many laboratories use two-photon microscopy through commercial suppliers, or homemade designs of considerable complexity.
-The integrated nature of these systems complicates customization, troubleshooting as well as grasping the principles of two-photon microscopy.
+The integrated nature of these systems complicates customization, troubleshooting, and \textcolor{blue}{training on the} principles of two-photon microscopy.
 Here, we present ``Twinkle'': a microscope for Two-photon Imaging in Neuroscience, and Kit for Learning and Education.
-It is a fully open, high-performance and cost-effective research and teaching microscope without any custom parts beyond what can be fabricated in a university machine shop.
-The instrument features a large field of view, using a modern objective with a long working distance and large back aperture to maximize the fluorescence signal.
+It is a fully open, high performing and \textcolor{blue}{easy-to-set-up microscope that can effectively be used for both education and research}.
+The instrument features \textcolor{blue}{a $>1\text{ mm}^2$ field of view}, using a modern objective with \textcolor{blue}{3 mm} working distance and \textcolor{blue}{two inch diameter optics combined with GaAsP photomultiplier tubes} to maximize the fluorescence signal.
 We document our experiences using this system as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open-source scientific instrumentation.
@@
 %
-Two-photon microscopy\cite{Denk1990, Svoboda1997, So2000, Helmchen2005} is a workhorse of modern systems neuroscience across species, and two-photon microscopes exist in many system neuroscience laboratories\cite{Luu2024, Grienberger2022}.
-For example, in the animal model \textit{Mus musculus} (mouse), two-photon microscopes have been used to classify the function and neural inventory of the retina \cite{Baden2016}, study sequential activity in cortex \cite{Harvey2012} and subcortical structures \cite{Nieh2021}, led to transformative insights into signals in the dopaminergic reward system \cite{Engelhard2019}, and revealed an organized map among grid cells \cite{Yu2018}.
-In non-human primates, two-photon microscopes have been used as optical brain computer interfaces \cite{Trautmann2021}, and to survey the spatial organization of motor cortex in reach movements \cite{Ebina2018}.
-They also have potential to further our understanding of the function of the primate retina \cite{Sharma2016, Schottdorf2021}.
-In Zebrafish, \textit{Danio rerio}, two-photon microscopy can image the entire brain with single cell resolution \cite{Renninger2013}.
-Two-photon microscopy has also become a standard method for monitoring neural activity in invertebrates.
-In the fruit fly, \textit{Drosophila melanogaster}, imaging from sparse, genetically specified neuron populations \cite{Seelig2010, Lin2022} has enabled many circuits to be functionally mapped, including auditory \cite{Baker2022}, courtship \cite{Deutsch2020, Roemschied2023}, and navigation circuits \cite{Kim2017}.
-Two-photon microscopes have also enabled volumetric pan-neuronal imaging, in which large portions of the whole fly brain can be recorded from with high temporal resolution \cite{Pacheco2021,Brezovec2024}.
-In \textit{Caenorhabditis elegans}, it allowed to measure an atlas of neural signal propagation \cite{Randi2023}.\newline
-However, these systems can be expensive and difficult to customize \cite{Diamanti2021}, while improvements and new inventions are published regularly, such as the incorporation of adaptive optics to improve the signal amplitude \cite{Yao2023}, the combination of two-photon imaging with two-photon stimulation for all-optical interrogation of neural circuits \cite{Nikolenko2008, Packer2012,Rickgauer2014}, and extremely large fields of view for mesoscopic imaging across brain areas \cite{Sofroniew2016}.
-Recently, several approaches have also been developed to increase the size of the volumes being imaged beyond the limits set by the traditional sampling strategy while keeping the time resolution constant.
-New approaches probing extended regions rely on signal demixing to reconstitute the underlying structure \cite{Song2017, Kazemipour2019}.
-Another approach uses a set of axially separated and temporally distinct foci to record the entire axial imaging range near-simultaneously \cite{Demas2021}.\newline
-The two-photon methods' popularity suggests the need for a simple platform, at reasonable cost, for practical education, dissemination, methods development and research.
-We developed a high-performance and cost-effective two-photon microscope that can easily be built in any neuroscience laboratory over the course of several days and can be effectively used for both teaching and research purposes.
+Two-photon microscopy\cite{Denk1990, Svoboda1997} \textcolor{blue}{is a key technology across the modern life sciences\cite{Zipfel2003}, for example, in physiology\cite{Ueki2020, Dunn2002}, cancer research \cite{Perry2012}, plant biology \cite{Cheung2010}, and neuroscience\cite{So2000, Helmchen2005}.
+New scientific use cases and technological improvements are published at a remarkable rate\cite{Luu2024}.} However, these instruments \textcolor{blue}{are often published without detailed building instructions and explanations}.
+This suggests the need for an \textcolor{blue}{easy-to-set-up microscope, at reasonable cost, that can be effectively used for education, dissemination, methods development and research.} We developed a high-performance and cost-effective two-photon microscope that can \textcolor{blue}{easily be produced} in many neuroscience laboratories.
 Reflecting its use for ``\textbf{TW}o-photon \textbf{I}maging in \textbf{N}euroscience, and \textbf{K}it for \textbf{L}earning and \textbf{E}ducation'', we chose the acronym Twinkle.
-Twinkle's open design makes the building experience ideal for teaching the principles of two-photon microscopy to the next generation of researchers.
-Here, we share our design, document system performance, explore possible research applications, and report our experiences collected during several teaching workshops.
+In this article, we share our design, document the performance of the system, explore possible research applications, and report our experiences collected during several teaching workshops.
+\textcolor{blue}{Complete CAD drawings, bill of materials, optics simulations, and detailed building instructions are provided in the supplement.}
 
@@
 As the focal point probes different locations, different quantities of fluorescence signal are detected.
-An image is then formed, mapping the detector photocurrent values to the locations of excitation volume: low and high photocurrents becoming respectively dark and bright pixels.
-Central to two-photon fluorescence excitation is the light source: a femtosecond-pulsed infrared laser of sufficient pulse energy to achieve, when focused by an objective lens, a photon density high enough for simultaneous absorption of two photons by a fluorescent molecule \cite{Denk1990, Svoboda1997, So2000, Helmchen2005}.
+An image is then formed, mapping the detector photocurrent values to the locations of excitation volume: low and high photocurrents, respectively, becoming dark and bright pixels.
+Central to two-photon fluorescence excitation is the light source: a femtosecond-pulsed infrared laser of sufficient pulse energy to achieve, when focused by an objective lens, a photon density high enough for simultaneous absorption of two photons by a fluorescent molecule.
 Here, we design an open and high-performing microscope that uses these principles.
-As such we have made all optical and mechanical designs, electronics, bill of materials, CAD assembly, testing results, and relevant schematics open to the public.
-Excluding laser and optical table, the cost is around US-\$ 110k (2024).
-A narrative of the design and high-level view is presented here.
-For further technical details, and complete built documentation, we refer the reader to \nameref{S1_Appendix}, and the repository at \url{https://github.com/BrainCOGS/Microscope}.
+As such, we have made all optical and mechanical designs, electronics, bill of materials, CAD assembly, testing results, and relevant schematics open to the public.
+\textcolor{blue}{Excluding laser and optical table, the cost is around US-\$ 110k (2024).
+Including laser and table, the cost is around US-\$ 190k (2024).} A narrative of the design and the high-level view is presented here.
+For further details, we refer the reader to \nameref{S1_Appendix}.
+All code, figures and text, CAD designs, optics simulations, and BOM are available at \url{https://github.com/BrainCOGS/Microscope}.
 
@@
 An overview of the microscope is shown in Fig.~\ref{fig1}.
-Fig.~\ref{fig1}A shows the system as a cartoon.
+Fig.~\ref{fig1}A,B shows the system as a cartoon.
 Full details will be provided below.
@@
 The choice of mounted scanners simplifies the design and construction, but it also leads to some optical distortions across the field of view.
-We found that this distortion does not exceed a few percent in our design (see below).
+\textcolor{blue}{We found that this distortion does not exceed 5\% in our design (see below)}.
 The combined scan and tube lenses magnify the beam further to fill the back aperture of the objective.
 Fluorescence from the specimen is then collected and brought to the aperture of two GaAsP photomultiplier tubes with suitable color filters.
-Fig.~\ref{fig1}B shows the CAD design of the entire assembly with important parts of the optical path labelled.
-Fig.~\ref{fig1}C shows an annotated picture of the microscope head.
-Notice that compared to the cartoon in Fig.~\ref{fig1}A, the optical path is folded with several mirrors.
+Fig.~\ref{fig1}C shows the CAD design of the entire assembly with important parts of the optical path labeled.
+Fig.~\ref{fig1}D shows an annotated picture of the microscope head.
+Notice that compared to the cartoon in Fig.~\ref{fig1}A,B, the optical path is folded with several mirrors.
 These mirrors make the microscope assembly more compact.
@@
     \includegraphics[width=\textwidth]{fig1.jpg}
-    \caption{{\bf System overview.} \textbf{A)} Cartoon of the layout.
-\textbf{B)} CAD drawing of the system on an optical table with several key components in the optical path highlighted.
-The spacing between two holes on the table is 1 inch.
-\textbf{C)} Photograph of the microscope head with key elements labelled.
-This section is visible in panel B.}
+    \caption{{\bf System overview.} \textbf{A)} \textcolor{blue}{Key components of the microscope head.
+Shaded colors illustrate beam deflection angles.
+\textbf{B)} Cartoon of the beam conditioning components.
+First the beam is split by 50\%, the intensity adjusted with an electro-optic modulator (EOM) and the beam width with a telescope before entering the microscope head.
+\textbf{C)} 3D drawing of the full microscope, highlighting beam conditioning subsystem (blue) and the microscope head (yellow).
+For scale, the spacing between two holes on the optical table is 1 inch or 2.5 cm.
+\textbf{D)} Photograph of the microscope head with key elements labeled.
+This section is visible in panel A.}}
     \label{fig1}
@@
 We set the orientation of the waveplate to split the beam into equal power components, the second one being eventually used for a second microscope installed on the other extremity of the table.
-In the CAD drawing, this second beam is sent to a beam block (LB1, Thorlabs).
-Next, the beam passes through an electro-optic modulator, a Pockels cell (350-80-LA-02, Conoptics).
+In the cartoon, this second beam is sent to a beam block (LB1, Thorlabs).
+\textcolor{blue}{We want to stress that this beam-splitting hardware is optional.
+However, modern lasers have enough power to supply two microscopes at the same time.
+It is therefore often strategic to split the beam into two beams, with half of the intensity each, to allow one laser (the most expensive component) to power two systems.} Next, the beam passes through an electro-optic modulator (EOM), a Pockels cell (350-80-LA-02, Conoptics).
 This device allows rapid and electronic control of the laser's power level.
@@
 Following the shutter, the beam travels though a $2\times$ telescope (GBE02-B, Thorlabs) doubling its diameter.
-Past the telescope, the beam is then reflected off several mirrors in a periscope configuration before entering a custom aluminium box housing, mounted to a 95 mm optical rail (XT95 series, Thorlabs), that houses the two scanning mirrors (CRS8K/6215H scanning mirror set, Novanta), shown in blue in  Fig.~\ref{fig1}C.
+Past the telescope, the beam is then reflected off several mirrors in a periscope configuration before entering a custom aluminium box housing, mounted to a 95 mm optical rail (XT95 series, Thorlabs), that houses the two scanning mirrors (CRS8K/6215H scanning mirror set, Novanta), shown in blue in Fig.~\ref{fig1}D.
 Leaving the scanners, the beam then travels first through the scan lens (green) and tube lens (red), passes through the long pass dichroic mirror of the collection box assembly (yellow) and finally the objective (cyan).
@@
 \subsection*{Optical design: Scan and tube lens}
-Like for all modern microscopes, infinity-corrected objectives are being used in this design.
+Like for all modern microscopes, infinity-corrected objectives are being used in this design, see Fig.~\ref{fig1}A.
 The incident laser light has to be collimated at the back aperture of the objective.
@@
 Notice how the rays converge in the image plane.
-\textbf{B)} CAD design built around the optical design in A, see also Fig.~\ref{fig1}B.
+\textbf{B)} CAD design built around the optical design in A, see also Fig.~\ref{fig1}C.
 \textbf{C)} Cuts through the scan and tube lens assemblies, which are fabricated from off-the-shelf lenses housed in SM2 lens tubes.
@@
 Once the separation between optical elements was optimized, a model was exported in CAD (Autodesk Inventor and Fusion 360), and the optomechanics was designed around it, see Fig.~\ref{fig2}B.
-The CAD design and lens groups are highlighted in Fig.~\ref{fig2}B,C (see Fig.~\ref{fig1}C of a photograph of the same part of the instrument).
+The CAD design and lens groups are highlighted in Fig.~\ref{fig2}B,C (see Fig.~\ref{fig1}D of a photograph of the same part of the instrument).
 The key properties that we optimized when designing the excitation system was an essentially flat, and diffraction limited focal point across the deflection angle range of the scanning mirrors.
@@
 Our microscope was mounted on a 16 inch thick optical table.
-The design was done in CAD Inventor and Fusion 360 (Autodesk), and the results shown in Fig.~\ref{fig1}B.
+The design was done in CAD Inventor and Fusion 360 (Autodesk), and the results shown in Fig.~\ref{fig1}C.
 The aim was a mechanical assembly that uses as few custom parts as possible.
@@
 When used for teaching, a careful assembly and alignment is viable with about a week of work.
-Regarding the footprint, the system can comfortably be built on an $4\times4$ ft area of table.
-The microscope documented here was setup on a $4\times8$ ft table, shared with a second microscope.
-The beam-splitting hardware is shown in Fig.~\ref{fig1}B as well.\newline
+\textcolor{blue}{When set up on an imperial-unit table, the system can comfortably be built on $4\times4 \text{ ft}^2$.
+The microscope documented here was built on a $4\times8\text{ ft}^2$ ft table, shared with a second microscope.
+In metric units, our microscope has a footprint of $\approx 1.5\text{ m}^2$.
+In other words, a standard $1.2\times2.5\text{ m}^2$ table can house two of the systems described here.} The beam-splitting hardware \textcolor{blue}{used for this arrangement} is shown in Fig.~\ref{fig1}B,C as well.\newline
 The custom mechanical components (e.g.
@@
 This allows the mechanical components sufficient degrees of freedom to optically align all key parts of the microscope.
-In the supplement, \nameref{S1_Appendix}, we go through this alignment procedure in detail.
+In the supplement, we go through this alignment procedure in detail.
 
@@
 \subsection*{Ancillary hardware}
-Our microscope is controlled with ScanImage \cite{Pologruto2003} running on a Windows PC equipped with a data acquisition system (DAQ), both from the same supplier (MBF Bioscience).\newline
-Typical  Ti:Sapphire tunable femtosecond pulsed laser source can be expensive.
+Our microscope is controlled with ScanImage \cite{Pologruto2003} running on a Windows PC equipped with a data acquisition system (DAQ), both from the same supplier (MBF Bioscience).
 For the work demonstrated here, we used a fixed-wavelength femtosecond laser systems, based on fiber technology (e.g.\cite{Bueno2019,Limpert2006,Wise2012,Young2015}).
-These systems come at a fraction of the cost, and they take up significantly less real estate on an optical table.
-The laser was controlled with the same PC as ScanImage through a USB connection.
+\textcolor{blue}{These devices come at $\approx 1/3$ of the cost of a Ti:Sapphire system, and take up significantly less real estate on the optical table.} Our laser, \textcolor{blue}{an Alcor 920 manufactured by Spark Lasers}, was controlled with the same PC as ScanImage through a USB connection.
 As the beam travels through a number of crystals, lenses, and mirrors with various chromatic properties, significant dispersion is introduced which increases pulse duration, reducing the two-photon absorption efficiency.
@@
 
-\subsection*{Animal procedure}
-All procedures performed in this study were approved by the Institutional Animal Care and Use Committee at Princeton University and were performed in accordance with the Guide for the Care and Use of Laboratory Animals \cite{Guide2011}.
+\subsection*{Ethics statement}
+\textcolor{blue}{Some of the data presented here were obtained from animals.
+Our work was conducted according to internationally accepted standards and we followed all laws and regulations about animal research in the United States and Germany.
+We used vertebrate animals in the form of GCaMP6f expressing transgenic Zebrafish (\textit{Danio rerio}) for \invivo imaging.
+Fish were bred and housed at the Princeton Neuroscience Institute.
+We used five day old larvae immobilized in 2\% low melting point Agarose in E3 medium.
+Larvae were sacrificed after the imaging sessions.
+As required by law, we have obtained prior approval by the Institutional Animal Care and Use Committee at Princeton University under Protocol Number 2033.
+Further \invivo imaging work was done in the adult fruit fly (\textit{Drosophila melanogaster}).
+In the United States, work in lower-level invertebrate species like the fruit fly does not require approval by the Institutional Animal Care and Use Committee.
+We also imaged a previously prepared fixed and stained histological sample obtained from a Wistar rat (\textit{Rattus norvegicus}).
+This specific sample was made by one of us during their PhD\cite{Schottdorf2018}.
+The animal was bred in the animal house of the Max Planck Institute for Experimental Medicine according to European and German guidelines for experimental animals, and work was carried out with authorization of the responsible federal state authority.
+Finally, we imaged plant material from the common Dandilion (\textit{Taraxacum officinale}) \textit{in vivo}.
+This experiment does not require ethics approval in the United States.}
 
@@
 %
-Here, we document the performance of the microscope and a few example applications using a Nikon NA 0.8 16$\times$ LWD objective (N16XLWD-PF, Thorlabs).
-We first determined the size and properties of the field of view with a 100~\textmu m grid (R1L3S3P, Thorlabs), imaged using a Fluorescein in water film through a standard \#1.5 ($\approx170\text{ \textmu m}$ thick) coverslip, see Fig.~\ref{fig5}A.
-The field of view exceeded $\approx 1\text{ mm}^2$ ($d\approx1.3\text{ mm}$ along the diagonal), and the field curvature was below the thickness of the thin Fluorescein film $\lesssim 10\text{ \textmu m}$.
-The maximum scan angle was limited by vignetting of the two inch diameter optics (we discuss this further in the teaching section).
-When measuring the local scale in \textmu m/px at low magnification across the field of view, we observed small deviations of $\Delta S \approx 0.1\text{ \textmu m/px}$ in the center when compared to the edges, while the overall range of magnifications across the field of view was tight, see Fig.~\ref{fig5}B.
-The average scale is $S=2.77\pm0.04\text{ \textmu m/px}$, which suggests a deviation from uniformity of $\Delta S/S = 0.1/2.8 \approx 4\%$.
 %
@@
 %
+Here, we document the performance of the microscope and a few example applications using a Nikon NA 0.8 16$\times$ LWD objective (N16XLWD-PF, Thorlabs).
+We first determined the size and properties of the field of view with a 100~\textmu m grid (R1L3S3P, Thorlabs), imaged using a Fluorescein in water film through a standard \#1.5 ($\approx170\text{ \textmu m}$ thick) coverslip, see Fig.~\ref{fig5}A.
+The field of view exceeded $\approx 1\text{ mm}^2$ ($d\approx1.3\text{ mm}$ along the diagonal), and the field curvature was below the thickness of the thin Fluorescein film $\lesssim 10\text{ \textmu m}$.
+The maximum scan angle was limited by vignetting of the two inch diameter optics (we discuss this further in the teaching section).
+When measuring the local scale in \textmu m/px at low magnification across the field of view, we observed small deviations of $\Delta S \approx 0.1\text{ \textmu m/px}$ in the center when compared to the edges, while the overall range of magnifications across the field of view was tight, see Fig.~\ref{fig5}B.
+The average scale is $S=2.77\pm0.04\text{ \textmu m/px}$, which suggests a deviation from uniformity of $\Delta S/S = 0.1/2.8 \approx 4\%$.
 Next, we imaged a uniform bath of Fluorescein, see Fig.~\ref{fig5}C.
@@
 
-Confident that the system operates as intended, we next imaged a number of representative samples that are readily available to us, namely plant material, a histological and a strongly scattering sample, see Fig.~\ref{fig6}.
+We next imaged a number of representative samples that are readily available to us, namely plant material, a histological and a strongly scattering sample, see Fig.~\ref{fig6}.
 The first samples was a Dandilion flower (Taraxacum officinale) \cite{Rupprecht2018}.
@@
     \includegraphics[width=\textwidth]{fig7.jpg}
-    \caption{{\bf Example Calcium imaging in transgenic Zebrafish (Danio rerio).} \textbf{A)} 3D rendering of a 300~\textmu m deep volumetric image of a 5 day old Zebrafish larva with Fiji\cite{Schindelin2019}.
+    \caption{{\bf Example Calcium imaging in transgenic Zebrafish (Danio rerio).} \textbf{A)} 3D rendering of a 300~\textmu m deep volumetric image of a five day old Zebrafish larva with Fiji\cite{Schindelin2019}.
 \textbf{B)} Dorsal slice through the same animal and two zoom views down to cellular scale.
@@
 Twinkle was assembled, disassembled, and reassembled three times by different groups of researchers and students.
-In the following paragraphs, we summarize our experiences, and produce two examples for what we consider useful learning experiences for two-photon microscopy.\newline
+In the following paragraphs, we summarize our experiences, and produce two examples for what we consider useful learning experiences for two-photon microscopy.
+\textcolor{blue}{The detailed building instructions and additional information are available the supplement, \nameref{S1_Appendix}}.\newline
 To organize our workshop, we freed around 2 weeks in the summer.
@@
 Then reassembly began, first setting up and aligning laser and beam-splitting hardware, then the Pockels cell, the shutter, telescope, and associated beam blocks (cf.
-Fig.~\ref{fig1}B).
+Fig.~\ref{fig1}B,C).
 This was done over the course of days 1-3 during which students became familiar working with safety goggles, and aligning lasers using a power meter and cards.
@@
 Following the conditioning of the beam, we then proceeded to assemble the mechanics of the microscope head (cf.
-Fig.~\ref{fig1}C).
+Fig.~\ref{fig1}D).
 Reassembling the box housing the scanning mirrors, the lens groups from individual elements, and the collection optics was done from days 3-6 (cf.
@@
 
-In this article, we have covered the design, building and alignment of a two-photon microscope.
-We then assessed its performance, and demonstrated several possible use cases, from plant physiology over material science to neuroscience.
-In the following lines, we will expand on issues raised in passing earlier, and conclude with a note about our instrument in the growing space of open source scientific instrumentation.
-
-\subsection*{Improvements to the microscope}
-
+In this article, we have covered the design, building, and alignment of a two-photon microscope.
+We then assessed its performance and demonstrated several possible use cases, from plant physiology over material science to neuroscience.
+\textcolor{blue}{In the following paragraphs, we will expand on some recent scientific use cases of two-photon microscopy, discuss improvements to the design, elaborate on its use for education,} and conclude with a note about our instrument in the growing space of open source scientific instrumentation.
+
+\subsection*{Scientific use cases}
+\textcolor{blue}{Based on its unique ability to image with high resolution and limited photo damage deep into scattering samples, two-photon microscopy became an important tool across the life sciences.
+For example, \textit{ex vivo}, two-photon microscopy can monitor, in three dimensions, both the living and cornified keratinocytes of the epidermis, the collagen/elastin fibers in the dermal layer of the skin \cite{So1998} or the dynamics of quiescent skeletal muscle stem cells embedded in the muscle at cellular resolution \cite{Ma2024}.
+\textit{In vivo}, two-photon microscopy allows to monitor the dynamics of viral infections in the lung \cite{Ueki2020}, cell vitality and apoptosis, fluid transport, receptor-mediated endocytosis, blood flow, and leukocyte trafficking in the kidney \cite{Dunn2002},
+blood vascular hemodynamics in the thymus \cite{Seyedhassantehrani2024}, stem cells in the skin \cite{Huang2017}, produces new insights into cancer \textit{ex vivo} and \textit{in vivo} \cite{Perry2012}, and even entered clinical practice \cite{Konig2007}.\newline
+Arguably, two-photon microscope is particularly transformative in systems neuroscience because it facilitates the non-invasive measurement of fast neuronal dynamics with single cell resolution in awake and behaving animals \cite{Luu2024, Grienberger2022}.
+In the mouse, \textit{Mus musculus}, two-photon microscopes have been used to classify the function and neural inventory of the retina \cite{Baden2016}, study sequential activity in cortex \cite{Harvey2012} and subcortical structures \cite{Nieh2021}, led to transformative insights into signals in the dopaminergic reward system \cite{Engelhard2019}, and revealed an organized map among grid cells \cite{Yu2018}.
+In non-human primates, two-photon microscopes have been used as optical brain computer interfaces \cite{Trautmann2021}, and to survey the spatial organization of motor cortex in reach movements \cite{Ebina2018}.
+They also have potential to further our understanding of the function of the primate retina \cite{Sharma2016, Schottdorf2021}.
+In the Zebrafish larva, \textit{Danio rerio}, two-photon microscopy can image the entire brain with single cell resolution \cite{Renninger2013}.
+Two-photon microscopy has also become a standard method for monitoring neural activity in invertebrates.
+In the fruit fly, \textit{Drosophila melanogaster}, imaging from sparse, genetically specified neuron populations \cite{Seelig2010, Lin2022} has enabled many circuits to be functionally mapped, including auditory \cite{Baker2022}, courtship \cite{Deutsch2020, Roemschied2023}, and navigation circuits \cite{Kim2017}.
+Two-photon microscopes have also enabled volumetric pan-neuronal imaging, in which large portions of the whole fly brain can be recorded from with high temporal resolution \cite{Pacheco2021,Brezovec2024}.
+In \textit{Caenorhabditis elegans}, it allowed to measure an atlas of neural signal propagation \cite{Randi2023}.\newline
+New inventions are published regularly, such as the incorporation of adaptive optics to improve the signal amplitude \cite{Yao2023}, the combination of two-photon imaging with two-photon stimulation for all-optical interrogation of neural circuits \cite{Nikolenko2008, Packer2012,Rickgauer2014}, and extremely large fields of view for mesoscopic imaging across brain areas \cite{Sofroniew2016}.
+Recently, several approaches have also been developed to increase the size of the volumes being imaged beyond the limits set by the traditional sampling strategy while keeping the time resolution constant.
+New approaches probing extended regions rely on signal demixing to reconstitute the underlying structure \cite{Song2017, Kazemipour2019}.
+Another approach uses a set of axially separated and temporally distinct foci to record the entire axial imaging range near-simultaneously \cite{Demas2021}.
+We hope that our work here can contribute further momentum to these exciting new research avenues.}
+
+\subsection*{Improvements/modifications to the microscope}
 (1) We used silver mirrors to direct the beam.
@@
 For simplicity, and similar to other designs \cite{Sofroniew2016}, we therefore used exclusively silver mirrors.
-However, for stimulation or ablation experiments, considerations might be different.
-\newline
+However, for stimulation or ablation experiments, considerations might be different.\newline
 (2) In our design, a piezoelectric collar is attached to the objective.
-Physically moving the objective along the optical axis allows to image several planes.
+Physically moving the objective along the optical axis allows to image several planes for fast \textcolor{blue}{volumetric imaging \invivo or tissue samples \textit{ex vivo}}.
 The time required by the piezoelectric collar to stabilize can reach the scale of 10 ms when using large and heavy objectives.
 In these cases, volumetric imaging is  best achieved using a ramp where the objective is constantly moving at the same speed, rather than doing steps of constant height for every planes.
-An electrically tunable lens (ETL) can be an alternative to the piezoobjective.
-These lenses have a variable focal length, usually from around 10 cm to infinity, that can be set with a control voltage within $<1\text{ ms}$.
-\newline
+An electrically tunable lens (ETL) \cite{Chen2016} or \textcolor{blue}{remote focusing} \cite{Botcherby2007} are an alternative to the piezoelectric collar.
+\textcolor{blue}{These techniques are necessary when the objective is difficult to move (such as a very heavy objective) or cannot be moved, for example during volumetric imaging combined with controlled stimulation, as moving the objective would also change the location of the stimulation spots.}\newline
 (3) Estimating the pulse duration suggests non-linear dispersion that we cannot correct.
@@
 That said, even when underfilled by the excitation beam, a large NA of the objective is beneficial to collect as much fluorescent light as possible.\newline
-(6) It can be interesting to some to combine the two-photon system with wide-field imaging.
+\textcolor{blue}{(6) When imaging fixed samples, movement artifacts are not an issue.
+For such experiments, particularly \textit{ex vivo} work, it would be strategic to fully fill the back aperture of the objective and produce a PSF that is as tight as possible.}\newline
+\textcolor{blue}{(7) Using an objective with an even larger numerical aperture can significantly increase collection efficiency.
+Our objective choice was made with long working distance in mind.
+Our $16\times$ water-immersion objective with a numerical aperture of 0.8 accepts around $36\%$ of the $4\pi$ square radiants of emission.
+A possible alternative, the Nikon $25\times$ with a slightly smaller 2 mm working distance, offers a numerical aperture of 1.10 and would collect $68\%$ of light; close to a $2\times$ improvement to collection efficiency.}\newline
+\textcolor{blue}{(8) Our microscope exhibits (small) field curvature.
+In neuroscience, field curvature is often not considered critical because samples are rarely flat.
+If the microscope was used for precision length measurements, for example in \textit{ex vivo} tissue samples or for lithography purposes, one would want to optimize field flatness.
+Very small field curvature can be obtained with commercial f-theta scan lenses.}\newline
+\textcolor{blue}{(9) Resonant scanning mirrors are fast, but cannot be steered.
+If a user was interested in imaging custom ROIs, the scanning mirror pair could be replaced with a pair of slow galvanometic mirrors, which can be controlled with high precision.}\newline
+(10) For some applications, it can be beneficial to combine the two-photon system with wide-field imaging.
 To this end, the two inch mirror above the collection optics can be replaced with a 800 or 900 nm short-pass filter followed by a tube lens and a camera.
-This would allow infrared imaging around 700 nm through the collection optics, as it is transparent above 665 nm.
-While this is relatively straightforward to do \cite{Rosenegger2014}, widefield epipfluorescence is harder to realize.\newline
-(7) Our fluorescence filters have an average optical density $>4$ in the range between 400 nm and 460 nm.
+This would allow infrared (IR) imaging around 700 nm through the collection optics, as it is transparent above 665 nm.
+\textcolor{blue}{Infrared illumination can be provided with an LED and a semitransparent mirror.
+This mirror could conveniently be housed in a flip mount to be removed from the optical path when the system is used for 2p imaging.} While this is relatively straightforward to implement \cite{Rosenegger2014}, wide-field fluorescence microscopy is harder to realize.\newline
+(11) Our fluorescence filters have an average optical density $>4$ in the range between 400 nm and 460 nm.
 This is advantageous for use in virtual reality systems, because light leaving a projector can be filtered to this range before projected on a dome surrounding the objective and animal.
@@
 This is a useful range for visual experiments in mice, but if other model organisms are desired, the optical filters need to be adjusted accordingly.\newline
-(8) Parts of our microscope can be replaced with commercial products.
+(12) Parts of our microscope can be replaced with commercial products.
 For example, we have used commercial telecentric scan lenses in the past \cite{Song2017, Rich2024} in combination with a three inch diameter tube lens.
@@
 While low field curvature is not always considered the highest priority in neuroscience applications, this can be a useful substitution.\newline
-(9) To aid mechanical stability, the aluminium plate forming the base of the head of the microscope could be replaced with a steel plate, or a thicker piece of aluminium, that is less prone to vibrations when bumped into.
+(13) To aid mechanical stability, the aluminium plate forming the base of the head of the microscope could be replaced with a steel plate, or a thicker piece of aluminium, that is less prone to vibrations when bumped into.
 This would also be important if one wanted to extend the microscope head to provide even more space around the objective.
@@
 \cite{Sheppard2020, Yao2023}.\newline
-Students might also become interested in further optimizing the optical design, or wonder why many lenses are used in lens groups.
-Questions like these can sometimes be linked to prior student knowledge.
+Students might also become interested in further optimizing the optical design, or wonder why many lenses are \textcolor{blue}{doublets and} used in lens groups.
+\textcolor{blue}{Some of these questions have intuitive answers.
+Doublets, for example, contain more glass surfaces that can be optimized to produce a better performing lens when compared to the two surfaces of a singlet\cite{ThorlabsLens}.
+To our knowledge, the first mentioning of the minimization of aberration by placement of several subsequent doublets was done by Joseph Lister in 1830 \cite{Lister1830}.
+This idea was used for many designs, including pairs of doublets in Pl\"ossl and Petzval eye pieces, or objectives themselves \cite{Zhang2019}}.
+Other questions can sometimes be linked to prior student knowledge.
 For example, for students interested in astronomy, the tube lens can be thought of as an eye piece with a long focal length and eye relief \cite{Smith2007}.
@@
 The lens in the human eye then focuses the collimated beams onto the retina.
-Pl\"ossl designs in astronomy are known to perform particularly well for long eye relief \cite{Smith2007, Nagler1983}, and are a common design in two-photon microscopes as well (e.g.
+The aforementioned Pl\"ossl designs are known to perform particularly well for long eye relief in astronomy \cite{Smith2007, Nagler1983}, and are a common design in two-photon microscopes as well (e.g.
 \cite{Rupprecht2024}).
@@
 Small surface imperfections will introduce optical difference across spot positions, and significantly affect field flatness, cf.
-Fig.~\ref{fig5}C,D,E.\newline
+Fig.~\ref{fig5}C,D,E.
+\textcolor{blue}{Small misalignment in the optical path can also lead to characteristic image artifacts, for illustrations see\cite{Corbett2014, Lees2024}, that can help to develop an intuition about how the system operates.}\newline
 Finally, it can be a useful learning experience to re-use parts from other microscopes, such as xy scanners from a confocal microscope\cite{Nikolenko2013}, and to mix and match parts to learn what works and what does not.
@@
 In this article, we described the instrument's mode of operation, and provide an overview of the design.
-For the complete and illustrated built instructions, please see \nameref{S1_Appendix} and our \nameref{repository}.
+For complete and illustrated built instructions, see the attached \nameref{S1_Appendix} and our \nameref{repository}.
 To aid discoverability, we have generated an Open Know How Manifest (OKH-manifest), located in the Online Repository.
@@
 The growing space of open-source instrumentation can improve science in several ways: (1) enabling faster innovation through lower costs and enabling work in low-resource settings.
-(2) facilitating review and inspection by avoiding black-box designs and (3) providing a benchmark for innovation towards next-generation technology.
-We hope that our instrument, combined with earlier designs \cite{Rosenegger2014, Mayrhofer2015, Tan1999}, and recent developments like the head mounted microscope \cite{Zong2022} or the Janelia Research Campus microscope \cite{Janelia2024}, can serve as a benchmark for future instruments.
+(2) Facilitating review and inspection by avoiding black-box designs and (3) providing a benchmark for innovation towards next-generation technology \cite{Lees2024}.
+We hope that our instrument, combined with earlier designs \cite{Rosenegger2014, Mayrhofer2015, Tan1999}, and recent developments, like the head mounted microscope \cite{Zong2022}, or the Janelia Research Campus microscope \cite{Janelia2024}, can serve as a benchmark for future instruments.
 Relatedly, we have contributed to other projects that follow this philosophy in microscopy \cite{Scott2018}, but also designing an open source ventilator during the COVID-19 pandemic \cite{LaChance2022,POVMC2022}, and a \textmu-contact printing device \cite{Samhaber2016}.
@@
 We recommend anyone embarking on this journey to engage with the community, to carefully think about effective solutions to their use-case and specific experiment at hand, and to adjust to the ever changing landscape of available technology.
-When adapting the optical path to their needs, we suggest to start at our lens combinations, and then optimize (at the very least) the lens spacings in Zemax.
-Technology develops rapidly, and many of the specific components mentioned here will be outdated in a few years.
-We believe that science progresses best if researchers understand their instrumentation, and leverage the current cutting edge of what is possible to further their science.\newline
+When adapting the optical path to their needs, we suggest starting at our lens combinations and then optimizing (at the very least) the lens spacings in Zemax.
+Technology develops rapidly and many of the specific components mentioned here will be outdated in a few years.
+We believe that science progresses best if researchers understand their instrumentation and leverage the current cutting edge of what is possible to further their science.\newline
 This work is free: you can redistribute it and/or modify it under the terms of the Creative Commons Attribution 4.0 International license, version 4 of the License, or (at your option) any later version (CC-BY-4.0).
@@
 
-\paragraph*{S1 Appendix}
+\paragraph*{S1 Appendix. This contains detailed construction instructions and technical details.}
 \label{S1_Appendix}
-A document with detailed build instructions and pictures of the microscope.
-
-\paragraph*{Online Repository}
+\textcolor{blue}{A \texttt{.pdf} file with numerous pictures, annotations, and detailed step-by-step building instructions for the microscope.
+The raw code, pictures, and vectorized versions of the figures are available in the online repository.}
+
+\paragraph*{Online Repository. This contains all the underlying materials of this article.}
 \label{repository}
-All CAD and optics design files, bill of materials, and other useful information: \url{https://github.com/BrainCOGS/Microscope}.
+\textcolor{blue}{A repository, hosted on github, including code, \texttt{.svg} figures, and the raw \texttt{.tex} files for this article and its supplement.
+In addition, we provide all CAD and optical design files, material billing and other useful information.
+The CAD files are provided in several standard formats.
+We have used Fusion 360.
+The optical design was performed in Ansys' OpticStudio (Zemax): \url{https://github.com/BrainCOGS/Microscope}.}
 
 \section*{Acknowledgments}
-MS and MD are supported by NIH grant U19NS132720.
-MS is also supported by a C.V.
-Starr fellowship and a Burroughs Wellcome Fund's Career Award at the Scientific Interface.
-AL was supported by the NSF through the Center for the Physics of Biological Function (PHY-1734030).
-We thank Beatrice Hadiwidjaja for transgenic Zebrafish husbandry, and Drs.
+\textcolor{blue}{We thank Beatrice Hadiwidjaja for the transgenic zebrafish husbandry and Drs.
 Lindsay Collins and Anthony Ambrosini for hospitality and accommodating our tinkering in the teaching lab of the Princeton Neuroscience Institute.
-We thank Kai Br\"oking for helpful comments.
+We thank Kai Br\"oking and Peter Rupprecht for helpful comments on the manuscript.}
 
@@
     \item \textbf{Conceptualization}: Stephan Y. Thiberge.
-    \item \textbf{Data curation}: Manuel Schottdorf, Mika Diamanti, Albert Lin, Stephan Y. Thiberge.
+    \item \textbf{Data curation}: Manuel Schottdorf, E. Mika Diamanti, Albert Lin, Stephan Y. Thiberge.
     \item \textbf{Formal analysis}: Manuel Schottdorf, E. Mika Diamanti, Albert Lin.
     \item \textbf{Funding acquisition}: Stephan Y. Thiberge.
-    \item \textbf{Investigation}: Manuel Schottdorf, P. Dylan Rich, E. Mika Diamanti, Albert Lin, Sina Tafazoli, Edward Nieh.
+    \item \textbf{Investigation}: Manuel Schottdorf, P. Dylan Rich, E. Mika Diamanti, Albert Lin, Sina Tafazoli, Edward H. Nieh.
     \item \textbf{Methodology}: Manuel Schottdorf, P. Dylan Rich, E. Mika Diamanti, Albert Lin, Sina Tafazoli, Edward H. Nieh, Stephan Y. Thiberge. 
@@
     \item \textbf{Writing – original draft}: Manuel Schottdorf.
-    \item \textbf{Writing – review \& editing}: Manuel Schottdorf, P. Dylan Rich, E. Mika Diamanti, Albert Lin, Sina Tafazoli, Stephan Thiberge.
+    \item \textbf{Writing – review \& editing}: Manuel Schottdorf, P. Dylan Rich, E. Mika Diamanti, Albert Lin, Sina Tafazoli, Stephan Y. Thiberge.
 \end{itemize}
@@
 
+\bibitem{Zipfel2003}
+Zipfel WR, Williams RM, Webb WW. Nonlinear magic: multiphoton microscopy in the biosciences. Nat Biotechnol. 2003 Nov;21(11):1369-77. doi: 10.1038/nbt899. PMID: 14595365.
+
+\bibitem{Ueki2020}
+Ueki H, Wang IH, Zhao D, Gunzer M, Kawaoka Y.
+Multicolor two-photon imaging of in vivo cellular pathophysiology upon influenza virus infection using the two-photon IMPRESS.
+Nat Protoc.
+2020 Mar;15(3):1041-1065.
+doi: 10.1038/s41596-019-0275-y.
+Epub 2020 Jan 29.
+PMID: 31996843; PMCID: PMC7086515.
+
+\bibitem{Dunn2002}
+Dunn KW, Sandoval RM, Kelly KJ, Dagher PC, Tanner GA, Atkinson SJ, Bacallao RL, Molitoris BA.
+Functional studies of the kidney of living animals using multicolor two-photon microscopy.
+Am J Physiol Cell Physiol.
+2002 Sep;283(3):C905-16.
+doi: 10.1152/ajpcell.00159.2002.
+PMID: 12176747.
+
+\bibitem{Perry2012}
+Perry SW, Burke RM, Brown EB.
+Two-photon and second harmonic microscopy in clinical and translational cancer research.
+Ann Biomed Eng.
+2012 Feb;40(2):277-91.
+doi: 10.1007/s10439-012-0512-9.
+Epub 2012 Jan 19.
+PMID: 22258888; PMCID: PMC3342697.
+
+\bibitem{Cheung2010}
+Cheung AY, Boavida LC, Aggarwal M, Wu HM, Feijó JA.
+The pollen tube journey in the pistil and imaging the in vivo process by two-photon microscopy.
+J Exp Bot.
+2010 Apr;61(7):1907-15.
+doi: 10.1093/jxb/erq062.
+Epub 2010 Apr 2.
+PMID: 20363865.
+
 \bibitem{So2000}
@@
 \bibitem{Helmchen2005}
-Helmchen F, Denk W. Deep tissue two-photon microscopy. Nat Methods. 2005 Dec;2(12):932-40. PMID: 16299478.
+Helmchen F, Denk W. Deep tissue two-photon microscopy. Nat Methods. 2005 Dec;2(12):932-40. doi: 10.1038/nmeth818. Erratum in: Nat Methods. 2006 Mar;3(3):235. PMID: 16299478.
 
@@
 Luu P, Fraser SE, Schneider F. More than double the fun with two-photon excitation microscopy. Commun Biol. 2024 Mar 26;7(1):364. doi: 10.1038/s42003-024-06057-0. PMID: 38531976; PMCID: PMC10966063.
+
+\bibitem{Bueno2019}
+Bueno JM, Ávila FJ, Artal P.
+Comparing the performance of a femto fiber-based laser and a Ti:sapphire used for multiphoton microscopy applications.
+Appl Opt.
+2019 May 10;58(14):3830-3835.
+doi: 10.1364/AO.58.003830.
+PMID: 31158196.
+
+\bibitem{Rosenegger2014}
+Rosenegger DG, Tran CH, LeDue J, Zhou N, Gordon GR.
+A high performance, cost-effective, open-source microscope for scanning two-photon microscopy that is modular and readily adaptable.
+PLoS One.
+2014 Oct 21;9(10):e110475.
+doi: 10.1371/journal.pone.0110475.
+PMID: 25333934; PMCID: PMC4204885.
+
+\bibitem{Mayrhofer2015}
+Mayrhofer JM, Haiss F, Haenni D, Weber S, Zuend M, Barrett MJ, Ferrari KD, Maechler P, Saab AS, Stobart JL, Wyss MT, Johannssen H, Osswald H, Palmer LM, Revol V, Schuh CD, Urban C, Hall A, Larkum ME, Rutz-Innerhofer E, Zeilhofer HU, Ziegler U, Weber B.
+Design and performance of an ultra-flexible two-photon microscope for in vivo research.
+Biomed Opt Express.
+2015 Oct 2;6(11):4228-37.
+doi: 10.1364/BOE.6.004228.
+PMID: 26600989; PMCID: PMC4646533.
+
+\bibitem{Janelia2024}
+Modular In Vivo Multi-photon Microscope 2.2 \url{https://www.janelia.org/open-science/mimms-22-2024}.
+
+\bibitem{Botcherby2007}
+Botcherby EJ, Juskaitis R, Booth MJ, Wilson T. Aberration-free optical refocusing in high numerical aperture microscopy. Opt Lett. 2007 Jul 15;32(14):2007-9. doi: 10.1364/ol.32.002007. PMID: 17632625.
+
+\bibitem{Botcherby2012}
+Botcherby EJ, Smith CW, Kohl MM, Débarre D, Booth MJ, Juškaitis R, Paulsen O, Wilson T.
+Aberration-free three-dimensional multiphoton imaging of neuronal activity at kHz rates.
+Proc Natl Acad Sci U S A.
+2012 Feb 21;109(8):2919-24.
+doi: 10.1073/pnas.1111662109.
+Epub 2012 Feb 6.
+PMID: 22315405; PMCID: PMC3286923.
+
+\bibitem{Sofroniew2016}
+Sofroniew NJ, Flickinger D, King J, Svoboda K.
+A large field of view two-photon mesoscope with subcellular resolution for in vivo imaging.
+Elife.
+2016 Jun 14;5:e14472.
+doi: 10.7554/eLife.14472.
+PMID: 27300105; PMCID: PMC4951199.
+
+\bibitem{Yao2023}
+Yao P, Liu R, Broggini T, Thunemann M, Kleinfeld D.
+Construction and use of an adaptive optics two-photon microscope with direct wavefront sensing.
+Nat Protoc.
+2023 Dec;18(12):3732-3766.
+doi: 10.1038/s41596-023-00893-w.
+Epub 2023 Nov 1.
+PMID: 37914781; PMCID: PMC11033548.
+
+\bibitem{Kidger2001}
+M. J. Kidger. Fundamental Optical Design. (SPIE, 2001). \url{https://spie.org/Publications/Book/397107}.
+
+\bibitem{Negrean2014}
+Negrean A, Mansvelder HD. Optimal lens design and use in laser-scanning microscopy. Biomed Opt Express. 2014 Apr 18;5(5):1588-609. doi: 10.1364/BOE.5.001588. PMID: 24877017; PMCID: PMC4026907.
+
+\bibitem{Smith2007}
+W. J. Smith. Modern Optical Engineering, 4th ed. (McGraw-Hill Professional, 2007). \url{https://spie.org/Publications/Book/781851}.
+
+\bibitem{Hong2022}
+Hong W, Dunsby C. Automatic tube lens design from stock optics for microscope remote-refocusing systems. Opt Express. 2022 Jan 31;30(3):4274-4287. doi: 10.1364/OE.450320. PMID: 35209667.
+
+\bibitem{Bumstead2018}
+Bumstead JR, Park JJ, Rosen IA, Kraft AW, Wright PW, Reisman MD, Côté DC, Culver JP.
+Designing a large field-of-view two-photon microscope using optical invariant analysis.
+Neurophotonics.
+2018 Apr;5(2):025001.
+doi: 10.1117/1.NPh.5.2.025001.
+Epub 2018 Feb 19.
+PMID: 29487876; PMCID: PMC5818100.
+
+\bibitem{Tsai2015}
+Tsai PS, Mateo C, Field JJ, Schaffer CB, Anderson ME, Kleinfeld D.
+Ultra-large field-of-view two-photon microscopy.
+Opt Express.
+2015 Jun 1;23(11):13833-47.
+doi: 10.1364/OE.23.013833.
+PMID: 26072755; PMCID: PMC4523368.
+
+\bibitem{Young2015}
+Young MD, Field JJ, Sheetz KE, Bartels RA, Squier J.
+A pragmatic guide to multiphoton microscope design.
+Adv Opt Photonics.
+2015 Jun 30;7(2):276-378.
+doi: 10.1364/AOP.7.000276.
+PMID: 27182429; PMCID: PMC4863715.
+
+\bibitem{Tsai2002}
+Tsai PS, et al.
+Principles, design, and construction of a two photon laser scanning microscope for in vitro and in vivo brain imaging.
+In: Frostig RD, editor.
+In Vivo Optical Imaging of Brain Function.
+CRC Press; Boca Raton: 2002.
+pp.
+113–171.
+\url{https://neurophysics.ucsd.edu/publications/tsai_book_chapter_crc_2002.pdf}.
+
+\bibitem{Pologruto2003}
+Pologruto TA, Sabatini BL, Svoboda K.
+ScanImage: flexible software for operating laser scanning microscopes.
+Biomed Eng Online.
+2003 May 17;2:13.
+doi: 10.1186/1475-925X-2-13.
+PMID: 12801419; PMCID: PMC161784.
+
+\bibitem{Limpert2006}
+Limpert J, Roser F, Schreiber T, Tunnermann A. High-power ultrafast fiber laser systems. IEEE Journal of Selected Topics in Quantum Electronics. 2006;12(2):233-244. doi: 10.1109/JSTQE.2006.872729.
+
+\bibitem{Wise2012}
+Wise FW.
+Femtosecond Fiber Lasers Based on Dissipative Processes for Nonlinear Microscopy.
+IEEE J Sel Top Quantum Electron.
+2012;18(4):1412-1421.
+doi: 10.1109/JSTQE.2011.2179919.
+PMID: 23869163; PMCID: PMC3712536.
+
+\bibitem{Song2017}
+Song A, Charles AS, Koay SA, Gauthier JL, Thiberge SY, Pillow JW, Tank DW.
+Volumetric two-photon imaging of neurons using stereoscopy (vTwINS).
+Nat Methods.
+2017 Apr;14(4):420-426.
+doi: 10.1038/nmeth.4226.
+Epub 2017 Mar 20.
+PMID: 28319111; PMCID: PMC5551981.
+
+\bibitem{Schottdorf2018}
+Schottdorf M. The reconstitution of visual cortical feature selectivity in vitro. PhD Thesis 2018. \url{http://dx.doi.org/10.53846/goediss-6721}.
+
+\bibitem{Rupprecht2018}
+Rupprecht P. Springtime for two-photon microscopy. Blogpost April 25 2018, \url{https://gcamp6f.com/2018/04/25/springtime-for-two-photon-microscopy/}.
+
+\bibitem{Nguyen2001}
+Nguyen QT, Callamaras N, Hsieh C, Parker I. Construction of a two-photon microscope for video-rate Ca(2+) imaging. Cell Calcium. 2001 Dec;30(6):383-93. doi: 10.1054/ceca.2001.0246. PMID: 11728133.
+
+\bibitem{Cong2017}
+Cong L, Wang Z, Chai Y, Hang W, Shang C, Yang W, Bai L, Du J, Wang K, Wen Q.
+Rapid whole brain imaging of neural activity in freely behaving larval zebrafish (Danio rerio).
+Elife.
+2017 Sep 20;6:e28158.
+doi: 10.7554/eLife.28158.
+PMID: 28930070; PMCID: PMC5644961.
+
+\bibitem{Schindelin2019}
+Schindelin J, Arganda-Carreras I, Frise E, Kaynig V, Longair M, Pietzsch T, Preibisch S, Rueden C, Saalfeld S, Schmid B, Tinevez JY, White DJ, Hartenstein V, Eliceiri K, Tomancak P, Cardona A.
+Fiji: an open-source platform for biological-image analysis.
+Nat Methods.
+2012 Jun 28;9(7):676-82.
+doi: 10.1038/nmeth.2019.
+PMID: 22743772; PMCID: PMC3855844.
+
+\bibitem{Pachitariu2016}
+Pachitariu M, Stringer C, Schröder S, Dipoppa M, Rossi LF, Carandini M, Harris KD.
+(2016).
+Suite2p: beyond 10,000 neurons with standard two-photon microscopy.
+BioRxiv, 061507.
+\url{https://www.biorxiv.org/content/10.1101/061507v2}.
+
+\bibitem{Pacheco2021}
+Pacheco DA, Thiberge SY, Pnevmatikakis E, Murthy M.
+Auditory activity is diverse and widespread throughout the central brain of Drosophila.
+Nat Neurosci.
+2021 Jan;24(1):93-104.
+doi: 10.1038/s41593-020-00743-y.
+Epub 2020 Nov 23.
+PMID: 33230320; PMCID: PMC7783861.
+
+\bibitem{Saidi2023}
+Saidi S, Shtrahman M.
+Evaluation of compact pulsed lasers for two-photon microscopy using a simple method for measuring two-photon excitation efficiency.
+Neurophotonics.
+2023 Oct;10(4):044303.
+doi: 10.1117/1.NPh.10.4.044303.
+Epub 2023 Nov 14.
+PMID: 38076726; PMCID: PMC10704185.
+
+\bibitem{So1998}
+So P, Kim H, Kochevar I. Two-Photon deep tissue ex vivo imaging of mouse dermal and subcutaneous structures. Opt Express. 1998 Oct 26;3(9):339-50. doi: 10.1364/oe.3.000339. PMID: 19384379.
+
+\bibitem{Ma2024}
+Ma N, Mourkioti F.
+Ex vivo two-photon imaging of whole-mount skeletal muscles to visualize stem cell behavior.
+STAR Protoc.
+2024 Mar 15;5(1):102772.
+doi: 10.1016/j.xpro.2023.102772.
+Epub 2023 Dec 11.
+PMID: 38085638; PMCID: PMC10733746.
+
+\bibitem{Seyedhassantehrani2024}
+Seyedhassantehrani N, Burns CS, Verrinder R, Okafor V, Abbasizadeh N, Spencer JA.
+Intravital two-photon microscopy of the native mouse thymus.
+PLoS One.
+2024 Aug 1;19(8):e0307962.
+doi: 10.1371/journal.pone.0307962.
+PMID: 39088574; PMCID: PMC11293686.
+
+\bibitem{Huang2017}
+Huang S, Rompolas P.
+Two-photon microscopy for intracutaneous imaging of stem cell activity in mice.
+Exp Dermatol.
+2017 May;26(5):379-383.
+doi: 10.1111/exd.13221.
+Epub 2017 Feb 20.
+PMID: 27676122; PMCID: PMC7405986.
+
+\bibitem{Konig2007}
+K\"onig K, Ehlers A, Riemann I, Schenkl S, Bückle R, Kaatz M. Clinical two-photon microendoscopy. Microsc Res Tech. 2007 May;70(5):398-402. doi: 10.1002/jemt.20445. PMID: 17393493.
 
@@
 
-\bibitem{Pacheco2021}
-Pacheco DA, Thiberge SY, Pnevmatikakis E, Murthy M.
-Auditory activity is diverse and widespread throughout the central brain of Drosophila.
-Nat Neurosci.
-2021 Jan;24(1):93-104.
-doi: 10.1038/s41593-020-00743-y.
-Epub 2020 Nov 23.
-PMID: 33230320; PMCID: PMC7783861.
-
 \bibitem{Brezovec2024}
-Bella E.
-Brezovec, Andrew B.
-Berger, Yukun A.
-Hao, Feng Chen, Shaul Druckmann, Thomas R.
-Clandinin, Mapping the neural dynamics of locomotion across the Drosophila brain, Current Biology, Volume 34, Issue 4, 2024,
-Pages 710-726.e4, ISSN 0960-9822, https://doi.org/10.1016/j.cub.2023.12.063.
+Brezovec BE, Berger AB, Hao YA, Chen F, Druckmann S, Clandinin TR.
+Mapping the neural dynamics of locomotion across the Drosophila brain.
+Curr Biol.
+2024 Feb 26;34(4):710-726.e4.
+doi: 10.1016/j.cub.2023.12.063.
+Epub 2024 Jan 18.
+PMID: 38242122.
 
@@
 
-\bibitem{Diamanti2021}
-Diamanti EM, Reddy CB, Schröder S, Muzzu T, Harris KD, Saleem AB, Carandini M.
-Spatial modulation of visual responses arises in cortex with active navigation.
-Elife.
-2021 Feb 4;10:e63705.
-doi: 10.7554/eLife.63705.
-PMID: 33538692; PMCID: PMC7861612.
-
-\bibitem{Yao2023}
-Yao P, Liu R, Broggini T, Thunemann M, Kleinfeld D.
-Construction and use of an adaptive optics two-photon microscope with direct wavefront sensing.
-Nat Protoc.
-2023 Dec;18(12):3732-3766.
-doi: 10.1038/s41596-023-00893-w.
-Epub 2023 Nov 1.
-PMID: 37914781; PMCID: PMC11033548.
-
 \bibitem{Rickgauer2014}
@@
 PMID: 23142873; PMCID: PMC3518588.
-
-\bibitem{Sofroniew2016}
-Sofroniew NJ, Flickinger D, King J, Svoboda K.
-A large field of view two-photon mesoscope with subcellular resolution for in vivo imaging.
-Elife.
-2016 Jun 14;5:e14472.
-doi: 10.7554/eLife.14472.
-PMID: 27300105; PMCID: PMC4951199.
-
-\bibitem{Song2017}
-Song A, Charles AS, Koay SA, Gauthier JL, Thiberge SY, Pillow JW, Tank DW.
-Volumetric two-photon imaging of neurons using stereoscopy (vTwINS).
-Nat Methods.
-2017 Apr;14(4):420-426.
-doi: 10.1038/nmeth.4226.
-Epub 2017 Mar 20.
-PMID: 28319111; PMCID: PMC5551981.
 
@@
 
-\bibitem{Bueno2019}
-Bueno JM, Ávila FJ, Artal P.
-Comparing the performance of a femto fiber-based laser and a Ti:sapphire used for multiphoton microscopy applications.
-Appl Opt.
-2019 May 10;58(14):3830-3835.
-doi: 10.1364/AO.58.003830.
-PMID: 31158196.
-
-\bibitem{Rosenegger2014}
-Rosenegger DG, Tran CHT, LeDue J, Zhou N, Gordon GR (2014) A High Performance, Cost-Effective, Open-Source Microscope for Scanning Two-Photon Microscopy that Is Modular and Readily Adaptable.
-PLoS ONE 9(10): e110475.
-https://doi.org/10.1371/journal.pone.0110475
-
-\bibitem{Mayrhofer2015}
-Mayrhofer JM, Haiss F, Haenni D, Weber S, Zuend M, Barrett MJ, Ferrari KD, Maechler P, Saab AS, Stobart JL, Wyss MT, Johannssen H, Osswald H, Palmer LM, Revol V, Schuh CD, Urban C, Hall A, Larkum ME, Rutz-Innerhofer E, Zeilhofer HU, Ziegler U, Weber B.
-Design and performance of an ultra-flexible two-photon microscope for in vivo research.
-Biomed Opt Express.
-2015 Oct 2;6(11):4228-37.
-doi: 10.1364/BOE.6.004228.
-PMID: 26600989; PMCID: PMC4646533.
-
-\bibitem{Janelia2024}
-Modular In Vivo Multi-photon Microscope 2.2 \url{https://www.janelia.org/open-science/mimms-22-2024}
-
-\bibitem{Botcherby2007}
-Botcherby EJ, Juskaitis R, Booth MJ, Wilson T. Aberration-free optical refocusing in high numerical aperture microscopy. Opt Lett. 2007 Jul 15;32(14):2007-9. doi: 10.1364/ol.32.002007. PMID: 17632625.
-
-\bibitem{Botcherby2012}
-Botcherby EJ, Smith CW, Kohl MM, Débarre D, Booth MJ, Juškaitis R, Paulsen O, Wilson T.
-Aberration-free three-dimensional multiphoton imaging of neuronal activity at kHz rates.
-Proc Natl Acad Sci U S A.
-2012 Feb 21;109(8):2919-24.
-doi: 10.1073/pnas.1111662109.
-Epub 2012 Feb 6.
-PMID: 22315405; PMCID: PMC3286923.
-
-\bibitem{Kidger2001}
-M. J. Kidger, Fundamental Optical Design (SPIE, 2001).
-
-\bibitem{Negrean2014}
-Negrean A, Mansvelder HD. Optimal lens design and use in laser-scanning microscopy. Biomed Opt Express. 2014 Apr 18;5(5):1588-609. doi: 10.1364/BOE.5.001588. PMID: 24877017; PMCID: PMC4026907.
-
-\bibitem{Smith2007}
-W. J. Smith, Modern Optical Engineering, 4th ed. (McGraw-Hill Professional, 2007).
-
-\bibitem{Hong2022}
-Hong W, Dunsby C. Automatic tube lens design from stock optics for microscope remote-refocusing systems. Opt Express. 2022 Jan 31;30(3):4274-4287. doi: 10.1364/OE.450320. PMID: 35209667.
-
-\bibitem{Bumstead2018}
-Bumstead JR, Park JJ, Rosen IA, Kraft AW, Wright PW, Reisman MD, Côté DC, Culver JP.
-Designing a large field-of-view two-photon microscope using optical invariant analysis.
-Neurophotonics.
-2018 Apr;5(2):025001.
-doi: 10.1117/1.NPh.5.2.025001.
-Epub 2018 Feb 19.
-PMID: 29487876; PMCID: PMC5818100.
-
-\bibitem{Tsai2015}
-Tsai PS, Mateo C, Field JJ, Schaffer CB, Anderson ME, Kleinfeld D.
-Ultra-large field-of-view two-photon microscopy.
-Opt Express.
-2015 Jun 1;23(11):13833-47.
-doi: 10.1364/OE.23.013833.
-PMID: 26072755; PMCID: PMC4523368.
-
-\bibitem{Young2015}
-Young MD, Field JJ, Sheetz KE, Bartels RA, Squier J.
-A pragmatic guide to multiphoton microscope design.
-Adv Opt Photonics.
-2015 Jun 30;7(2):276-378.
-doi: 10.1364/AOP.7.000276.
-PMID: 27182429; PMCID: PMC4863715.
-
-\bibitem{Tsai2002}
-Tsai PS, et al.
-Principles, design, and construction of a two photon laser scanning microscope for in vitro and in vivo brain imaging.
-In: Frostig RD, editor.
-In Vivo Optical Imaging of Brain Function.
-CRC Press; Boca Raton: 2002.
-pp.
-113–171.
-\url{https://neurophysics.ucsd.edu/publications/tsai_book_chapter_crc_2002.pdf}
-
-\bibitem{Pologruto2003}
-Pologruto TA, Sabatini BL, Svoboda K. ScanImage: Flexible software for operating laser scanning microscopes. BioMed Eng OnLine 2, 13 (2003). \url{https://doi.org/10.1186/1475-925X-2-13}
-
-\bibitem{Limpert2006}
-J.
-Limpert, F.
-Roser, T.
-Schreiber, A.
-Tunnermapnn, High-power ultrafast fiber laser systems.
-in IEEE Journal of Selected Topics in Quantum Electronics, vol.
-12, no.
-2, pp.
-233-244, March-April 2006, doi: 10.1109/JSTQE.2006.872729.
-
-\bibitem{Wise2012}
-Wise FW.
-Femtosecond Fiber Lasers Based on Dissipative Processes for Nonlinear Microscopy.
-IEEE J Sel Top Quantum Electron.
-2012;18(4):1412-1421.
-doi: 10.1109/JSTQE.2011.2179919.
-PMID: 23869163; PMCID: PMC3712536.
-
-\bibitem{Guide2011}
-National Research Council (US) Committee for the Update of the Guide for the Care and Use of Laboratory Animals.
-Guide for the Care and Use of Laboratory Animals.
-8th ed.
-Washington (DC): National Academies Press (US); 2011.
-PMID: 21595115.
-
-\bibitem{Rupprecht2018}
-Rupprecht P. Springtime for two-photon microscopy. Blogpost April 25 2018, \url{https://gcamp6f.com/2018/04/25/springtime-for-two-photon-microscopy/}
-
-\bibitem{Nguyen2001}
-Nguyen QT, Callamaras N, Hsieh C, Parker I. Construction of a two-photon microscope for video-rate Ca(2+) imaging. Cell Calcium. 2001 Dec;30(6):383-93. doi: 10.1054/ceca.2001.0246. PMID: 11728133.
-
-\bibitem{Cheung2010}
-Cheung AY, Boavida LC, Aggarwal M, Wu HM, Feijó JA.
-The pollen tube journey in the pistil and imaging the in vivo process by two-photon microscopy.
-J Exp Bot.
-2010 Apr;61(7):1907-15.
-doi: 10.1093/jxb/erq062.
-Epub 2010 Apr 2.
-PMID: 20363865.
-
-\bibitem{Schottdorf2018}
-Schottdorf M. The reconstitution of visual cortical feature selectivity in vitro. PhD Thesis 2018. \url{http://dx.doi.org/10.53846/goediss-6721}
-
-\bibitem{Cong2017}
-Cong L, Wang Z, Chai Y, Hang W, Shang C, Yang W, Bai L, Du J, Wang K, Wen Q.
-Rapid whole brain imaging of neural activity in freely behaving larval zebrafish (Danio rerio).
-Elife.
-2017 Sep 20;6:e28158.
-doi: 10.7554/eLife.28158.
-PMID: 28930070; PMCID: PMC5644961.
-
-\bibitem{Schindelin2019}
-Schindelin J, Arganda-Carreras I, Frise E, Kaynig V, Longair M, Pietzsch T, Preibisch S, Rueden C, Saalfeld S, Schmid B, Tinevez JY, White DJ, Hartenstein V, Eliceiri K, Tomancak P, Cardona A.
-Fiji: an open-source platform for biological-image analysis.
-Nat Methods.
-2012 Jun 28;9(7):676-82.
-doi: 10.1038/nmeth.2019.
-PMID: 22743772; PMCID: PMC3855844.
-
-\bibitem{Pachitariu2016}
-Pachitariu M, Stringer C, Schröder S, Dipoppa M, Rossi LF, Carandini M, Harris KD.
-(2016).
-Suite2p: beyond 10,000 neurons with standard two-photon microscopy.
-BioRxiv, 061507.
-\url{https://www.biorxiv.org/content/10.1101/061507v2}
-
-\bibitem{Zipfel2003}
-Zipfel WR, Williams RM, Webb WW. Nonlinear magic: multiphoton microscopy in the biosciences. Nat Biotechnol. 2003 Nov;21(11):1369-77. doi: 10.1038/nbt899. PMID: 14595365.
-
-\bibitem{Saidi2023}
-Saidi S, Shtrahman M.
-Evaluation of compact pulsed lasers for two-photon microscopy using a simple method for measuring two-photon excitation efficiency.
-Neurophotonics.
-2023 Oct;10(4):044303.
-doi: 10.1117/1.NPh.10.4.044303.
-Epub 2023 Nov 14.
-PMID: 38076726; PMCID: PMC10704185.
-
 \bibitem{Rupprecht2019}
@@
 Zenodo.
-https://doi.org/10.5281/zenodo.2592465 \url{https://ptrrupprecht.github.io/Photon-yield-and-pulse-dispersion/}
+https://doi.org/10.5281/zenodo.2592465 \url{https://ptrrupprecht.github.io/Photon-yield-and-pulse-dispersion/}.
+
+\bibitem{Chen2016}
+Chen JL, Voigt FF, Javadzadeh M, Krueppel R, Helmchen F.
+Long-range population dynamics of anatomically defined neocortical networks.
+Elife.
+2016 May 24;5:e14679.
+doi: 10.7554/eLife.14679.
+PMID: 27218452; PMCID: PMC4929001.
 
@@
 Humana, New York, NY.
-\url{https://doi.org/10.1007/978-1-4939-9702-2_1}
+\url{https://doi.org/10.1007/978-1-4939-9702-2_1}.
 
@@
 
+\bibitem{ThorlabsLens}
+Thorlabs Lens tutorial: Achromatic Lenses. 2024. \url{https://www.thorlabs.com/newgrouppage9.cfm?objectgroup_id=8790}.
+
+\bibitem{Lister1830}
+Lister JJ. XIII. On some properties in achromatic object-glasses applicable to the improvement of the microscope. Phil. Trans. R. Soc. 1830 Jan; 120: 187-200. doi: 10.1098/rstl.1830.0015
+
+\bibitem{Zhang2019}
+Zhang, Y, Gross, H. Systematic design of microscope objectives. Part I: System review and analysis. Adv. Opt. Techn. 2019. 8(5): 313-347. doi: 10.1515/aot-2019-0002
+
 \bibitem{Nagler1983}
-Nagler A. Plossl type eyepiece for use in astronomical instruments. US-Patent US4482217A 1983
-\url{https://patents.google.com/patent/US4482217A/en}
+Nagler A. Plossl type eyepiece for use in astronomical instruments. US-Patent US4482217A. 1983.
+\url{https://patents.google.com/patent/US4482217A/en}.
 
@@
 \bibitem{Rudolf1897}
-Rudolf P. Objekt-Glass. US-Patent US583336A 1897 \url{https://patents.google.com/patent/US583336A/en}.
+Rudolf P. Objekt-Glass. US-Patent US583336A. 1897. \url{https://patents.google.com/patent/US583336A/en}.
+
+\bibitem{Corbett2014}
+Corbett AD, Burton RA, Bub G, Salter PS, Tuohy S, Booth MJ, Wilson T.
+Quantifying distortions in two-photon remote focussing microscope images using a volumetric calibration specimen.
+Front Physiol.
+2014 Oct 8;5:384.
+doi: 10.3389/fphys.2014.00384.
+PMID: 25339910; PMCID: PMC4189333.
+
+\bibitem{Lees2024}
+Lees RM, Bianco IH, Campbell RAA, Orlova N, Peterka DS, Pichler B, Smith SL, Yatsenko D, Yu CH, Packer AM.
+Standardised Measurements for Monitoring and Comparing Multiphoton Microscope Systems.
+bioRxiv [Preprint].
+2024 Jan 23:2024.01.23.576417.
+doi: 10.1101/2024.01.23.576417.
+PMID: 38328224; PMCID: PMC10849699.
 
@@
 \bibitem{Zajdel2016}
-Zajdel TJ, Maharbiz MM (2016) Teaching design with a tinkering-driven robot hack. Proceedings of 2016 IEEE Frontiers in Education Conference (FIE) \url{https://ieeexplore.ieee.org/document/7757484}
+Zajdel TJ, Maharbiz MM (2016) Teaching design with a tinkering-driven robot hack. Proceedings of 2016 IEEE Frontiers in Education Conference (FIE) \url{https://ieeexplore.ieee.org/document/7757484}.
 
@@
 The Princeton Open Ventilation Monitor Collaboration et al.
-Inexpensive Multipatient Respiratory Monitoring Syshttps://www.yapsutube.com/watch?v=uYOF-YggWAgtem for Helmet Ventilation During COVID-19 Pandemic.
+Inexpensive Multipatient Respiratory Monitoring System for Helmet Ventilation During COVID-19 Pandemic.
 ASME.
@@
 Devices.
-March 2022; 16(1): 011003.
-https://doi.org/10.1115/1.4053386
+2022 March; 16(1):011003.
+doi: 10.1115/1.4053386.
 
@@
 \bibitem{Suo2021}
-D.
-Suo, U.
-Ghai, E.
-Minasyan, P.
-Gradu, X.
-Chen, N.
-Agarwal, C.
-Zhang, K.
-Singh, J.
-LaChance, T.
-Zajdel, M.
-Schottdorf, D.
-Cohen, E.
-Hazan.
-Machine Learning for Medical Ventilator Control”, Machine Learning for Health (ML4H), available on arXiv: 2102.06779 (2022)
+Suo D, Ghai U, Minasyan E, Gradu P, Chen X, Agarwal N, Zhang C, Singh K, LaChance J, Zajdel T, Schottdorf M, Cohen D, Hazan E.
+Machine Learning for Medical Ventilator Control.
+Machine Learning for Health (ML4H) at NeurIPS.
+2021.
+doi: 10.48550/arXiv.2111.10434.
+arXiv: 2102.06779 (2022)
 
 \bibitem{Schottdorf2024}
-Schottdorf M, Yu G, Walker EY.
-Data science and its future in large neuroscience collaborations.
-bioRxiv [Preprint].
-2024 Mar 25:2024.03.20.585936.
-doi: 10.1101/2024.03.20.585936.
-PMID: 38585895; PMCID: PMC10996530.
+Schottdorf M, Yu G, Walker EY. Data science and its future in large neuroscience collaborations. Neuron. 2024 Sep 25;112(18):3007-3012. doi: 10.1016/j.neuron.2024.08.017. PMID: 39326391.
 

### 2024-12-28 documentation/supplement.tex
Revision of article
Addresses the reviewer concerns:
(1) Changes to text and organization
(2) New Fig 1 and suppl. Fig. 11

@@
 \usepackage{wasysym}
+\usepackage{mathbbol}
 
@@
 \newcommand{\invivo}{\textit{in vivo}~}
+\newcommand{\complexi}{i}
 %% END MACROS SECTION
@@
 
-\subsection{Miscellaneous tools}
-\begin{itemize}
-    \item Use a high quality duster to remove any residue from optical surfaces.
+\subsection{Miscellaneous tools and tips}
+The following tools are used throughout the build process:
+\begin{itemize}
+    \item A high quality duster to remove any residue from optical surfaces.
 We use a Miller-Stephenson Aero-Duster Ultra MS-222L, in addition to lens tissues (MC-5, Thorlabs) and Methanol (Sigma-Aldrich).
@@
 \end{itemize}
-
-\subsection{Miscellaneous tips}
+%
+The following general tips might be of help as well:
 \begin{itemize}
@@
 \subsection{Beam conditioning}
-An overview of the system for beam conditioning is shown in Fig.~\ref{sfig1} with key items labelled by capital letters. The following lines will cover the items, and their alignment.
+An overview of the system for beam conditioning is shown in Fig.~\ref{sfig1} with key items labeled by capital letters. The following lines will cover the items, and their alignment.
 %
@@
     \caption{{\bf Overall view of the beam conditioning path on the optical table.} Shown is a photograph of the components used to condition the beam for our microscope.
-Key components of the system are labelled with capital letters.
+Key components of the system are labeled with capital letters.
 The laser is shown as a red transparent line with intensity color coded.
@@
     \caption{{\bf Overall view of the scanning post.} \textbf{A)} Side few.
-Key components of the system are labelled with capital letters.
+Key components of the system are labeled with capital letters.
 These are explained in the text together with a note on how to align these components.
-Importantly, the machined block (C) houses the scanning mirrors, and the scan lens assembly is placed in the SM2 house labelled (E).
+Importantly, the machined block (C) houses the scanning mirrors, and the scan lens assembly is placed in the SM2 house labeled (E).
 \textbf{B)} Frontal view.
@@
     \includegraphics[width=\textwidth]{sfig5.jpg}
-    \caption{{\bf Overall view of the microscope head.} Key components of the system are labelled with capital letters.
+    \caption{{\bf Overall view of the microscope head.} Key components of the system are labeled with capital letters.
 These are explained in the text together with a note on how to align these components.}
@@
     \includegraphics[width=.5\textwidth]{sfig6.jpg}
-  \caption{{\bf Side view of the microscope head.} Key components of the system are labelled with capital letters.
+  \caption{{\bf Side view of the microscope head.} Key components of the system are labeled with capital letters.
 These are explained in the text together with a note on how to align these components.\newline
@@
 The function is described in the main manuscript.
-A pictures of the collection optics box is shown in Fig.~\ref{sfig9}B with key components labelled.
+A pictures of the collection optics box is shown in Fig.~\ref{sfig9}B with key components labeled.
 Here, we will focus on the assembly and their alignment.
@@
 \textbf{B)} The collection optics during the assembly process, similar to panel A.
-Key components are labelled (see text).
+Key components are labeled (see text).
 EDITS TO MAKE IN THE ARROWS}
@@
     \caption{{\bf The scanning mirror box.} \textbf{A)} The custom aluminium box housing the pair of scanning mirrors.
-\textbf{B)} Close-up of the same box with key parts labelled: A: Two windows (WG11010-B, Thorlabs) to keep dust out.
+\textbf{B)} Close-up of the same box with key parts labeled: A: Two windows (WG11010-B, Thorlabs) to keep dust out.
 B: Attachment of the box to the 95 mm optical rail.
@@
   \caption{{\bf Scanner electronics.} \textbf{A)} Overview of all scanning mirror parts.
-Key parts are labelled with capital letters.
+Key parts are labeled with capital letters.
 Optomechanics were covered in Fig.~\ref{sfig10}.
 All electrical drivers were placed in the yellow circuit box.
-\textbf{B)} Power supply and connection of the scanning mirrors with key parts labelled by capital letters.
-The inset shows the scanning mirror driver boards provided by Novanta and mounted in the yellow circuit box.
+\textbf{B)} Power supply and connection of the scanning mirrors with key parts labeled by capital letters.
+\textcolor{blue}{\textbf{C)} Wiring diagram for the $\pm 28\text{ V}$ power supply, using two galvanically isolated supplies.
+\textbf{D)} The scanning mirror driver boards, provided by Novanta, and mounted in the yellow circuit box.
 The smaller driver circuit (blue) powers the resonant scanner.
 The larger circuit board (green) drives the slow galvanometer.
-The circuit boards are mounted to the aluminium walls with screws and heat transfer compound.}
+The circuit boards are mounted to the aluminium walls with screws and heat transfer compound.
+\textbf{E)} Same box as in D, but from the outside and key parts labeled by capital letters.}}
   \label{sfig11}
@@
 This overall improves dynamical properties.
-The controller requires three voltage inputs, respectively -28 V, 0 V, and +28 V.
-The 0 V is also grounded.
-The second power supply to the left provides 12 V for the resonant scanner.
-The supplies are connected to the power supply ports on the prototype box, and the signal lines are connected to the MBF Bioscience DAQ system.
-Key components in the figure are labelled with capital letters.
+The controller for the slow scanner requires three supplies respectively: -28 V, 0 V, and +28 V.
+\\
+\textcolor{blue}{To provide these three signals, we used a power supply with two galvanically isolated and adjustable output channels, that can be connected in series (Note: not every power supply can do this.
+We used a GPD-3303D from Gw Instek that allows this function with the SER/INDEP key).
+The voltage of each of the two unconnected channels was set to +28 V.
+To produce the three supply signals, we used these two channels in series.
+In other words, we connect the positive terminal of the first channel to the negative terminal of the second channel.
+As the channels are otherwise not connected to a common ground (this is meant with the words ``galvanically isolated''), this does not produce a short circuit.
+Instead, this link effectively provides a new reference point, relative to which the first supply produces a negative -28 V supply, and the second supply produces the +28 V supply.
+This is illustrated in Fig.~\ref{sfig11}C.
+In this arrangement, a multimeter would read between points G and I +28 V, between G and F -28 V, and between F and I +56 V.
+The supply of the resonant scanners is simpler, as it only requires a single +12 V line.
+The supplies are connected to the power supply ports on the prototype box, in which the two driver boards reside, see Fig.~\ref{sfig11}D.
+Signal lines are connected on the outside with coaxial cables to the MBF Bioscience DAQ system, see Fig.~\ref{sfig11}E.} Key components in the panels are labeled with capital letters.
 These are as follows:
@@
     \item \textbf{B)} Have CH 1 turned on.
-    \item \textbf{C)} Press the ``Ser/Indep'' button. This wires the two channels together to a shared references to provide the $\pm 28\text{ V}$ and the 0 V reference line.
-    \item \textbf{D)} This enables our power supply unit. Only when pressed, power is sourced to the galvanometer driver board.
+    \item \textbf{C)} Press the ``Ser/Indep'' button. This wires the two channels together to a shared references to provide the $\pm 28\text{ V}$ and the 0 V reference line, see Fig.~\ref{sfig11}C.
+    \item \textbf{D)} This button enables our power supply unit. Only when pressed, power is sourced to the galvanometer driver board.
     \item \textbf{E)} CC/CV indicator light. Make sure that the device is set to CV (constant voltage).
-    \item \textbf{F)} The -28 V output line (black). This is connected to the -28 V line on the electronics box (shown below).
-    \item \textbf{G)} The reference lines, 0 V (white) connected to the 0 V line on the electronics box.
+    \item \textbf{F)} The -28 V output line (black). This is connected to the -28 V line on the electronics box (shown below in Fig.~\ref{sfig11}E).
+    \item \textbf{G)} The reference lines, 0 V (white) connected to the 0 V line on the electronics box, see Fig.~\ref{sfig11}E.
     \item \textbf{H)} Connects the reference line to ground.
@@
 Component B are the two potentiometers to set the two channel gains.
-\textbf{B)} Inside view of the potentiometer box with key components labelled (see text).
+\textbf{B)} Inside view of the potentiometer box with key components labeled (see text).
 \textbf{C)} Connector attached to the controller box before plugging into the PMTs.
@@
     \item It is recommended to periodically image a bead sample to validate the PSF, as well as a Fluorescein bath to detect possible misalignment.
+For a detailed protocol, see Lees et al.
+\cite{Lees2024}.
     \item Be mindful of imaging artifacts. When suspecting an issue, go back to the basics, and isolate the error.
@@
 
+\section{Deriving the intensity-dispersion relation}
+\textcolor{blue}{In the main article, we stated that the expected fluorescence $I(\varphi)$ as function of group delay dispersion $\varphi$ applied to a $\varphi_0$-dispersed Gaussian pulse of full-width-at-half-maximum $\Delta\tau$ can be written as
+\begin{eqnarray}
+    I(\varphi)=I_0 \left(1+16\log(2)^2\frac{(\varphi+\varphi_0)^2}{\Delta\tau^4}\right)^{-1/2}\label{main}.
+\end{eqnarray}
+To derive this expression, consider the electrical field of a Gaussian pulse of amplitude $E_0$, width $\Delta t$, center frequency $\omega_0$, phase $\Theta$, and centered at time $t=0$:
+\begin{eqnarray}
+E(t)=E_0\exp\left(-\frac{t^2}{4\Delta t^2}\right)\cdot\exp\left(-\complexi\left(\omega_0 t + \Theta\right)\right).
+\end{eqnarray}
+Its intensity is 
+\begin{eqnarray}
+P(t) = |E(t)|^2 = |E_0|^2 \exp\left(-\frac{t^2}{2\Delta t^2}\right)\label{intens}.
+\end{eqnarray}
+In the Fourier domain, the spectral content of this wave package is:
+\begin{eqnarray}
+\tilde{E}(\omega)=E_0\cdot\sqrt{2}\Delta t\, \exp\left(-\complexi\,\Theta -\Delta t^2(\omega - \omega_0)^2\right).
+\end{eqnarray}
+In the linear regime, frequency-dependent dispersion changes the electric field to
+\begin{eqnarray}
+\tilde{E}(\omega)\to\tilde{E}(\omega)\cdot\exp\left(\complexi\,\phi(\omega-\omega_0)\right)
+\end{eqnarray}
+with phase shift $\phi(\omega-\omega_0)$.
+We approximate this function to quadratic order $\phi(\omega-\omega_0)\approx a + b(\omega-\omega_0) + \frac{c}{2}(\omega-\omega_0)^2$.
+With this approximation, we obtain the Fourier representation of the electric field of the dispersed pulse:
+\begin{eqnarray}
+\tilde{E}^\text{disp}(\omega)=\tilde{E}(\omega)\cdot\exp\left(\complexi\,\left(a + b(\omega-\omega_0) + \frac{c}{2}(\omega-\omega_0)^2\right)\right).
+\end{eqnarray}
+Coefficient $a$ causes a phase shift and coefficient $b$ a time shift.
+Both do not change pulse width.
+Computing the inverse Fourier transform to obtain $E^\text{disp}(t)$ allows to compute the intensity of the dispersed pulse as
+\begin{eqnarray}
+P^\text{disp}(t) = |E^\text{disp}(t)|^2 = |E_0|^2\frac{2\Delta t^2}{\sqrt{c^2 + 4\Delta t^4}}\exp\left(-\frac{2(b+t)^2\Delta t^2}{c^2+4\Delta t^4}\right)\label{intens_disp}.
+\end{eqnarray}
+If the average power of the laser across dispersion compensation settings $c$ is constant, the prefactor is approximately constant.
+Comparison with Eq.
+\eqref{intens} then shows that the pulse has broadened in time to $\Delta t\to \frac{\sqrt{c^2+4\Delta t^4}}{2\Delta t}$.
+Rewriting the widths of the dispersed pulse in the more common full-width-at-half-maximum $\Delta\tau$, using $\Delta t \to \Delta\tau/\sqrt{8\log(2)}$ for a Gaussian pulse, we obtain
+\begin{eqnarray}
+\Delta\tau^\text{disp} = \frac{\sqrt{\Delta\tau^4 + 16\log(2)^2c^2}}{2 \Delta\tau\sqrt{\log(4)}}.
+\end{eqnarray}
+The two-photon fluorescence intensity $I$ is proportional to the inverse of the pulse width, and the group delay dispersion is composed of the original dispersion $\varphi_0$ and the applied correction $\varphi$, so that $c \to \varphi_0 + \varphi$.
+We obtain
+\begin{eqnarray}
+I(\varphi) \propto \frac{1}{\Delta\tau^\text{disp}} = \frac{2 \Delta\tau\sqrt{\log(4)}}{\sqrt{\Delta\tau^4 + 16\log(2)^2(\varphi_0 + \varphi)^2}} = \frac{2\sqrt{\log(4)}}{\Delta\tau}\frac{1}{\sqrt{1 + 16\log(2)^2\frac{(\varphi_0 + \varphi)^2}{\Delta\tau^4}}}.
+\end{eqnarray}
+Absorbing the constants $\frac{2\sqrt{\log(4)}}{\Delta\tau}\to I_0$ yields Eq.~\eqref{main}.
+The same result for pulse broadening, with $16\log(2)^2\approx 7.68\dots$, is stated as Eq.~(3) in \cite{Zipfel2003}.
+}
 \nolinenumbers
@@
 
+\bibitem{Lees2024}
+Lees RM, Bianco IH, Campbell RAA, Orlova N, Peterka DS, Pichler B, Smith SL, Yatsenko D, Yu CH, Packer AM.
+Standardised Measurements for Monitoring and Comparing Multiphoton Microscope Systems.
+bioRxiv [Preprint].
+2024 Jan 23:2024.01.23.576417.
+doi: 10.1101/2024.01.23.576417.
+PMID: 38328224; PMCID: PMC10849699.
+
+\bibitem{Zipfel2003}
+Zipfel WR, Williams RM, Webb WW. Nonlinear magic: multiphoton microscopy in the biosciences. Nat Biotechnol. 2003 Nov;21(11):1369-77. doi: 10.1038/nbt899. PMID: 14595365.
+
 \end{thebibliography}

### 2025-01-03 article/Article.tex
A few more typos fixed; text streamlined

@@
 It is a fully open, high performing and \textcolor{blue}{easy-to-set-up microscope that can effectively be used for both education and research}.
-The instrument features \textcolor{blue}{a $>1\text{ mm}^2$ field of view}, using a modern objective with \textcolor{blue}{3 mm} working distance and \textcolor{blue}{two inch diameter optics combined with GaAsP photomultiplier tubes} to maximize the fluorescence signal.
+The instrument features \textcolor{blue}{a $>1\text{ mm}$ field of view}, using a modern objective with \textcolor{blue}{3 mm} working distance and \textcolor{blue}{two inch diameter optics combined with GaAsP photomultiplier tubes} to maximize the fluorescence signal.
 We document our experiences using this system as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open-source scientific instrumentation.
@@
 In two-photon laser-scanning microscopy\cite{Denk1990}, laser light is focused to a small excitation volume,  the ``focal point'', which is moved across the sample by the intermediary of resonant and galvanometric scanning mirrors.
-As the focal point probes different locations, different quantities of fluorescence signal are detected.
-An image is then formed, mapping the detector photocurrent values to the locations of excitation volume: low and high photocurrents, respectively, becoming dark and bright pixels.
+As the focal point probes different locations, different quantities of fluorescence light are produced by the sample.
+\textcolor{blue}{This light is collected by a sensitive detector in the form of an electronically measurable photocurrent.} An image is then formed, mapping the detector photocurrent values to the locations of excitation volume: low and high photocurrents, respectively, becoming dark and bright pixels.
 Central to two-photon fluorescence excitation is the light source: a femtosecond-pulsed infrared laser of sufficient pulse energy to achieve, when focused by an objective lens, a photon density high enough for simultaneous absorption of two photons by a fluorescent molecule.
 Here, we design an open and high-performing microscope that uses these principles.
-As such, we have made all optical and mechanical designs, electronics, bill of materials, CAD assembly, testing results, and relevant schematics open to the public.
+As such, we have made all optical and mechanical designs, electronics, bill of materials (BOM), CAD assembly, testing results, and relevant schematics open to the public.
 \textcolor{blue}{Excluding laser and optical table, the cost is around US-\$ 110k (2024).
-Including laser and table, the cost is around US-\$ 190k (2024).} A narrative of the design and the high-level view is presented here.
+Including laser and table, the cost is around US-\$ 200k (2024).} A narrative of the design and the high-level view is presented here.
 For further details, we refer the reader to \nameref{S1_Appendix}.
-All code, figures and text, CAD designs, optics simulations, and BOM are available at \url{https://github.com/BrainCOGS/Microscope}.
+All code, figures and text, CAD designs, optics simulations, and BOM are available on  \url{https://github.com/BrainCOGS/Microscope} \textcolor{blue}{and on Zenodo \cite{Zenodo2024}.}
 
 \subsection*{Design specifications}
-To summarize our design goals, we aimed for a mechanical and optical assembly using as many off-the-shelf components as possible, with only few custom aluminium parts that can be machined in any university machine shop.
+We aimed for a mechanical and optical assembly using as many off-the-shelf components as possible, with only few custom aluminium parts that can be machined in any university machine shop.
 Our design  facilitates the adaptation for \invivo imaging by providing a large space for the organism and ancillary hardware.
@@
 Operating at a fixed wavelength, these systems come at the fraction of the cost of a tunable Ti:Sapphire laser \cite{Bueno2019}.\newline
-We aimed for (1) $\gtrapprox20\text{ cm}$ of free space around the objective in all directions to aid integration of the microscope with various peripheral equipment such as behavior recording and stimulation, and the sample stage, and (2) imaging on a  $\approx 700\times 700\text{ \textmu m}^2$ minimum size field of view which is typical for imaging brain tissue at cellular resolution.
+More specifically, we aimed for (1) $\gtrapprox20\text{ cm}$ of free space around the objective in all directions to aid integration of the microscope with various peripheral equipment such as behavior boxes or a sample stage, and (2) imaging on a  $\approx 700\times 700\text{ \textmu m}^2$ minimum size field of view which is typical for imaging brain tissue at cellular resolution.
 (3) Compared to earliest open designs\cite{Rosenegger2014, Mayrhofer2015}, our system can make use of the large Numerical Aperture (NA) of  modern long-working-distance objectives to collect more fluorescence, but requires to adapt our design to their larger back apertures \cite{Janelia2024}.\newline
@@
 Full details will be provided below.
-In short, we chose a Spark Alcor 920 nm femtosecond pulsed laser, whose beam diameter is  extended by a $2\times$ magnification telescope, before it reaches the scanning mirrors.
+In short, we chose a 920 nm femtosecond pulsed laser, whose beam diameter is extended by a $2\times$ magnification telescope, before it reaches the scanning mirrors.
 The scanning mirrors are purchased as a mount-assembled set.
 Located as close as possible to each other, as we will see in the alignment procedure, neither of them can be exactly positioned in the focal plane of the scan lens.
-The choice of mounted scanners simplifies the design and construction, but it also leads to some optical distortions across the field of view.
+The choice of mounted scanners simplifies the design and construction, but leads to optical distortions across the field of view.
 \textcolor{blue}{We found that this distortion does not exceed 5\% in our design (see below)}.
-The combined scan and tube lenses magnify the beam further to fill the back aperture of the objective.
+The combined scan and tube lenses magnify the beam further to fill the objective's back aperture.
 Fluorescence from the specimen is then collected and brought to the aperture of two GaAsP photomultiplier tubes with suitable color filters.
@@
 \textcolor{blue}{When set up on an imperial-unit table, the system can comfortably be built on $4\times4 \text{ ft}^2$.
-The microscope documented here was built on a $4\times8\text{ ft}^2$ ft table, shared with a second microscope.
+The microscope documented here was built on a $4\times8\text{ ft}^2$ table, shared with a second microscope.
 In metric units, our microscope has a footprint of $\approx 1.5\text{ m}^2$.
@@
 We mount the circuit boards in a custom electronics box (Gold Box, Acopian), making sure to use heat transfer compound between the circuit boards and the aluminium box, and to mount them securely together with screws.
-At time of purchase, we requested the controller of the slow galvanometer to be configured for usage at $\pm 28\text{ V}$ (the manufacturer default is $\pm 24\text{ V}$ ).
-This overall improves dynamical properties.
-The controller requires three voltage inputs, respectively -28 V, 0 V, and +28 V.
-The 0 V is also grounded.
-The second power supply provides 12 V for the resonant scanner.
+At time of purchase, we requested the controller of the slow galvanometer to be configured for usage at $\pm 28\text{ V}$ (the manufacturer default is $\pm 24\text{ V}$).
+In our experience, this  improves dynamical properties.
+The controller requires three supply lines, -28 V, 0 V, and +28 V.
+\textcolor{blue}{To provide these voltages, we used a power supply with two galvanically isolated and adjustable outputs (not every power supply supports this function).
+The voltage of each of the two channels was set to +28 V.
+To produce the three supplies, we used these two channels in series.
+In other words, we connect the positive terminal of the first channel to the negative terminal of the second channel.
+As the channels are otherwise not connected to a common ground (this is meant with the words ``galvanically isolated''), this does not produce a short circuit.
+Instead, this link effectively provides a new reference point, relative to which the first supply produces a negative -28 V supply, and the second supply produces the +28 V supply.
+More details are provided in the supplement.} The second power supply provides 12 V for the resonant scanner.
 It is beneficial to choose a power supply that can stably produce these voltages for years.
@@
     \includegraphics[width=\textwidth]{fig6.jpg}
-    \caption{{\bf Example imaging data from simple samples.} \textbf{A)} Autofluorescence of a part of a dandilion flower (Taraxacum officinale) \textit{in vivo}.
+    \caption{{\bf Example imaging data from simple samples.} \textbf{A)} Autofluorescence of a part of a dandilion flower (\textit{Taraxacum officinale}) \textit{in vivo}.
 Notice the pollen grains embedded in the plant material.
@@
 We next imaged a number of representative samples that are readily available to us, namely plant material, a histological and a strongly scattering sample, see Fig.~\ref{fig6}.
-The first samples was a Dandilion flower (Taraxacum officinale) \cite{Rupprecht2018}.
+The first samples was a Dandilion flower (\textit{Taraxacum officinale}) \cite{Rupprecht2018}.
 Autofluorescence in plant material is a good test to separate compounds fluorescing in the red and green channels respectively, while also exhibiting complex three-dimensional structure \cite{Cheung2010, Nguyen2001}.
@@
 Fig.~\ref{fig5}), the image quality here deteriorates with depth.\newline
-Next, we imaged neural activity \textit{in vivo} in both larval zebrafish (Danio rerio) and adult \textit{Drosophila melanogaster}. 
+Next, we imaged neural activity \textit{in vivo} in both larval zebrafish (\textit{Danio rerio}) and adult \textit{Drosophila melanogaster}. 
 %
@@
 Neurons in this organism express the fluorescent protein GCaMP6f in their nuclei whose green fluorescence strongly depends on the cellular concentration of Calcium ions.
-We imaged a 5-day old larva immobilized in 2\% low melting point Agarose in E3 medium, see Fig.~\ref{fig7}.
+We imaged a five day old larva immobilized in 2\% low melting point Agarose in E3 medium, see Fig.~\ref{fig7}.
 We first performed a volumetric scan of the organism, Fig.~\ref{fig7}A shows a rendering in Fiji \cite{Schindelin2019}, and then focused on a plane with a large number of visible neurons, Fig.~\ref{fig7}B.
@@
 We imaged 6-day-old transgenic adult flies which express GCaMP6s and myr-tdTomato pan-neuronally, labeling all neurons cytoplasmically.
-We volumetrically imaged a volume approximately 300 x 350 x 50 ~\textmu m in scale, spanning a fraction of the central brain of the fly (Fig.~\ref{fig8}B).
+We volumetrically imaged a volume approximately $300\times350\times50 \text{ \textmu m}^3$ in scale, spanning a fraction of the central brain of the fly (Fig.~\ref{fig8}B).
 We then motion-corrected and segmented the GCaMP6s volume into regions of interest (ROIs) with spatial clustering algorithms \cite{Pacheco2021}, revealing diverse spontaneous calcium activity (Fig.~\ref{fig8}C).
@@
 Reassembling the box housing the scanning mirrors, the lens groups from individual elements, and the collection optics was done from days 3-6 (cf.
-Fig.~\ref{fig2}, \ref{fig3}, \ref{fig4}) After this was done, we assessed the performance of the instrument and fine tuned it on days 7-8 (cf.
+Figs.~\ref{fig2}, \ref{fig3}, \ref{fig4}) After this was done, we assessed the performance of the instrument and fine tuned it on days 7-8 (cf.
 Fig.~\ref{fig5}).
@@
 If students are interested in dispersion of the laser pulse and its correction, a more challenging experiment and analysis are shown in Fig.~\ref{fig9}B.
-Here, students used the fluorescence at fixed laser power for different values of dispersion compensation to infer the laser pulse width.
+Here, students used the fluorescence at fixed laser power for different values of the dispersion compensation to infer the laser pulse width without the use of an additional autocorrelator.
 This is possible because the efficiency of two-photon fluorescence depends inversely on the pulse duration \cite{Denk1990, Zipfel2003}.
@@
 This suggests detectable non-linear dispersion that we cannot compensate with our optics.
-Note that analyses like these, relating laser physics and fluorescence, are close to the research frontier\cite{Saidi2023}.
+Note that analyses like these, relating laser physics and fluorescence, are close to the research frontier\cite{Piazza2016,Saidi2023}.
 
@@
 \textcolor{blue}{Infrared illumination can be provided with an LED and a semitransparent mirror.
-This mirror could conveniently be housed in a flip mount to be removed from the optical path when the system is used for 2p imaging.} While this is relatively straightforward to implement \cite{Rosenegger2014}, wide-field fluorescence microscopy is harder to realize.\newline
+This mirror could conveniently be housed in a flip mount to be removed from the optical path when the system is used for two-photon imaging.} While this is relatively straightforward to implement \cite{Rosenegger2014}, wide-field fluorescence microscopy is harder to realize.\newline
 (11) Our fluorescence filters have an average optical density $>4$ in the range between 400 nm and 460 nm.
@@
 In addition to training researchers on how to set up a two-photon microscope, we aimed to provide examples of imaging data that are not neuroscience related, and do not require the handling of animals or living neurons (cf.
-Fig.~\ref{fig5}, \ref{fig6}, \ref{fig9}).
+Figs.~\ref{fig5}, \ref{fig6}, \ref{fig9}).
 Other samples are possible as well (such as cheese \cite{Nguyen2001}).
@@
 For example, the simulated point spread functions and their analysis in Fig.~\ref{fig2} were computed in Matlab, using the Zemax API.
-The code is provided in our repository.
+The code is provided in our repository \cite{Zenodo2024}.
 This allows for fast optimization of system parameters by effectively scanning through lens spacing, lens types, and the like.
@@
 The scan lens assembly is particularly sensitive to this, because the incoming laser beam is concentrated into a small region that gets scanned across the surface of the lens.
-Small surface imperfections will introduce optical difference across spot positions, and significantly affect field flatness, cf.
+Small surface imperfections will introduce noticeable differences across spot positions, and significantly affect field flatness, cf.
 Fig.~\ref{fig5}C,D,E.
 \textcolor{blue}{Small misalignment in the optical path can also lead to characteristic image artifacts, for illustrations see\cite{Corbett2014, Lees2024}, that can help to develop an intuition about how the system operates.}\newline
-Finally, it can be a useful learning experience to re-use parts from other microscopes, such as xy scanners from a confocal microscope\cite{Nikolenko2013}, and to mix and match parts to learn what works and what does not.
+Finally, it can be a useful learning experience to re-use parts from other microscopes, such as XY scanners from a confocal microscope\cite{Nikolenko2013}, and to mix and match parts to learn what works and what does not.
 It is an important learning experience to understand failure modes.
@@
 \subsection*{Open scientific instrumentation}
-In this article, we described the instrument's mode of operation, and provide an overview of the design.
-For complete and illustrated built instructions, see the attached \nameref{S1_Appendix} and our \nameref{repository}.
+In this article, we summarized the instrument's mode of operation, and provided a design overview.
+For complete and illustrated building instructions, see the attached \nameref{S1_Appendix} and our \nameref{repository}.
 To aid discoverability, we have generated an Open Know How Manifest (OKH-manifest), located in the Online Repository.
 Our project is also certified by the open source hardware association (OSHWA UID US002677).\newline
-The growing space of open-source instrumentation can improve science in several ways: (1) enabling faster innovation through lower costs and enabling work in low-resource settings.
-(2) Facilitating review and inspection by avoiding black-box designs and (3) providing a benchmark for innovation towards next-generation technology \cite{Lees2024}.
+The growing space of open-source instrumentation can improve science in several ways: (1) enabling faster innovation through lower costs and enabling work in low-resource settings, (2) facilitating review and inspection by avoiding black-box designs and (3) providing a benchmark for innovation towards next-generation technology \cite{Lees2024}.
 We hope that our instrument, combined with earlier designs \cite{Rosenegger2014, Mayrhofer2015, Tan1999}, and recent developments, like the head mounted microscope \cite{Zong2022}, or the Janelia Research Campus microscope \cite{Janelia2024}, can serve as a benchmark for future instruments.
-Relatedly, we have contributed to other projects that follow this philosophy in microscopy \cite{Scott2018}, but also designing an open source ventilator during the COVID-19 pandemic \cite{LaChance2022,POVMC2022}, and a \textmu-contact printing device \cite{Samhaber2016}.
-Making these devices fully open has informed the narrative in this article, the design and organization of the published files, and also the choice of an open access journal.
-Finally, the open approach can make two-photon microscopy more accessible to researchers, thereby greatly expanding the ability to train students in approaching such technology and producing new inventions.
-In our ventilator work, this has led to one of the first devices using deep reinforcement learning that performed superior to classical control schemes \cite{Suo2021}.
-Future will tell how the community will make best use of Twinkle.
+Relatedly, we have contributed to other projects that follow this philosophy in microscopy \cite{Scott2018}, but also in mechanical ventilation during the COVID-19 pandemic \cite{LaChance2022,POVMC2022}, and a \textmu-contact printing device \cite{Samhaber2016}.
+These experiences have informed this article's narrative, the design and organization of the published files, and also the choice of an open access journal.
+We hope that our open approach can make two-photon microscopy more accessible to researchers, thereby greatly expanding the ability to train students and producing new inventions.
+Our ventilator work has led to one of the first devices using deep reinforcement learning that performed superior to classical control schemes \cite{Suo2021}.
+Future will tell how our community will make best use of Twinkle.
 The world is moving towards more open technology \cite{Schottdorf2024}, in particular in the microscopy community \cite{Hohlbein2022}.
@@
 Technology develops rapidly and many of the specific components mentioned here will be outdated in a few years.
-We believe that science progresses best if researchers understand their instrumentation and leverage the current cutting edge of what is possible to further their science.\newline
+These parts should be updated as needed.
+We hope that the narrative in this article helps to make such future replacements straight forward.\newline
 This work is free: you can redistribute it and/or modify it under the terms of the Creative Commons Attribution 4.0 International license, version 4 of the License, or (at your option) any later version (CC-BY-4.0).
 This work is distributed in the hope that it will be useful, but without any warranty, to the extent permitted by law; without even the implied warranty of merchantability or fitness for a particular purpose.
-A copy of the License is provided in our repository.
+A copy of the License is provided in our repository \cite{Zenodo2024}.
 For more details, see \url{http://www.gnu.org/licenses/}.
@@
 
-\paragraph*{S1 Appendix. This contains detailed construction instructions and technical details.}
+\paragraph*{S1 Appendix. This contains illustrated construction instructions and technical details.}
 \label{S1_Appendix}
@@
 The CAD files are provided in several standard formats.
-We have used Fusion 360.
-The optical design was performed in Ansys' OpticStudio (Zemax): \url{https://github.com/BrainCOGS/Microscope}.}
+The optical design was performed in Ansys' OpticStudio (Zemax): \url{https://github.com/BrainCOGS/Microscope}.
+A static DOI for the materials used in thie article is available on Zenodo \cite{Zenodo2024}.}
 
@@
 
+\bibitem{Zenodo2024}
+Manuel Schottdorf et al. (2024). BrainCOGS/Microscope: Concept (all versions). Zenodo. \url{https://doi.org/10.5281/zenodo.14566943}.
+
 \bibitem{Bueno2019}
@@
 PMID: 33230320; PMCID: PMC7783861.
+
+\bibitem{Piazza2016}
+Piazza V, de Vito G, Farrokhtakin E, Ciofani G, Mattoli V.
+Femtosecond-Laser-Pulse Characterization and Optimization for CARS Microscopy.
+PLoS One.
+2016 May 25;11(5):e0156371.
+doi: 10.1371/journal.pone.0156371.
+PMID: 27224203; PMCID: PMC4880195.
 
@@
 (2019).
-PTRRupprecht/Photon-yield-and-pulse-dispersion: Photon yield and pulse dispersion, version 1 (Version version1).
+PTRRupprecht/Photon-yield-and-pulse-dispersion: Photon yield and pulse dispersion, Version 1.
 Zenodo.
-https://doi.org/10.5281/zenodo.2592465 \url{https://ptrrupprecht.github.io/Photon-yield-and-pulse-dispersion/}.
+\url{https://doi.org/10.5281/zenodo.2592465} and \url{https://ptrrupprecht.github.io/Photon-yield-and-pulse-dispersion/}.
 

### 2025-01-03 documentation/supplement.tex
A few more typos fixed; text streamlined

@@
 \end{center}
-\caption{\textbf{Overview of the approximate cost in 2024-US\$} Note that this list excludes the optical table, and any other infrastructure costs such as compressors for air, and associated power supplies.
+\caption{\textbf{Overview of the approximate cost in US-\$ (2024).} Note that this list excludes the optical table, and any other infrastructure costs such as compressors for air, and associated power supplies.
 This is just a summary.
@@
 However, use common sense.
-Do not follow these instructions blindly (or you will follow these instructions blindly).
+Do not follow these instructions blindly (or you might follow these instructions blindly).
 Like all open instrumentation (under CC-BY-4.0), this work is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY, to the extent permitted by law; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.
@@
 This will be important later to reproduce the exact same position of the alignment tool with the Pockels cell.
-        \item Connect the Pockels cell (M350-80-LA, Conoptics) to the driver as per the Conoptics instructions (p1m and p2m go to J1m and J2m, p1 and p2 go to the controller).
+        \item Connect the Pockels cell (M350-80-LA, Conoptics) to the driver as per the Conoptics instructions (\texttt{p1m} and \texttt{p2m} go to \texttt{J1m} and \texttt{J2m}, \texttt{p1} and \texttt{p2} go to the controller).
 The controller settings are shown in Fig.~\ref{sfig2}.
@@
         %
-        \item Next, determine the best orientation of the Pockels cell, by measuring the controller's voltage for different Pockels cell rotations.
-For each rotation of the Pockels cell, measure its transmission while turning the dial on the Conoptics controller from one end to the other.
-Iterate this for different orientations of the Pockels cell until an optimum is found.
+        \item Next, determine the best orientation of the Pockels cell: For several rotations of the Pockels cell, measure its transmission while turning the dial on the Conoptics controller from one end to the other.
+Iterate this for different orientations of the Pockels cell until an optimum is found at which the dynamic range is greatest.
+This optimal orientation allows to adjust the laser power in the widest range.
 An example of different transmission curves is shown in the main manuscript, Fig.
 9A.
-The optimal orientation allows to adjust the laser power in the widest range.
         \item The Pockels Cell splits the input beam into a transmitted and a rejected beam.
@@
     \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs).
-While we used a round 2 inch mirror, this should be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs).
+While we used a round $\diameter2\text{ inch}$ mirror, this should be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs).
 This would increase the field-of-view because the cross-section of an ellipse at 45 degrees is a circle.
@@
 The gap in between can be reduced to zero using adjustable length SM1 lens tube (e.g.
-SM1V10, Thorlabs, not shown in CAD) and can be further closed by a small portion of  lens tube cover (SC600, Thorlabs).
+SM1V10, Thorlabs, not shown in CAD) and can be further closed by a small piece of  lens tube cover (SC600, Thorlabs).
     \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}A) so that light travels through the center of the scanning mirrors and up the 95 mm rail.
@@
 As the mirror (component F in Fig.~\ref{sfig4}) is not installed yet, an IR detection card can conveniently be taped to the ceiling to make sure that the beam is on-axis.
-Of note, the resonant scanner is at its origin point when no power is being provided, but the slow galvanometer needs to be provided 0 Volt to position the mirror at its origin point.
+Of note, the resonant scanner is at its origin point when no power is being provided, but the slow galvanometer needs to be provided 0 V to position the mirror at its origin point.
 This can be done through the voltage supply, or to a good approximation through ScanImage by setting the scan mode to the highest possible zoom level.
@@
 Switch the room lights off, wait a few minutes to adapt to the darkness then mount the PMTs on their respective ports.
-Of note, when ordering the PMTs from Hamamatsu, one can request PMTs with particularly low dark count to reduce noise.
+Of note, when ordering the PMTs from Hamamatsu, one can request PMTs with particularly low dark count and high quantum efficiency to reduce noise.
+We typically request a quantum efficiency of at least 45\% at 520 nm, and a dark count of 4000 cps or below at 25 degree Celcius.
 
@@
 This will reveal more subtle misalignment and aberration in the optics.
-We use a mix of 5000:1 100 nm fluorescent beads (``Dragon Green'' 480/520 from Bangs Laboratories) in in 1\% Agarose.
+We use a 5000:1 mix of 100 nm fluorescent beads (``Dragon Green'' 480/520 from Bangs Laboratories) in in 1\% Agarose.
 To prepare this sample, take the beads from the fridge, vortex the container, take the 10 \textmu l and 49.5 g of water.
@@
 Bring your sample to the microscope, and record a z-stack.
-Use low laser power to not damage the bead, or saturate the PMTs.
+Use low laser power to not damage the beads, or saturate the PMTs.
 The example shown was recorded with 5\% laser power at 99.9 zoom for 40 z-slices with 0.5 \textmu m spacing.
@@
     \item \textbf{A)} The construction of the collection optics box starts with a side panel attached to the base with stainless steel button head hex screws, 8-32 thread size, 1/2 inch long.
-    \item \textbf{B)} Next, we attach the front panel. This is connected  with stainless steel Phillips flat head screws, 82 degree countersink angle, 4-40 Thread, 1/8 in long and undercut.
+    \item \textbf{B)} Next, we attach the front panel. This is connected  with stainless steel Phillips flat head screws, 82 degree countersink angle, 4-40 thread size, 1/8 inch long and undercut.
     \item \textbf{C)} Then we install the first lens, a LA1384-A plano-convex lens (Thorlabs), see Fig.~\ref{sfig9}.
@@
     \item \textbf{F)} Next, we fix the condenser lenses (ACL25416U-A, Thorlabs) in their housing plates.
-The convex part is facing towards the inside of the box, and set with nylon set screws (Stainless Steel Nylon-Tip Set Screw, 4-40 Thread, 1/8 inch long).
+The convex part is facing towards the inside of the box, and set with nylon set screws (Stainless Steel Nylon-Tip Set Screw, 4-40 thread size, 1/8 inch long).
 The holders are then fixed together with stainless steel socket head screw, 8-32 thread size, 3/8 inch long.
     \item \textbf{G)} With the condensers in place, we can install the optical band-pass filters in front of them.
-First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread, 1/8 inch long).
+First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread size, 1/8 inch long).
 Orientation is important: For this brand of filters, the arrow is following the light path, i.e.
@@
     \item \textbf{J)} The piece containing the 525 nm and 600 nm band-pass filters and the dichroic mirror is connected to the larger metal box with stainless steel socket head screw, 4-40 thread size, 3/4 inch long.
-    \item \textbf{K)} The bottom piece (bottom per the view of the picture in Fig.~\ref{sfig9}B) of the PMT box is attached using 4-40, undercut, 3/16 inch screws.
+    \item \textbf{K)} The bottom piece (bottom per the view of the picture in Fig.~\ref{sfig9}B) of the PMT box is attached using 4-40 thread size, undercut, 3/16 inch long screws.
     \item \textbf{L)} PMT plate.
@@
 The other side has a shallow cut out for the screw head to sit.
-The plate with the PMT attached screws into the rest of the assembly using 4-40 5/16 inch, socket cap screws.
+The plate with the PMT attached screws into the rest of the assembly using 4-40 thread size, 5/16 inch long socket cap screws.
     \item \textbf{M)} Next, we install an IR block filter (Semrock BrightLine Multiphoton Filter FF01-680/SP-50, AVR Optics). This filter is sandwiched between two rings (SM2RR).
-    \item \textbf{N)} Then we close the second panel with 8/32, 1/2 inch, socket cap screws.
+    \item \textbf{N)} Then we close the second panel with 8-32 thread size, 1/2 inch long socket cap screws.
     \item \textbf{O)} The piezoelectric holder is attached to the aluminium part using the adapter that comes with it. Be careful to not damage the Serial Cable connected to the holder.
-    \item \textbf{P)} The lid is attached using 8/32, 3/8 inch, undercut screws.
-Finish off by securing the rest of the front plate screws (component B) using 4-40 thread, 1/8 inch screws.
-Screw in the piece holding M to the lid using 4-40, 1/2 inch, socket cap screws.
-    \item \textbf{Q)} Attach the top cover using 4-40, undercut, 3/16 inch screws.
+    \item \textbf{P)} The lid is attached using 8-32 thread size, 3/8 inch long, undercut screws.
+Finish off by securing the rest of the front plate screws (component B) using 4-40 thread size, 1/8 inch long screws.
+Screw in the piece holding M to the lid using 4-40 thread size, 1/2 inch long socket cap screws.
+    \item \textbf{Q)} Attach the top cover using 4-40 thread size, undercut, 3/16 inch long screws.
 \end{enumerate}
@@
 \textbf{C)} Bottom part of the aluminium box.
-A: the windows, and B: screws to attach the box to the drop-on rail carriage via four 0.75 inch tall 1 inch diameter posts.
+A: the windows, and B: screws to attach the box to the drop-on rail carriage via four 3/4 inch tall $\diameter1\text{ inch}$ diameter posts.
 \textbf{D)} The scanning mirrors are mounted to the lid using heat transfer compound.
@@
 \\
-\textcolor{blue}{To provide these three signals, we used a power supply with two galvanically isolated and adjustable output channels, that can be connected in series (Note: not every power supply can do this.
+\textcolor{blue}{To provide these three signals, we used a power supply with two galvanically isolated and adjustable output channels, that can be connected in series (Note: not every power supply supports this function.
 We used a GPD-3303D from Gw Instek that allows this function with the SER/INDEP key).
@@
     \item Solder pins 7 and 8 together on each of the two displays. The displays are component \textbf{A} in Fig.~\ref{sfig12}A,B.
-    \item Solder 2.5 inch long, and 5 inch long pieces of wires to pin 12 on the top display.
-    \item Solder the other end of the 2.5 inch piece of wire and a new 1 inch piece of wire to pin 3 (+5 V return).
-    \item Solder the other end of the 1 inch piece of wire and a 1.5 inch and 3 inch pieces to display pin 6 (DP1).
-    \item Solder the other end of the 1.5 inch piece and another 1 inch piece to pin 3 (+5 V return) of the bottom display.
-    \item Solder the other end of the 1 inch piece and a new 2 inch piece to pin 6 (DP1) of the bottom display.
-    \item Solder the other end of the 2 inch piece to pin 12 (input lo) of the bottom display.
-    \item Solder the other end of the 3 inch piece from pin 6 (DP1) of the top display and a new 12 inch piece of wire to the middle pin of the left potentiometer.
-    \item Solder a 12 inch piece of wire to pin 3 (closest to the knob) on the left potentiometer (50 kOhm, 3590S-1-503L, Bourns).
+    \item Solder 2.5 inch long and 5 inch long pieces of wires to pin 12 on the top display.
+    \item Solder the other end of the 2.5 inch long piece of wire and a new 1 inch long piece of wire to pin 3 (+5 V return).
+    \item Solder the other end of the 1 inch long piece of wire, and add 1.5 inch and 3 inch long pieces to display pin 6 (DP1).
+    \item Solder the other end of the 1.5 inch long piece and another 1 inch long piece to pin 3 (+5 V return) of the bottom display.
+    \item Solder the other end of the 1 inch long piece and a new 2 inch long piece to pin 6 (DP1) of the bottom display.
+    \item Solder the other end of the 2 inch long piece to pin 12 (input lo) of the bottom display.
+    \item Solder the other end of the 3 inch long piece from pin 6 (DP1) of the top display and a new 12 inch long piece of wire to the middle pin of the left potentiometer.
+    \item Solder a 12 inch long piece of wire to pin 3 (closest to the knob) on the left potentiometer (50 kOhm, 3590S-1-503L, Bourns).
 These are the two big blue parts, component \textbf{B}, in Fig.~\ref{sfig12}A,B.
-    \item Solder a 12 inch piece of wire and 5 inch piece of wire to pin 11 (input hi) on the top display.
-    \item Solder the other end of the 5 inch piece of wire to pin 1 (furthest from the knob) on the left potentiometer.
-    \item Solder a 5 inch piece of wire to pin 1 and pin 2 (+5 V supply) of the top display.
-    \item Solder the other end of the 5 inch piece of wire to the middle pin on the side opposite to where it says ON/ON on the switch.
-    \item Solder a 12 inch piece of wire and 5 inch piece of wire to pin 11 (input hi) on the bottom display.
-    \item Solder the other side of the 5 inch piece of wire to pin 1 (further from the knob) on the right potentiometer.
-    \item Solder a 12 inch piece of wire to pin 3 (closest to the knob) on the right potentiometer.
-    \item Solder a 12 inch piece of wire and the other end of the wire connected to pin 12 of the top display to pin 2 (middle pin) on the right potentiometer.
-    \item Solder a 6 inch piece of wire to the middle pin on the side adjacent to where it says ON/ON on the switch (component \textbf{C}).
-    \item Solder a 3 inch piece of wire to the left pin (left with the words being oriented the correct direction) on the side adjacent to where it says ON/ON on the switch.
-    \item Solder the other end of the 3 inch piece of wire and a 12 inch piece of wire to the left pin (left with words being oriented the correct direction) of the second switch on the side opposite to ON/ON words.
-    \item Solder a 12 inch piece of wire to middle pin on the second switch on the side opposite to the ON/ON words.
-    \item Solder a 6 inch piece of wire to left pin on the potentiometer used for the  +5 V supply of the display (component \textbf{D}).
-    \item Solder a 6 inch piece of wire to right pin on the same potentiometer.
-    \item Solder a 4 inch piece of wire to center pin on the same potentiometer. 
+    \item Solder a 12 inch long piece of wire and 5 inch long piece of wire to pin 11 (input hi) on the top display.
+    \item Solder the other end of the 5 inch long piece of wire to pin 1 (furthest from the knob) on the left potentiometer.
+    \item Solder a 5 inch long piece of wire to pin 1 and pin 2 (+5 V supply) of the top display.
+    \item Solder the other end of the 5 inch long piece of wire to the middle pin on the side opposite to where it says ON/ON on the switch.
+    \item Solder a 12 inch long piece of wire and a 5 inch long piece of wire to pin 11 (input hi) on the bottom display.
+    \item Solder the other side of the 5 inch long piece of wire to pin 1 (further from the knob) on the right potentiometer.
+    \item Solder a 12 inch long piece of wire to pin 3 (closest to the knob) on the right potentiometer.
+    \item Solder a 12 inch long piece of wire and the other end of the wire connected to pin 12 of the top display to pin 2 (middle pin) on the right potentiometer.
+    \item Solder a 6 inch long piece of wire to the middle pin on the side adjacent to where it says ON/ON on the switch (component \textbf{C}).
+    \item Solder a 3 inch long piece of wire to the left pin (left with the words being oriented the correct direction) on the side adjacent to where it says ON/ON on the switch.
+    \item Solder the other end of the 3 inch long piece of wire and a 12 inch long piece of wire to the left pin (left with words being oriented the correct direction) of the second switch on the side opposite to ON/ON words.
+    \item Solder a 12 inch long piece of wire to middle pin on the second switch on the side opposite to the ON/ON words.
+    \item Solder a 6 inch long piece of wire to left pin on the potentiometer used for the  +5 V supply of the display (component \textbf{D}).
+    \item Solder a 6 inch long piece of wire to right pin on the same potentiometer.
+    \item Solder a 4 inch long piece of wire to center pin on the same potentiometer. 
     \item Connect the left and right pins to the banana plugs and set the potentiometer to 5 V going across BEFORE connecting the middle wire to the rest of the controller circuit! 
-    \item Solder the other end of the 4 inch wire and another 4 inch piece of wire to the middle pin on the second switch on the side adjacent to the ON/ON words.
-    \item Solder the other end of the 4 inch piece of wire to the right pin (right with words being oriented in the correct direction) on the side opposite to the ON/ON words on the first switch.
-    \item Solder a 5 inch piece of wire to the right pin (right with words being oriented the correct direction) on the side adjacent to where it says ON/ON on the second switch.
+    \item Solder the other end of the 4 inch long wire and another 4 inch long piece of wire to the middle pin on the second switch on the side adjacent to the ON/ON words.
+    \item Solder the other end of the 4 inch long piece of wire to the right pin (right with words being oriented in the correct direction) on the side opposite to the ON/ON words on the first switch.
+    \item Solder a 5 inch long piece of wire to the right pin (right with words being oriented the correct direction) on the side adjacent to where it says ON/ON on the second switch.
     \item Solder the other end of the wire to pin 1 and pin 2 (+5 V supply) on the bottom display.
-    \item Trim the wires from the middle pin of the gain adjusters by around 5 inch, connect those two wires, the wire furthest from the dial on the potentiometer, and two 12 inch wires by twisting together.
-    \item Solder a 3 inch wire to the white banana plug and screw it in the housing. This is component \textbf{E} in in Fig.~\ref{sfig12}B.
-    \item Solder a 3 inch wire to the red banana plug and screw it in the housing.
+    \item Trim the wires from the middle pin of the gain adjusters by around 5 inch, connect those two wires, the wire furthest from the dial on the potentiometer, and two 12 inch long wires by twisting together.
+    \item Solder a 3 inch long wire to the white banana plug and screw it in the housing. This is component \textbf{E} in in Fig.~\ref{sfig12}B.
+    \item Solder a 3 inch long wire to the red banana plug and screw it in the housing.
     \item Connect the twisted together wires to the white banana plug.
@@
 
-\section{Deriving the intensity-dispersion relation}
+\section{Deriving the relationship between intensity and dispersion}
 \textcolor{blue}{In the main article, we stated that the expected fluorescence $I(\varphi)$ as function of group delay dispersion $\varphi$ applied to a $\varphi_0$-dispersed Gaussian pulse of full-width-at-half-maximum $\Delta\tau$ can be written as

### 2025-01-10 article/Article.tex
final updates before resubmission

@@
 Many laboratories use two-photon microscopy through commercial suppliers, or homemade designs of considerable complexity.
-The integrated nature of these systems complicates customization, troubleshooting, and \textcolor{blue}{training on the} principles of two-photon microscopy.
+The integrated nature of these systems complicates customization, troubleshooting, and \textcolor{black}{training on the} principles of two-photon microscopy.
 Here, we present ``Twinkle'': a microscope for Two-photon Imaging in Neuroscience, and Kit for Learning and Education.
-It is a fully open, high performing and \textcolor{blue}{easy-to-set-up microscope that can effectively be used for both education and research}.
-The instrument features \textcolor{blue}{a $>1\text{ mm}$ field of view}, using a modern objective with \textcolor{blue}{3 mm} working distance and \textcolor{blue}{two inch diameter optics combined with GaAsP photomultiplier tubes} to maximize the fluorescence signal.
-We document our experiences using this system as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open-source scientific instrumentation.
+It is a fully open, high performing and \textcolor{black}{easy-to-set-up microscope that can effectively be used for both education and research}.
+The instrument features \textcolor{black}{a $>1\text{ mm}$ field of view}, using a modern objective with \textcolor{black}{3 mm} working distance and \textcolor{black}{2 inch diameter optics combined with GaAsP photomultiplier tubes} to maximize the fluorescence signal.
+We document our experiences using this system as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open scientific instrumentation.
 
@@
 %
-Two-photon microscopy\cite{Denk1990, Svoboda1997} \textcolor{blue}{is a key technology across the modern life sciences\cite{Zipfel2003}, for example, in physiology\cite{Ueki2020, Dunn2002}, cancer research \cite{Perry2012}, plant biology \cite{Cheung2010}, and neuroscience\cite{So2000, Helmchen2005}.
-New scientific use cases and technological improvements are published at a remarkable rate\cite{Luu2024}.} However, these instruments \textcolor{blue}{are often published without detailed building instructions and explanations}.
-This suggests the need for an \textcolor{blue}{easy-to-set-up microscope, at reasonable cost, that can be effectively used for education, dissemination, methods development and research.} We developed a high-performance and cost-effective two-photon microscope that can \textcolor{blue}{easily be produced} in many neuroscience laboratories.
+Two-photon microscopy\cite{Denk1990, Svoboda1997} \textcolor{black}{is a key technology across the modern life sciences\cite{Zipfel2003}, for example, in physiology\cite{Ueki2020, Dunn2002}, cancer research \cite{Perry2012}, plant biology \cite{Cheung2010}, and neuroscience\cite{So2000, Helmchen2005}.
+New scientific use cases and technological improvements are produced at a remarkable rate\cite{Luu2024}.} However, these instruments \textcolor{black}{are often published without detailed building instructions and explanations}.
+This suggests the need for an \textcolor{black}{easy-to-set-up microscope, at reasonable cost, that can be effectively used for education, dissemination, methods development and research.} We developed a high-performance and cost-effective two-photon microscope that can \textcolor{black}{easily be produced} in many neuroscience laboratories.
 Reflecting its use for ``\textbf{TW}o-photon \textbf{I}maging in \textbf{N}euroscience, and \textbf{K}it for \textbf{L}earning and \textbf{E}ducation'', we chose the acronym Twinkle.
 In this article, we share our design, document the performance of the system, explore possible research applications, and report our experiences collected during several teaching workshops.
-\textcolor{blue}{Complete CAD drawings, bill of materials, optics simulations, and detailed building instructions are provided in the supplement.}
+\textcolor{black}{Complete CAD drawings, bill of materials, optics simulations, and detailed building instructions are provided in the supplement.}
 
@@
 As the focal point probes different locations, different quantities of fluorescence light are produced by the sample.
-\textcolor{blue}{This light is collected by a sensitive detector in the form of an electronically measurable photocurrent.} An image is then formed, mapping the detector photocurrent values to the locations of excitation volume: low and high photocurrents, respectively, becoming dark and bright pixels.
+\textcolor{black}{This light is collected by a sensitive detector in the form of an electronically measurable photocurrent.} An image is then formed, mapping the detector photocurrent values to the locations of excitation volume: low and high photocurrents, respectively, becoming dark and bright pixels.
 Central to two-photon fluorescence excitation is the light source: a femtosecond-pulsed infrared laser of sufficient pulse energy to achieve, when focused by an objective lens, a photon density high enough for simultaneous absorption of two photons by a fluorescent molecule.
@@
 As such, we have made all optical and mechanical designs, electronics, bill of materials (BOM), CAD assembly, testing results, and relevant schematics open to the public.
-\textcolor{blue}{Excluding laser and optical table, the cost is around US-\$ 110k (2024).
+\textcolor{black}{Excluding laser and optical table, the cost is around US-\$ 110k (2024).
 Including laser and table, the cost is around US-\$ 200k (2024).} A narrative of the design and the high-level view is presented here.
 For further details, we refer the reader to \nameref{S1_Appendix}.
-All code, figures and text, CAD designs, optics simulations, and BOM are available on  \url{https://github.com/BrainCOGS/Microscope} \textcolor{blue}{and on Zenodo \cite{Zenodo2024}.}
+All code, figures and text, CAD designs, optics simulations, and BOM are available on  \url{https://github.com/BrainCOGS/Microscope} \textcolor{black}{and on Zenodo \cite{Zenodo2024}.}
 
@@
 The choice of mounted scanners simplifies the design and construction, but leads to optical distortions across the field of view.
-\textcolor{blue}{We found that this distortion does not exceed 5\% in our design (see below)}.
+\textcolor{black}{We found that this distortion does not exceed 5\% in our design (see below)}.
 The combined scan and tube lenses magnify the beam further to fill the objective's back aperture.
@@
     \includegraphics[width=\textwidth]{fig1.jpg}
-    \caption{{\bf System overview.} \textbf{A)} \textcolor{blue}{Key components of the microscope head.
+    \caption{{\bf System overview.} \textbf{A)} \textcolor{black}{Key components of the microscope head.
 Shaded colors illustrate beam deflection angles.
@@
 In the cartoon, this second beam is sent to a beam block (LB1, Thorlabs).
-\textcolor{blue}{We want to stress that this beam-splitting hardware is optional.
+\textcolor{black}{We want to stress that this beam-splitting hardware is optional.
 However, modern lasers have enough power to supply two microscopes at the same time.
@@
 When used for teaching, a careful assembly and alignment is viable with about a week of work.
-\textcolor{blue}{When set up on an imperial-unit table, the system can comfortably be built on $4\times4 \text{ ft}^2$.
+\textcolor{black}{When set up on an imperial-unit table, the system can comfortably be built on $4\times4 \text{ ft}^2$.
 The microscope documented here was built on a $4\times8\text{ ft}^2$ table, shared with a second microscope.
 In metric units, our microscope has a footprint of $\approx 1.5\text{ m}^2$.
-In other words, a standard $1.2\times2.5\text{ m}^2$ table can house two of the systems described here.} The beam-splitting hardware \textcolor{blue}{used for this arrangement} is shown in Fig.~\ref{fig1}B,C as well.\newline
+In other words, a standard $1.2\times2.5\text{ m}^2$ table can house two of the systems described here.} The beam-splitting hardware \textcolor{black}{used for this arrangement} is shown in Fig.~\ref{fig1}B,C as well.\newline
 The custom mechanical components (e.g.
@@
 The controller requires three supply lines, -28 V, 0 V, and +28 V.
-\textcolor{blue}{To provide these voltages, we used a power supply with two galvanically isolated and adjustable outputs (not every power supply supports this function).
+\textcolor{black}{To provide these voltages, we used a power supply with two galvanically isolated and adjustable outputs (not every power supply supports this function).
 The voltage of each of the two channels was set to +28 V.
@@
 For the work demonstrated here, we used a fixed-wavelength femtosecond laser systems, based on fiber technology (e.g.\cite{Bueno2019,Limpert2006,Wise2012,Young2015}).
-\textcolor{blue}{These devices come at $\approx 1/3$ of the cost of a Ti:Sapphire system, and take up significantly less real estate on the optical table.} Our laser, \textcolor{blue}{an Alcor 920 manufactured by Spark Lasers}, was controlled with the same PC as ScanImage through a USB connection.
+\textcolor{black}{These devices come at $\approx 1/3$ of the cost of a Ti:Sapphire system, and take up significantly less real estate on the optical table.} Our laser, \textcolor{black}{an Alcor 920 manufactured by Spark Lasers}, was controlled with the same PC as ScanImage through a USB connection.
 As the beam travels through a number of crystals, lenses, and mirrors with various chromatic properties, significant dispersion is introduced which increases pulse duration, reducing the two-photon absorption efficiency.
@@
 \subsection*{Ethics statement}
-\textcolor{blue}{Some of the data presented here were obtained from animals.
+\textcolor{black}{Some of the data presented here were obtained from animals.
 Our work was conducted according to internationally accepted standards and we followed all laws and regulations about animal research in the United States and Germany.
@@
 In the following paragraphs, we summarize our experiences, and produce two examples for what we consider useful learning experiences for two-photon microscopy.
-\textcolor{blue}{The detailed building instructions and additional information are available the supplement, \nameref{S1_Appendix}}.\newline
+\textcolor{black}{The detailed building instructions and additional information are available the supplement, \nameref{S1_Appendix}}.\newline
 To organize our workshop, we freed around 2 weeks in the summer.
@@
 We then assessed its performance and demonstrated several possible use cases, from plant physiology over material science to neuroscience.
-\textcolor{blue}{In the following paragraphs, we will expand on some recent scientific use cases of two-photon microscopy, discuss improvements to the design, elaborate on its use for education,} and conclude with a note about our instrument in the growing space of open source scientific instrumentation.
+\textcolor{black}{In the following paragraphs, we will expand on some recent scientific use cases of two-photon microscopy, discuss improvements to the design, elaborate on its use for education,} and conclude with a note about our instrument in the growing space of open source scientific instrumentation.
 
 \subsection*{Scientific use cases}
-\textcolor{blue}{Based on its unique ability to image with high resolution and limited photo damage deep into scattering samples, two-photon microscopy became an important tool across the life sciences.
+\textcolor{black}{Based on its unique ability to image with high resolution and limited photo damage deep into scattering samples, two-photon microscopy became an important tool across the life sciences.
 For example, \textit{ex vivo}, two-photon microscopy can monitor, in three dimensions, both the living and cornified keratinocytes of the epidermis, the collagen/elastin fibers in the dermal layer of the skin \cite{So1998} or the dynamics of quiescent skeletal muscle stem cells embedded in the muscle at cellular resolution \cite{Ma2024}.
@@
 Another approach uses a set of axially separated and temporally distinct foci to record the entire axial imaging range near-simultaneously \cite{Demas2021}.
-We hope that our work here can contribute further momentum to these exciting new research avenues.}
+}
 
@@
 (2) In our design, a piezoelectric collar is attached to the objective.
-Physically moving the objective along the optical axis allows to image several planes for fast \textcolor{blue}{volumetric imaging \invivo or tissue samples \textit{ex vivo}}.
+Physically moving the objective along the optical axis allows to image several planes for fast \textcolor{black}{volumetric imaging \invivo or tissue samples \textit{ex vivo}}.
 The time required by the piezoelectric collar to stabilize can reach the scale of 10 ms when using large and heavy objectives.
 In these cases, volumetric imaging is best achieved using a ramp where the objective is constantly moving at the same speed, rather than doing steps of constant height for every planes.
-An electrically tunable lens (ETL) \cite{Chen2016} or \textcolor{blue}{remote focusing} \cite{Botcherby2007} are an alternative to the piezoelectric collar.
-\textcolor{blue}{These techniques are necessary when the objective is difficult to move (such as a very heavy objective) or cannot be moved, for example during volumetric imaging combined with controlled stimulation, as moving the objective would also change the location of the stimulation spots.}\newline
+An electrically tunable lens (ETL) \cite{Chen2016} or \textcolor{black}{remote focusing} \cite{Botcherby2007} are an alternative to the piezoelectric collar.
+\textcolor{black}{These techniques are a good alternative when the objective is difficult to move (such as a very heavy objective) or cannot be moved, for example during volumetric imaging combined with controlled stimulation, as moving the objective would also change the location of the stimulation spots.}\newline
 (3) Estimating the pulse duration suggests non-linear dispersion that we cannot correct.
@@
 That said, even when underfilled by the excitation beam, a large NA of the objective is beneficial to collect as much fluorescent light as possible.\newline
-\textcolor{blue}{(6) When imaging fixed samples, movement artifacts are not an issue.
+\textcolor{black}{(6) When imaging fixed samples, movement artifacts are not an issue.
 For such experiments, particularly \textit{ex vivo} work, it would be strategic to fully fill the back aperture of the objective and produce a PSF that is as tight as possible.}\newline
-\textcolor{blue}{(7) Using an objective with an even larger numerical aperture can significantly increase collection efficiency.
+\textcolor{black}{(7) Using an objective with an even larger numerical aperture can significantly increase collection efficiency.
 Our objective choice was made with long working distance in mind.
-Our $16\times$ water-immersion objective with a numerical aperture of 0.8 accepts around $36\%$ of the $4\pi$ square radiants of emission.
-A possible alternative, the Nikon $25\times$ with a slightly smaller 2 mm working distance, offers a numerical aperture of 1.10 and would collect $68\%$ of light; close to a $2\times$ improvement to collection efficiency.}\newline
-\textcolor{blue}{(8) Our microscope exhibits (small) field curvature.
+The $16\times$ water-immersion objective with a numerical aperture of 0.8 accepts around $10\%$ of the $4\pi$ square radiants of emission.
+A possible alternative, the Nikon $25\times$ with a slightly smaller 2 mm working distance, offers a numerical aperture of 1.10 and would collect $22\%$ of light, an improvement of $2.2\times$ to collection efficiency.}\newline
+\textcolor{black}{(8) Our microscope exhibits (small) field curvature.
 In neuroscience, field curvature is often not considered critical because samples are rarely flat.
@@
 Very small field curvature can be obtained with commercial f-theta scan lenses.}\newline
-\textcolor{blue}{(9) Resonant scanning mirrors are fast, but cannot be steered.
-If a user was interested in imaging custom ROIs, the scanning mirror pair could be replaced with a pair of slow galvanometic mirrors, which can be controlled with high precision.}\newline
+\textcolor{black}{(9) Resonant scanning mirrors are fast, but cannot be steered.
+If a user was interested in imaging in custom regions of interest, the scanning mirror pair could be replaced with a pair of slow galvanometic mirrors, which can be controlled with high precision.
+Alternatively, a third scanning mirror can be used to move the imaging area to a different location.
+The third mirror would need to ne conjugated to the resonant scanner.
+These scan heads are currently available commercially, e.g.
+the Vidrio Rapid Multi Region Scanhead.}\newline
 (10) For some applications, it can be beneficial to combine the two-photon system with wide-field imaging.
-To this end, the two inch mirror above the collection optics can be replaced with a 800 or 900 nm short-pass filter followed by a tube lens and a camera.
+To this end, the two inch mirror above the collection optics could be replaced with a 800 or 850 nm short-pass dichroic mirror followed by a tube lens and a camera.
 This would allow infrared (IR) imaging around 700 nm through the collection optics, as it is transparent above 665 nm.
-\textcolor{blue}{Infrared illumination can be provided with an LED and a semitransparent mirror.
-This mirror could conveniently be housed in a flip mount to be removed from the optical path when the system is used for two-photon imaging.} While this is relatively straightforward to implement \cite{Rosenegger2014}, wide-field fluorescence microscopy is harder to realize.\newline
+\textcolor{black}{Infrared illumination can be provided with an LED.} While this is relatively straightforward to implement \cite{Rosenegger2014}, our microscope design is not compatible with the implementation of wide-field fluorescence.\newline
 (11) Our fluorescence filters have an average optical density $>4$ in the range between 400 nm and 460 nm.
@@
 For example, we have used commercial telecentric scan lenses in the past \cite{Song2017, Rich2024} in combination with a three inch diameter tube lens.
-These come at higher cost and introduce higher dispersion, but exhibit very low field curvature on a very large field of view.
+These come at higher cost and eventually introduce higher dispersion, but exhibit very low field curvature on a very large field of view.
 While low field curvature is not always considered the highest priority in neuroscience applications, this can be a useful substitution.\newline
@@
 \cite{Sheppard2020, Yao2023}.\newline
-Students might also become interested in further optimizing the optical design, or wonder why many lenses are \textcolor{blue}{doublets and} used in lens groups.
-\textcolor{blue}{Some of these questions have intuitive answers.
+Students might also become interested in further optimizing the optical design, or wonder why many lenses are \textcolor{black}{doublets and} used in lens groups.
+\textcolor{black}{Some of these questions have intuitive answers.
 Doublets, for example, contain more glass surfaces that can be optimized to produce a better performing lens when compared to the two surfaces of a singlet\cite{ThorlabsLens}.
@@
 Fig.~\ref{fig5}C,D,E.
-\textcolor{blue}{Small misalignment in the optical path can also lead to characteristic image artifacts, for illustrations see\cite{Corbett2014, Lees2024}, that can help to develop an intuition about how the system operates.}\newline
+\textcolor{black}{Small misalignment in the optical path can also lead to characteristic image artifacts, for illustrations see\cite{Corbett2014, Lees2024}, that can help to develop an intuition about how the system operates.}\newline
 Finally, it can be a useful learning experience to re-use parts from other microscopes, such as XY scanners from a confocal microscope\cite{Nikolenko2013}, and to mix and match parts to learn what works and what does not.
@@
 Our project is also certified by the open source hardware association (OSHWA UID US002677).\newline
-The growing space of open-source instrumentation can improve science in several ways: (1) enabling faster innovation through lower costs and enabling work in low-resource settings, (2) facilitating review and inspection by avoiding black-box designs and (3) providing a benchmark for innovation towards next-generation technology \cite{Lees2024}.
+The growing space of open instrumentation can improve science in several ways: (1) enabling faster innovation through lower costs and enabling work in low-resource settings, (2) facilitating review and inspection by avoiding black-box designs and (3) providing a benchmark for innovation towards next-generation technology \cite{Lees2024}.
 We hope that our instrument, combined with earlier designs \cite{Rosenegger2014, Mayrhofer2015, Tan1999}, and recent developments, like the head mounted microscope \cite{Zong2022}, or the Janelia Research Campus microscope \cite{Janelia2024}, can serve as a benchmark for future instruments.
@@
 \label{S1_Appendix}
-\textcolor{blue}{A \texttt{.pdf} file with numerous pictures, annotations, and detailed step-by-step building instructions for the microscope.
+\textcolor{black}{A \texttt{.pdf} file with numerous pictures, annotations, and detailed step-by-step building instructions for the microscope.
 The raw code, pictures, and vectorized versions of the figures are available in the online repository.}
@@
 \label{repository}
-\textcolor{blue}{A repository, hosted on github, including code, \texttt{.svg} figures, and the raw \texttt{.tex} files for this article and its supplement.
+\textcolor{black}{A repository, hosted on github, including code, \texttt{.svg} figures, and the raw \texttt{.tex} files for this article and its supplement.
 In addition, we provide all CAD and optical design files, material billing and other useful information.
@@
 \section*{Acknowledgments}
-\textcolor{blue}{We thank Beatrice Hadiwidjaja for the transgenic zebrafish husbandry and Drs.
+\textcolor{black}{We thank Beatrice Hadiwidjaja for the transgenic zebrafish husbandry and Drs.
 Lindsay Collins and Anthony Ambrosini for hospitality and accommodating our tinkering in the teaching lab of the Princeton Neuroscience Institute.

### 2025-01-10 documentation/supplement.tex
final updates before resubmission

@@
 Learn from people experienced with these devices and work carefully.\newline
-During alignment, always wear goggles (ours were ML1 by NoIR LaserShields with an optical density $>7$ in the relevant range around $920\text{ nm}$), remove jewelry and watches, and use the low laser power (“alignment mode”) whenever possible.
+During alignment, always wear goggles (ours were ML1 by NoIR LaserShields with an optical density $>7$ in the relevant range around $920\text{ nm}$), remove jewelry and watches, only use-reflective tools, do not store unnecessary items on the optical table, and use the low laser power (“alignment mode”) whenever possible.
 Once the assembly progresses further, full power mode is necessary.
@@
 However, use common sense.
-Do not follow these instructions blindly (or you might follow these instructions blindly).
+Do not follow these instructions blindly (or you might follow these instructions blindly in the future).
 Like all open instrumentation (under CC-BY-4.0), this work is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY, to the extent permitted by law; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.
@@
 \textbf{B)} Power supply and connection of the scanning mirrors with key parts labeled by capital letters.
-\textcolor{blue}{\textbf{C)} Wiring diagram for the $\pm 28\text{ V}$ power supply, using two galvanically isolated supplies.
+\textcolor{black}{\textbf{C)} Wiring diagram for the $\pm 28\text{ V}$ power supply, using two galvanically isolated supplies.
 \textbf{D)} The scanning mirror driver boards, provided by Novanta, and mounted in the yellow circuit box.
@@
 \\
-\textcolor{blue}{To provide these three signals, we used a power supply with two galvanically isolated and adjustable output channels, that can be connected in series (Note: not every power supply supports this function.
+\textcolor{black}{To provide these three signals, we used a power supply with two galvanically isolated and adjustable output channels, that can be connected in series (Note: not every power supply supports this function.
 We used a GPD-3303D from Gw Instek that allows this function with the SER/INDEP key).
@@
  For safety, it is good practice to shield the laser path. In addition to safety concerns, it will also help in keeping dust and dirt away from optical components.
+\newpage
 
 \section{Deriving the relationship between intensity and dispersion}
-\textcolor{blue}{In the main article, we stated that the expected fluorescence $I(\varphi)$ as function of group delay dispersion $\varphi$ applied to a $\varphi_0$-dispersed Gaussian pulse of full-width-at-half-maximum $\Delta\tau$ can be written as
+\textcolor{black}{We stated that the expected fluorescence $I(\varphi)$ as function of group delay dispersion $\varphi$ applied to a $\varphi_0$-dispersed Gaussian pulse of full-width-at-half-maximum $\Delta\tau$ can be written as
 \begin{eqnarray}
@@
 \end{eqnarray}
-If the average power of the laser across dispersion compensation settings $c$ is constant, the prefactor is approximately constant.
 Comparison with Eq.
@@
 }
+
 \nolinenumbers

### 2025-01-21 documentation/supplement.tex
Fixed Typo in supplement.

@@
 Learn from people experienced with these devices and work carefully.\newline
-During alignment, always wear goggles (ours were ML1 by NoIR LaserShields with an optical density $>7$ in the relevant range around $920\text{ nm}$), remove jewelry and watches, only use-reflective tools, do not store unnecessary items on the optical table, and use the low laser power (“alignment mode”) whenever possible.
+During alignment, always wear goggles (ours were ML1 by NoIR LaserShields with an optical density $>7$ in the relevant range around $920\text{ nm}$), remove jewelry and watches, only use non-reflective tools, do not store unnecessary items on the optical table, and use the low laser power (“alignment mode”) whenever possible.
 Once the assembly progresses further, full power mode is necessary.
